### 2018-02-28 paper/paper.tex
Added write-up

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2017}

\usepackage{nips_2017}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

\title{Active Transfer Learning}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

\section{Preliminaries}

\paragraph{Markov Decision Processes}
We define a Markov decision process (MDP) as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor. We assume the reward function to be uniformly bounded by a constant $R_{max}>0$. A deterministic policy $\pi : \mathcal{S} \rightarrow \mathcal{A}$ is a mapping from states to actions. At the beginning of each episode of interaction, the initial state $s_0$ is drawn from $p_0$. Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated. The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)=\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$. To this end, we define the optimal value function $Q^*(s,a)$ as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter. Then, an optimal policy $\pi^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi^*(s) = \argmax_a Q^*(s,a)$ for all states $s$. It can be shown (e.g., \cite{puterman1994markov}) that $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$ defined by $TQ(s,a) = \mathcal{R}(s,a) + \gamma\mathbb{E}_{\mathcal{P}}[\max_{a'}Q(s',a')]$ for any value function $Q$. From now on, we adopt the term $Q$-function to denote any plausible value function, i.e., any function $Q : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R}$ uniformly bounded by $\frac{R_{max}}{1-\gamma}$.

We define the Bellman error (or Bellman residual) of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$. Notice that a $Q$-function $Q$ is optimal if, and only if, $||B(Q)||_{\infty} = 0$.

\paragraph{Multitask Settings}

We represent tasks $\tau$ as MDPs with shared state and action spaces, but with potentially different values for all other parameters. We assume the existence of a distribution $\mathcal{D}$ over tasks, i.e., $\tau \sim \mathcal{D}$, and we suppose that we are able to sample from such distribution.

\section{Approach}

We start by noticing that the task distribution $\mathcal{D}$ clearly induces a distribution over optimal $Q$-functions. Then, our goal is to estimate such distribution from the set of source tasks and use it as a prior for speeding up the learning process in the target task.

We assume states and actions to be drawn from a fixed joint distribution $\mu$. We define the set of $Q$-functions of our interest as the set $\mathcal{Q}^{\epsilon}$ of all $Q$ functions whose Bellman error $B(Q)$ is in some $\epsilon$-ball defined by the $l_p$-norm $|| \cdot ||_{p,\mu}$:
\begin{equation}
\mathcal{Q}^{\epsilon} = \left\{ Q\in\mathcal{Q} \mid || B(Q) ||_{p,\mu}^p \leq \epsilon \right\}
\end{equation}
Given a dataset of $N$ samples $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^N$, we can approximate the $l_p$-norm of the Bellman error of a $Q$-function $Q$ as:
\begin{equation}
||B(Q)||_{p,D}^p = \frac{1}{N}\sum_{i=1}^N \left\lvert r_i + \gamma\max_{a'}Q(s_i',a') - Q(s_i,a_i) \right\rvert^p
\end{equation}

\begin{theorem}
Let $Q$ be a $Q$-function with empirical Bellman error, computed on a dataset $D$ of $N$ i.i.d. samples, given by $||B(Q)||_{p,D}^p = \hat{q}$. Then, for any $\epsilon >= 0$:
\begin{equation}
P\left(Q\in\mathcal{Q}^{\epsilon} \mid ||B(Q)||_{p,D}^p = \hat{q}\right) \leq exp\left( -\frac{2N\max\{\epsilon-\hat{q},0\}^2}{\left(\frac{2R_{max}}{1-\gamma}\right)^{2p}} \right)
\end{equation}
\end{theorem}
\begin{proof}
Assume $\hat{q}>\epsilon$. Then:
\begin{align*}
P\left(Q\in\mathcal{Q}^{\epsilon} \mid ||B(Q)||_{p,D}^p = \hat{q}\right) =\ & 
P\left(|| B(Q) ||_{p,\mu}^p \leq \epsilon \mid ||B(Q)||_{p,D}^p = \hat{q}\right) \\ =\ &
P\left(|| B(Q) ||_{p,\mu}^p - \hat{q} \leq \epsilon - \hat{q} \mid ||B(Q)||_{p,D}^p = \hat{q}\right)
\end{align*}
Notice that $\mathbb{E}[\hat{q}] = || B(Q) ||_{p,\mu}^p$ and that $\epsilon - \hat{q} < 0$ by assumption. Then, we can apply Hoeffding's inequality to write:
\begin{equation*}
P\left(Q\in\mathcal{Q}^{\epsilon} \mid ||B(Q)||_{p,D}^p = \hat{q}\right) \leq exp\left( -\frac{2N(\epsilon-\hat{q})^2}{\left(\frac{2R_{max}}{1-\gamma}\right)^{2p}} \right)
\end{equation*}
Finally, when $\hat{q} \leq \epsilon$, the probability can be straightforwardly upper-bounded by $1$. Combining the two results concludes the proof.
\end{proof}
\begin{theorem}
Let $Q$ be a $Q$-function with empirical Bellman error, computed on a dataset $D$ of $N$ i.i.d. samples, given by $||B(Q)||_{p,D}^p = \hat{q}$. Then, for any $\epsilon >= 0$:
\begin{equation*}
P\left( ||B(Q)||_{p,D}^p = \hat{q} \mid Q\in\mathcal{Q}^{\epsilon} \right) \leq \frac{\epsilon}{\hat{q}}
\end{equation*}
\begin{proof}
\begin{align*}
P\left( ||B(Q)||_{p,D}^p = \hat{q} \mid Q\in\mathcal{Q}^{\epsilon} \right) =\ &
P\left( ||B(Q)||_{p,D}^p = \hat{q} \mid || B(Q) ||_{p,\mu}^p \leq \epsilon \right)\\ \leq\ &
P\left( ||B(Q)||_{p,D}^p \geq \hat{q} \mid || B(Q) ||_{p,\mu}^p \leq \epsilon \right)\\ \leq\ &
\frac{E[||B(Q)||_{p,D}^p]}{\hat{q}}\\ \leq\ &
\frac{\epsilon}{\hat{q}}
\end{align*}
The first inequality is straightforward, the second one is from Markov's inequality, while the third one is due to the fact that $Q\in\mathcal{Q}^{\epsilon}$.
\end{proof}
\end{theorem}

\section{Related Works}

List of any paper that relates to our approach together with a brief description:
\begin{itemize}
\item \cite{osband2014generalization}: the authors propose a method for efficient exploration via randomized value functions. The optimal $Q$-function is computed by bayesian LSVI and, after each update, parameters are sampled from the posterior. Then, the agent follows a greedy policy with respect to the sampled $Q$-function. Regret bounds are provided.
\item \cite{osband2016deep}: the authors extend the idea of randomized value functions to drive exploration in deep RL. A posterior distribution over $Q$-functions is approximated via bootstrapping. In each episode, the agent acts greedily with respect to a $Q$-function sampled from the approximated posterior.
\item \cite{chen2017ucb}: the authors build on top of bootstrapped DQNs to provide UCB-like exploration bonuses. In a previous (?) version of the paper, exploration bonuses based on information gain are also proposed.
\end{itemize}

\section{Experiments}

\section{Conclusion}

{\small 
\bibliography{biblio.bib}
\bibliographystyle{plain}
}
\newpage
\appendix

\section{Proofs}

\end{document}

### 2018-02-28 paper/paper.tex
Added least-squares to the write-up

@@
 \usepackage{amsthm}
+\usepackage{bm}
+\usepackage{todonotes}
 
@@
 
+\subsection{Regularized Bellman Residual Minimization with Gaussian Priors}
+
+Consider solving the target task given a dataset $D$ of $N$ samples. The posterior distribution over optimal $Q$-functions is:
+\begin{equation}
+P(Q^* \mid D) \propto P(D \mid Q^*)P(Q^*)
+\end{equation}
+Bounding the likelihood $P(D \mid Q^*)$ ({\color{red}FIND A BETTER DERIVATION}) and taking the maximum of the log-posterior, we obtain the following optimization problem:
+\begin{equation}
+\min_{Q\in\mathcal{Q}} ||B(Q)||_{p,D}^p - \log P(Q) 
+\end{equation}
+Then, let us specify a particular hypothesis space $\mathcal{Q}$. We consider $Q$-functions $Q_{\bm{w}}$ parameterized by the vector $\bm{w}$. Our optimization problem becomes:
+\begin{equation}
+\min_{\bm{w}} ||B(\bm{w})||_{p,D}^p - \log P(\bm{w}) 
+\end{equation}
+We model the prior distribution over the optimal parameters $\bm{w}$ as a Gaussian. That is, we assume:
+\begin{equation}
+P(\bm{w}) = \mathcal{N}(\bm{\mu},\bm{\Sigma})
+\end{equation}
+Then, our optimization, adopting the $l_2$-norm, becomes:
+\begin{equation} \label{eq:optim}
+\min_{\bm{w}} ||B(\bm{w})||_{D}^2 + ||\bm{w}-\bm{\mu}||_{\bm{\Sigma}} = \min_{\bm{w}} \frac{1}{N}\sum_{i=1}^N\left\lvert y_i - Q_{\bm{w}}(s_i,a_i) \right\rvert^2 + ||\bm{w}-\bm{\mu}||_{\bm{\Sigma}}
+\end{equation}
+where $y_i = r_i + \gamma\max_{a'}Q_{\bm{w}}(s_i',a')$ and $||\bm{x}||_{\bm{A}} \triangleq \bm{x}^T\bm{A}^{-1}\bm{x}$ for $\bm{A}$ positive definite matrix.
+
+\paragraph{Linear model}
+
+We assume a linear model for the $Q$-functions: $Q_{\bm{w}}(s,a) = \bm{w}^T\bm{\phi}(s,a)$.
+Here $\bm{\phi}$ is a $K$-dimensional feature vector.
+Then, the solution to the optimization problem of Eq.
+\eqref{eq:optim} can be computed in closed form as follows:
+\begin{equation}
+\bm{w}^* = \left( \bm{A}^T\bm{A} + \bm{\Sigma}^{-1} \right)^{-1} \left( \bm{A}^T\bm{b} + \bm{\Sigma}^{-1}\bm{\mu} \right) 
+\end{equation}
+where $\bm{A}$ is an $N\times K$ matrix containing the feature vectors at each data point $(s_i,a_i)$ and $\bm{b}$ is an $N$-dimensional vector containing their targets $y_i$.
+
 \section{Related Works}

### 2018-03-15 paper/paper.tex
Edits to the writeup

@@
 
-We define the Bellman error (or Bellman residual) of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$. Notice that a $Q$-function $Q$ is optimal if, and only if, $||B(Q)||_{\infty} = 0$.
+We define the Bellman residual of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$. Notice that a $Q$-function $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
 
@@
 
-We assume states and actions to be drawn from a fixed joint distribution $\mu$.
-We define the set of $Q$-functions of our interest as the set $\mathcal{Q}^{\epsilon}$ of all $Q$ functions whose Bellman error $B(Q)$ is in some $\epsilon$-ball defined by the $l_p$-norm $|| \cdot ||_{p,\mu}$:
+Consider solving the target task given a dataset $D$ of $N$ samples. The posterior distribution over optimal $Q$-functions is:
 \begin{equation}
-\mathcal{Q}^{\epsilon} = \left\{ Q\in\mathcal{Q} \mid || B(Q) ||_{p,\mu}^p \leq \epsilon \right\}
+P(Q \mid D) \propto P(D \mid Q)P(Q),
 \end{equation}
-Given a dataset of $N$ samples $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^N$, we can approximate the $l_p$-norm of the Bellman error of a $Q$-function $Q$ as:
+where $P(D \mid Q)$ is the likelihood of observing the dataset $D$ given that $Q$ is optimal and $P(Q)$ is the prior distribution induced by $\mathcal{D}$.
+Computing the likelihood requires knowing the transition and reward models of the current task (i.e., the MDP model), which are not available in practice.
+However, since we are conditioned on the fact that $Q$ is optimal, we can derive a simple approximation.
+We consider the empirical Bellman error $||B(Q)||_{p,D}^p$ under the $l_p$-norm defined as:
 \begin{equation}
@@
 \end{equation}
-
-\begin{theorem}
-Let $Q$ be a $Q$-function with empirical Bellman error, computed on a dataset $D$ of $N$ i.i.d. samples, given by $||B(Q)||_{p,D}^p = \hat{q}$. Then, for any $\epsilon >= 0$:
+Assuming states and actions to be drawn from a fixed joint distribution $\mu$, we have $||B(Q)||_{p,\mu}^p = 0$ whenever $Q$ is optimal.
+Then, the probability of observing a dataset $D$ clearly decreases exponentially as $||B(Q)||_{p,D}^p$, for  an optimal $Q$, increases.
+This can be seen, for instance, by applying Hoeffding's inequality.
+Thus, a natural way to model the likelihood $P(D \mid Q)$ is:
 \begin{equation}
-P\left(Q\in\mathcal{Q}^{\epsilon} \mid ||B(Q)||_{p,D}^p = \hat{q}\right) \leq exp\left( -\frac{2N\max\{\epsilon-\hat{q},0\}^2}{\left(\frac{2R_{max}}{1-\gamma}\right)^{2p}} \right)
+P(D \mid Q) \propto e^{-\lambda N ||B(Q)||_{p,D}^p}
 \end{equation}
-\end{theorem}
-\begin{proof}
-Assume $\hat{q}>\epsilon$. Then:
-\begin{align*}
-P\left(Q\in\mathcal{Q}^{\epsilon} \mid ||B(Q)||_{p,D}^p = \hat{q}\right) =\ & 
-P\left(|| B(Q) ||_{p,\mu}^p \leq \epsilon \mid ||B(Q)||_{p,D}^p = \hat{q}\right) \\ =\ &
-P\left(|| B(Q) ||_{p,\mu}^p - \hat{q} \leq \epsilon - \hat{q} \mid ||B(Q)||_{p,D}^p = \hat{q}\right)
-\end{align*}
-Notice that $\mathbb{E}[\hat{q}] = || B(Q) ||_{p,\mu}^p$ and that $\epsilon - \hat{q} < 0$ by assumption. Then, we can apply Hoeffding's inequality to write:
-\begin{equation*}
-P\left(Q\in\mathcal{Q}^{\epsilon} \mid ||B(Q)||_{p,D}^p = \hat{q}\right) \leq exp\left( -\frac{2N(\epsilon-\hat{q})^2}{\left(\frac{2R_{max}}{1-\gamma}\right)^{2p}} \right)
-\end{equation*}
-Finally, when $\hat{q} \leq \epsilon$, the probability can be straightforwardly upper-bounded by $1$. Combining the two results concludes the proof.
-\end{proof}
-\begin{theorem}
-Let $Q$ be a $Q$-function with empirical Bellman error, computed on a dataset $D$ of $N$ i.i.d. samples, given by $||B(Q)||_{p,D}^p = \hat{q}$. Then, for any $\epsilon >= 0$:
-\begin{equation*}
-P\left( ||B(Q)||_{p,D}^p = \hat{q} \mid Q\in\mathcal{Q}^{\epsilon} \right) \leq \frac{\epsilon}{\hat{q}}
-\end{equation*}
-\begin{proof}
-\begin{align*}
-P\left( ||B(Q)||_{p,D}^p = \hat{q} \mid Q\in\mathcal{Q}^{\epsilon} \right) =\ &
-P\left( ||B(Q)||_{p,D}^p = \hat{q} \mid || B(Q) ||_{p,\mu}^p \leq \epsilon \right)\\ \leq\ &
-P\left( ||B(Q)||_{p,D}^p \geq \hat{q} \mid || B(Q) ||_{p,\mu}^p \leq \epsilon \right)\\ \leq\ &
-\frac{E[||B(Q)||_{p,D}^p]}{\hat{q}}\\ \leq\ &
-\frac{\epsilon}{\hat{q}}
-\end{align*}
-The first inequality is straightforward, the second one is from Markov's inequality, while the third one is due to the fact that $Q\in\mathcal{Q}^{\epsilon}$.
-\end{proof}
-\end{theorem}
+where $\lambda$ is a constant hyperparameter.
+Intuitively, this indicates that $D$ is more likely when it induces low empirical Bellman error under an optimal $Q$-function.
+Furthermore, as the number of available samples $N$ increases, the distribution becomes more peaked at zero since the empirical Bellman error converges to the true Bellman error.
+In the limit $N \rightarrow \infty$:
+\begin{equation}
+P(D \mid Q) \propto I_{\left\{ ||B(Q)||_{p,D}^p = 0 \right\}}
+\end{equation}
 
@@
 
-Consider solving the target task given a dataset $D$ of $N$ samples. The posterior distribution over optimal $Q$-functions is:
-\begin{equation}
-P(Q^* \mid D) \propto P(D \mid Q^*)P(Q^*)
-\end{equation}
-Bounding the likelihood $P(D \mid Q^*)$ ({\color{red}FIND A BETTER DERIVATION}) and taking the maximum of the log-posterior, we obtain the following optimization problem:
+Taking the maximum of the log-posterior, we obtain the following optimization problem:
 \begin{equation}
@@
 \end{equation}
-Then, let us specify a particular hypothesis space $\mathcal{Q}$. We consider $Q$-functions $Q_{\bm{w}}$ parameterized by the vector $\bm{w}$. Our optimization problem becomes:
+Let us specify a particular hypothesis space $\mathcal{Q}$. We consider $Q$-functions $Q_{\bm{w}}$ parameterized by the vector $\bm{w}$. Our optimization problem becomes:
 \begin{equation}
@@
 where $\bm{A}$ is an $N\times K$ matrix containing the feature vectors at each data point $(s_i,a_i)$ and $\bm{b}$ is an $N$-dimensional vector containing their targets $y_i$.
+The resulting algorithm is a regularized version of LSVI.
+
+\paragraph{Neural network}
+
+We model $Q_{\bm{w}}(s,a)$ as a neural network with parameters $\bm{w}$.
+Then, the gradient of the objective function of Eq.
+\eqref{eq:optim} can be easily computed by standard backpropagation.
+The resulting algorithm is a regularized version of NFQI.
+
+\subsection{Variational Inference for Gaussian Distributions}
+
+TODO
 

### 2018-03-16 paper/paper.tex
Edits to the writeup 2

@@
 
-\subsection{Variational Inference for Gaussian Distributions}
+\subsection{Variational Inference for Efficient Exploration}
 
-TODO
+A major drawback of the maximum-a-posteriori (MAP) approach is that it does not explicitly estimate the posterior distribution $P(Q \mid D)$.
+Thus, given a dataset $D$, the algorithm consistently chooses the same MAP $Q$-function, and the only way to allow learning is to introduce a simple form of exploration (e.g., $\epsilon$-greedy or softmax), whose drawbacks are well-known.
+The advantages of a more time-coherent exploration strategy such as posterior sampling (or Thompson sampling) have already been proved by many existing works (CITE).
+In particular, direct posterior sampling of $Q$-functions (also known as value function randomization), when a distribution is available, have been proven to be very effective and scalable.
+Thus, we known extend our previous approach to explicitly estimate $P(Q \mid D)$, so as to allow efficient exploration of the target task.
+The main complication is that, as mentioned earlier, we cannot compute the likelihood $P(D \mid Q)$ explicitly, but we only have access to a model that is proportional to it.
+Then, estimating the posterior distribution is clearly intractable since it requires computing the marginal likelihood $P(D) = \int P(D \mid Q) dQ$.
+Thus, we resort variational inference (CITE) to approximate the intractable posterior with a simpler distribution from which we are able to sample.
+
+The main idea behind variational inference is to approximate the posterior $P(Q | D)$ with a simpler distribution $q_{\bm{\phi}}(Q)$, parameterized by the vector $\bm{\phi}$, from which we can easily get samples.
+The best approximation is chosen in terms of the Kullback-Leibler (KL) divergence between the two distributions, that is:
+\begin{equation}
+\min_{\bm{\phi}} KL\left(q_{\bm{\phi}}(Q)\ ||\ P(Q \mid D)\right)
+\end{equation}
+It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
+\begin{equation}
+\text{ELBO}(\bm{\phi}) = \mathbb{E}_{Q \sim q_{\bm{\phi}}}\left[ \log P(D | Q) \right] - KL\left(q_{\bm{\phi}}(Q)\ ||\ P(Q)\right)
+\end{equation}
+As before, we assume a parametric form $Q_{\bm{w}}$ for representing $Q$-functions.
+Thus, we reduce distributions over functions to distributions over vectors $\bm{w} \in \mathbb{R}^K$.
+Given a specific form for the approximate posterior $q_{\bm{\phi}(\bm{w})}$ and the prior $P(\bm{w})$, our inference problem reduces to:
+\begin{equation} \label{eq:vi}
+\min_{\bm{\phi}} \mathbb{E}_{\bm{w} \sim q_{\bm{\phi}}}\left[ \lambda N ||B(\bm{w})||_{D}^2 \right] + KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right)
+\end{equation}
+Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low empirical Bellman error (first term), and staying close to the prior distribution that is learned from the set of source tasks (second term).
+The factor $N$ multiplying $||B(\bm{w})||_{D}^2$ makes sure that, as the number of samples goes to infinity, only the first term is considered in the optimization.
+In such case, all probability mass go over the (approximate) fixed-point of the optimal Bellman operator.
+On the other hand, for small values of $N$, there is less evidence that the empirical Bellman error closely estimate the true one, thus giving more importance to staying close to the prior.
+
+Depending on the choice of the prior and approximate posterior distributions, the optimization problem of Eq.
+\eqref{eq:vi} might still be very hard to solve.
+We now propose some suitable choices that make the problem efficiently solvable.
+
+\paragraph*{Gaussian distributions}
+
+We model both the prior and the approximate posterior as Gaussian distributions: $P(\bm{w}) = \mathcal{N}(\bar{\bm{\mu}},\bar{\bm{\Sigma}})$ and $q_{\bm{\phi}}(\bm{w}) = \mathcal{N}(\bm{\mu},\bm{\Sigma})$, respectively.
+For the sake of simplicity, we assume $\bm{\Sigma} = \text{diag}(\sigma_1^2,\dots,\sigma_K^2)$ and $\bar{\bm{\Sigma}} = \text{diag}(\bar{\sigma}_1^2,\dots,\bar{\sigma}_K^2)$.
+Notice, in this case, that the parameter vector $\bm{\phi}$ is $[\mu_1,\dots,\mu_K,\sigma_1^2,\dots,\sigma_K^2]$.
+The KL divergence between the two distributions can be computed in closed form as:
+\begin{equation}
+KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bar{\bm{\Sigma}} \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bar{\bm{\Sigma}}^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bar{\bm{\mu}})^T \bar{\bm{\Sigma}}^{-1} (\bm{\mu} - \bar{\bm{\mu}}) -K \right)
+\end{equation}
+To solve the optimization problem of Eq.
+\eqref{eq:vi} we adopt stochastic backpropagation (CITE).
+Thus, we need to compute the gradient of the objective function $\mathcal{L}(\bm{\phi})$ of Eq.
+\eqref{eq:vi} with respect to each component of $\bm{\phi}$.
+This can be easily done for the second term:
+\begin{equation}
+\nabla_{\bm{\mu}} KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right) = \bar{\bm{\Sigma}}^{-1} (\bm{\mu} - \bar{\bm{\mu}})
+\end{equation}
+\begin{equation}
+\nabla_{\sigma_k^2} KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right) = \frac{1}{2}\left( \frac{1}{\bar{\sigma}_k^2} - \frac{1}{\sigma_k^2} \right)
+\end{equation}
+For the first term, we have to compute the gradient of an expectation with respect to the parameters of the Gaussian distribution under which the expectation is taken.
+For the mean, we can resort to Thm.
+X of (CITE Bonnet 1964):
+\begin{equation}
+\nabla_{\mu_k} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N \nabla_{w_k} ||B(\bm{w})||_{D}^2 \right]
+\end{equation}
+For the covariance, we can resort to Thm. Y of (CITE Price 1958):
+\begin{equation}
+\nabla_{\sigma_k^2} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N ||B(\bm{w})||_{D}^2 \right] = \frac{1}{2}\mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N \nabla_{w_k,w_k}^2 ||B(\bm{w})||_{D}^2 \right]
+\end{equation}
+We refer the reader to (CITE Deepmind) for a simple proofs of these two theorems.
+
+It only remains to compute the gradient and Hessian of the empirical Bellman error $||B(\bm{w})||_{D}^2$ with respect to $\bm{w}$. Recall that:
+\begin{equation}
+||B(\bm{w})||_{D}^2 = \frac{1}{N}\sum_{i=1}^N \left( r_i + \gamma\max_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i) \right)^2
+\end{equation}
 

### 2018-03-16 algorithms/simple_rl.py
implemented anisotropic grbf

@@ -35,6 +35,8 @@ def simple_RL(mdp, Q, epsilon=0, K=1, batch_size=1, render=False, verbose=False,
             targets = [Q.compute_bellman_target(samples[a][:, 1:]) for a in range(n_act)]
             for a in range(n_act):
                 if feat[a].shape[0] > 0:
+                    print(a)
+                    print(np.shape(feat[a]))
                     if prior_parameters is None:
                          w = lsvi.RegularizedLSVI.solve(feat[a], targets[a], prior=False)
                     else:

### 2018-03-16 features/agrbf.py

@@ -2,23 +2,27 @@ import numpy as np
 """
 Isotropic Gaussian RBF Features
 """
-class GaussianRBF:
+class AGaussianRBF:
 
-    def __init__(self, mean, variance, K=2, dims=2):
+    def __init__(self, mean, covar, K=2, dims=2):
         """
         :param mean: (np.ndarray) mean vector Kxdim
-        :param variance: (np.ndarray)  variance vector Kx1
+        :param covar: (np.ndarray)  Covariances vector (Kxdim)xdim
         :param K: number of basis functions
         :param dims: dimension of the input
 
         """
         assert mean.shape == (K, dims)
-        assert variance.shape == (K,)
+        assert covar.shape == (K * dims, K)
 
         self._K = K
         self._mean = mean
         self._dims = dims
-        self._var = variance
+        self._precision = np.zeros(covar.shape)
+        for k in range(self._K):
+            self._precision[k*dims:(k+1)*dims, :] = np.linalg.inv(covar[k*dims:(k+1)*dims, :])
+
+
 
     def _compute(self, point):
 
@@ -31,8 +35,7 @@ class GaussianRBF:
 
         for k in range(self._K):
             dif = self._mean[k, :] - point
-            dif = np.dot(dif, dif)
-            val.append(np.exp(-dif/(2*self._var[k])))
+            val.append(np.exp(1/2*(dif @ self._precision[k*self._dims:(k+1)*self._dims, :] @ dif)))
         f = np.asarray(val, order='F')
         f = f/np.sum(f)
         return f
@@ -60,12 +63,13 @@ class GaussianRBF:
 
 if __name__ == '__main__':
     mean = np.array([[1, 2], [3, 4]])
-    var = np.array([3, 8])
+    covar = np.vstack((np.eye(2), np.eye(2)))
 
-    rbf = GaussianRBF(mean, var)
+    rbf = AGaussianRBF(mean, covar)
 
     data = np.random.random((100, 2))
 
     matrix = rbf(data)
-    print(matrix)
     print(rbf(np.array([1, 2])))
+    print(matrix)
+

### 2018-03-16 algorithms/linear_q_function.py
change bellman target computation to only numpy operations

@@ -5,20 +5,22 @@ import utils
 
 class LinearQFunction:
 
-    def __init__(self, actions, features, params=None, state_dim=1, action_dim=1, gamma=0.99):
+    def __init__(self, actions, features, params=None, state_dim=1, action_dim=1, gamma=0.99, regressor_per_action=True):
         """
         :param actions: tuple with the possible actions available
         :param features: feature object
         :param gamma: discount factor
-        :param params: initial parameters
+        :param params: initial parameters (np.ndarray n_features x n_actions or n_features x 1)
         :param state_dim: dimension of the state vector
         :param action_dim: dimension of the action vector
+        :param regressor_per_action: boolean flag to have or not a regressor per action available
 
         """
+
         self.actions = actions
         self._features = features
         self._gamma = gamma
-        self._w = [params for i in range(len(actions))]
+        self._w = params
         self._state_dim = state_dim
         self._action_dim = action_dim
 
@@ -35,28 +37,25 @@ class LinearQFunction:
         r = self._state_dim + self._action_dim
         t = list()
         a = self._state_dim
-        for i in range(samples.shape[0]):
-            qs = list()
-            fts = self._features(samples[i, s_prime: s_prime + self._state_dim])
-            for a in self.actions:
-                qs.append(np.dot(self._w[a], fts))
-            t.append((samples[i, r] + self._gamma * max(qs)) if samples[i, -1] == 0 else samples[i, r])
-        return np.array(t)
+
+        fts = self._features(samples[:, s_prime: s_prime + self._state_dim])
+        qs = np.max(np.dot(fts, self._w), axis=1)
+        t = samples[:, r] + self._gamma * qs * (1-samples[:, -1])
+        return t
 
 
     def update_weights(self, w, action=None):
         """
         Update the weights of the regressors
-        :param w: vector of weights or list of vectors of weights
+        :param w: matrix of weights (one regressor per column)
         :param action: specific action to which update the regressor's parameters
         """
         if action is None:
-            for i in range(len(w)):
-                assert w[i].shape == self._w[i].shape
+            assert w.shape == self._w.shape
             self._w = w
         else:
-            assert w.shape == self._w[action].shape
-            self._w[action] = w
+            assert w.shape == self._w[:, action].shape
[…]

### 2018-03-16 features/grbf.py

@@ -57,6 +57,8 @@ class GaussianRBF:
 
         return np.asarray(features)
 
+    def number_of_actions(self):
+        return self._K
 
 if __name__ == '__main__':
     mean = np.array([[1, 2], [3, 4]])

### 2018-03-16 algorithms/linear_q_function.py
added assertions to the linear q constructor

@@ -6,6 +6,7 @@ import utils
 class LinearQFunction:
 
     def __init__(self, actions, features, params=None, state_dim=1, action_dim=1, gamma=0.99, regressor_per_action=True):
+
         """
         :param actions: tuple with the possible actions available
         :param features: feature object
@@ -16,13 +17,24 @@ class LinearQFunction:
         :param regressor_per_action: boolean flag to have or not a regressor per action available
 
         """
+        if params is not None:
+            if regressor_per_action:
+                assert params.shape == (features.number_of_features(), len(actions))
+            else:
+                assert params.shape == (features.number_of_features(),)
+
+        else:
+            if regressor_per_action:
+                self._w = np.zeros((features.number_of_features(), len(actions)))
+            else:
+                self._w = np.zeros((features.number_of_features(),))
 
         self.actions = actions
         self._features = features
         self._gamma = gamma
-        self._w = params
         self._state_dim = state_dim
         self._action_dim = action_dim
+        self._isRxA = regressor_per_action
 
 
     def compute_bellman_target(self, samples):
@@ -35,9 +47,7 @@ class LinearQFunction:
 
         s_prime = self._state_dim + self._action_dim + 1
         r = self._state_dim + self._action_dim
-        t = list()
         a = self._state_dim
-
         fts = self._features(samples[:, s_prime: s_prime + self._state_dim])
         qs = np.max(np.dot(fts, self._w), axis=1)
         t = samples[:, r] + self._gamma * qs * (1-samples[:, -1])

### 2018-03-16 features/agrbf.py

@@ -61,6 +61,9 @@ class AGaussianRBF:
         return np.asarray(features)
 
 
+    def number_of_features(self):
+        return self._K
+
 if __name__ == '__main__':
     mean = np.array([[1, 2], [3, 4]])
     covar = np.vstack((np.eye(2), np.eye(2)))

### 2018-03-16 features/grbf.py

@@ -57,7 +57,7 @@ class GaussianRBF:
 
         return np.asarray(features)
 
-    def number_of_actions(self):
+    def number_of_features(self):
         return self._K
 
 if __name__ == '__main__':

### 2018-03-16 paper/paper.tex
Edits to the writeup 3

@@
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newcommand{\mm}{\operatornamewithlimits{mm}}
 
@@
 \end{equation}
+A major complication is that computing the gradient with respect to $\bm{w}$ requires differentiating through the maximum operator.
+In iterative approaches such as Fitted Q-Iteration (FQI) or Deep Q-Networks (DQNs), this is typically solved by computing the Bellman target using the previous weights and adapting the current weights so that the resulting Q-functions matches the target.
+In such case, no differentiation through the maximum operator is required.
+However, in our case there is no previous weight: we simply want to now what is the Bellman error of any given weight $\bm{w}$ and we are thus required to differentiate through the maximum operator when updating the approximate posterior, which is not possible in practice.
+To solve this issue, we replace the max with the \textit{mellowmax} operator defined by:
+\begin{equation}
+\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
+\end{equation}
+where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
+The mellowmax operator has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
+Replacing max with the mellowmax operator, we obtain a new approximation to the Bellman residual:
+\begin{equation}
+\widetilde{B}(\bm{w})(s,a) \triangleq \mathcal{R}(s,a) + \gamma\mathbb{E}_{\mathcal{P}}[\mm_{a'}Q_{\bm{w}}(s',a')] - Q_{\bm{w}}(s,a)
+\end{equation}
+and to the empirical Bellman error:
+\begin{equation}
+||\widetilde{B}(\bm{w})||_{D}^2 = \frac{1}{N}\sum_{i=1}^N \left( r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i) \right)^2
+\end{equation}
+Of fundamental importance, this last quantity is now differentiable with respect to $\bm{w}$.
+
+Differentiating trough the mellowmax operator with respect to $\bm{w}$ is now very simple:
+\begin{align}
+\nabla_{\bm{w}_k}\mm_a Q_{\bm{w}}(s,a) =\ & 
+\nabla_{\bm{w}_k} \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \\ =\ &
+\frac{1}{\kappa}\frac{1}{\frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}}\frac{1}{|\mathcal{A}|}\sum_a \nabla_{\bm{w}_k} e^{\kappa Q_{\bm{w}}(s,a)} \\ =\ &
+\frac{1}{\kappa}\frac{1}{\frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}}\frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \kappa \nabla_{\bm{w}_k} Q_{\bm{w}}(s,a) \\ =\ &
+\frac{\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \nabla_{\bm{w}_k} Q_{\bm{w}}(s,a)}{\sum_a e^{\kappa Q_{\bm{w}}(s,a)}}
+\end{align}
+The diagonal of the Hessian can also be computed straightforwardly:
+\begin{align}
+\nabla_{\bm{w}_k,\bm{w}_k}^2 \mm_a Q_{\bm{w}}(s,a) =\ &
+\nabla_{\bm{w}_k}\frac{\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \nabla_{\bm{w}_k} Q_{\bm{w}}(s,a)}{\sum_a e^{\kappa Q_{\bm{w}}(s,a)}} \\ =\ &
+\frac{\nabla_{\bm{w}_k}\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \nabla_{\bm{w}_k} Q_{\bm{w}}(s,a)}{\sum_a e^{\kappa Q_{\bm{w}}(s,a)}} + \nabla_{\bm{w}_k}\left( \frac{1}{\sum_a e^{\kappa Q_{\bm{w}}(s,a)}} \right)\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \nabla_{\bm{w}_k} Q_{\bm{w}}(s,a) \\ =\ &
+(\kappa + 1)\frac{\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \nabla_{\bm{w}_k,\bm{w}_k}^2 Q_{\bm{w}}(s,a)}{\sum_a e^{\kappa Q_{\bm{w}}(s,a)}} - \kappa\frac{\left(\sum_a e^{\kappa Q_{\bm{w}}(s,a)} \nabla_{\bm{w}_k} Q_{\bm{w}}(s,a)\right)^2}{\left(\sum_a e^{\kappa Q_{\bm{w}}(s,a)}\right)^2}
+\end{align}
 

### 2018-03-16 paper/paper.tex
Edits to the writeup 4

@@
 \usepackage{todonotes}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 \newcommand{\mm}{\operatornamewithlimits{mm}}
+
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 
+Finally, we show how to compute the gradient and the Hessian of $||\widetilde{B}(\bm{w})||_D^2$ with respect to $\bm{w}$ when we use a linear model $Q_{\bm{w}}(s,a) = \bm{w}^T\bm{\phi}(s,a)$.
+Let $y_i(\bm{w}) = r_i + \gamma\mm_{a'}\bm{w}^T\bm{\phi}(s_i',a')$.
+The gradient can be computed as:
+\begin{align}
+\nabla_{\bm{w}_k} ||\widetilde{B}(\bm{w})||_D^2 =\ & 
+\frac{1}{N}\sum_{i=1}^N \nabla_{\bm{w}_k} \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)^2 \\ =\ &
+\frac{2}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \nabla_{\bm{w}_k}y_i(\bm{w}) - \nabla_{\bm{w}_k}\bm{w}^T\bm{\phi}(s_i,a_i)) \right) \\ =\ &
+\frac{2}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \gamma\nabla_{\bm{w}_k}\mm_{a'}\bm{w}^T\bm{\phi}(s_i',a') - \phi_k(s_i,a_i)) \right) \\ =\ &
+\frac{2}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \gamma\frac{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))}{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}} - \phi_k(s_i,a_i)) \right)
+\end{align}
+Similarly, the diagonal of the Hessian is:
+\begin{align}
+\nabla_{\bm{w}_k,\bm{w}_k}^2 ||\widetilde{B}(\bm{w})||_D^2 =\ & 
+\frac{1}{N}\sum_{i=1}^N \nabla_{\bm{w}_k,\bm{w}_k}^2 \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)^2 \\ =\ &
+\frac{2}{N}\sum_{i=1}^N \nabla_{\bm{w}_k} \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \gamma\frac{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))}{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}} - \phi_k(s_i,a_i)) \right) \\ =\ &
+\frac{2}{N}\sum_{i=1}^N \left( \gamma\frac{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))}{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}} - \phi_k(s_i,a_i)) \right)^2 \\ \ \ & - \frac{2\kappa}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right) \frac{\left(\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))\right)^2}{\left(\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}\right)^2}
+\end{align}
+
+We are now ready to present our algorithm for transfer-based exploration via posterior sampling. This is shown in Alg. \ref{alg:transfer}.
+
+\begin{algorithm}
+\begin{algorithmic}
+\REQUIRE Prior mean $\bar{\bm{\mu}}$, prior covariance $\bar{\bm{\Sigma}}$, likelihood weight $\lambda$, mellowmax parameter $\kappa$, learning rate $\eta$, feature vector $\bm{\phi}$
+\ENSURE Greedy policy $\pi$
+\\\hrulefill
+
+\STATE{Initialize posterior: $\bm{\mu} \leftarrow \bar{\bm{\mu}}, \bm{\Sigma} \leftarrow \bar{\bm{\Sigma}}$}
+\STATE{Initialize dataset: $D = \emptyset$}
+\REPEAT
+
+\STATE{Sample $Q$-function: $\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})$}
+\STATE{Sample initial state: $s_0 \sim p_0$}
+
+\FOR{$h=0,\dots,H$}
+\STATE{Take action $a_h = \argmax_a \bm{w}^T\bm{\phi}(s_h,a)$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}(\cdot | s_h,a_h)$}
+\STATE{Collect reward $r_h = \mathcal{R}(s_h,a_h)$}
+\STATE{Add sample to the dataset: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
+\STATE{Compute ELBO: $\mathcal{L}(\bm{\mu},\bm{\Sigma}) = \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N ||\widetilde{B}(\bm{w})||_{D}^2 \right] + KL(\mathcal{N}(\bm{\mu},\bm{\Sigma})\ ||\ \mathcal{N}(\bar{\bm{\mu}},\bar{\bm{\Sigma}}))$}
+\STATE{Compute gradients $\nabla_{\bm{\mu}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$ and $\nabla_{\bm{\Sigma}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$}
+\STATE{Update posterior parameters: $\bm{\mu} \leftarrow \bm{\mu} - \eta\nabla_{\bm{\mu}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$ and $\bm{\Sigma} \leftarrow \bm{\Sigma} - \eta\nabla_{\bm{\Sigma}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$}
+\ENDFOR
+
+\UNTIL{done}
+\STATE{Sample final parameters: $\bm{w}^* \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})$ (or take the MAP: $\bm{w}^* = \bm{\mu}$)}
+\RETURN{Greedy policy: $\pi(s) = \argmax_a \bm{w}^* \bm{\phi}(s,a)$}
+\end{algorithmic}
+\caption{Variational Exploration under Gaussian Approximation} \label{alg:transfer}
+\end{algorithm}
+
 \section{Related Works}

### 2018-03-19 utils.py
Added better version of plot_Q() to utils.py

@@ -1,6 +1,7 @@
 import numpy as np
 import pickle
 from time import sleep
+import matplotlib.pyplot as plt
 
 
 def evaluate_policy(mdp, policy, criterion='discounted', n_episodes=1, initial_states=None, render=False):
@@ -156,3 +157,62 @@ def load_object(file_name):
 
     with open(file_name + ".pkl", 'rb') as file:
         return pickle.load(file)
+
+
+def plot_Q(Q, size=(5,5)):
+
+    V = [[], [], [], []]
+    Vmax = []
+    pi = []
+    X = np.arange(0.0, size[0]+.1, 0.1)
+    Y = np.arange(0.0, size[1]+.1, 0.1)
+
+    for x in X:
+        for y in Y:
+            vals = Q.compute_all_actions(np.array([y, x]))
+            Vmax.append(np.max(vals))
+            pi.append(np.argmax(vals))
+            vals = vals.reshape(4,1)
+            V[0].append(vals[0])
+            V[1].append(vals[1])
+            V[2].append(vals[2])
+            V[3].append(vals[3])
+
+    for v in V:
+        v[-1][0] = 0.0
+    Vmax[-1] = 0.0
+    V = [np.flip(np.array(v).reshape(X.size, X.size), axis=0) for v in V]
+
+    fig, ax = plt.subplots(3, 2)
+    f00 = ax[0, 0].imshow(V[0], cmap="hot", interpolation="gaussian")
+    ax[0, 0].set_title("UP (black)")
+    ax[0, 0].axes.get_yaxis().set_visible(False)
+    ax[0, 0].axes.get_xaxis().set_visible(False)
+    f01 = ax[0, 1].imshow(V[1], cmap="hot", interpolation="gaussian")
+    ax[0, 1].set_title("RIGHT (red)")
+    ax[0, 1].axes.get_yaxis().set_visible(False)
+    ax[0, 1].axes.get_xaxis().set_visible(False)
+    f10 = ax[1, 0].imshow(V[2], cmap="hot", interpolation="gaussian")
+    ax[1, 0].set_title("DOWN (orange)")
+    ax[1, 0].axes.get_yaxis().set_visible(False)
+    ax[1, 0].axes.get_xaxis().set_visible(False)
+    f11 = ax[1, 1].imshow(V[3], cmap="hot", interpolation="gaussian")
[…]

### 2018-03-19 VariationalTransfer/BellmanOperator.py
fix bugs in feature agrbf and implemented basic FQI for training in source tasks

@@ -6,21 +6,26 @@ class BellmanOperator:
     Optimal Bellman Operator
     """
 
-    def __init__ (self, Q, gamma=0.99):
+    def __init__ (self, Q=None, gamma=0.99):
         self._Q = Q
         self._gamma = gamma
 
     def __call__(self, mdp_samples):
-        s_prime = self._Q.state_dim + self._Q.action_dim + 1
-        r = self._Q.state_dim + self._Q.action_dim
-        a = self._Q.state_dim
-        qs = np.max(self._Q.compute_all_actions(mdp_samples[:, s_prime: s_prime + self._state_dim]), axis=1)
+        s_prime = self._Q.get_statedim() + self._Q.get_actiondim() + 1
+        r = self._Q.get_statedim() + self._Q.get_actiondim()
+        a = self._Q.get_statedim()
+        qs = np.max(self._Q.compute_all_actions(mdp_samples[:, s_prime: s_prime + self._Q.get_statedim()]), axis=1)
         return mdp_samples[:, r] + self._gamma * qs * (1 - mdp_samples[:, -1])
 
     def bellman_residual(self, mdp_samples):
-        s = self._Q.state_dim
-        a = self._Q.state_dim
-        r = self._Q.state_dim + self._Q._action_dim
+        s = 0
+        a = self._Q.get_statedim()
+        r = self._Q.get_statedim() + self._Q.get_actiondim()
         residuals = -self._Q(mdp_samples[:, 0:r]) + self.__call__(mdp_samples)
         return residuals
 
+    def set_Q(self, Q):
+        self._Q = Q
+
+    def get_Q(self):
+        return self._Q

### 2018-03-19 VariationalTransfer/LinearQRegressor.py

@@ -11,31 +11,46 @@ class LinearQRegressor:
         if initial_params is not None:
             assert initial_params.size == features.number_of_features()
             self._w = initial_params
-
-        self._actions = actions
+        else:
+            self._w = np.zeros(features.number_of_features())
+        self.actions = actions[:, np.newaxis]
         self._features = features
-        self.state_dim = state_dim
-        self.action_dim = action_dim
+        self._state_dim = state_dim
+        self._action_dim = action_dim
 
     def update_weights(self, weights):
         assert weights.shape == self._w.shape
         self._w = weights
 
     def compute_all_actions(self, state):
-        t = np.hstack((np.tile(state, (self._actions.size, 1)), self._actions))
+
+        s = state[:, np.newaxis].T if state.ndim == 1 else state
+        n_state = s.shape[0]
+        s = np.repeat(s, self.actions.size, axis=0)
+        a = np.tile(self.actions, (n_state, 1))
+        t = np.hstack((s, a))
         f = self._features(t)
-        return np.dot(f, self._w).reshape(state.shape[0], self._actions.size)
+        return np.dot(f, self._w).reshape(n_state, self.actions.size)
 
     def compute_gradient(self, state_action):
         return self._features(state_action)
 
     def compute_gradient_all_actions(self, state):
-        t = np.hstack((np.tile(state, (self._actions.size, 1)), self._actions))
+        t = np.hstack((np.tile(state, (self.actions.size, 1)), self.actions))
         f = self._features(t)
-        return f.reshape(state.shape[0], self._actions.size, f.shape[1])
+        return f.reshape(state.shape[0], self.actions.size, f.shape[1])
 
     def compute_diag_hessian_all_actions(self, state):
-        return np.zeros((state.shape[0], self._actions.size, self._features.number_of_features()))
+        return np.zeros((state.shape[0], self.actions.size, self._features.number_of_features()))
 
     def __call__(self, state_action):
         return np.dot(self._features(state_action), self._w)
+
+    def compute_features(self, samples):
+        return self._features(samples[:, 0: self._state_dim + self._action_dim])
+
+    def get_statedim(self):
+        return self._state_dim
+
+    def get_actiondim(self):
+        return self._action_dim

### 2018-03-19 VariationalTransfer/MellowBellmanOperator.py

@@ -5,7 +5,7 @@ import algorithms
 Optimal Bellman Operator with Mellowmax
 """
 class MellowBellmanOperator(algorithms.BellmanOperator):
-    def __init__(self, Q, gamma=0.99, kappa=1e6):
+    def __init__(self, Q=None, gamma=0.99, kappa=1e6):
         super(MellowBellmanOperator, self).__init__(Q, gamma)
         self._kappa = kappa
 
@@ -27,7 +27,7 @@ class MellowBellmanOperator(algorithms.BellmanOperator):
         return bellman_grad, bellman_hess
 
     def _mellow_max(self, q_values):
-        qs = self._normalized_mm_exp(q_values)
+        qs = np.sum(self._normalized_mm_exp(q_values), axis=1)
         return np.log(qs/q_values.shape[1])/self._kappa
 
     def _normalized_mm_exp(self, q_values, c=0):
@@ -57,9 +57,6 @@ class MellowBellmanOperator(algorithms.BellmanOperator):
              - self._kappa * (np.sum(qs[:, :, np.newaxis] * q_gradient, axis=1)/qs_sum)**2
         grad = np.sum(qs[:, :, np.newaxis] * q_gradient, axis=1)/qs_sum
         return grad, diag_hess
-
-    def get_Q(self):
-        return self._Q
 
 
 """

### 2018-03-19 features/agrbf.py

@@ -29,13 +29,12 @@ class AGaussianRBF:
         :param point: np.ndarray (dim)
         :return: feature vector: np.ndarray
         """
-
+        features = list()
         for k in range(self._K):
             dif = self._mean[k, :] - point
-            val = np.exp(1/2*(dif @ self._precision[:, :] @ dif))
-        f = np.asarray(val, order='F')
-        f = f/np.sum(f)
-        return f
+            val = np.exp(-1/2 * (dif @ self._precision[:, :, k] @ dif))
+            features.append(val)
+        return np.array(features)
 
     def __call__(self, x):
         if x.ndim == 2:

### 2018-03-19 scripts/run_gaussian_var_transfer.py

@@ -1,14 +1,66 @@
 import numpy as np
-import matplotlib.pyplot as plt
 import envs.walled_gridworld as wgw
-import VariationalTransfer as vt
+import VariationalTransfer.LinearQRegressor as linq
+import VariationalTransfer.BellmanOperator as bellmanop
 import features.agrbf as rbf
 import utils
+import algorithms.e_greedy_policy as policy
+import algorithms.regularized_lsvi as lsvi
+from scripts.run_nfqi import plot_Q
+
+
+"""
+    FQI with linear regressor for Q(s,a) 
+"""
+def linearFQI(mdp, Q, epsilon=0, n_iter=1, batch_size=1, render=False, verbose=False, n_fit=20, bellman_operator=None):
+    pol = policy.eGreedyPolicy(Q, Q.actions, epsilon)
+    pol_g = policy.eGreedyPolicy(Q, Q.actions, 0)
+    r = list()
+    n_act = len(Q.actions)
+
+    rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
+    r.append(rew)
+    plot_Q(Q, size=tuple(mdp.size))
+
+    samples = utils.generate_episodes(mdp, pol, batch_size, render=False)
+    feat = Q.compute_features(samples[:, 1:])
+
+    if bellman_operator is None:
+        bellman = bellmanop.BellmanOperator(Q)
+    else:
+        bellman_operator.set_Q(Q)
+        bellman = bellman_operator
+
+    for i in range(n_iter):
+        new_samples = utils.generate_episodes(mdp, pol, batch_size, render=False)
+        samples = np.vstack((samples, new_samples))
+        feat = np.vstack((feat, Q.compute_features(new_samples[:, 1:])))
+
+        for k in range(n_fit):
+            targets = bellman(samples[:, 1:])
+            w = lsvi.RegularizedLSVI.solve(feat, targets, prior=False)
+            Q.update_weights(w)
+
+        if render:
+            mdp._render(close=True)
+
+        plot_Q(Q, size=tuple(mdp.size))
+        rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
+        r.append(rew)
+        if verbose:
+            print("===============================================")
+            print("Iteration " + str(i))
+            print("Reward: " + str(rew))
[…]

### 2018-03-19 utils.py

@@ -47,7 +47,7 @@ def _single_eval(mdp, policy, criterion, initial_state, render):
         a = policy.sample_action(s)
         if render:
             mdp._render(a=a)
-            sleep(0.05)
+            sleep(0.01)
         s, r, done, _ = mdp.step(a)
         score += r * gamma ** t
         t += 1

### 2018-03-19 features/agrbf.py
improve performance of AGRBF features. Fix bugs in variational gaussian class and in mellow bellman operator

@@ -26,15 +26,19 @@ class AGaussianRBF:
 
         """
         Computes a feature vector for the point given
-        :param point: np.ndarray (dim)
+        :param point: np.ndarray (n x dim)
         :return: feature vector: np.ndarray
         """
-        features = list()
-        for k in range(self._K):
-            dif = self._mean[k, :] - point
-            val = np.exp(-1/2 * (dif @ self._precision[:, :, k] @ dif))
-            features.append(val)
-        return np.array(features)
+        shape_mean = (int(point.size/self._dims), 1)
+        shape_prec = (1,1, shape_mean[0])
+        dif = np.tile(self._mean, shape_mean) - np.repeat(point, int(self._K), axis=0)
+        dif2 = dif.T[:, np.newaxis, :]
+        prec = np.tile(self._precision, shape_prec)
+        temp = np.sum(dif2 * prec, axis=0).T
+        temp = np.exp(-0.5 * np.sum(temp * dif, axis=1).reshape(shape_mean[0], self._K))
+        res = temp/np.sum(temp, axis=1)[:, np.newaxis]
+
+        return res
 
     def __call__(self, x):
         if x.ndim == 2:
@@ -50,12 +54,7 @@ class AGaussianRBF:
         :return: feature matrix (np.ndarray) with feature vector for each row.
         """
         assert data.shape[1] == self._dims
-        features = []
-        for x in range(data.shape[0]):
-            features.append(self._compute(data[x, :]))
-
-        return np.asarray(features)
-
+        return self._compute(data)
 
     def number_of_features(self):
         return self._K

### 2018-04-28 buffer.py
Added replay buffer class and identity features

@@ -1,0 +1,41 @@
+import numpy as np
+
+
+class Buffer:
+    """A replay buffer with efficient sample addition"""
+
+    def __init__(self, capacity, state_dim):
+        # The columns are (t,s,a,r,s_prime,done)
+        self._buffer = np.zeros((capacity, 1 + state_dim + 1 + 1 + state_dim + 1))
+        self._next = 0
+        self._capacity = capacity
+        self.n_samples = 0
+        self._a_idx = 1 + state_dim
+        self._r_idx = self._a_idx + 1
+        self._s_idx = self._r_idx + 1
+
+    def add_sample(self, t, s, a, r, s_prime, done):
+        """Adds a single sample to the buffer. Returns the updated number of samples"""
+        self._buffer[self._next, 0] = t
+        self._buffer[self._next, 1:self._a_idx] = s
+        self._buffer[self._next, self._a_idx] = a
+        self._buffer[self._next, self._r_idx] = r
+        self._buffer[self._next, self._s_idx:-1] = s_prime
+        self._buffer[self._next, -1] = 1 if done else 0
+
+        self._next = self._next + 1 if self._next < self._capacity - 1 else 0
+        self.n_samples = min(self.n_samples + 1, self._capacity)
+        return self.n_samples
+
+    def add_all(self, dataset):
+        """Adds all samples in dataset to the buffer. Returns the updated number of samples"""
+        # TODO this function can be made more efficient. Anyway, it should be used only for initialization
+        for i in range(dataset.shape[0]):
+            self.add_sample(dataset[i, 0], dataset[i, 1:self._a_idx], dataset[i, self._a_idx], dataset[i, self._r_idx],
+                            dataset[i, self._s_idx:-1], dataset[i, -1])
+        return self.n_samples
+
+    def sample_batch(self, batch_size):
+        """Samples a minibatch from the replay buffer"""
+        idx = np.random.randint(self.n_samples, size=batch_size)
+        return self._buffer[idx, :]

### 2018-04-28 features/identity.py

@@ -1,0 +1,31 @@
+import numpy as np
+
+
+class Identity:
+    """Identity features"""
+
+    def __init__(self, K, state_dim, n_actions):
+        self._K = K
+        self._state_dim = state_dim
+        self._n_actions = n_actions
+        self._idx = [np.arange(0,K, dtype=np.int32) * n_actions + a for a in range(self._n_actions)]
+
+    def _get_mask(self, a):
+        mask = np.zeros((a.shape[0], int(self._K * 4)))
+        for i in range(self._n_actions):
+            mask[np.ix_(a == i, self._idx[i])] = 1
+        return mask
+
+    def _compute(self, point):
+        mask = self._get_mask(point[:, -1])
+        return point[:, :-1] * mask
+
+    def __call__(self, sa):
+        """Computes the features of the given array sa N x (state_dim * n_actions + 1)"""
+        if sa.ndim == 2:
+            return self._compute(sa)
+        elif sa.ndim == 1:
+            return self._compute(sa[np.newaxis])
+
+    def number_of_features(self):
+        return int(self._K * self._n_actions)

### 2018-04-28 backup/run_nt_maze.py
Added function to compute basis for states only + backed-up scripts

@@ -2,10 +2,8 @@ import sys
 sys.path.append("../")
 
 import numpy as np
-from envs.walled_gridworld import WalledGridworld
-from envs.marcellos_gridworld import MarcellosGridworld
-from features.agrbf import build_features_gw
-from approximators.linear import LinearQFunction
+from envs.emaze import Maze
+from approximators.mlp import MLPQFunction
 from operators.mellow import MellowBellmanOperator
 from policies import EpsilonGreedy, ScheduledEpsilonGreedy
 import utils
@@ -21,16 +19,22 @@ def run(mdp, seed=None):
         np.random.seed(seed)
 
     # Build the features
-    features = build_features_gw(gw_size, n_basis, n_actions, state_dim, action_dim)
+    # features = build_features_maze(gw_size, n_basis, n_actions, state_dim, action_dim)
+
     # Create BellmanOperator
     operator = MellowBellmanOperator(kappa, tau, xi, gamma, state_dim, action_dim)
+
     # Create Q Function
-    Q = LinearQFunction(features, np.arange(n_actions), state_dim, action_dim)
+    layers = [l1]
+    if l2 > 0:
+        layers.append(l2)
+    Q = MLPQFunction(state_dim, n_actions, layers=layers)
+
     # Initialize policies
     schedule = np.linspace(eps_start,eps_end,exploration_fraction*max_iter)
-    pi = ScheduledEpsilonGreedy(Q, Q.actions, schedule)
-    pi_u = EpsilonGreedy(Q, Q.actions, epsilon=1)
-    pi_g = EpsilonGreedy(Q, Q.actions, epsilon=0)
+    pi = ScheduledEpsilonGreedy(Q, np.arange(n_actions), schedule)
+    pi_u = EpsilonGreedy(Q, np.arange(n_actions), epsilon=1)
+    pi_g = EpsilonGreedy(Q, np.arange(n_actions), epsilon=0)
 
     # Add random episodes if needed
     dataset = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes) if random_episodes > 0 else None
@@ -66,14 +70,22 @@ def run(mdp, seed=None):
         # Step
         s_prime, r, done, _ = mdp.step(a)
         # Build the new sample and add it to the dataset
-        dataset = utils.add_sample(dataset, buffer_size, h, s, a, r, s_prime, done)
[…]

### 2018-04-28 backup/run_nt_nn.py

@@ -2,10 +2,8 @@ import sys
 sys.path.append("../")
 
 import numpy as np
-from envs.walled_gridworld import WalledGridworld
-from envs.marcellos_gridworld import MarcellosGridworld
-from features.agrbf import build_features_gw
-from approximators.linear import LinearQFunction
+from envs.cartpole import CartPoleEnv
+from approximators.mlp import MLPQFunction
 from operators.mellow import MellowBellmanOperator
 from policies import EpsilonGreedy, ScheduledEpsilonGreedy
 import utils
@@ -14,23 +12,23 @@ from joblib import Parallel, delayed
 import datetime
 import time
 
-
 def run(mdp, seed=None):
 
     if seed is not None:
         np.random.seed(seed)
 
-    # Build the features
-    features = build_features_gw(gw_size, n_basis, n_actions, state_dim, action_dim)
     # Create BellmanOperator
     operator = MellowBellmanOperator(kappa, tau, xi, gamma, state_dim, action_dim)
     # Create Q Function
-    Q = LinearQFunction(features, np.arange(n_actions), state_dim, action_dim)
+    layers = [l1]
+    if l2 > 0:
+        layers.append(l2)
+    Q = MLPQFunction(state_dim, n_actions, layers=layers)
     # Initialize policies
     schedule = np.linspace(eps_start,eps_end,exploration_fraction*max_iter)
-    pi = ScheduledEpsilonGreedy(Q, Q.actions, schedule)
-    pi_u = EpsilonGreedy(Q, Q.actions, epsilon=1)
-    pi_g = EpsilonGreedy(Q, Q.actions, epsilon=0)
+    pi = ScheduledEpsilonGreedy(Q, np.arange(n_actions), schedule)
+    pi_u = EpsilonGreedy(Q, np.arange(n_actions), epsilon=1)
+    pi_g = EpsilonGreedy(Q, np.arange(n_actions), epsilon=0)
 
     # Add random episodes if needed
     dataset = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes) if random_episodes > 0 else None
@@ -66,7 +64,7 @@ def run(mdp, seed=None):
         # Step
         s_prime, r, done, _ = mdp.step(a)
         # Build the new sample and add it to the dataset
-        dataset = utils.add_sample(dataset, buffer_size, h, s, a, r, s_prime, done)
[…]

### 2018-04-28 backup/run_vt_mixtures.py

@@ -1,0 +1,505 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.walled_gridworld import WalledGridworld
+from envs.marcellos_gridworld import MarcellosGridworld
+from features.agrbf import build_features_gw
+from approximators.linear import LinearQFunction
+from operators.mellow import MellowBellmanOperator
+from policies import EpsilonGreedy
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+import time
+
+prior_eigen = None
+cholesky_mask = None;
+
+def unpack(params):
+    """Unpacks a parameter vector into c, mu, L"""
+    c = params[:C]
+    mus = params[C:C + C * K]
+    mu = mus.reshape(C, K)
+    Ls = params[C + C * K:]
+    L = Ls.reshape(C, K, K)
+    return c, mu, L
+
+
+def pack(c, mu, L):
+    """Packs c and mu and L into a parameter vector"""
+    params = np.concatenate((c, mu.flatten(), L.flatten()), axis=0)
+    return params
+
+
+def clip(params):
+    """Makes sure the Cholesky factor L is well-defined"""
+    global cholesky_mask
+    c, mu, L = unpack(params)
+    cholesky_mask = np.eye(K, dtype=bool) if cholesky_mask is None else cholesky_mask
+    for i in range(C):
+        mask = np.logical_and(L[i, :, :] < cholesky_clip, cholesky_mask)
+        L[i, :, :][mask] = cholesky_clip
+        L[i, :, :][np.triu_indices(K, 1)] = 0
+    return pack(c, mu, L)
+
+
+def sample_posterior(params):
+    """Samples a Q function from the posterior distribution"""
+    c, mu, L = unpack(params)
+    cluster = np.random.choice(np.arange(C), p=c)
+    return np.dot(L[cluster, : , :], np.random.randn(K,)) + mu[cluster, :]
+
+
+def normal_KL(c, mu, Sigma, c_bar, mu_bar, Sigma_bar, precision=None):
+    """ Computes the KL between normals for two GMMs """
+
+    global prior_eigen
+
[…]

### 2018-04-28 backup/run_vt_nn.py

@@ -2,10 +2,8 @@ import sys
 sys.path.append("../")
 
 import numpy as np
-from envs.walled_gridworld import WalledGridworld
-from envs.marcellos_gridworld import MarcellosGridworld
-from features.agrbf import build_features_gw
-from approximators.linear import LinearQFunction
+from envs.cartpole import CartPoleEnv
+from approximators.mlp import MLPQFunction
 from operators.mellow import MellowBellmanOperator
 from policies import EpsilonGreedy
 import utils
@@ -13,6 +11,7 @@ import argparse
 from joblib import Parallel, delayed
 import datetime
 import time
+
 
 def unpack(params):
     """Unpacks a parameter vector into mu and L"""
@@ -77,15 +76,19 @@ def run(mdp, seed=None):
     if seed is not None:
         np.random.seed(seed)
 
-    # Build the features
-    features = build_features_gw(gw_size, n_basis, n_actions, state_dim, action_dim)
     # Create BellmanOperator
     operator = MellowBellmanOperator(kappa, tau, xi, gamma, state_dim, action_dim)
     # Create Q Function
-    Q = LinearQFunction(features, np.arange(n_actions), state_dim, action_dim)
+    layers = [l1]
+    if l2 > 0:
+        layers.append(l2)
+    Q = MLPQFunction(state_dim, n_actions, layers=layers)
+    # Set number of weights
+    global K
+    K = Q._nn.num_weights
     # Initialize policies
-    pi_u = EpsilonGreedy(Q, Q.actions, epsilon=1)
-    pi_g = EpsilonGreedy(Q, Q.actions, epsilon=0)
+    pi_u = EpsilonGreedy(Q, np.arange(n_actions), epsilon=1)
+    pi_g = EpsilonGreedy(Q, np.arange(n_actions), epsilon=0)
 
     # Add random episodes if needed
     dataset = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes) if random_episodes > 0 else None
@@ -138,11 +141,11 @@ def run(mdp, seed=None):
         # If we do not use time coherent exploration, resample parameters
         Q._w = sample_posterior(params) if not time_coherent else Q._w
         # Take greedy action wrt current Q-function
-        a = np.array([np.argmax(Q.value_actions(s))])
+        a = np.argmax(Q.value_actions(s))
         # Step
[…]

### 2018-04-28 features/agrbf.py

@@ -83,6 +83,24 @@ def build_features_gw(gw_size, n_basis, n_actions, state_dim, action_dim):
 
     return AGaussianRBF(mean, covar, K=K, dims=state_dim + action_dim)
 
+
+def build_features_gw_state(gw_size, n_basis, state_dim):
+    """Create ARBF for gridworld as functions of the state only"""
+    # Number of features
+    K = n_basis ** 2
+    # Build the features
+    x = np.linspace(0, gw_size, n_basis)
+    y = np.linspace(0, gw_size, n_basis)
+    mean_x, mean_y = np.meshgrid(x, y)
+    mean = np.hstack((mean_x.reshape(K, 1), mean_y.reshape(K, 1)))
+
+    state_var = (gw_size / (n_basis - 1) / 3) ** 2
+    covar = np.eye(state_dim) * state_var
+    covar = np.tile(covar, (K, 1))
+
+    return AGaussianRBF(mean, covar, K=K, dims=state_dim)
+
+
 if __name__ == '__main__':
     mean = np.array([[1, 2], [3, 4]])
     print(mean)

### 2018-04-28 algorithms/LinearFQI.py
Removed old files

@@ -1,53 +1,0 @@
-import numpy as np
-import utils
-from VariationalTransfer import BellmanOperator as bellmanop
-from algorithms import e_greedy_policy as policy, regularized_lsvi as lsvi
-
-"""
-Implementation of linear FQI procedure with a unique regressor for Q function.
-"""
-def linearFQI(mdp, Q, epsilon=0, n_iter=1, batch_size=1, render=False, verbose=False, n_fit=20, bellman_operator=None, r_seed=None):
-
-    if r_seed is not None:
-        np.random.seed(r_seed)
-
-    pol = policy.eGreedyPolicy(Q, Q.actions, epsilon)
-    pol_g = policy.eGreedyPolicy(Q, Q.actions, 0)
-    r = list()
-    rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
-    r.append(rew)
-    if verbose:
-        utils.plot_Q(Q, size=tuple(mdp.size))
-
-    samples = utils.generate_episodes(mdp, pol, batch_size, render=False)
-    feat = Q.compute_features(samples[:, 1:])
-
-    if bellman_operator is None:
-        bellman = bellmanop.BellmanOperator(Q)
-    else:
-        bellman_operator.set_Q(Q)
-        bellman = bellman_operator
-
-    for i in range(n_iter):
-        new_samples = utils.generate_episodes(mdp, pol, batch_size, render=False)
-        samples = np.vstack((samples, new_samples))
-        feat = np.vstack((feat, Q.compute_features(new_samples[:, 1:])))
-
-        for k in range(n_fit):
-            targets = bellman(samples[:, 1:])
-            w = lsvi.RegularizedLSVI.solve(feat, targets, prior=False)
-            Q.update_weights(w)
-
-        if render:
-            mdp._render(close=True)
-
-        rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
-        r.append(rew)
-        if verbose:
-            print("===============================================")
-            print("Iteration " + str(i))
-            print("Reward: " + str(rew))
-            print("===============================================")
-            utils.plot_Q(Q, size=tuple(mdp.size))
-
-    return r, Q

### 2018-04-28 algorithms/e_greedy_policy.py

@@ -1,18 +1,0 @@
-import numpy as np
-
-class eGreedyPolicy:
-
-    def __init__(self, Q, actions, epsilon=0):
-        self._q = Q
-        self._e = epsilon
-        self._actions = actions
-
-    def sample_action(self, s):
-        q_a = self._q.compute_all_actions(s)
-        max_a = np.argmax(q_a)
-
-        t = np.random.rand(1)
-        if t < 1-self._e:
-            return self._actions[max_a]
-        else:
-            return self._actions[np.random.randint(0, len(self._actions))]

### 2018-04-28 algorithms/linear_q_function.py

@@ -1,92 +1,0 @@
-import numpy as np
-import features.grbf as rbf
-import algorithms.regularized_lsvi as lsvi
-import utils
-
-class LinearQFunction:
-
-    def __init__(self, actions, features, params=None, state_dim=1, action_dim=1, gamma=0.99):
-
-        """
-        :param actions: tuple with the possible actions available
-        :param features: feature object
-        :param gamma: discount factor
-        :param params: initial parameters (np.ndarray n_features x n_actions or n_features x 1)
-        :param state_dim: dimension of the state vector
-        :param regressor_per_action: boolean flag to have or not a regressor per action available
-
-        """
-        if params is not None:
-            assert params.shape == (features.number_of_features(), len(actions))
-            self._w = params
-        else:
-            self._w = np.zeros((features.number_of_features(), len(actions)))
-
-        self.actions = actions
-        self._features = features
-        self._gamma = gamma
-        self._state_dim = state_dim
-        self._action_dim = action_dim
-
-
-    def compute_bellman_target(self, samples):
-        """
-        Computes target as a sampled application of the Bellman optimal operator
-        :param samples: samples of the form (s,a,r,s',terminating), one per row (Nx5)
-        :return:
-        """
-        s_prime = self._state_dim + self._action_dim + 1
-        r = self._state_dim + self._action_dim
-        a = self._state_dim
-        fts = self._features(samples[:, s_prime: s_prime + self._state_dim])
-        qs = np.max(np.dot(fts, self._w), axis=1)
-        t = samples[:, r] + self._gamma * qs * (1-samples[:, -1])
-        return t
-
-
-    def update_weights(self, w, action=None):
-        """
-        Update the weights of the regressors
-        :param w: matrix of weights (one regressor per column)
-        :param action: specific action to which update the regressor's parameters
-        """
-        if action is None:
-            assert w.shape == self._w.shape
-            self._w = w
-        else:
-            assert w.shape == self._w[:, action].shape
-            self._w[:, action] = w
-
-    def compute_all_actions(self, state):
-         return np.dot(self._features(state), self._w.T)
-
-    def compute_features(self, samples):
-        return self._features(samples[:, 0: self._state_dim])
-
-    def __call__(self, state, action):
[…]

### 2018-04-28 algorithms/nn_q_function.py

@@ -1,153 +1,0 @@
-import numpy as np
-from keras.models import Sequential
-from keras.layers.core import Dense,Activation
-from keras.optimizers import Adam
-import tensorflow as tf
-
-
-def get_regularizer(mu, sigma_inv, reg_lambda):
-    if mu is None or sigma_inv is None:
-        return None
-
-    assert mu.shape[0] == sigma_inv.shape[0] and mu.shape[0] == sigma_inv.shape[1]
-
-    mu_tf = tf.constant(mu, dtype=tf.float32)
-    sigma_inv_tf = tf.constant(sigma_inv, dtype=tf.float32)
-
-    def reg(weight_matrix):
-        diff = tf.subtract(tf.reshape(weight_matrix, [-1]), mu_tf)
-        return reg_lambda * tf.matmul(tf.matmul(tf.expand_dims(diff,0), sigma_inv_tf), tf.expand_dims(diff,-1))
-    return reg
-
-
-class NNQ:
-
-    def __init__(self, actions, state_dim, gamma=0.99, layers=(32,32), activation="relu", prior_mean=None, prior_cov=None, reg_lambda = 1.0):
-        """
-        :param actions: list of discrete actions
-        :param state_dim: the state dimension (scalar > 0)
-        :param gamma: discount factor
-        :param layers: tuple containing the number of neurons in each layer
-        :param activation: activation functions
-        :param prior_mean: mean of the Gaussian prior
-        :param prior_cov: covariance matrix of the Gaussian prior
-        """
-        self.actions = actions
-        self.n_actions = len(actions)
-        # Binarize the actions
-        tmp = np.eye(self.n_actions)
-        self.bin_actions = [tmp[i,:] for i in range(self.n_actions)]
-        self._state_dim = state_dim
-        self._gamma = gamma
-
-        # Compute the size of each weight vector
-        sizes = []
-        sizes.append((state_dim + self.n_actions) * layers[0])
-        sizes.append(layers[0])
-        for l in range(len(layers) - 1):
-            sizes.append(layers[l] * layers[l + 1])
-            sizes.append(layers[l + 1])
-        sizes.append(layers[-1])
-        sizes.append(1)
-
-        if prior_mean is not None and prior_cov is not None:
-            # Split the prior for different layers
-            means = np.split(prior_mean, np.cumsum(sizes)[:-1])
-            prior_cov = np.diag(prior_cov)
[…]

### 2018-04-28 algorithms/regularized_lsvi.py

@@ -1,27 +1,0 @@
-import numpy as np
-
-class RegularizedLSVI:
-    """
-    Implementation of a regularized (by a normal prior over the parameters of Q) value iteration method.
-    """
-    @staticmethod
-    def solve(features, target, mean=None, covariance=None, prior=True, lamb=0.1):
-        """
-        :param features: matrix of feature vectors
-        :param mean: np.ndarray mean of the prior gaussian over the parameters
-        :param covariance: np.ndarray covariance matrix of the prior gaussian over parameters
-        :param target: np.ndarray with the target values for the fitting
-        :return:
-        """
-        prec = 1
-
-        if prior:
-            assert features.shape[1] == mean.size
-            assert covariance.shape == (mean.size, mean.size)
-            assert target.shape[0] == features.shape[0]
-            prec = np.linalg.inv(covariance)
-
-        X = np.dot(features.T, features)
-        Y = (np.dot(features.T, target) + np.dot(prec, mean)) if prior else np.dot(features.T, target)
-        w = np.dot(np.linalg.inv(X + prec) if prior else np.linalg.inv(X + lamb*np.eye(X.shape[0])), Y)
-        return w

### 2018-04-28 algorithms/simple_rl.py

@@ -1,100 +1,0 @@
-import numpy as np
-import envs.walled_gridworld as env
-import utils
-import algorithms.e_greedy_policy as policy
-import algorithms.linear_q_function as Q
-import algorithms.regularized_lsvi as lsvi
-import features.grbf as grbf
-import matplotlib.pyplot as plt
-from scripts.run_nfqi import plot_Q
-
-
-"""
-Implementation of a simple RL algorithm based on an e-greedy policy and a linearly parameterized Q function
-
-"""
-def simple_RL(mdp, Q, epsilon=0, K=1, batch_size=1, render=False, verbose=False, n_fit=20, prior_parameters=None):
-    pol = policy.eGreedyPolicy(Q, Q.actions, epsilon)
-    pol_g = policy.eGreedyPolicy(Q, Q.actions, 0)
-    r = list()
-    n_act = len(Q.actions)
-
-    rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
-    r.append(rew)
-    plot_Q(Q, size=tuple(mdp.size))
-
-    samples = _generate_episodes(mdp, pol, n_act, batch_size, render=False)
-    feat = [Q.compute_features(samples[a][:, 1:]) for a in range(n_act)]
-
-    for i in range(K):
-        new_samples = _generate_episodes(mdp, pol, n_act, batch_size, render=False)
-        samples = _stack(samples, new_samples)
-        feat = _stack(feat, [Q.compute_features(new_samples[a][:, 1:]) for a in range(n_act)])
-
-        for k in range(n_fit):
-            targets = [Q.compute_bellman_target(samples[a][:, 1:]) for a in range(n_act)]
-            for a in range(n_act):
-                if feat[a].shape[0] > 0:
-                    print(a)
-                    print(np.shape(feat[a]))
-                    if prior_parameters is None:
-                         w = lsvi.RegularizedLSVI.solve(feat[a], targets[a], prior=False)
-                    else:
-                        w = lsvi.RegularizedLSVI.solve(feat[a], targets[a], prior_parameters[0][a], prior_parameters[1][a], prior=True)
-                    Q.update_weights(w, a)
-
-        if render:
-            mdp._render(close=True)
-
-        plot_Q(Q, size=tuple(mdp.size))
[…]

### 2018-04-28 algorithms/transfer_normal_prior.py

@@ -1,136 +1,0 @@
-import numpy as np
-import algorithms.linear_q_function as Q
-import features.grbf as grbf
-import algorithms.simple_rl as rl
-import utils
-import matplotlib.pyplot as plt
-import os.path
-import envs.walled_gridworld as wgw
-
-def transfer_rl(mdp, Q, prior_parameters, epsilon=0, K=1, batch_size=1, verbose=False, render=False, n_fit=20):
-
-    # Sample weights to initialize Q
-    w = list()
-    for a in Q.actions:
-        # w.append(np.random.multivariate_normal(prior_parameters[0][a], prior_parameters[1][a]))
-        w.append(prior_parameters[0][a])
-    print(prior_parameters[0][0])
-    print(prior_parameters[1][0])
-    Q.update_weights(w)
-
-    # Run RL
-    return rl.simple_RL(mdp, Q, epsilon, K, batch_size, render, verbose, n_fit, prior_parameters)
-
-
-"""
-Solves the Walled Gridworld for 5 different door positions and uses the induced prior over Q functions 
-to solve a random tasks from the sources.
-"""
-if __name__ == '__main__':
-
-    #Initial parameters
-    grid_size = 5
-    k = (grid_size+1)**2
-    worlds = list()
-    q_functions = list()
-    n_acts = 4
-
-    #Load saved
-    prior_loaded = False
-    if os.path.isfile("prior_information_" + str(grid_size) + ".pkl"):
-        prior_means, prior_variances = utils.load_object("prior_information_" + str(grid_size))
-        prior_loaded = True
-
-
-    # Create features for the gridworld
-    mean = np.array([[x, y] for x in range(grid_size+1) for y in range(grid_size+1)])
-    variance = (np.ones(k)/2)**2
-    feat = grbf.GaussianRBF(mean, variance, K=k)
-
-
-    sources_loaded = False
-    if os.path.isfile("source_tasks_5_walled_grid.pkl"):
-        worlds, q_functions = utils.load_object("source_tasks_5_walled_grid")
-        sources_loaded = True
-
-
-
-    if not sources_loaded:
-        # Create Tasks (Environments)
-        for pos in range(1, grid_size+1):
-            w = wgw.WalledGridworld(np.asarray((grid_size, grid_size)), door_x=pos)
-            worlds.append(w)
[…]

### 2018-04-28 walled_gridworld/agents/dp_solver.py

@@ -1,24 +1,0 @@
-import numpy as np
-
-"""
-Apply iteratively the Optimal Bellman Operator to solve the Environment.
-"""
-def qvalue_iteration(env, gamma=0.99, theta=0.01):
-    q = np.zeros((env.nS, env.nA))
-    change = theta+1
-    while (abs(change) > theta):
-        deltas = []
-        for s in range(0, env.nS):
-            for a in range(0, env.nA):
-                delta = -q[s, a] + (env.P[s][a][0][2] + gamma*expected_max_q_value(s, a, q, env))
-                q[s, a] = q[s, a] + delta
-                deltas.append(delta)
-        change = max(deltas)
-    return q
-
-def expected_max_q_value(s,a,q,env):
-    Qnext = 0
-    qmax = np.max(q,1)
-    for prob, snext, rew, terminal in env.P[s][a]:
-        Qnext += prob * qmax[snext]
-    return Qnext

### 2018-04-28 walled_gridworld/agents/sourcetasks_solver.py

@@ -1,58 +1,0 @@
-from walled_gridworld.envs import walled_gridworld_env as wgw
-import dp_solver as dp
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import axes3d, Axes3D
-
-tasks = []
-q_stars = []
-
-N = 5
-
-for i in range(N):
-    tasks.append(wgw.WalledGridworld(N, i))
-
-for t in tasks:
-    q_stars.append(dp.qvalue_iteration(t))
-
-
-qall = np.asanyarray(q_stars)   # Optimal Q functions in array form
-qavg = np.average(qall, 0)      # Average optimal Q function
-qmin = np.min(qall, 0)
-qmax = np.max(qall, 0)
-
-
-start = (0, 0)
-close_goal = (N-2, N-2)
-wall1 = (N//2, N//2)
-wall2 = (N//2 + 1, N//2)
-wall3 = (N//2 - 1, N//2)
-
-actions = ("UP", "RIGHT", "DOWN", "LEFT")
-
-for a in range(4):
-    fig, axs = plt.subplots(N, N)
-    fig.suptitle("Action: " + actions[a])
-    for j in range(N):
-        for i in range(N):
-            axs[i, j].hist(qall[:, np.ravel_multi_index((i, j), (N, N)), a], bins='doane')
-            axs[i, j].set_title("Position " + str((i, j)))
-
-
-
-# State Space
-
-X = np.arange(N)
-Y = np.arange(N)
-X, Y = np.meshgrid(X, Y)
-Vavg = np.average(np.max(qall, 2), 0)
-Vstd = np.std(np.max(qall, 2), 0)
-VavgGrid = Vavg.reshape((N, N))
-
-f = plt.figure()
-ax = f.gca(projection='3d')
-ax.plot_surface(X, Y, VavgGrid)
-ax.plot_surface(X, Y, (Vavg + Vstd).reshape((N, N)))
-ax.plot_surface(X, Y, (Vavg - Vstd).reshape((N, N)))
-ax.set_title("Value Function")
-plt.show()

### 2018-04-28 walled_gridworld/envs/walled_gridworld_env.py

@@ -1,92 +1,0 @@
-import os, subprocess, time, signal
-import gym
-from gym import error, spaces
-from gym import utils
-from gym.utils import seeding
-from gym.envs.toy_text import discrete
-import numpy as np
-
-UP = 0
-RIGHT = 1
-DOWN = 2
-LEFT = 3
-
-NORMAL_R = -1
-HIT_WALL_R = -10
-GOAL_R = 100
-
-
-class WalledGridworld(discrete.DiscreteEnv):
-
-    def __init__(self, n=5, passage=-1):
-        self.shape = (n, n)
-        self.start_state_index = np.ravel_multi_index((0, 0), self.shape)
-
-        nS = np.prod(self.shape)
-        nA = 4
-
-        # Wall
-        self._pass = np.randint(0, n) if passage == -1 else passage
-        self._wall = np.zeros(self.shape, dtype=np.bool)
-        self._wall[n//2, :] = True
-        self._wall[n//2, self._pass] = False;
-
-        # Calculate transition probabilities and rewards
-        P = {}
-        for s in range(nS):
-            position = np.unravel_index(s, self.shape)
-            P[s] = {a: [] for a in range(nA)}
-            P[s][UP] = self._calculate_transition_prob(position, [1, 0])
-            P[s][RIGHT] = self._calculate_transition_prob(position, [0, 1])
-            P[s][DOWN] = self._calculate_transition_prob(position, [-1, 0])
-            P[s][LEFT] = self._calculate_transition_prob(position, [0, -1])
-
-        # Calculate initial state distribution
-        isd = np.zeros(nS)
-        isd[self.start_state_index] = 1.0
-
-        super(WalledGridworld, self).__init__(nS, nA, P, isd)
-
-    def _limit_coordinates(self, coord):
-
-        coord[0] = min(coord[0], self.shape[0] - 1)
-        coord[0] = max(coord[0], 0)
-        coord[1] = min(coord[1], self.shape[1] - 1)
-        coord[1] = max(coord[1], 0)
-        return coord
-
-
-    def _calculate_transition_prob(self, current, delta):
-
-        new_position = np.array(current) + np.array(delta)
-        new_position = self._limit_coordinates(new_position).astype(int)
-        new_state = np.ravel_multi_index(tuple(new_position), self.shape)
-        if self._wall[tuple(new_position)]:
-            return [(1.0, np.ravel_multi_index(tuple(current), self.shape), HIT_WALL_R, False)]
[…]

### 2018-04-28 scripts/mm_train_sources.py
Removed old scripts

@@ -1,246 +1,0 @@
-import numpy as np
-from features.agrbf import AGaussianRBF
-from envs.walled_gridworld import WalledGridworld
-from VariationalTransfer.LinearQRegressor import LinearQRegressor
-from algorithms.e_greedy_policy import eGreedyPolicy
-import utils
-import argparse
-from joblib import Parallel, delayed
-
-import sys
-sys.path.append("../")
-
-# Global parameters
-kappa = 100.
-gamma = 0.99
-xi = 1.0
-tau = 0.0
-batch_size = 1
-gradient_batch = 1000
-epsilon = 1
-max_iter = 300
-n_fit = 1
-gw_size = 5
-n_actions = 4
-state_dim = 2
-action_dim = 1
-n_basis = 6
-render = False
-verbose = True
-n_jobs = 1
-n_tasks = 1
-
-# Adam params
-m_t = 0
-v_t = 0
-t = 0
-eps = 1e-8
-alpha = 0.01
-beta_1 = 0.9
-beta_2 = 0.999
-
-
-def gradient(Q, data):
-
-    r = Q.get_statedim() + Q.get_actiondim()
-    s_prime = r + 1
-    br = bellman_residual(Q, data)
-    assert br.shape == (data.shape[0],)
-    mm_gradient = gradient_mm(Q, data[:, s_prime:s_prime+Q.get_statedim()], data[:, -1])
-    assert mm_gradient.shape == (data.shape[0], K)
-    q_gradient = Q.compute_gradient(data[:, 0:r])
-    assert q_gradient.shape == (data.shape[0], K)
-    b_grad = xi * gamma * mm_gradient - q_gradient
-    assert b_grad.shape == (data.shape[0], K)
-    bellman_grad = 2 * np.sum(br[:, np.newaxis] * b_grad * softmax(br ** 2)[:, np.newaxis], axis=0)
-    assert bellman_grad.shape == (K,)
-
-    return bellman_grad
-
-
-def gradient_mm(Q, states, done):
-
-    q_values = Q.compute_all_actions(states, done)
-    assert q_values.shape == (states.shape[0],n_actions)
-    q_gradient = Q.compute_gradient_all_actions(states) * (1 - done)[:, np.newaxis, np.newaxis]
-    assert q_gradient.shape == (states.shape[0],n_actions,K)
-    qs = mm_exp(q_values, np.max(q_values, axis=1))
-    assert qs.shape == (states.shape[0],n_actions)
-    qs_sum = np.sum(qs, axis=1)
[…]

### 2018-04-28 scripts/run_gaussian_var_transfer.py

@@ -1,112 +1,0 @@
-import numpy as np
-import envs.walled_gridworld as wgw
-import envs.marcellos_gridworld as mgw
-import VariationalTransfer.LinearQRegressor as linq
-import VariationalTransfer.BellmanOperator as bellmanop
-import VariationalTransfer.BellmanOperator as bellman
-import VariationalTransfer.VarTransfer as vartrans
-import VariationalTransfer.Distributions as dist
-import features.agrbf as rbf
-import utils
-import algorithms.e_greedy_policy as policy
-import algorithms.regularized_lsvi as lsvi
-
-
-"""
-    FQI with linear regressor for Q(s,a) 
-"""
-def linearFQI(mdp, Q, epsilon=0, n_iter=1, batch_size=1, render=False, verbose=False, n_fit=20, bellman_operator=None, r_seed=None):
-    pol = policy.eGreedyPolicy(Q, Q.actions, epsilon)
-    pol_g = policy.eGreedyPolicy(Q, Q.actions, 0)
-    r = list()
-    n_act = len(Q.actions)
-
-    rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
-    r.append(rew)
-    # utils.plot_Q(Q, size=tuple(mdp.size))
-
-    samples = utils.generate_episodes(mdp, pol, batch_size, render=False)
-    feat = Q.compute_features(samples[:, 1:])
-
-    if bellman_operator is None:
-        bellman = bellmanop.BellmanOperator(Q)
-    else:
-        bellman_operator.set_Q(Q)
-        bellman = bellman_operator
-
-    if r_seed is not None:
-        np.random.seed(r_seed)
-
-    for i in range(n_iter):
-        new_samples = utils.generate_episodes(mdp, pol, batch_size, render=False)
-        samples = np.vstack((samples, new_samples))
-        feat = np.vstack((feat, Q.compute_features(new_samples[:, 1:])))
-
-        for k in range(n_fit):
-            targets = bellman(samples[:, 1:])
-            w = lsvi.RegularizedLSVI.solve(feat, targets, prior=False)
-            Q.update_weights(w)
-
-        if render:
-            mdp._render(close=True)
-
-        rew, _, _, _ = utils.evaluate_policy(mdp, pol_g, n_episodes=5, initial_states=np.array([0., 0.]), render=render)
-        r.append(rew)
[…]

### 2018-04-28 scripts/run_mgw.py

@@ -1,98 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from algorithms.simple_rl import simple_RL
-import features.grbf as grbf
-import envs.marcellos_gridworld as env
-import algorithms.linear_q_function as Q
-import algorithms.transfer_normal_prior as tr
-import utils
-
-
-"""
-Test transfer with linear regressors and RBF in Marcello's Gridworld
-"""
-if __name__ == '__main__':
-    n = 5
-    acts = 4
-    k = (n + 1) * (n + 1)
-    door_1 = n/2
-    episodes = 50
-    saved_prior = True
-
-    # Create features for the gridworld
-    mean = np.array([[x, y] for x in range(n + 1) for y in range(n + 1)])
-    variance = (np.ones(k) / 2) ** 2
-    feat = grbf.GaussianRBF(mean, variance, K=k)
-
-    if not saved_prior:
-        # Create tasks
-        worlds = list()
-        q_functions = list()
-        for door_2 in range(1, n + 1):
-            w = env.MarcellosGridworld(np.asarray((n, n)), door_x=(door_1, door_2-0.5))
-            worlds.append(w)
-            q_functions.append(
-                Q.LinearQFunction(range(acts), feat, params=np.zeros(k), state_dim=w.state_dim, action_dim=w.action_dim))
-
-        # Solve the Tasks
-        rew = list()
-        for i in range(len(worlds)):
-            print("Solving World with port at " + str(i + 1))
-            r = simple_RL(worlds[i], q_functions[i], epsilon=0.2, K=episodes, batch_size=2, verbose=True, render=False)
-            rew.append(np.array(r))
-
-        rew = np.array(rew)
-        # Set induced prior parameters
-        prior_means = list()
-        prior_variances = list()
-        weights = [q._w for q in q_functions]
-        for a in range(acts):
-            m = sum([w[a] for w in weights]) / len(weights)
-            # covar = sum(map(lambda x: x.reshape(k,1) @ x.reshape(1,k), [w[a]-m for w in weights]))/len(weights)
-            covar = sum(map(lambda x: np.diag(x * x), [w[a] - m for w in weights])) / len(weights)
-            prior_means.append(m)
-            prior_variances.append(covar)
-
-        utils.save_object((prior_means, prior_variances), "prior_information_" + str(n) + "_first_fixed")
[…]

### 2018-04-28 scripts/run_mm.py

@@ -1,242 +1,0 @@
-import numpy as np
-from features.agrbf import AGaussianRBF
-from envs.walled_gridworld import WalledGridworld
-from VariationalTransfer.LinearQRegressor import LinearQRegressor
-from algorithms.e_greedy_policy import eGreedyPolicy
-import utils
-import argparse
-from joblib import Parallel, delayed
-
-# Global parameters
-kappa = 100.
-gamma = 0.99
-xi = 1.0
-tau = 0.0
-eta = 0.1
-batch_size = 1
-gradient_batch = 1000
-epsilon = 1
-max_iter = 300
-n_fit = 1
-gw_size = 5
-n_actions = 4
-state_dim = 2
-action_dim = 1
-n_basis = 6
-K = n_basis ** 2 * n_actions
-render = False
-verbose = True
-n_jobs = 1
-n_runs = 1
-
-# Adam params
-m_t = 0
-v_t = 0
-t = 0
-eps = 10e-8
-alpha = 0.01
-beta_1 = 0.9
-beta_2 = 0.999
-
-
-def gradient(Q, data):
-
-    r = Q.get_statedim() + Q.get_actiondim()
-    s_prime = r + 1
-    br = bellman_residual(Q, data)
-    assert br.shape == (data.shape[0],)
-    mm_gradient = gradient_mm(Q, data[:, s_prime:s_prime+Q.get_statedim()], data[:, -1])
-    assert mm_gradient.shape == (data.shape[0], K)
-    q_gradient = Q.compute_gradient(data[:, 0:r])
-    assert q_gradient.shape == (data.shape[0], K)
-    b_grad = xi * gamma * mm_gradient - q_gradient
-    assert b_grad.shape == (data.shape[0], K)
-    bellman_grad = 2 * np.sum(br[:, np.newaxis] * b_grad * softmax(br ** 2)[:, np.newaxis], axis=0)
-    assert bellman_grad.shape == (K,)
-
-    return bellman_grad
-
-
-def gradient_mm(Q, states, done):
-
-    q_values = Q.compute_all_actions(states, done)
-    assert q_values.shape == (states.shape[0],n_actions)
-    q_gradient = Q.compute_gradient_all_actions(states) * (1 - done)[:, np.newaxis, np.newaxis]
-    assert q_gradient.shape == (states.shape[0],n_actions,K)
-    qs = mm_exp(q_values, np.max(q_values, axis=1))
[…]

### 2018-04-28 scripts/run_nfqi.py

@@ -1,151 +1,0 @@
-import numpy as np
-import envs.walled_gridworld as env
-import utils
-import algorithms.e_greedy_policy as policy
-from algorithms.nn_q_function import NNQ
-import matplotlib.pyplot as plt
-
-
-def plot_Q(Q, size=(5,5)):
-
-    V = [[], [], [], []]
-    Vmax = []
-    X = np.arange(0.0, size[0]+.1, 0.1)
-    Y = np.arange(0.0, size[1]+.1, 0.1)
-    for x in X:
-        for y in Y:
-            vals = Q.compute_all_actions(np.array([y, x]))
-            Vmax.append(np.max(vals))
-            vals = vals.reshape(4,1)
-            V[0].append(vals[0])
-            V[1].append(vals[1])
-            V[2].append(vals[2])
-            V[3].append(vals[3])
-    for v in V:
-        v[-1][0] = 0.0
-    V = [np.flip(np.array(v).reshape(X.size, X.size), axis=0) for v in V]
-    fig, ax = plt.subplots(2, 2)
-    ax[0, 0].imshow(V[0], cmap="hot", interpolation="gaussian")
-    ax[0, 0].set_title("UP")
-    ax[0, 1].imshow(V[1], cmap="hot", interpolation="gaussian")
-    ax[0, 1].set_title("RIGHT")
-    ax[1, 0].imshow(V[2], cmap="hot", interpolation="gaussian")
-    ax[1, 0].set_title("DOWN")
-    ax[1, 1].imshow(V[3], cmap="hot", interpolation="gaussian")
-    ax[1, 1].set_title("LEFT")
-
-    plt.figure()
-    plt.title("Value Function")
-    plt.imshow(np.flip(np.array(Vmax).reshape(X.size, Y.size), axis=0), cmap="hot", interpolation="gaussian")
-
-    plt.show()
-
-
-def solve_task(mdp, Q, epsilon=0.2, n_iter=20, n_fit=1, batch_size=1, render=False, verbose=False):
-    pi_exp = policy.eGreedyPolicy(Q, Q.actions, epsilon)
-    pi_eval = policy.eGreedyPolicy(Q, Q.actions, 0)
-
-    rewards = []
-    rewards.append(utils.evaluate_policy(mdp, pi_eval, initial_states=[np.array([0., 0.]) for _ in range(5)], render=render)[0])
-    if verbose:
-        print("===============================================")
-        print("Zero-shot: {0}".format(rewards[-1]))
[…]

### 2018-04-28 scripts/run_nt2.py

@@ -1,0 +1,225 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.walled_gridworld import WalledGridworld
+from envs.marcellos_gridworld import MarcellosGridworld
+from features.agrbf import build_features_gw,build_features_gw2
+from features.identity import Identity
+from approximators.linear import LinearQFunction
+from operators.mellow import MellowBellmanOperator
+from policies import EpsilonGreedy, ScheduledEpsilonGreedy
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+import time
+from buffer import Buffer
+
+
+def run(mdp, seed=None):
+
+    if seed is not None:
+        np.random.seed(seed)
+
+    # Build the features
+    rbf_sa = build_features_gw(gw_size, n_basis, n_actions, state_dim, action_dim)
+    iden = Identity(K / n_actions, state_dim, n_actions)
+    rbf_s = build_features_gw2(gw_size, n_basis, state_dim)
+    # Create BellmanOperator
+    operator = MellowBellmanOperator(kappa, tau, xi, gamma, K, action_dim)
+    # Create Q Function
+    Q = LinearQFunction(iden, np.arange(n_actions), K, action_dim)
+    # Initialize policies
+    schedule = np.linspace(eps_start,eps_end,exploration_fraction*max_iter)
+    pi = ScheduledEpsilonGreedy(Q, Q.actions, schedule)
+    pi_u = EpsilonGreedy(Q, Q.actions, epsilon=1)
+    pi_g = EpsilonGreedy(Q, Q.actions, epsilon=0)
+
+    # Add random episodes if needed
+    dts = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes) if random_episodes > 0 else None
+    dtsf = None
+    if dts is not None:
+        t, s, a, r, s_prime, absorbing, sa = utils.split_data(dts, state_dim, action_dim)
+        old = rbf_sa(sa)
+        sf = np.repeat(rbf_s(s), n_actions, axis=1)
+        sfp = np.repeat(rbf_s(s_prime), n_actions, axis=1)
+        dtsf = np.concatenate((t[:,np.newaxis],sf,a,r[:,np.newaxis],sfp,absorbing[:,np.newaxis]), axis=1)
+        t, s, a, r, s_prime, absorbing, sa = utils.split_data(dtsf, K, action_dim)
+        new = iden(sa)
+        assert np.allclose(old,new)
+
[…]

### 2018-04-28 scripts/simple_curriculum_rl.py

@@ -1,58 +1,0 @@
-import numpy as np
-import envs.walled_gridworld as wgw
-import algorithms.linear_q_function as Q
-import features.grbf as grbf
-import algorithms.simple_rl as rl
-import utils
-import algorithms.transfer_normal_prior as transfer
-import algorithms.simple_rl as rl
-
-if __name__ == '__main__':
-
-    # Initial parameters
-    grid_size = 5
-    k = (grid_size + 1) ** 2
-    worlds = list()
-    q_functions = list()
-    n_acts = 4
-
-    # Create features for the gridworld
-    mean = np.array([[x, y] for x in range(grid_size + 1) for y in range(grid_size + 1)])
-    variance = (np.ones(k) / 2) ** 2
-    feat = grbf.GaussianRBF(mean, variance, K=k)
-
-    # # Create Tasks (Environments)
-    # for pos in range(1, grid_size + 1):
-    #     w = wgw.WalledGridworld(np.asarray((grid_size, grid_size)), door_x=pos)
-    #     worlds.append(w)
-    #     q_functions.append(Q.LinearQFunction(range(n_acts), feat, params=np.zeros(k), state_dim=w.state_dim, action_dim=w.action_dim))
-
-    worlds, _ = utils.load_object("source_tasks_5_walled_grid")
-
-
-    # Permute order of the tasks
-    # tasks = np.random.permutation(np.arange(0, len(worlds)))
-    tasks = range(len(worlds))
-    prior_mean = [np.zeros(k) for _ in range(n_acts)]
-    prior_variances = [1e200*np.eye(k) for _ in range(n_acts)]
-
-    # Run RL transferring knowledge from the past tasks
-    weights = list()
-    scores = list()
-    for t in tasks:
-        q = Q.LinearQFunction(range(n_acts), feat, params=np.zeros(k), state_dim=worlds[t].state_dim, action_dim=worlds[t].action_dim)
-        if len(weights) > 1:
-            r = transfer.transfer_rl(worlds[t], q, (prior_mean, prior_variances), epsilon=0.11, batch_size=10, K=10, verbose=True, render=True)
-        else:
-            r = rl.simple_RL(worlds[t], q, epsilon=0.2, K=10, batch_size=2, verbose=True, render=True)
-
-        weights.append(q._w)
-        scores.append(r)
-        # Update mean&variance
-        for a in range(n_acts):
-            m = sum([w[a] for w in weights])/len(weights)
[…]

### 2018-04-28 scripts/test_vi.py

@@ -1,61 +1,0 @@
-import numpy as np
-from features.agrbf import AGaussianRBF
-from envs.walled_gridworld import WalledGridworld
-from envs.marcellos_gridworld import MarcellosGridworld
-from VariationalTransfer.LinearQRegressor import  LinearQRegressor
-from VariationalTransfer.Distributions import AnisotropicNormalPosterior
-from VariationalTransfer.BellmanOperator import LinearQBellmanOperator
-from VariationalTransfer.VarTransfer import VarTransferGaussian
-import utils
-
-gw_size = 5
-n_actions = 4
-state_dim = 2
-action_dim = 1
-n_basis = 6
-K = n_basis ** 2 * n_actions
-
-x = np.linspace(0, gw_size, n_basis)
-y = np.linspace(0, gw_size, n_basis)
-a = np.linspace(0, n_actions - 1, n_actions)
-mean_x, mean_y, mean_a = np.meshgrid(x, y, a)
-mean = np.hstack((mean_x.reshape(K, 1), mean_y.reshape(K, 1), mean_a.reshape(K, 1)))
-assert mean.shape == (K,3)
-
-state_var = (gw_size / (n_basis - 1) / 3) ** 2
-action_var = 0.1 ** 2
-covar = np.eye(state_dim + action_dim)
-covar[0:state_dim, 0:state_dim] *= state_var
-covar[-1, -1] *= action_var
-assert covar.shape == (3,3)
-covar = np.tile(covar, (K, 1))
-assert covar.shape == (3*K,3)
-
-# features
-features = AGaussianRBF(mean, covar, K=K, dims=state_dim + action_dim)
-
-prior_mean = np.zeros(K)
-prior_variance = np.ones(K)*0.1
-
-prior_mean, prior_variance = utils.load_object("sources_gridworld_5")
-
-# Create Target task
-mdp = WalledGridworld(np.array([gw_size, gw_size]), door_x=0.5)
-q = LinearQRegressor(features, np.arange(n_actions), state_dim, action_dim)
-prior = AnisotropicNormalPosterior(prior_mean, prior_variance)
-x=prior.sample(nsamples=5)
-bellman = LinearQBellmanOperator(q, gamma=mdp.gamma)
-# bellman = LinearQMellowBellman(q, gamma=mdp.gamma)
-var = VarTransferGaussian(mdp, bellman, prior, learning_rate=1e-4, likelihood_weight=100)
-
-r = list()
-elbos = list()
[…]

### 2018-04-28 scripts/train_sources.py

@@ -1,144 +1,0 @@
-import numpy as np
-from features.agrbf import AGaussianRBF
-from envs.walled_gridworld import WalledGridworld
-from envs.marcellos_gridworld import MarcellosGridworld
-from VariationalTransfer.LinearQRegressor import LinearQRegressor
-from algorithms.LinearFQI import linearFQI
-import utils
-from joblib import Parallel, delayed
-import argparse
-
-def train_gridworld(filename, gw_size=5, n_actions=4, n_basis=6, n_sources=5, n_iter=50, epsilon=0.2, n_jobs=20, n_fit=20, verbose=False):
-    state_dim = 2
-    action_dim = 1
-    K = n_basis**2 * n_actions
-    x = np.linspace(0, gw_size, n_basis)
-    y = np.linspace(0, gw_size, n_basis)
-    a = np.linspace(0, n_actions - 1, n_actions)
-    mean_x, mean_y, mean_a = np.meshgrid(x, y, a)
-    mean = np.hstack((mean_x.reshape(K, 1), mean_y.reshape(K, 1), mean_a.reshape(K, 1)))
-    assert mean.shape == (K, 3)
-
-    state_var = (gw_size / (n_basis - 1) / 3) ** 2
-    action_var = 0.1 ** 2
-    covar = np.eye(state_dim + action_dim)
-    covar[0:state_dim, 0:state_dim] *= state_var
-    covar[-1, -1] *= action_var
-    assert covar.shape == (3, 3)
-    covar = np.tile(covar, (K, 1))
-    assert covar.shape == (3 * K, 3)
-
-    features = AGaussianRBF(mean, covar, K=K, dims=state_dim + action_dim)
-    worlds = list()
-    q_function = LinearQRegressor(features, np.arange(n_actions), state_dim, action_dim)
-    for i in range(n_sources):
-        x = np.random.ranf(1)[0] * (gw_size - 1) + 0.5
-        worlds.append(WalledGridworld(size=np.array((gw_size, gw_size)), door_x=x))
-
-    if n_jobs == 1:
-        results = [linearFQI(worlds[i], q_function, epsilon=epsilon, \
-                                                         n_fit=n_fit, n_iter=n_iter, render=False, verbose=verbose) for i in range(n_sources) \
-                for _ in range(n_sources)]
-    elif n_jobs > 1:
-        seeds = [np.random.random_integers(100000) for _ in range(n_sources)]
[…]

### 2018-04-28 NIPS 2018/main.tex
Added algorithms/nt.py and scripts/run_gw.py

--- 2018-03-16 paper/paper.tex
@@
 % \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2017
-%
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2017}
+% before loading nips_2018
 
-\usepackage{nips_2017}
+% ready for submission
+\usepackage{nips_2018}
+
+% to compile a preprint version, e.g., for submission to arXiv, add
+% add the [preprint] option:
+% \usepackage[preprint]{nips_2018}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2017}
+% \usepackage[final]{nips_2018}
+
+% to avoid loading the natbib package, add option nonatbib:
+% \usepackage[nonatbib]{nips_2018}
 
@@
 \usepackage{todonotes}
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newcommand{\mm}{\operatornamewithlimits{mm}}
 
-\title{Active Transfer Learning}
+\title{Formatting instructions for NIPS 2018}
 
@@
 \begin{abstract}
+  The abstract paragraph should be indented \nicefrac{1}{2}~inch
+  (3~picas) on both the left- and right-hand margins. Use 10~point
+  type, with a vertical spacing (leading) of 11~points.  The word
+  \textbf{Abstract} must be centered, bold, and in point size 12. Two
+  line spaces precede the abstract. The abstract must be limited to
+  one paragraph.
 \end{abstract}
@@
 
-\section{Preliminaries}
+\section{Background}
 
-\paragraph{Markov Decision Processes}
+\subsection{Markov Decision Processes}
+
 We define a Markov decision process (MDP) as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
@@
 Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated.
-The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)=\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$.
+The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$.
 To this end, we define the optimal value function $Q^*(s,a)$ as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter.
@@
 
-We define the Bellman residual of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$. Notice that a $Q$-function $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
+We define the Bellman residual of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$.
+Notice that a $Q$-function $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
+Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected Bellman error of $Q$ is defined as the expected Bellman residual of $Q$ under $\mu$.
+Although minimizing the empirical Bellman error would be
 
-\paragraph{Multitask Settings}
+\subsection{Variational Inference}
 
-We represent tasks $\tau$ as MDPs with shared state and action spaces, but with potentially different values for all other parameters.
-We assume the existence of a distribution $\mathcal{D}$ over tasks, i.e., $\tau \sim \mathcal{D}$, and we suppose that we are able to sample from such distribution.
+\section{Variational Transfer Learning}
 
-\section{Approach}
+\subsection{Algorithm}
 
-We start by noticing that the task distribution $\mathcal{D}$ clearly induces a distribution over optimal $Q$-functions.
-Then, our goal is to estimate such distribution from the set of source tasks and use it as a prior for speeding up the learning process in the target task.
+\subsection{Gaussian Variational Transfer}
 
-Consider solving the target task given a dataset $D$ of $N$ samples. The posterior distribution over optimal $Q$-functions is:
-\begin{equation}
-P(Q \mid D) \propto P(D \mid Q)P(Q),
-\end{equation}
-where $P(D \mid Q)$ is the likelihood of observing the dataset $D$ given that $Q$ is optimal and $P(Q)$ is the prior distribution induced by $\mathcal{D}$.
-Computing the likelihood requires knowing the transition and reward models of the current task (i.e., the MDP model), which are not available in practice.
-However, since we are conditioned on the fact that $Q$ is optimal, we can derive a simple approximation.
-We consider the empirical Bellman error $||B(Q)||_{p,D}^p$ under the $l_p$-norm defined as:
-\begin{equation}
-||B(Q)||_{p,D}^p = \frac{1}{N}\sum_{i=1}^N \left\lvert r_i + \gamma\max_{a'}Q(s_i',a') - Q(s_i,a_i) \right\rvert^p
-\end{equation}
-Assuming states and actions to be drawn from a fixed joint distribution $\mu$, we have $||B(Q)||_{p,\mu}^p = 0$ whenever $Q$ is optimal.
-Then, the probability of observing a dataset $D$ clearly decreases exponentially as $||B(Q)||_{p,D}^p$, for  an optimal $Q$, increases.
-This can be seen, for instance, by applying Hoeffding's inequality.
-Thus, a natural way to model the likelihood $P(D \mid Q)$ is:
-\begin{equation}
-P(D \mid Q) \propto e^{-\lambda N ||B(Q)||_{p,D}^p}
-\end{equation}
-where $\lambda$ is a constant hyperparameter.
-Intuitively, this indicates that $D$ is more likely when it induces low empirical Bellman error under an optimal $Q$-function.
-Furthermore, as the number of available samples $N$ increases, the distribution becomes more peaked at zero since the empirical Bellman error converges to the true Bellman error.
-In the limit $N \rightarrow \infty$:
-\begin{equation}
-P(D \mid Q) \propto I_{\left\{ ||B(Q)||_{p,D}^p = 0 \right\}}
-\end{equation}
-
-\subsection{Regularized Bellman Residual Minimization with Gaussian Priors}
-
-Taking the maximum of the log-posterior, we obtain the following optimization problem:
-\begin{equation}
-\min_{Q\in\mathcal{Q}} ||B(Q)||_{p,D}^p - \log P(Q) 
-\end{equation}
-Let us specify a particular hypothesis space $\mathcal{Q}$. We consider $Q$-functions $Q_{\bm{w}}$ parameterized by the vector $\bm{w}$. Our optimization problem becomes:
-\begin{equation}
-\min_{\bm{w}} ||B(\bm{w})||_{p,D}^p - \log P(\bm{w}) 
-\end{equation}
-We model the prior distribution over the optimal parameters $\bm{w}$ as a Gaussian. That is, we assume:
-\begin{equation}
-P(\bm{w}) = \mathcal{N}(\bm{\mu},\bm{\Sigma})
-\end{equation}
-Then, our optimization, adopting the $l_2$-norm, becomes:
-\begin{equation} \label{eq:optim}
-\min_{\bm{w}} ||B(\bm{w})||_{D}^2 + ||\bm{w}-\bm{\mu}||_{\bm{\Sigma}} = \min_{\bm{w}} \frac{1}{N}\sum_{i=1}^N\left\lvert y_i - Q_{\bm{w}}(s_i,a_i) \right\rvert^2 + ||\bm{w}-\bm{\mu}||_{\bm{\Sigma}}
-\end{equation}
-where $y_i = r_i + \gamma\max_{a'}Q_{\bm{w}}(s_i',a')$ and $||\bm{x}||_{\bm{A}} \triangleq \bm{x}^T\bm{A}^{-1}\bm{x}$ for $\bm{A}$ positive definite matrix.
-
-\paragraph{Linear model}
-
-We assume a linear model for the $Q$-functions: $Q_{\bm{w}}(s,a) = \bm{w}^T\bm{\phi}(s,a)$.
-Here $\bm{\phi}$ is a $K$-dimensional feature vector.
-Then, the solution to the optimization problem of Eq.
-\eqref{eq:optim} can be computed in closed form as follows:
-\begin{equation}
-\bm{w}^* = \left( \bm{A}^T\bm{A} + \bm{\Sigma}^{-1} \right)^{-1} \left( \bm{A}^T\bm{b} + \bm{\Sigma}^{-1}\bm{\mu} \right) 
-\end{equation}
-where $\bm{A}$ is an $N\times K$ matrix containing the feature vectors at each data point $(s_i,a_i)$ and $\bm{b}$ is an $N$-dimensional vector containing their targets $y_i$.
-The resulting algorithm is a regularized version of LSVI.
-
-\paragraph{Neural network}
-
-We model $Q_{\bm{w}}(s,a)$ as a neural network with parameters $\bm{w}$.
-Then, the gradient of the objective function of Eq.
-\eqref{eq:optim} can be easily computed by standard backpropagation.
-The resulting algorithm is a regularized version of NFQI.
-
-\subsection{Variational Inference for Efficient Exploration}
-
-A major drawback of the maximum-a-posteriori (MAP) approach is that it does not explicitly estimate the posterior distribution $P(Q \mid D)$.
-Thus, given a dataset $D$, the algorithm consistently chooses the same MAP $Q$-function, and the only way to allow learning is to introduce a simple form of exploration (e.g., $\epsilon$-greedy or softmax), whose drawbacks are well-known.
-The advantages of a more time-coherent exploration strategy such as posterior sampling (or Thompson sampling) have already been proved by many existing works (CITE).
-In particular, direct posterior sampling of $Q$-functions (also known as value function randomization), when a distribution is available, have been proven to be very effective and scalable.
-Thus, we known extend our previous approach to explicitly estimate $P(Q \mid D)$, so as to allow efficient exploration of the target task.
-The main complication is that, as mentioned earlier, we cannot compute the likelihood $P(D \mid Q)$ explicitly, but we only have access to a model that is proportional to it.
-Then, estimating the posterior distribution is clearly intractable since it requires computing the marginal likelihood $P(D) = \int P(D \mid Q) dQ$.
-Thus, we resort variational inference (CITE) to approximate the intractable posterior with a simpler distribution from which we are able to sample.
-
-The main idea behind variational inference is to approximate the posterior $P(Q | D)$ with a simpler distribution $q_{\bm{\phi}}(Q)$, parameterized by the vector $\bm{\phi}$, from which we can easily get samples.
-The best approximation is chosen in terms of the Kullback-Leibler (KL) divergence between the two distributions, that is:
-\begin{equation}
-\min_{\bm{\phi}} KL\left(q_{\bm{\phi}}(Q)\ ||\ P(Q \mid D)\right)
-\end{equation}
-It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
-\begin{equation}
-\text{ELBO}(\bm{\phi}) = \mathbb{E}_{Q \sim q_{\bm{\phi}}}\left[ \log P(D | Q) \right] - KL\left(q_{\bm{\phi}}(Q)\ ||\ P(Q)\right)
-\end{equation}
-As before, we assume a parametric form $Q_{\bm{w}}$ for representing $Q$-functions.
-Thus, we reduce distributions over functions to distributions over vectors $\bm{w} \in \mathbb{R}^K$.
-Given a specific form for the approximate posterior $q_{\bm{\phi}(\bm{w})}$ and the prior $P(\bm{w})$, our inference problem reduces to:
-\begin{equation} \label{eq:vi}
-\min_{\bm{\phi}} \mathbb{E}_{\bm{w} \sim q_{\bm{\phi}}}\left[ \lambda N ||B(\bm{w})||_{D}^2 \right] + KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right)
-\end{equation}
-Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low empirical Bellman error (first term), and staying close to the prior distribution that is learned from the set of source tasks (second term).
-The factor $N$ multiplying $||B(\bm{w})||_{D}^2$ makes sure that, as the number of samples goes to infinity, only the first term is considered in the optimization.
-In such case, all probability mass go over the (approximate) fixed-point of the optimal Bellman operator.
-On the other hand, for small values of $N$, there is less evidence that the empirical Bellman error closely estimate the true one, thus giving more importance to staying close to the prior.
-
-Depending on the choice of the prior and approximate posterior distributions, the optimization problem of Eq.
-\eqref{eq:vi} might still be very hard to solve.
-We now propose some suitable choices that make the problem efficiently solvable.
-
-\paragraph*{Gaussian distributions}
-
-We model both the prior and the approximate posterior as Gaussian distributions: $P(\bm{w}) = \mathcal{N}(\bar{\bm{\mu}},\bar{\bm{\Sigma}})$ and $q_{\bm{\phi}}(\bm{w}) = \mathcal{N}(\bm{\mu},\bm{\Sigma})$, respectively.
-For the sake of simplicity, we assume $\bm{\Sigma} = \text{diag}(\sigma_1^2,\dots,\sigma_K^2)$ and $\bar{\bm{\Sigma}} = \text{diag}(\bar{\sigma}_1^2,\dots,\bar{\sigma}_K^2)$.
-Notice, in this case, that the parameter vector $\bm{\phi}$ is $[\mu_1,\dots,\mu_K,\sigma_1^2,\dots,\sigma_K^2]$.
-The KL divergence between the two distributions can be computed in closed form as:
-\begin{equation}
-KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bar{\bm{\Sigma}} \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bar{\bm{\Sigma}}^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bar{\bm{\mu}})^T \bar{\bm{\Sigma}}^{-1} (\bm{\mu} - \bar{\bm{\mu}}) -K \right)
-\end{equation}
-To solve the optimization problem of Eq.
-\eqref{eq:vi} we adopt stochastic backpropagation (CITE).
-Thus, we need to compute the gradient of the objective function $\mathcal{L}(\bm{\phi})$ of Eq.
-\eqref{eq:vi} with respect to each component of $\bm{\phi}$.
-This can be easily done for the second term:
-\begin{equation}
-\nabla_{\bm{\mu}} KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right) = \bar{\bm{\Sigma}}^{-1} (\bm{\mu} - \bar{\bm{\mu}})
-\end{equation}
-\begin{equation}
-\nabla_{\sigma_k^2} KL\left(q_{\bm{\phi}}(\bm{w})\ ||\ P(\bm{w})\right) = \frac{1}{2}\left( \frac{1}{\bar{\sigma}_k^2} - \frac{1}{\sigma_k^2} \right)
-\end{equation}
-For the first term, we have to compute the gradient of an expectation with respect to the parameters of the Gaussian distribution under which the expectation is taken.
-For the mean, we can resort to Thm.
-X of (CITE Bonnet 1964):
-\begin{equation}
-\nabla_{\mu_k} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N \nabla_{w_k} ||B(\bm{w})||_{D}^2 \right]
-\end{equation}
-For the covariance, we can resort to Thm. Y of (CITE Price 1958):
-\begin{equation}
-\nabla_{\sigma_k^2} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N ||B(\bm{w})||_{D}^2 \right] = \frac{1}{2}\mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N \nabla_{w_k,w_k}^2 ||B(\bm{w})||_{D}^2 \right]
-\end{equation}
-We refer the reader to (CITE Deepmind) for a simple proofs of these two theorems.
-
-It only remains to compute the gradient and Hessian of the empirical Bellman error $||B(\bm{w})||_{D}^2$ with respect to $\bm{w}$. Recall that:
-\begin{equation}
-||B(\bm{w})||_{D}^2 = \frac{1}{N}\sum_{i=1}^N \left( r_i + \gamma\max_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i) \right)^2
-\end{equation}
+\subsection{Mixture of Gaussian Variational Transfer}
 
@@
 
-List of any paper that relates to our approach together with a brief description:
-\begin{itemize}
-\item \cite{osband2014generalization}: the authors propose a method for efficient exploration via randomized value functions.
-The optimal $Q$-function is computed by bayesian LSVI and, after each update, parameters are sampled from the posterior.
-Then, the agent follows a greedy policy with respect to the sampled $Q$-function.
-Regret bounds are provided.
-\item \cite{osband2016deep}: the authors extend the idea of randomized value functions to drive exploration in deep RL.
-A posterior distribution over $Q$-functions is approximated via bootstrapping.
-In each episode, the agent acts greedily with respect to a $Q$-function sampled from the approximated posterior.
-\item \cite{chen2017ucb}: the authors build on top of bootstrapped DQNs to provide UCB-like exploration bonuses.
-In a previous (?) version of the paper, exploration bonuses based on information gain are also proposed.
-\end{itemize}
+\section{Experiments}
 
-\section{Experiments}
+\subsection{Gridworld}
+
+\subsection{Classic Control}
+
+\subsection{Maze Navigation}
 
@@
 }
+
 \newpage
@@
 
-\section{Proofs}
-
 \end{document}

### 2018-04-28 algorithms/nt.py

@@ -1,0 +1,131 @@
+import numpy as np
+from policies import EpsilonGreedy, ScheduledEpsilonGreedy
+from buffer import Buffer
+import utils
+import time
+
+
+def learn(mdp,
+          Q,
+          operator,
+          max_iter=5000,
+          buffer_size=10000,
+          batch_size=50,
+          alpha=0.001,
+          train_freq=1,
+          eval_freq=50,
+          eps_start=1.0,
+          eps_end=0.02,
+          exploration_fraction=0.2,
+          random_episodes=0,
+          eval_states=None,
+          eval_episodes=1,
+          mean_episodes=50,
+          preprocess=lambda x: x,
+          seed=None,
+          render=False,
+          verbose=True):
+    if seed is not None:
+        np.random.seed(seed)
+
+    # Initialize policies
+    schedule = np.linspace(eps_start, eps_end, exploration_fraction * max_iter)
+    pi = ScheduledEpsilonGreedy(Q, np.arange(mdp.action_space.n), schedule)
+    pi_u = EpsilonGreedy(Q, np.arange(mdp.action_space.n), epsilon=1)
+    pi_g = EpsilonGreedy(Q, np.arange(mdp.action_space.n), epsilon=0)
+
+    # Add random episodes if needed
+    init_samples = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes,
+                                           preprocess=preprocess) if random_episodes > 0 else None
+
+    # Figure out the effective state-dimension after preprocessing is applied
+    eff_state_dim = preprocess(np.zeros(mdp.state_dim)).size
+
+    # Create replay buffer
+    buffer = Buffer(buffer_size, eff_state_dim)
+    n_init_samples = buffer.add_all(init_samples) if random_episodes > 0 else 0
+
+    # Results
+    iterations = []
+    episodes = []
+    n_samples = []
+    evaluation_rewards = []
+    learning_rewards = []
+    episode_rewards = [0.0]
+    l_2 = []
+    l_inf = []
+
+    # Adam initial params
+    m_t = 0
+    v_t = 0
+    t = 0
+
+    # Init env
+    s = mdp.reset()
+    h = 0
+
+    start_time = time.time()
+
+    # Learning
+    for i in range(max_iter):
+
+        # Take epsilon-greedy action wrt current Q-function
+        s_prep = preprocess(s)
+        a = pi.sample_action(s_prep)
+        # Step
+        s_prime, r, done, _ = mdp.step(a)
[…]

### 2018-04-28 scripts/run_gw.py

@@ -1,0 +1,134 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.walled_gridworld import WalledGridworld
+from envs.marcellos_gridworld import MarcellosGridworld
+from features.agrbf import build_features_gw_state
+from features.identity import Identity
+from approximators.linear import LinearQFunction
+from operators.mellow import MellowBellmanOperator
+from algorithms.nt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=100)
+parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--exploration_fraction", default=0.2)
+parser.add_argument("--eps_start", default=1.0)
+parser.add_argument("--eps_end", default=0.02)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha", default=0.001)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=5)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=6)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="nt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
+xi = float(args.xi)
+tau = float(args.tau)
+batch_size = int(args.batch_size)
+max_iter = int(args.max_iter)
+buffer_size = int(args.buffer_size)
+random_episodes = int(args.random_episodes)
+exploration_fraction = float(args.exploration_fraction)
[…]

### 2018-04-28 utils.py

@@ -4,7 +4,8 @@ from time import sleep
 import matplotlib.pyplot as plt
 
 
-def evaluate_policy(mdp, policy, criterion='discounted', n_episodes=1, initial_states=None, render=False):
+def evaluate_policy(mdp, policy, criterion='discounted', n_episodes=1, initial_states=None,
+                    preprocess=lambda x: x, render=False):
     """
     Evaluates a policy on a given MDP.
 
@@ -27,15 +28,15 @@ def evaluate_policy(mdp, policy, criterion='discounted', n_episodes=1, initial_s
     assert criterion == 'average' or criterion == 'discounted'
 
     if initial_states is None or type(initial_states) is np.ndarray:
-        scores = [_single_eval(mdp, policy, criterion, initial_states, render) for _ in range(n_episodes)]
+        scores = [_single_eval(mdp, policy, criterion, initial_states, preprocess, render) for _ in range(n_episodes)]
     elif type(initial_states) is list:
-        scores = [_single_eval(mdp, policy, criterion, init_state, render) for init_state in initial_states]
+        scores = [_single_eval(mdp, policy, criterion, init_state, preprocess, render) for init_state in initial_states]
 
     scores = np.array(scores)
     return np.mean(scores[:, 0]), np.std(scores[:, 0]), np.mean(scores[:, 1]), np.std(scores[:, 1])
 
 
-def _single_eval(mdp, policy, criterion, initial_state, render):
+def _single_eval(mdp, policy, criterion, initial_state, preprocess, render):
 
     score = 0
     gamma = mdp.gamma if criterion == "discounted" else 1
@@ -45,7 +46,7 @@ def _single_eval(mdp, policy, criterion, initial_state, render):
 
     while t < mdp.horizon:
 
-        a = policy.sample_action(s)
+        a = policy.sample_action(preprocess(s))
         if render:
             mdp._render(a=a)
             sleep(0.01)
@@ -58,7 +59,7 @@ def _single_eval(mdp, policy, criterion, initial_state, render):
     return score if criterion == "discounted" else score / t, t
 
 
-def generate_episodes(mdp, policy, n_episodes=1, render=False):
+def generate_episodes(mdp, policy, n_episodes=1, preprocess=lambda x: x, render=False):
     """
     Generates episodes in a given mdp using a given policy
 
[…]

### 2018-04-28 algorithms/nt.py
Added get_info() function to MDPs

@@ -128,4 +128,4 @@ def learn(mdp,
     run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf]
     weights = np.array(Q._w)
 
-    return [mdp.door_x, weights, run_info]
+    return [mdp.get_info(), weights, run_info]

### 2018-04-28 envs/three_room_gw.py

@@ -15,13 +15,13 @@ Info
 """
 
 
-class WalledGridworld(gym.Env):
+class ThreeRoomGridworld(gym.Env):
     metadata = {
         'render.modes': ['human', 'rgb_array'],
         'video.frames_per_second': 15
     }
 
-    def __init__(self, size=np.array([10, 10]), door_x=5, door_width=1):
+    def __init__(self, size=np.array([10, 10]), door_x=(5,5), door_width=(1,1)):
         # General MDP parameters
         self.horizon = 50
         self.gamma = 0.99
@@ -37,10 +37,14 @@ class WalledGridworld(gym.Env):
         self.step_length = 1
         self.door_x = door_x
         self.door_width = door_width
-        self.wall1_p1 = np.array([0, size[1] / 2])
-        self.wall1_p2 = np.array([max(0., door_x - door_width / 2), size[1] / 2])
-        self.wall2_p1 = np.array([min(door_x + door_width / 2, size[1]), size[1] / 2])
-        self.wall2_p2 = np.array([size[1], size[1] / 2])
+        self.wall1_p1 = np.array([0, size[1] * 2 / 3])
+        self.wall1_p2 = np.array([max(0., door_x[1] - door_width[1] / 2), size[1] * 2 / 3])
+        self.wall2_p1 = np.array([min(door_x[1] + door_width[1] / 2, size[0]), size[1] * 2 / 3])
+        self.wall2_p2 = np.array([size[1], size[1] * 2 / 3])
+        self.wall3_p1 = np.array([0, size[1] / 3])
+        self.wall3_p2 = np.array([max(0., door_x[0] - door_width[0] / 2), size[1] / 3])
+        self.wall4_p1 = np.array([min(door_x[0] + door_width[0] / 2, size[0]), size[1] / 3])
+        self.wall4_p2 = np.array([size[0], size[1] / 3])
 
         # State space: [0,width]x[0,height]
         self.observation_space = spaces.Box(low=np.array([0, 0]), high=size)
@@ -50,6 +54,9 @@ class WalledGridworld(gym.Env):
 
         self.reset()
         self.viewer = None
+
+    def get_info(self):
+        return ["three-room-gw", self.door_x]
 
     def reset(self, state=None):
         if state is None:
@@ -96,7 +103,9 @@ class WalledGridworld(gym.Env):
 
         # Check whether the agent hit a wall
         if self._check_intersect(s, self.current_position, self.wall1_p1, self.wall1_p2) or \
[…]

### 2018-04-28 envs/two_room_gw.py

@@ -15,13 +15,13 @@ Info
 """
 
 
-class MarcellosGridworld(gym.Env):
+class TwoRoomGridworld(gym.Env):
     metadata = {
         'render.modes': ['human', 'rgb_array'],
         'video.frames_per_second': 15
     }
 
-    def __init__(self, size=np.array([10, 10]), door_x=(5,5), door_width=(1,1)):
+    def __init__(self, size=np.array([10, 10]), door_x=5, door_width=1):
         # General MDP parameters
         self.horizon = 50
         self.gamma = 0.99
@@ -37,14 +37,10 @@ class MarcellosGridworld(gym.Env):
         self.step_length = 1
         self.door_x = door_x
         self.door_width = door_width
-        self.wall1_p1 = np.array([0, size[1] * 2 / 3])
-        self.wall1_p2 = np.array([max(0., door_x[1] - door_width[1] / 2), size[1] * 2 / 3])
-        self.wall2_p1 = np.array([min(door_x[1] + door_width[1] / 2, size[0]), size[1] * 2 / 3])
-        self.wall2_p2 = np.array([size[1], size[1] * 2 / 3])
-        self.wall3_p1 = np.array([0, size[1] / 3])
-        self.wall3_p2 = np.array([max(0., door_x[0] - door_width[0] / 2), size[1] / 3])
-        self.wall4_p1 = np.array([min(door_x[0] + door_width[0] / 2, size[0]), size[1] / 3])
-        self.wall4_p2 = np.array([size[0], size[1] / 3])
+        self.wall1_p1 = np.array([0, size[1] / 2])
+        self.wall1_p2 = np.array([max(0., door_x - door_width / 2), size[1] / 2])
+        self.wall2_p1 = np.array([min(door_x + door_width / 2, size[1]), size[1] / 2])
+        self.wall2_p2 = np.array([size[1], size[1] / 2])
 
         # State space: [0,width]x[0,height]
         self.observation_space = spaces.Box(low=np.array([0, 0]), high=size)
@@ -54,6 +50,9 @@ class MarcellosGridworld(gym.Env):
 
         self.reset()
         self.viewer = None
+
+    def get_info(self):
+        return ["two-room-gw", self.door_x]
 
     def reset(self, state=None):
         if state is None:
@@ -100,9 +99,7 @@ class MarcellosGridworld(gym.Env):
 
         # Check whether the agent hit a wall
         if self._check_intersect(s, self.current_position, self.wall1_p1, self.wall1_p2) or \
[…]

### 2018-04-28 scripts/run_gw.py

@@ -2,8 +2,8 @@ import sys
 sys.path.append("../")
 
 import numpy as np
-from envs.walled_gridworld import WalledGridworld
-from envs.marcellos_gridworld import MarcellosGridworld
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
 from features.agrbf import build_features_gw_state
 from features.identity import Identity
 from approximators.linear import LinearQFunction
@@ -73,9 +73,9 @@ file_name = str(args.file_name)
 doors = [np.random.uniform(0.5, gw_size - 0.5) if door < 0 else door for _ in range(n_runs)]
 doors2 = [np.random.uniform(0.5, gw_size - 0.5) if door2 < 0 else door2 for _ in range(n_runs)]
 if env == "two-room-gw":
-    mdps = [WalledGridworld(np.array([gw_size, gw_size]), door_x=d) for d in doors]
+    mdps = [TwoRoomGridworld(np.array([gw_size, gw_size]), door_x=d) for d in doors]
 elif env == "three-room-gw":
-    mdps = [MarcellosGridworld(np.array([gw_size, gw_size]), door_x=(d1,d2)) for (d1,d2) in zip(doors,doors2)]
+    mdps = [ThreeRoomGridworld(np.array([gw_size, gw_size]), door_x=(d1,d2)) for (d1,d2) in zip(doors,doors2)]
 eval_states = [np.array([0., 0.]) for _ in range(10)]
 
 state_dim = mdps[0].state_dim

### 2018-04-28 algorithms/nt.py
Correction

@@ -37,6 +37,10 @@ def learn(mdp,
     # Add random episodes if needed
     init_samples = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes,
                                            preprocess=preprocess) if random_episodes > 0 else None
+    if random_episodes > 0:
+        t, s, a, r, s_prime, absorbing, sa = utils.split_data(init_samples, mdp.state_dim, mdp.action_dim)
+        init_samples = np.concatenate((t[:, np.newaxis], preprocess(s), a, r[:, np.newaxis], preprocess(s_prime),
+                                       absorbing[:, np.newaxis]), axis=1)
 
     # Figure out the effective state-dimension after preprocessing is applied
     eff_state_dim = preprocess(np.zeros(mdp.state_dim)).size

### 2018-04-28 algorithms/gvt.py
Added gvt.py

@@ -1,0 +1,242 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from policies import EpsilonGreedy
+from buffer import Buffer
+import utils
+import time
+
+
+def unpack(params, K):
+    """Unpacks a parameter vector into mu and L"""
+    mu = params[:K]
+    L = params[K:].reshape(K,K)
+    return mu, L
+
+
+def pack(mu, L):
+    """Packs mu and L into a parameter vector"""
+    return np.concatenate((mu, L.flatten()))
+
+
+def clip(params, cholesky_clip, K):
+    """Makes sure the Cholensky factor L is well-defined"""
+    mu, L = unpack(params, K)
+    # Clip the diagonal to 0.01
+    mask = np.logical_and(L < cholesky_clip, np.eye(K, dtype=bool))
+    L[mask] = cholesky_clip
+    # Make sure L is lower triangular
+    L[np.triu_indices(K, 1)] = 0
+    return pack(mu, L)
+
+
+def sample_posterior(params, K):
+    """Samples a Q function from the posterior distribution"""
+    mu, L = unpack(params, K)
+    return np.dot(L, np.random.randn(K,)) + mu
+
+
+def objective(samples, params, Q, mu_bar, Sigma_bar_inv, operator, n_samples, lambda_, n_weights):
+    """Computes the negative ELBO"""
+    mu, L = unpack(params, Q._w.size)
+    # We add a small constant to make sure Sigma is always positive definite
+    Sigma = np.dot(L, L.T)
+    weights, _ = utils.sample_mvn(n_weights, mu, L)
+    likelihood = operator.expected_bellman_error(Q, samples, weights)
+    assert likelihood >= 0
+    kl = utils.KL(mu, Sigma, mu_bar, Sigma_bar_inv)
+    assert kl >= 0
+    return likelihood + lambda_ * kl / n_samples
+
+
+def gradient(samples, params, Q, mu_bar, Sigma_bar_inv, operator, n_samples, lambda_, n_weights):
+    """Computes the objective function gradient"""
+    mu, L = unpack(params, Q._w.size)
+    ws, vs = utils.sample_mvn(n_weights, mu, L)
+    be_grad = operator.gradient_be(Q, samples, ws)
+    # Gradient of the expected Bellman error wrt mu
+    ebe_grad_mu = np.average(be_grad, axis=0)
+    # Gradient of the expected Bellman error wrt L.
[…]

### 2018-04-28 scripts/run_gvt_gw.py

@@ -1,0 +1,148 @@
+import sys
+
+sys.path.append("../")
+
+import numpy as np
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
+from features.agrbf import build_features_gw_state
+from features.identity import Identity
+from approximators.linear import LinearQFunction
+from operators.mellow import MellowBellmanOperator
+from algorithms.gvt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.1)
+parser.add_argument("--lambda_", default=0.001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--sigma_reg", default=0.0001)
+parser.add_argument("--cholesky_clip", default=0.0001)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=5)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=6)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/gw5x5")
+
+# Read arguments
+args = parser.parse_args()
[…]

### 2018-04-28 algorithms/gvt.py
Added random samples from prior to GVT

@@ -96,23 +96,7 @@ def learn(mdp,
         np.random.seed(seed)
 
     # Initialize policies
-    pi_u = EpsilonGreedy(Q, np.arange(mdp.action_space.n), epsilon=1)
     pi_g = EpsilonGreedy(Q, np.arange(mdp.action_space.n), epsilon=0)
-
-    # Add random episodes if needed
-    init_samples = utils.generate_episodes(mdp, pi_u, n_episodes=random_episodes,
-                                           preprocess=preprocess) if random_episodes > 0 else None
-    if random_episodes > 0:
-        t, s, a, r, s_prime, absorbing, sa = utils.split_data(init_samples, mdp.state_dim, mdp.action_dim)
-        init_samples = np.concatenate((t[:, np.newaxis], preprocess(s), a, r[:, np.newaxis], preprocess(s_prime),
-                                       absorbing[:, np.newaxis]), axis=1)
-
-    # Figure out the effective state-dimension after preprocessing is applied
-    eff_state_dim = preprocess(np.zeros(mdp.state_dim)).size
-
-    # Create replay buffer
-    buffer = Buffer(buffer_size, eff_state_dim)
-    n_init_samples = buffer.add_all(init_samples) if random_episodes > 0 else 0
 
     # Get number of features
     K = Q._w.size
@@ -129,6 +113,25 @@ def learn(mdp,
     Sigma_bar_inv = np.linalg.inv(Sigma_bar + np.eye(K) * sigma_reg)
     # We initialize the parameters at the prior with smaller regularization (just to make sure Sigma_bar is pd)
     params = clip(pack(mu_bar, np.linalg.cholesky(Sigma_bar + np.eye(K) * cholesky_clip)), cholesky_clip, K)
+
+    # Add random episodes if needed
+    if random_episodes > 0:
+        init_samples = list()
+        for i in range(random_episodes):
+            Q._w = sample_posterior(params, K)
+            init_samples.append(utils.generate_episodes(mdp, pi_g, n_episodes=1, preprocess=preprocess))
+        init_samples = np.concatenate(init_samples)
+
+        t, s, a, r, s_prime, absorbing, sa = utils.split_data(init_samples, mdp.state_dim, mdp.action_dim)
+        init_samples = np.concatenate((t[:, np.newaxis], preprocess(s), a, r[:, np.newaxis], preprocess(s_prime),
+                                       absorbing[:, np.newaxis]), axis=1)
+
[…]

### 2018-04-28 algorithms/mgvt.py
Added mgvt.py

@@ -1,0 +1,395 @@
+import numpy as np
+from policies import EpsilonGreedy
+from buffer import Buffer
+import utils
+import time
+
+prior_eigen = None
+cholesky_mask = None
+
+
+def unpack(params, C, K):
+    """Unpacks a parameter vector into c, mu, L"""
+    c = params[:C]
+    mus = params[C:C + C * K]
+    mu = mus.reshape(C, K)
+    Ls = params[C + C * K:]
+    L = Ls.reshape(C, K, K)
+    return c, mu, L
+
+
+def pack(c, mu, L):
+    """Packs c and mu and L into a parameter vector"""
+    params = np.concatenate((c, mu.flatten(), L.flatten()), axis=0)
+    return params
+
+
+def clip(params, cholesky_clip, C, K):
+    """Makes sure the Cholesky factor L is well-defined"""
+    global cholesky_mask
+    c, mu, L = unpack(params, C, K)
+    cholesky_mask = np.eye(K, dtype=bool) if cholesky_mask is None else cholesky_mask
+    for i in range(C):
+        mask = np.logical_and(L[i, :, :] < cholesky_clip, cholesky_mask)
+        L[i, :, :][mask] = cholesky_clip
+        L[i, :, :][np.triu_indices(K, 1)] = 0
+    return pack(c, mu, L)
+
+
+def sample_posterior(params, C, K):
+    """Samples a Q function from the posterior distribution"""
+    c, mu, L = unpack(params, C, K)
+    cluster = np.random.choice(np.arange(C), p=c)
+    return np.dot(L[cluster, : , :], np.random.randn(K,)) + mu[cluster, :]
+
+
+def normal_KL(c, mu, Sigma, c_bar, mu_bar, Sigma_bar, precision=None):
+    """ Computes the KL between normals for two GMMs """
+
+    global prior_eigen
+
+    Sigma_bar_inv = np.linalg.inv(Sigma_bar) if precision is None else precision
+    inv_b = Sigma_bar_inv[np.newaxis]
+    if prior_eigen is None:
+        prior_eigen, _ = np.linalg.eig(Sigma_bar[np.newaxis])
+
+    posterior_eigen, _ = np.linalg.eig(Sigma[:, np.newaxis])
+    posterior_eigen = np.real(posterior_eigen)
+    posterior_eigen[posterior_eigen < 0] = 1e-10
[…]

### 2018-04-28 scripts/run_mgvt_gw.py

@@ -1,0 +1,160 @@
+import sys
+
+sys.path.append("../")
+
+import numpy as np
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
+from features.agrbf import build_features_gw_state
+from features.identity import Identity
+from approximators.linear import LinearQFunction
+from operators.mellow import MellowBellmanOperator
+from algorithms.mgvt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.1)
+parser.add_argument("--lambda_", default=0.000001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=5)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=6)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/gw5x5")
+parser.add_argument("--eta", default=1e-6)  # learning rate for
[…]

### 2018-05-02 algorithms/mgvt_torch.py
optimizations done with pytorch on the KL computations

@@ -1,0 +1,424 @@
+import numpy as np
+from policies import EpsilonGreedy
+from buffer import Buffer
+import utils
+import time
+
+from torch.distributions import MultivariateNormal
+import torch
+
+prior_eigen = None
+cholesky_mask = None
+prior_normal = None
+posterior_normal = None
+
+def unpack(params, C, K):
+    """Unpacks a parameter vector into c, mu, L"""
+    c = params[:C]
+    mus = params[C:C + C * K]
+    mu = mus.reshape(C, K)
+    Ls = params[C + C * K:]
+    L = Ls.reshape(C, K, K)
+    return c, mu, L
+
+
+def pack(c, mu, L):
+    """Packs c and mu and L into a parameter vector"""
+    params = np.concatenate((c, mu.flatten(), L.flatten()), axis=0)
+    return params
+
+
+def clip(params, cholesky_clip, C, K):
+    """Makes sure the Cholesky factor L is well-defined"""
+    global cholesky_mask
+    c, mu, L = unpack(params, C, K)
+    cholesky_mask = np.eye(K, dtype=bool) if cholesky_mask is None else cholesky_mask
+    for i in range(C):
+        mask = np.logical_and(L[i, :, :] < cholesky_clip, cholesky_mask)
+        L[i, :, :][mask] = cholesky_clip
+        L[i, :, :][np.triu_indices(K, 1)] = 0
+    return pack(c, mu, L)
+
+
+def sample_posterior(params, C, K):
+    """Samples a Q function from the posterior distribution"""
+    c, mu, L = unpack(params, C, K)
+    cluster = np.random.choice(np.arange(C), p=c)
+    return np.dot(L[cluster, : , :], np.random.randn(K,)) + mu[cluster, :]
+
+
+def normal_KL(c, mu, Sigma, c_bar, mu_bar, Sigma_bar, L=None, precision=None):
+    """ Computes the KL between normals for two GMMs """
+    global prior_eigen
+    Sigma_bar_inv = np.linalg.inv(Sigma_bar) if precision is None else precision
+    inv_b = Sigma_bar_inv[np.newaxis]
+    if prior_eigen is None:
+        prior_eigen, _ = np.linalg.eig(Sigma_bar[np.newaxis])
+
+    if L is None:
+        posterior_eigen, _ = np.linalg.eig(Sigma[:, np.newaxis])
+    else:
[…]

### 2018-05-02 NIPS 2018/main.tex

@@
 
-We define the Bellman residual of a $Q$-function $Q$ as $B(Q) \triangleq TQ - Q$.
-Notice that a $Q$-function $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
-Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected Bellman error of $Q$ is defined as the expected Bellman residual of $Q$ under $\mu$.
-Although minimizing the empirical Bellman error would be
+When learning the optimal value function, a quantity of interest is how close a given $Q$-function is to the fixed-point of the Bellman operator.
+This is given by its Bellman residual, defined by $B(Q) \triangleq TQ - Q$.
+Notice that $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
+Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\mu$, $\mathbb{E}_{\mu}\left[ B^2(Q) \right]$.
+Although minimizing the empirical Bellman error is an appealing objective, it is well-known that an unbiased estimator requires two independent samples of the next state $s'$ of each $s,a$ (e.g., \cite{} \todo{cite Maillard}).
+In practice, the empirical Bellman error is typically replaced by the TD error, which approximates the former using a single transition sample.
+Given a dataset of $N$ samples, the TD error is computed as $\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.
 
 \subsection{Variational Inference}
+
+When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
+\begin{equation}\label{eq:bayes}
+p(\bm{w} | D) = \frac{p(D | \bm{w})p(\bm{w})}{p(D)} = \frac{p(D | \bm{w})p(\bm{w})}{\int_{\bm{w}} p(D | \bm{w})p(\bm{w})},
+\end{equation}
+is typically intractable for many models of interest (e.g., when working with deep neural networks) due to difficulties in computing the integral of Eq.
+\eqref{eq:bayes}.
+The main intuition behind variational inference \cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$.
+The latter is chosen in a parametric family, with variational parameters $\bm{\xi}$, as the minimizer of the Kullback-Leibler (KL) divergence w.r.t.
+$p$:
+\begin{equation}
+\min_{\bm{\xi}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w} \mid D)\right)
+\end{equation}
+It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
+\begin{equation}
+\text{ELBO}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[ \log p(D | \bm{w}) \right] - KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
+\end{equation}
+Intuitively, the best approximation is the one that maximizes the expected log-likelihood of the data, while minimizing the KL divergenge w.r.t. the prior $p(\bm{w})$.
 
@@
 \subsection{Mixture of Gaussian Variational Transfer}
+
+\section{Theoretical Analysis}
 
@@
 
+\section{Proofs of Theorems}
+
 \end{document}

### 2018-05-02 algorithms/mgvt_torch.py
optimizations done with pytorch on the KL computations - fix defaults

@@ -252,7 +252,7 @@ def learn(mdp,
           seed=None,
           render=False,
           verbose=True,
-          ukl_tight_freq=100):
+          ukl_tight_freq=1):
 
     if seed is not None:
         np.random.seed(seed)

### 2018-05-02 approximators/mlp_torch.py
fix bug init

@@ -15,7 +15,7 @@ class MLPQFunction(QFunction):
     """
     def __init__(self, state_dim, n_actions, layers=(32,), initial_params=None):
         self._nn = Net(state_dim, n_actions, layers)
-        self.__w = np.random.randn(self._nn.n_weights) * 0.1 if initial_params is None else initial_params
+        self._w = np.random.randn(self._nn.n_weights) * 0.1 if initial_params is None else initial_params
         self._state_dim = state_dim
         self._n_actions = n_actions
 

### 2018-05-05 scripts/run_gvt_cartpole.py
tune default parameters

@@ -31,11 +31,11 @@ parser.add_argument("--mean_episodes", default=20)
 parser.add_argument("--l1", default=32)
 parser.add_argument("--l2", default=0)
 parser.add_argument("--alpha_adam", default=0.001)
-parser.add_argument("--alpha_sgd", default=0.00001)
-parser.add_argument("--lambda_", default=0.01)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.0001)
 parser.add_argument("--time_coherent", default=False)
-parser.add_argument("--n_weights", default=10)
-parser.add_argument("--n_source", default=2)
+parser.add_argument("--n_weights", default=5)
+parser.add_argument("--n_source", default=5)
 parser.add_argument("--sigma_reg", default=0.0001)
 parser.add_argument("--cholesky_clip", default=0.0001)
 # Cartpole parameters (default = randomize
@@ -85,7 +85,7 @@ mc = [np.random.uniform(0.5, 1.5) if cart_mass < 0 else cart_mass for _ in range
 mp = [np.random.uniform(0.1, 0.3) if pole_mass < 0 else pole_mass for _ in range(n_runs)]
 l = [np.random.uniform(0.2, 1.0) if pole_length < 0 else pole_length for _ in range(n_runs)]
 mdps = [CartPoleEnv(a,b,c) for a,b,c in zip(mc,mp,l)]
-n_eval_episodes = 5
+n_eval_episodes = 15
 
 state_dim = mdps[0].state_dim
 action_dim = 1

### 2018-05-06 NIPS 2018/main.tex
Added mellow-max theorem to the paper

@@
 \usepackage{algorithmic}
+\usepackage{thmtools, thm-restate}
+
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{remark}{Remark}
+\newtheorem{definition}{Definition}
+\newtheorem{proposition}{Proposition}
 
@@
 \newcommand{\mm}{\operatornamewithlimits{mm}}
-
+\newcommand{\wt}[1]{\widetilde{#1}}
+\newcommand{\wh}[1]{\widehat{#1}}
+\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
+\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
 \title{Formatting instructions for NIPS 2018}
@@
 
+In this section, we theoretically analyze our variational transfer algorithm...
+
+A first important question that we need to answer is whether replacing max with mellow-max in the Bellman operator constitutes a strong approximation or not.
+It has been proved \cite{} \todo{Cite MM} that the mellow Bellman operator is a contraction under the $L_{\infty}$-norm and, thus, has a unique fixed-point.
+However, how such fixed-point differs from the one of the optimal Bellman operator remains an open question.
+Since mellow-max monotonically converges to max as $\kappa \rightarrow \infty$, it would be desirable if the corresponding operator also monotonically converged to the optimal one.
+We confirm that this property actually holds in the following theorem.
+
+\begin{restatable}{theorem}{thmm} \label{th:mm}
+Let $V$ be the fixed-point of the optimal Bellman operator $T$, and $Q$ the corresponding action-value function.
+Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$.
+Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}).
+Let $\nu$ be a probability measure over the state-space and $p \geq 1$.
+Then:
+\begin{equation}
+\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{1-\gamma}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
+\end{equation}
+\end{restatable}
+
 \section{Related Works}
@@
 
+\thmm*
+\begin{proof}
+We begin by noticing that:
+\begin{align*}
+\norm{V-\wt{V}}_{\nu,p}^p =\ & \norm{TV - \wt{T}\wt{V}}_{\nu,p}^p \\ =\ &
+\norm{TV - \wt{T}V + \wt{T}V - \wt{T}\wt{V}}_{\nu,p}^p \\ \leq\ &
+\norm{TV - \wt{T}V}_{\nu,p}^p + \norm{\wt{T}V - \wt{T}\wt{V}}_{\nu,p}^p \\ \leq\ &
+\norm{TV - \wt{T}V}_{\nu,p}^p + \gamma\norm{V - \wt{V}}_{\nu,p}^p
+\end{align*}
+where the first inequality follows from Minkowsky's inequality and the second one from the contraction property of the mellow Bellman operator. This implies that:
+\begin{align} \label{eq:mm1}
+\norm{V-\wt{V}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TV - \wt{T}V}_{\nu,p}^p
+\end{align}
+Let us bound the norm on the right-hand side separately.
+In order to do that, we will bound the function $\abs{TV(s) - \wt{T}V(s)}$ point-wisely for any state $s$.
+By applying the definition of the optimal and mellow Bellman operators, we obtain:
+\begin{align*}
+\abs{TV(s) - \wt{T}V(s)} =\ & \abs{\max_{a}\lbrace R(s,a) + \gamma\mathbb{E}\left[V(s')\right] \rbrace - \mm_{a}\lbrace R(s,a) + \gamma\mathbb{E}\left[V(s')\right] \rbrace}\\ =\ & \abs{\max_a Q(s,a) - \mm_a Q(s,a)}
+\end{align*}
+Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta$ induced by $\kappa$ \cite{}\todo{Cite MM}.
+Thus, we can write:
+\begin{align} \label{eq:mm2}
+\abs{\max_a Q(s,a) - \mm_a Q(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q(s,a) - \sum_a \pi_{\beta}(a|s)Q(s,a)}\notag\\ =\ & \abs{\sum_a Q(s,a) \left( \pi^*(a|s) - \pi_{\beta}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q(s,a)} \abs{\pi^*(a|s) - \pi_{\beta}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta}(a|s)}
+\end{align}
+where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q$ and $\pi_{\beta}$ is the Boltzmann distribution induced by $Q$ with inverse temperature $\beta$:
+\begin{align*}
+\pi_{\beta}(a|s) = \frac{e^{\beta Q(s,a)}}{\sum_{a'}e^{\beta Q(s,a')}}
+\end{align*}
+Denote by $a_1(s)$ the optimal action for state $s$ under $Q$. We can then write:
+\begin{align} \label{eq:mm3}
+\sum_a\abs{\pi^*(a|s) - \pi_{\beta}(a|s)} =\ & \abs{\pi^*(a_1(s)|s) - \pi_{\beta}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi^*(a|s) - \pi_{\beta}(a|s)}\notag\\ =\ & \abs{1 - \pi_{\beta}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi_{\beta}(a|s)}\notag\\ =\ & 2\abs{1 - \pi_{\beta}(a_1(s)|s)}
+\end{align}
+Finally, let us bound this last term:
+\begin{align} \label{eq:mm4}
+\abs{1 - \pi_{\beta}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta Q(s,a_1(s))}}{\sum_{a'}e^{\beta Q(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta \left( Q(s,a_1(s)) - Q(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta g(s)}}{\sum_{a'}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta g(s)}}{e^{\beta g(s)} + \sum_{a' \neq a_1(s)}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta g(s)}}{e^{\beta g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
+\end{align}
+Combining Eq. \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:
+\begin{align*}
+\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2R_{max}}{1-\gamma}\abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
+\end{align*}
+Taking the norm and plugging this into Eq. \eqref{eq:mm1} concludes the proof.
+\end{proof}
+
 \end{document}

### 2018-05-07 NIPS 2018/main.tex
Added new results to the paper

@@
 
-\section{Background}
+\section{Preliminaries}
 
@@
 Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}).
-Let $\nu$ be a probability measure over the state-space and $p \geq 1$.
-Then:
+Let $\nu$ be a probability measure over the state-space.
+Then, for any $p \geq 1$:
 \begin{equation}
-\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{1-\gamma}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
+\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{(1-\gamma)^2}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
 \end{equation}
@@
 
-\section{Proofs of Theorems}
+\section{Proofs}
 
@@
 
+\begin{lemma}
+Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
+Assume $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$.
+Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
+\begin{equation}
+\norm{Q - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\end{equation}
+\end{lemma}
+\begin{proof}
+First notice that:
+\begin{align*}
+\norm{Q - Q^*} =\ & \norm{Q + TQ - TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \norm{TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \gamma\norm{Q - Q^*}\\ =\ & \norm{B(Q)} + \gamma\norm{Q - Q^*}
+\end{align*}
+which implies that:
+\begin{align*}
+\norm{Q - Q^*} \leq\ \frac{1}{1-\gamma}\norm{B(Q)}
+\end{align*}
+Then we can write:
+\begin{align*}
+P\left( \norm{Q - Q^*} > \epsilon \right) \leq P\left(\norm{B(Q)} > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
+\end{align*}
+Settings the right-hand side equal to $\delta$ and solving for $\epsilon$ concludes the proof.
+\end{proof}
+
+\begin{corollary}
+Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
+Assume $\wt{Q}$ is the unique fixed-point of the mellow Bellman operator $\wt{T}$.
+Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
+\begin{equation}
+\norm{Q - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\end{equation}
+\end{corollary}
+
+\begin{lemma}\label{lemma:l2}
+Assume $Q$-functions belong to a parametric space of functions bounded by $\frac{R_{max}}{1-\gamma}$.
+Let $p$ and $q$ be arbitrary distributions over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
+Consider a dataset $D$ of $N$ samples and define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
+\begin{equation}\label{eq:lemma2-1}
+\mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_q\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{equation}
+\begin{equation}\label{eq:lemma2-2}
+\mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_q\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{equation}
+\end{lemma}
+\begin{proof}
+From Hoeffding's inequality we have:
+\begin{align*}
+P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] - \norm{B(\bm{w})}_D^2} > \epsilon \right) \leq 2exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
+\end{align*}
+which implies that, for any $\delta>0$, with probability at least $1-\delta$:
+\begin{align*}
+\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] - \norm{B(\bm{w})}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+Under independence assumptions, the expected TD error can be re-written as:
+\begin{align*}
+\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[b(\bm{w})^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right] + \mathbb{E}_{\mathcal{P}}\left[b(\bm{w})\right]^2\right]\\ =\ & v(\bm{w}) + \norm{B(\bm{w})}_{\nu}^2
+\end{align*}
+where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$. Thus:
+\begin{align}\label{eq:hoeff}
+\abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align}
+From the change of measure inequality \cite{}\todo{Find a reference for this}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
+\begin{align*}
+\log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \geq \mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p)
+\end{align*}
+Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2}$, we obtain:
+\begin{align*}
+\mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p) \leq \log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \leq 4\frac{R_{max}^2 \lambda^{-1}N}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+where the second inequality holds since the right-hand side of \eqref{eq:hoeff} does not depend on $\bm{w}$. Finally, we can explicitly write:
+\begin{align*}
+\mathbb{E}_q\left[ \abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+from which the lemma follows straightforwardly.
+\end{proof}
+
+\begin{lemma}
+Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
+Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
+Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, for any $\delta > 0$, with probability at least $1-\delta$:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align*}
+\end{lemma}
+\begin{proof}
+Let us use Lemma \ref{lemma:l2} for the specific choice $q=q_{\wh{\xi}}$. From Eq. \eqref{eq:lemma2-1}, we have:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+where the second inequality holds since $v(\bm{w}) > 0$, while the equality holds from the definition of $\wh{\xi}$.
+We can now use Eq.
+\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right]$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align*}
+This concludes the proof.
+\end{proof}
+
 \end{document}

### 2018-05-08 scripts/run_gvt_cartpole.py
change defaults

@@ -21,8 +21,8 @@ parser = argparse.ArgumentParser()
 parser.add_argument("--kappa", default=100.)
 parser.add_argument("--xi", default=0.5)
 parser.add_argument("--tau", default=0.0)
-parser.add_argument("--batch_size", default=50)
-parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--batch_size", default=500)
+parser.add_argument("--max_iter", default=10000)
 parser.add_argument("--buffer_size", default=10000)
 parser.add_argument("--random_episodes", default=0)
 parser.add_argument("--train_freq", default=1)
@@ -32,10 +32,10 @@ parser.add_argument("--l1", default=32)
 parser.add_argument("--l2", default=0)
 parser.add_argument("--alpha_adam", default=0.001)
 parser.add_argument("--alpha_sgd", default=0.0001)
-parser.add_argument("--lambda_", default=0.0001)
+parser.add_argument("--lambda_", default=0.00001)
 parser.add_argument("--time_coherent", default=False)
-parser.add_argument("--n_weights", default=5)
-parser.add_argument("--n_source", default=5)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
 parser.add_argument("--sigma_reg", default=0.0001)
 parser.add_argument("--cholesky_clip", default=0.0001)
 # Cartpole parameters (default = randomize

### 2018-05-08 scripts/run_mgvt_cartpole.py

@@ -3,8 +3,6 @@ import sys
 sys.path.append("../")
 
 import numpy as np
-from features.agrbf import build_features_gw_state
-from features.identity import Identity
 from envs.cartpole import CartPoleEnv
 from approximators.mlp_torch import MLPQFunction
 from operators.mellow_torch import MellowBellmanOperator
@@ -23,16 +21,16 @@ parser = argparse.ArgumentParser()
 parser.add_argument("--kappa", default=100.)
 parser.add_argument("--xi", default=0.5)
 parser.add_argument("--tau", default=0.0)
-parser.add_argument("--batch_size", default=50)
+parser.add_argument("--batch_size", default=500)
 parser.add_argument("--max_iter", default=10000)
 parser.add_argument("--buffer_size", default=10000)
 parser.add_argument("--random_episodes", default=0)
 parser.add_argument("--train_freq", default=1)
 parser.add_argument("--eval_freq", default=100)
 parser.add_argument("--mean_episodes", default=50)
-parser.add_argument("--alpha_adam", default=0.005)
+parser.add_argument("--alpha_adam", default=0.001)
 parser.add_argument("--alpha_sgd", default=0.0001)
-parser.add_argument("--lambda_", default=0.000001)
+parser.add_argument("--lambda_", default=0.00001)
 parser.add_argument("--time_coherent", default=False)
 parser.add_argument("--n_weights", default=10)
 parser.add_argument("--n_source", default=10)
@@ -47,7 +45,7 @@ parser.add_argument("--n_jobs", default=1)
 parser.add_argument("--n_runs", default=1)
 parser.add_argument("--file_name", default="mgvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
 parser.add_argument("--source_file", default="source_tasks/")
-parser.add_argument("--eta", default=1e-5)  # learning rate for
+parser.add_argument("--eta", default=1e-6)  # learning rate for
 parser.add_argument("--eps", default=0.001)  # precision for the initial posterior approximation and upperbound tighting
 parser.add_argument("--bandwidth", default=.00001)  # Bandwidth for the Kernel Estimator
 parser.add_argument("--post_components", default=1)  # number of components of the posterior family
@@ -143,6 +141,7 @@ def run(mdp, seed=None):
 
[…]

### 2018-05-08 scripts/run_gvt_maze.py
added gvt script for maze

@@ -1,0 +1,149 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.emaze import Maze
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.gvt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+from random import shuffle
+
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--render", default=False)
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=32)
+parser.add_argument("--max_iter", default=300000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=100)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+
+parser.add_argument("--maze", default=-1)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=32)
+parser.add_argument("--file_name", default="nt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--mazes_file", default="../scripts/mazes10")
+
+#GVT parameters
+parser.add_argument("--alpha_adam", default=0.01)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.0001)
+parser.add_argument("--n_weights", default=20)
+parser.add_argument("--n_source", default=5)
+parser.add_argument("--sigma_reg", default=0.0001)
+parser.add_argument("--cholesky_clip", default=0.0001)
+parser.add_argument("--source_file", default="source_tasks/cartpole_100s_32nn")
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
+xi = float(args.xi)
+tau = float(args.tau)
+batch_size = int(args.batch_size)
+max_iter = int(args.max_iter)
+buffer_size = int(args.buffer_size)
[…]

### 2018-05-08 NIPS 2018/main.tex

@@
 Notice that $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
-Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\mu$, $\mathbb{E}_{\mu}\left[ B^2(Q) \right]$.
+Furthermore, if we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, the squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\nu$, $\norm{B(Q)}_{\nu}^2=\mathbb{E}_{\mu}\left[ B^2(Q) \right]$.
 Although minimizing the empirical Bellman error is an appealing objective, it is well-known that an unbiased estimator requires two independent samples of the next state $s'$ of each $s,a$ (e.g., \cite{} \todo{cite Maillard}).
 In practice, the empirical Bellman error is typically replaced by the TD error, which approximates the former using a single transition sample.
-Given a dataset of $N$ samples, the TD error is computed as $\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.
+Given a dataset of $N$ samples, the TD error is computed as $\norm{B(Q)}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.
 

### 2018-05-08 NIPS 2018/main.tex
Updates

@@
 
-\subsection{Algorithm}
+In this section, we describe our variational approach to transfer in RL.
+In Section \ref{sec:alg}, we start by introducing our algorithm from a high-level perspective, in such a way that it can be used for any choice of prior and posterior distributions.
+Then, in Sections \ref{sec:gvt} and \ref{sec:mgvt}, we propose practical implementations based on Gaussian prior/posterior and mixture of Gaussian prior/posterior, respectively.
 
-\subsection{Gaussian Variational Transfer}
+\subsection{Algorithm}\label{sec:alg}
 
-\subsection{Mixture of Gaussian Variational Transfer}
+We begin with a simple consideration: the distribution $\mathcal{D}$ over tasks clearly induces a distribution over optimal $Q$-functions.
+Since, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
+Furthermore, assume we know such distribution and we are given a new task $\tau$ to solve.
+Then, our main intuition is that it is possible to design an algorithm that efficiently explores $\tau$ so as to quickly adapt the prior distribution in a Bayesian fashion to put all probability mass over the optimal $Q$-function of $\tau$.
+
+We consider a parametric family of $Q$-functions $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$.
+For simplicity, we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$\footnote{In practice, this is easily achieved by truncation.}.
+Then, we can reduce our prior distribution over $Q$-functions to a prior distribution over weights $p(\bm{w})$.
+Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ we want to solve.
+Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as in Eq.
+\ref{eq:bayes}.
+Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$.
+In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get a tractable posterior \cite{}\todo{Cite somebody}.
+On the other hand, we take a PAC-Bayesian approach to derive a more general and meaningful posterior form.
+Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$.
+Then, given a prior $p(\bm{w})$ we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
+\begin{equation}
+q(\bm{w}) = \frac{e^{-\Lambda\norm{B(\bm{w})}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B(\bm{w}')}_D^2}p(d\bm{w}')}
+\end{equation}
+for some parameter $\Lambda > 0$.
+Since $\Lambda$ is typically chosen to increase with the number of samples $N$, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
+Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood, $q$ becomes a classic Bayesian posterior.
+Unfortunately, the integral at the denominator of $q$ is still intractable to compute even for simple $Q$-function models.
+Thus, we propose a variational approximation $q_{\xi}$ in a simpler family of distributions parameterized by $\xi \in \Xi$.
+Then, our problem reduces to finding the variational parameters $\xi$ such that $q_{\xi}$ minimizes the KL divergence w.r.t.
+$q$:
+\begin{align} \label{eq:elbo}
+\min_{\bm{\xi}\in\Xi} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ q(\bm{w})\right) = \min_{\bm{\xi}\in\Xi}\mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
+\end{align}
+where the last objective is the well-knwon \textit{evidence lower bound} (ELBO) \cite{}\todo{Cite}.
+Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term).
+Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t.
+the variational parameters, our objective can be easily optimized with any stochastic optimization algorithm.
+Notice, however, that differentiating w.r.t.
+$\bm{\xi}$ typically requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t.
+$\bm{w}$ (e.g., when using the reparameterization trick \cite{}\todo{Cite Deepmind}).
+Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
+In iterative approaches (e.g., DQNs), this is typically solved by keeping the targets fixed at each iteration, thus without differentiating them.
+However, our algorithm ...
+\todo{Find good motivation}.
+To solve this issue, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
+\begin{equation}
+\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
+\end{equation}
+where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
+The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
+Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
+the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
+
+\subsection{Gaussian Variational Transfer}\label{sec:gvt}
+
+\subsection{Mixture of Gaussian Variational Transfer}\label{sec:mgvt}
 

### 2018-05-08 algorithms/gvt.py
added sources argument to mgvt, gvt. Scripts for maze experiments

@@ -91,7 +91,8 @@ def learn(mdp,
           source_file=None,
           seed=None,
           render=False,
-          verbose=True):
+          verbose=True,
+          sources=None):
 
     if seed is not None:
         np.random.seed(seed)
@@ -107,7 +108,7 @@ def learn(mdp,
     K = Q._w.size
 
     # Load weights and construct prior distribution
-    weights = utils.load_object(source_file)
+    weights = utils.load_object(source_file) if sources is None else sources
     ws = np.array([w[1] for w in weights])
     np.random.shuffle(ws)
     # Take only the first n_source weights
@@ -117,7 +118,7 @@ def learn(mdp,
     # We use higher regularization for the prior to prevent the ELBO from diverging
     Sigma_bar_inv = np.linalg.inv(Sigma_bar + np.eye(K) * sigma_reg)
     # We initialize the parameters at the prior with smaller regularization (just to make sure Sigma_bar is pd)
-    params = clip(pack(mu_bar, np.linalg.cholesky(Sigma_bar + np.eye(K) * cholesky_clip)), cholesky_clip, K)
+    params = clip(pack(mu_bar, np.linalg.cholesky(Sigma_bar + np.eye(K) * cholesky_clip**2)), cholesky_clip, K)
 
     # Add random episodes if needed
     if random_episodes > 0:
@@ -158,6 +159,9 @@ def learn(mdp,
     v_t = 0
     t = 0
 
+    # RMSprop for Variance
+    v_t_var = 0.
+
     # Init env
     s = mdp.reset()
     h = 0
@@ -187,6 +191,7 @@ def learn(mdp,
             params, t, m_t, v_t = utils.adam(params, g, t, m_t, v_t, alpha=adam_mask)
             # Take a gradient step for L
             params = utils.sgd(params, g, alpha=sgd_mask)
+            # params,v_t_var = utils.rmsprop(params, g, v_t_var, alpha=sgd_mask)
             # Clip parameters
             params = clip(params, cholesky_clip, K)
 

### 2018-05-08 algorithms/mgvt_torch.py

@@ -253,7 +253,8 @@ def learn(mdp,
           seed=None,
           render=False,
           verbose=True,
-          ukl_tight_freq=1):
+          ukl_tight_freq=1,
+          sources=None):
 
     if seed is not None:
         np.random.seed(seed)
@@ -280,7 +281,7 @@ def learn(mdp,
     C = post_components
 
     # Load weights and construct prior distribution
-    weights = utils.load_object(source_file)
+    weights = utils.load_object(source_file) if sources is None else sources
     ws = np.array([w[1] for w in weights])
     np.random.shuffle(ws)
     # Take only the first n_source weights

### 2018-05-08 scripts/run_mgvt_maze.py

@@ -1,0 +1,165 @@
+import sys
+
+sys.path.append("../")
+
+import numpy as np
+from envs.emaze import Maze
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.mgvt_torch import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+import numpy as np
+
+from random import shuffle
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=500)
+parser.add_argument("--max_iter", default=10000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.00001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Door at -1 means random positions over all runs
+parser.add_argument("--maze", default=-1)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=32)
+parser.add_argument("--mazes_file", default="../scripts/mazes10")
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="mgvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="../scripts/mazes10x10_ns20_32x32nn_uniqueInit")
+parser.add_argument("--eta", default=1e-6)  # learning rate for
+parser.add_argument("--eps", default=0.001)  # precision for the initial posterior approximation and upperbound tighting
[…]

### 2018-05-08 scripts/run_gvt_maze.py
scripts for maze transfer

@@ -23,8 +23,8 @@ parser.add_argument("--render", default=False)
 parser.add_argument("--kappa", default=100.)
 parser.add_argument("--xi", default=0.5)
 parser.add_argument("--tau", default=0.0)
-parser.add_argument("--batch_size", default=32)
-parser.add_argument("--max_iter", default=300000)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=20000)
 parser.add_argument("--buffer_size", default=50000)
 parser.add_argument("--random_episodes", default=0)
 parser.add_argument("--train_freq", default=1)
@@ -36,7 +36,7 @@ parser.add_argument("--n_runs", default=1)
 parser.add_argument("--maze", default=-1)
 parser.add_argument("--l1", default=32)
 parser.add_argument("--l2", default=32)
-parser.add_argument("--file_name", default="nt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
 parser.add_argument("--mazes_file", default="../scripts/mazes10")
 
 #GVT parameters
@@ -47,7 +47,8 @@ parser.add_argument("--n_weights", default=20)
 parser.add_argument("--n_source", default=5)
 parser.add_argument("--sigma_reg", default=0.0001)
 parser.add_argument("--cholesky_clip", default=0.0001)
-parser.add_argument("--source_file", default="source_tasks/cartpole_100s_32nn")
+parser.add_argument("--source_file", default="../scripts/mazes10x10_ns20_32x32nn_uniqueInit")
+parser.add_argument("--time_coherent", default=False)
 
 # Read arguments
 args = parser.parse_args()
@@ -77,25 +78,30 @@ lambda_ = float(args.lambda_)
 n_weights = int(args.n_weights)
 sigma_reg = float(args.sigma_reg)
 cholesky_clip = float(args.cholesky_clip)
-parser.add_argument("--time_coherent", default=False)
-parser.add_argument("--n_source", default=5)
 n_source = int(args.n_source)
 source_file = str(args.source_file)
 time_coherent = bool(args.time_coherent)
+
 
 # Generate tasks
 
 np.random.seed(485)
 
 mazes = utils.load_object(mazes_file)
[…]

### 2018-05-08 scripts/run_mgvt_maze.py

@@ -24,8 +24,8 @@ parser = argparse.ArgumentParser()
 parser.add_argument("--kappa", default=100.)
 parser.add_argument("--xi", default=0.5)
 parser.add_argument("--tau", default=0.0)
-parser.add_argument("--batch_size", default=500)
-parser.add_argument("--max_iter", default=10000)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=20000)
 parser.add_argument("--buffer_size", default=10000)
 parser.add_argument("--random_episodes", default=0)
 parser.add_argument("--train_freq", default=1)

### 2018-05-08 algorithms/gvt_torch.py
fix bug. implemented KL gradient in gvt usint torch. change run_gvt_maze to use torch gvt

@@ -1,0 +1,292 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from policies import EpsilonGreedy
+from approximators.mlp_torch import MLPQFunction
+from buffer import Buffer
+import utils
+import time
+import torch
+
+
+prior_eigen_torch = None
+
+def unpack(params, K):
+    """Unpacks a parameter vector into mu and L"""
+    mu = params[:K]
+    L = params[K:].reshape(K,K)
+    return mu, L
+
+
+def pack(mu, L):
+    """Packs mu and L into a parameter vector"""
+    return np.concatenate((mu, L.flatten()))
+
+
+def clip(params, cholesky_clip, K):
+    """Makes sure the Cholensky factor L is well-defined"""
+    mu, L = unpack(params, K)
+    # Clip the diagonal to 0.01
+    mask = np.logical_and(L < cholesky_clip, np.eye(K, dtype=bool))
+    L[mask] = cholesky_clip
+    # Make sure L is lower triangular
+    L[np.triu_indices(K, 1)] = 0
+    return pack(mu, L)
+
+
+def sample_posterior(params, K):
+    """Samples a Q function from the posterior distribution"""
+    mu, L = unpack(params, K)
+    return np.dot(L, np.random.randn(K,)) + mu
+
+
+def objective(samples, params, Q, mu_bar, Sigma_bar_inv, operator, n_samples, lambda_, n_weights):
+    """Computes the negative ELBO"""
+    mu, L = unpack(params, Q._w.size)
+    # We add a small constant to make sure Sigma is always positive definite
+    Sigma = np.dot(L, L.T)
+    weights, _ = utils.sample_mvn(n_weights, mu, L)
+    likelihood = operator.expected_bellman_error(Q, samples, weights)
+    assert likelihood >= 0
+    kl = utils.KL(mu, Sigma, mu_bar, Sigma_bar_inv)
+    assert kl >= 0
+    return likelihood + lambda_ * kl / n_samples
+
+
+def normal_KL3(mu, Sigma, mu_bar, Sigma_bar, L=None, precision=None):
+    """ Computes the KL between normals for two GMMs using pytorch tensors """
+    #mu, sigma, L must be torch tensors
+    global prior_eigen_torch
+    Sigma_bar_inv = np.linalg.inv(Sigma_bar) if precision is None else precision
+    inv_b = torch.from_numpy(Sigma_bar_inv)
[…]

### 2018-05-08 algorithms/mgvt_torch.py

@@ -76,7 +76,7 @@ def normal_KL3(c, mu, Sigma, c_bar, mu_bar, Sigma_bar, L=None, precision=None):
     Sigma_bar_inv = np.linalg.inv(Sigma_bar) if precision is None else precision
     inv_b = torch.from_numpy(Sigma_bar_inv[np.newaxis])
     if prior_eigen is None:
-        prior_eigen_torch, _ = torch.from_numpy(np.linalg.eig(Sigma_bar[np.newaxis]))
+        prior_eigen_torch = torch.from_numpy(np.real(np.linalg.eig(Sigma_bar[np.newaxis])[0]))
     else:
         prior_eigen_torch = torch.from_numpy(prior_eigen)
 

### 2018-05-08 scripts/run_gvt_maze.py

@@ -5,7 +5,7 @@ import numpy as np
 from envs.emaze import Maze
 from approximators.mlp_torch import MLPQFunction
 from operators.mellow_torch import MellowBellmanOperator
-from algorithms.gvt import learn
+from algorithms.gvt_torch import learn
 import utils
 import argparse
 from joblib import Parallel, delayed
@@ -40,10 +40,10 @@ parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now
 parser.add_argument("--mazes_file", default="../scripts/mazes10")
 
 #GVT parameters
-parser.add_argument("--alpha_adam", default=0.01)
+parser.add_argument("--alpha_adam", default=0.001)
 parser.add_argument("--alpha_sgd", default=0.0001)
 parser.add_argument("--lambda_", default=0.0001)
-parser.add_argument("--n_weights", default=20)
+parser.add_argument("--n_weights", default=10)
 parser.add_argument("--n_source", default=5)
 parser.add_argument("--sigma_reg", default=0.0001)
 parser.add_argument("--cholesky_clip", default=0.0001)

### 2018-05-08 NIPS 2018/main.tex
Updates

@@
 Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
-In iterative approaches (e.g., DQNs), this is typically solved by keeping the targets fixed at each iteration, thus without differentiating them.
-However, our algorithm ...
-\todo{Find good motivation}.
-To solve this issue, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
+This rarely represents a problem since typical value-based algorithm are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}).
+However, in our case ...
+\todo[inline]{What is a good motivation for the fact that we need a residual algorithm?} To solve this issue, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
 \begin{equation}
@@
 the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
+\todo[inline]{Here we need to talk about residual algorithms and their improved gradient} We show our main algorithm in Alg.
+\ref{alg:transfer}.
+We start by estimating a prior distribution from the given set of source $Q$-functions (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
+such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters, however this does not always hold in practice.} (line 2).
+Then, at each time step of interaction, we re-sample the weights from the current approximate posterior and act greedily w.r.t.
+the corresponding $Q$-function (lines 7,8).
+This resembles the well-known Thompson sampling adopted in multi-armed bandits \cite{}\todo{Cite somebody} and allows our algorithm to efficiently explore the target task.
+In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
+After collecting and storing the new experience (lines 9-11), we draw a batch of samples from the replay buffer and a batch of weights from the posterior (line 12).
+We use these to approximate the ELBO, compute its gradient, and finally update the variational parameters (lines 13-15).
+
+The main advantage of our approach is that it exploits knowledge from the source tasks to perform an efficient adaptive exploration.
+Intuitively, during the first steps of interaction, our algorithm has no idea about what is the current task.
+However, it can rely on the learned prior to take early informed decisions.
+As the learning process goes on, it will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing TD error.
+From that point, sampling from the posterior is approximately equivalent to deterministically taking the best weights, and no more exploration will be performed.
+
+\begin{algorithm}
+\begin{algorithmic}
+\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch sizes $M_D$ and $M_{\mathcal{W}}$, prior weight $\lambda$
+\\\hrulefill
+
+\STATE{Estimate prior $p(\bm{w})$ from $\mathcal{W}_s$}
+\STATE{Initialize variational parameters: $\bm{\xi} \leftarrow \argmin_{\bm{\xi}} KL(q_{\bm{\xi}}||p)$}
+\STATE{Initialize replay buffer: $D = \emptyset$}
+\REPEAT
+
+\STATE{Sample initial state: $s_0 \sim p_0^{(\tau)}$}
+
+\WHILE{$s_h$ is not terminal}
+\STATE{Sample weights: $\bm{w} \sim q_{\bm{\xi}}(\bm{w})$}
+\STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$}
+\STATE{Collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
+\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
+\STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M_D}$ from $D$ and $\mathcal{W} = \left\{ \bm{w}_1, \bm{w}_2, \dots, \bm{w}_{M_{\mathcal{W}}} \right\}$ from $q_{\bm{\xi}}$}
+\STATE{Approximate ELBO: $\mathcal{L}(\bm{\xi}) = \frac{1}{M_{\mathcal{W}}}\sum_{\bm{w}\in\mathcal{W}}\norm{B(\bm{w})}_{D'}^2 - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}\ ||\ p\right)$}
+\STATE{Compute the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$}
+\STATE{Update $\bm{\xi}$ in the direction of $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using any stochastic optimizer (e.g., ADAM)}
+\ENDWHILE
+
+\UNTIL{forever}
+\end{algorithmic}
+\caption{Variational Transfer} \label{alg:transfer}
+\end{algorithm}
 

### 2018-05-09 NIPS 2018/main.tex
Updates

@@
 the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
-\todo[inline]{Here we need to talk about residual algorithms and their improved gradient} We show our main algorithm in Alg.
+\todo[inline]{Here we need to talk about residual algorithms and their improved gradient}
+
+Our main algorithm is shown in Alg.
 \ref{alg:transfer}.
@@
 the corresponding $Q$-function (lines 7,8).
-This resembles the well-known Thompson sampling adopted in multi-armed bandits \cite{}\todo{Cite somebody} and allows our algorithm to efficiently explore the target task.
+This resembles the well-known Thompson sampling adopted in multi-armed bandits \cite{}\todo{Cite} and allows our algorithm to efficiently explore the target task.
 In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
@@
 However, it can rely on the learned prior to take early informed decisions.
-As the learning process goes on, it will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing TD error.
+As the learning process goes on, it will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
 From that point, sampling from the posterior is approximately equivalent to deterministically taking the best weights, and no more exploration will be performed.
@@
 \begin{algorithm}
-\begin{algorithmic}
+\begin{algorithmic}[1]
 \REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch sizes $M_D$ and $M_{\mathcal{W}}$, prior weight $\lambda$
@@
 \STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
-\STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M_D}$ from $D$ and $\mathcal{W} = \left\{ \bm{w}_1, \bm{w}_2, \dots, \bm{w}_{M_{\mathcal{W}}} \right\}$ from $q_{\bm{\xi}}$}
+\STATE{Sample batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M_D}$ from $D$ and $\mathcal{W} = \left\{ \bm{w}_1, \bm{w}_2, \dots, \bm{w}_{M_{\mathcal{W}}} \right\}$ from $q_{\bm{\xi}}$}
 \STATE{Approximate ELBO: $\mathcal{L}(\bm{\xi}) = \frac{1}{M_{\mathcal{W}}}\sum_{\bm{w}\in\mathcal{W}}\norm{B(\bm{w})}_{D'}^2 - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}\ ||\ p\right)$}
@@
 
+We now restrict ourselves to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement.
+We assume that optimal $Q$-functions according to our task distribution (or better, their weights) follow a multivariate Gaussian law.
+That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using, e.g., maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
+Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$.
+To prevent the covariance from going not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $L$ instead.
+Under Gaussian distributions, all quantity of interest for using Alg.
+\ref{alg:transfer} can be computed very easily.
+The KL divergence between the prior and approximate posterior can be computed in closed-form as:
+\begin{equation}
+KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
+\end{equation}
+for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are \cite{}\todo{Cite matrix cookboox}:
+\begin{equation}
+\nabla_{\bm{\mu}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p)
+\end{equation}
+\begin{equation}
+\nabla_{\bm{L}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1}\bm{L} - (\bm{L}^{-1})^T
+\end{equation}
+Finally, the gradients w.r.t.
+the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{}\todo{Cite deepmind and another}):
+\begin{equation}
+\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\end{equation}
+\begin{equation}
+\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\end{equation}
+
 \subsection{Mixture of Gaussian Variational Transfer}\label{sec:mgvt}
+
+Although the Gaussian assumption of the previous section is very appealing as it allows for a simple and efficient way of computing the variational objective and its gradients, we believe that such assumption almost never holds in practice.
+In fact, even for families of tasks in which the reward and transition models follow a Gaussian law, the $Q$-values might be far from it.
 

### 2018-05-09 NIPS 2018/main.tex
Updatrs

@@
 \end{align}
-where the last objective is the well-knwon \textit{evidence lower bound} (ELBO) \cite{}\todo{Cite}.
+where the last objective is the well-known (negative) \textit{evidence lower bound} (ELBO) \cite{}\todo{Cite}.
 Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term).
@@
 In fact, even for families of tasks in which the reward and transition models follow a Gaussian law, the $Q$-values might be far from it.
+Depending on the family of tasks under consideration and, since we are learning a distribution over weights, on the chosen function approximator, the prior might have arbitrarily complex shapes.
+When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely too fail at transferring knowledge, thus reducing to almost random exploration.
+We now propose a variant to successfully solve this problem, while keeping the algorithm simple and efficient enough to be applied in practice.
+In order to capture arbitrarily complex distributions, we use a kernel estimator \cite{}\todo{} for learning our prior.
+Assume we are given a set $\mathcal{W}_s$ of weights from the source tasks.
+Then, our estimated prior places a single isotropic Gaussian over each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$\footnote{Notice that this is slightly different than the typical kernel estimator (e.g., \cite{})}.
+This takes the form of a mixture of Gaussians with equally weighted components.
+Consistently with the prior, we model our approximate posterior as a mixture of Gaussians.
+However, we allow a different number of components (typically much less than the prior's) and we adopt full covariances instead of only diagonals, so that our posterior has the potential to match complex distributions with less components.
+Using $C$ components, our posterior is $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$, with variational parameters $\bm{\xi} = (\bm{\mu}_1,\dots,\bm{\mu}_C,\bm{\Sigma}_1,\dots,\bm{\Sigma}_C)$.
+Once again, we learn Cholesky factors instead of full covariances.
+
+Although this new model has the potential to capture much more complex distributions, it poses a major complication: the KL divergence between two mixture of Gaussians is well-known to have no closed-form equation.
+To solve this issue, we can rely on an upper bound to such quantity, so that negative ELBO we are optimizing still represents an upper bound on the KL between the approximate and true posterior.
+However, this turns out to be non-trivial as well.
+In fact, it is very easy to bound the KL between two mixtures with the KLs between each couple of components.
+However, the loss of information is such that minimizing the upper bound via gradient methods converges to a local optimum in which all components tend to go to the same point, thus almost reducing to the single Gaussian case.
+To solve this issue, we adopt the variational upper bound proposed in \cite{}\todo{Cite UB}, which we found to be able to preserve the needed information.
+We report it here for the sake of completeness.
+See the original paper for the proof.
+\begin{theorem}
+Let $p = \sum_{i} c_i^{(p)} f_i^{(p)}$ and $q = \sum_{j} c_j^{(q)} f_j^{(q)}$ be two mixture of Gaussian distributions, where $f_i^{(p)} = \mathcal{N}(\bm{\mu}_i^{(p)},\bm{\Sigma}_i^{(p)})$ denotes the i-th component of $p$, $c_i^{(p)}$ denotes its weight, and similarly for $q$.
+Introduce two vectors $\chi^{(1)}$ and $\chi^{(2)}$ such that $c_i^{(p)} = \sum_j \chi^{(2)}_{j,i}$ and $c_j^{(q)} = \sum_i \chi^{(1)}_{i,j}$.
+Then:
+\begin{equation}
+KL(p||q) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{i,j} \chi^{(2)}_{j,i}KL(f_i^{(p)}||f_j^{(q)})
+\end{equation}
+%\begin{equation}
+%\chi^{(2)}_{i,j} = \frac{c_j^{(q)}\chi^{(1)}_{j,i}}{\sum_{i'} \chi^{(1)}%_{j,i'}},\ \ \ \ \chi^{(1)}_{j,i} = \frac{c_i^{(p)}\chi^{(2)}_{i,j}e^{-%KL(f_i^{(p)}||f_j^{(q)})}}{\sum_{j'}\chi^{(2)}_{i,j'}e^{-KL(f_i^{(p)}||f_{j'}%^{(q)})}}
+%\end{equation}
+\end{theorem}
+Our new algorithm replaces the KL with the above-mentioned upper bound.
+Each time we require its value, we have to recompute the parameters $\chi^{(1)}$ and $\chi^{(2)}$ that tighten the bound.
+As shown in \cite{}\todo{cite them again}, this can be achieved by a simple fixed-point procedure.
+Furthermore, both terms in the approximate negative ELBO are now linear combinations of functions of the variational parameters for different components, thus their gradients can be straightforwardly derived from the ones of the Gaussian case.
 

### 2018-05-09 scripts/run_gvt_maze.py
added possibility to run a maze many runs with a source set that does not contain it

@@ -101,7 +101,9 @@ if maze == -1:
         envs.append(mdps[i % len(mdps)])
         sources.append([w for w in weights if not np.array_equal(w[0][-1], envs[-1].walls) and not np.array_equal(w[0][-2], envs[-1])])
 else:
-    mdps = [mdps[maze] for i in range(n_runs)]
+    envs = [mdps[maze] for i in range(n_runs)]
+    sources = [w for w in weights if not np.array_equal(w[0][-1], envs[-1].walls) and not np.array_equal(w[0][-2], envs[-1])]
+    sources = [sources for i in range(n_runs)]
 
 state_dim = mdps[0].state_dim
 action_dim = 1

### 2018-05-09 scripts/run_mgvt_maze.py

@@ -107,7 +107,10 @@ if maze == -1:
         envs.append(mdps[i % len(mdps)])
         sources.append([w for w in weights if not np.array_equal(w[0][-1], envs[-1].walls) and not np.array_equal(w[0][-2], envs[-1].goal)])
 else:
-    mdps = [mdps[maze] for i in range(n_runs)]
+    envs = [mdps[maze] for i in range(n_runs)]
+    sources = [w for w in weights if
+               not np.array_equal(w[0][-1], envs[-1].walls) and not np.array_equal(w[0][-2], envs[-1])]
+    sources = [sources for i in range(n_runs)]
 
 state_dim = mdps[0].state_dim
 action_dim = 1

### 2018-05-09 NIPS 2018/main.tex
Updates

@@
 
-\subsection{Markov Decision Processes}
-
 We define a Markov decision process (MDP) as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
@@
 
-\subsection{Variational Inference}
-
-When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
-\begin{equation}\label{eq:bayes}
-p(\bm{w} | D) = \frac{p(D | \bm{w})p(\bm{w})}{p(D)} = \frac{p(D | \bm{w})p(\bm{w})}{\int_{\bm{w}} p(D | \bm{w})p(\bm{w})},
-\end{equation}
-is typically intractable for many models of interest (e.g., when working with deep neural networks) due to difficulties in computing the integral of Eq.
+%\subsection{Variational Inference}
+%
+%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
+%\begin{equation}\label{eq:bayes}
+%p(\bm{w} | D) = \frac{p(D | \bm{w})p(\bm{w})}{p(D)} = \frac{p(D | \bm{w})p(\bm{w})}{\int_{\bm{w}} p(D | \bm{w})p(\bm{w})},
+%\end{equation}
+%is typically intractable for many models of interest (e.g., when working with deep neural networks) due to difficulties in computing the integral of Eq.
 \eqref{eq:bayes}.
@@
 $p$:
-\begin{equation}
-\min_{\bm{\xi}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w} \mid D)\right)
-\end{equation}
-It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
-\begin{equation}
-\text{ELBO}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[ \log p(D | \bm{w}) \right] - KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
-\end{equation}
-Intuitively, the best approximation is the one that maximizes the expected log-likelihood of the data, while minimizing the KL divergenge w.r.t. the prior $p(\bm{w})$.
+%\begin{equation}
+%\min_{\bm{\xi}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w} \mid D)\right)
+%\end{equation}
+%It is well-known that minimizing the KL divergence is equivalent to maximizing the so-called \textit{evidence lower bound} (ELBO), which is defined as:
+%\begin{equation}
+%\text{ELBO}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[ \log p(D | \bm{w}) \right] - KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
+%\end{equation}
+%Intuitively, the best approximation is the one that maximizes the expected log-likelihood of the data, while minimizing the KL divergenge w.r.t. the prior $p(\bm{w})$.
 
@@
 Furthermore, assume we know such distribution and we are given a new task $\tau$ to solve.
-Then, our main intuition is that it is possible to design an algorithm that efficiently explores $\tau$ so as to quickly adapt the prior distribution in a Bayesian fashion to put all probability mass over the optimal $Q$-function of $\tau$.
+Our goal is to design an algorithm that efficiently explores $\tau$ so as to quickly adapt the prior distribution in a Bayesian fashion to put all probability mass over the optimal $Q$-function of $\tau$.
 
-We consider a parametric family of $Q$-functions $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$.
+We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$.
 For simplicity, we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$\footnote{In practice, this is easily achieved by truncation.}.
 Then, we can reduce our prior distribution over $Q$-functions to a prior distribution over weights $p(\bm{w})$.
-Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ we want to solve.
-Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as in Eq.
-\ref{eq:bayes}.
+Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
+Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$.
 Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$.
-In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get a tractable posterior \cite{}\todo{Cite somebody}.
-On the other hand, we take a PAC-Bayesian approach to derive a more general and meaningful posterior form.
+In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors \cite{}\todo{Cite somebody}.
+However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability of the approach.
+Thus, we take a different approach to derive a more general and meaningful solution.
 Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$.
-Then, given a prior $p(\bm{w})$ we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
-\begin{equation}
+Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
+\begin{equation}\label{eq:gibbs}
 q(\bm{w}) = \frac{e^{-\Lambda\norm{B(\bm{w})}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B(\bm{w}')}_D^2}p(d\bm{w}')}
@@
 for some parameter $\Lambda > 0$.
-Since $\Lambda$ is typically chosen to increase with the number of samples $N$, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
-Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood, $q$ becomes a classic Bayesian posterior.
-Unfortunately, the integral at the denominator of $q$ is still intractable to compute even for simple $Q$-function models.
-Thus, we propose a variational approximation $q_{\xi}$ in a simpler family of distributions parameterized by $\xi \in \Xi$.
-Then, our problem reduces to finding the variational parameters $\xi$ such that $q_{\xi}$ minimizes the KL divergence w.r.t.
-$q$:
+Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
+Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior.
+Although we now have an appealing distribution, the integral at the denominator of \eqref{eq:gibbs} is intractable to compute even for simple $Q$-function models.
+Thus, we propose a variational approximation $q_{\bm{\xi}}$ by considering a simpler family of distributions parameterized by $\bm{\xi} \in \Xi$.
+Then, our problem reduces to finding the variational parameters $\bm{\xi}$ such that $q_{\bm{\xi}}$ minimizes the Kullback-Leibler (KL) divergence w.r.t.
+the Gibbs posterior $q$.
+From the theory of variational inference (e.g., \cite{}\todo{cite}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
 \begin{align} \label{eq:elbo}
-\min_{\bm{\xi}\in\Xi} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ q(\bm{w})\right) = \min_{\bm{\xi}\in\Xi}\mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
+\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
 \end{align}
-where the last objective is the well-known (negative) \textit{evidence lower bound} (ELBO) \cite{}\todo{Cite}.
 Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term).
 Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t.
-the variational parameters, our objective can be easily optimized with any stochastic optimization algorithm.
-Notice, however, that differentiating w.r.t.
-$\bm{\xi}$ typically requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t.
-$\bm{w}$ (e.g., when using the reparameterization trick \cite{}\todo{Cite Deepmind}).
-Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
-This rarely represents a problem since typical value-based algorithm are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}).
-However, in our case ...
-\todo[inline]{What is a good motivation for the fact that we need a residual algorithm?} To solve this issue, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
-\begin{equation}
-\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
-\end{equation}
-where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
-The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
-Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
-the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
-\todo[inline]{Here we need to talk about residual algorithms and their improved gradient}
+the variational parameters $\bm{\xi}$, our objective can be easily optimized with any stochastic optimization algorithm.
 
-Our main algorithm is shown in Alg.
-\ref{alg:transfer}.
-We start by estimating a prior distribution from the given set of source $Q$-functions (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
+We now highlight our general transfer procedure in Alg.
+\ref{alg:transfer}, while deferring a description of practical implementations with specific choices for the distributions involved to the next two sections.
+Given a set of weights $\mathcal{W}_s$ from the source tasks, we start by estimating the prior distribution (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
 such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters, however this does not always hold in practice.} (line 2).
@@
 the corresponding $Q$-function (lines 7,8).
-This resembles the well-known Thompson sampling adopted in multi-armed bandits \cite{}\todo{Cite} and allows our algorithm to efficiently explore the target task.
+This resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{}\todo{Cite} and allows our algorithm to efficiently explore the target task.
 In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
 After collecting and storing the new experience (lines 9-11), we draw a batch of samples from the replay buffer and a batch of weights from the posterior (line 12).
-We use these to approximate the ELBO, compute its gradient, and finally update the variational parameters (lines 13-15).
+We use these to approximate the negative ELBO, compute its gradient, and finally update the variational parameters (lines 13-15).
 
@@
 As the learning process goes on, it will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
-From that point, sampling from the posterior is approximately equivalent to deterministically taking the best weights, and no more exploration will be performed.
+From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
+Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any function approximator for the $Q$-functions and any family for the pior and posterior distributions can be adopted.
+For the latter, we describe two practical choices in the next two sections.
 
-\begin{algorithm}
+\begin{algorithm}[t]
 \begin{algorithmic}[1]
@@
 \STATE{Sample batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M_D}$ from $D$ and $\mathcal{W} = \left\{ \bm{w}_1, \bm{w}_2, \dots, \bm{w}_{M_{\mathcal{W}}} \right\}$ from $q_{\bm{\xi}}$}
-\STATE{Approximate ELBO: $\mathcal{L}(\bm{\xi}) = \frac{1}{M_{\mathcal{W}}}\sum_{\bm{w}\in\mathcal{W}}\norm{B(\bm{w})}_{D'}^2 - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}\ ||\ p\right)$}
+\STATE{Approximate objective: $\mathcal{L}(\bm{\xi}) = \frac{1}{M_{\mathcal{W}}}\sum_{\bm{w}\in\mathcal{W}}\norm{B(\bm{w})}_{D'}^2 - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}\ ||\ p\right)$}
 \STATE{Compute the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$}
@@
 
-\section{Theoretical Analysis}
+\subsection{Optimizing the TD error}
+
+From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t.
+$\bm{\xi}$ requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t.
+$\bm{w}$.
+Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
+This rarely represents a problem since typical value-based algorithm are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}).
+However, in our case ...
+\todo[inline]{What is a good motivation for the fact that we need a residual algorithm?} To solve this issue, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
+\begin{equation}
+\mm_a Q_{\bm{w}}(s,a) = \frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_a e^{\kappa Q_{\bm{w}}(s,a)}
+\end{equation}
+where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
+We defer a theoretical analysis of the consequences of this approximation to Section \ref{sec:theory}.
+The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
+Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
+the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
+\todo[inline]{Here we need to talk about residual algorithms and how to improve their gradient}
+
+\section{Theoretical Analysis}\label{sec:theory}
 

### 2018-05-09 algorithms/gvt.py
logging the episode rewards

@@ -146,6 +146,7 @@ def learn(mdp,
     evaluation_rewards = []
     learning_rewards = []
     episode_rewards = [0.0]
+    episode_t = []
     l_2 = []
     l_inf = []
     fvals = []
@@ -206,6 +207,7 @@ def learn(mdp,
             s = mdp.reset()
             h = 0
             Q._w = sample_posterior(params, K)
+            episode_t.append(i)
 
         # Evaluate model
         if i % eval_freq == 0:
@@ -249,7 +251,7 @@ def learn(mdp,
                 print("Iter {} Episodes {} Rew(G) {} Rew(L) {} Fval {} L2 {} L_inf {} time {:.1f} s".format(
                     i, episodes[-1], rew, learning_rew, fval, l_2_err, l_inf_err, elapsed_time))
 
-    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals]
+    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals, episode_rewards[:len(episode_t)], episode_t]
     weights = np.array(mu)
 
     return [mdp.get_info(), weights, run_info]

### 2018-05-09 algorithms/gvt_torch.py

@@ -183,9 +183,11 @@ def learn(mdp,
     evaluation_rewards = []
     learning_rewards = []
     episode_rewards = [0.0]
+    episode_t = []
     l_2 = []
     l_inf = []
     fvals = []
+
 
     # Create masks for ADAM and SGD
     adam_mask = pack(np.ones(K) * alpha_adam, np.zeros((K,K)))  # ADAM learns only \mu
@@ -243,6 +245,7 @@ def learn(mdp,
             s = mdp.reset()
             h = 0
             Q._w = sample_posterior(params, K)
+            episode_t.append(i)
 
         # Evaluate model
         if i % eval_freq == 0:
@@ -286,7 +289,7 @@ def learn(mdp,
                 print("Iter {} Episodes {} Rew(G) {} Rew(L) {} Fval {} L2 {} L_inf {} time {:.1f} s".format(
                     i, episodes[-1], rew, learning_rew, fval, l_2_err, l_inf_err, elapsed_time))
 
-    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals]
+    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals, episode_rewards[:len(episode_t)], episode_t]
     weights = np.array(mu)
 
     return [mdp.get_info(), weights, run_info]

### 2018-05-09 algorithms/mgvt.py

@@ -294,6 +294,7 @@ def learn(mdp,
     l_2 = []
     l_inf = []
     fvals = []
+    episode_t = []
 
     # Create masks for ADAM and SGD
     adam_mask = pack(np.zeros(C), np.ones((C,K)) * alpha_adam, np.zeros((C,K,K)))  # ADAM learns only \mu
@@ -347,6 +348,7 @@ def learn(mdp,
             s = mdp.reset()
             h = 0
             Q._w = sample_posterior(params, C, K)
+            episode_t.append(i)
 
         # Evaluate model
         if i % eval_freq == 0:
@@ -394,7 +396,7 @@ def learn(mdp,
                 print("Iter {} Episodes {} Rew(G) {} Rew(L) {} Fval {} L2 {} L_inf {} time {:.1f} s".format(
                     i, episodes[-1], rew, learning_rew, fval, l_2_err, l_inf_err, elapsed_time))
 
-    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals]
+    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals, episode_rewards[:len(episode_t)], episode_t]
     weights = np.array(mu)
 
     return [mdp.get_info(), weights, run_info]

### 2018-05-09 algorithms/mgvt_torch.py

@@ -333,6 +333,7 @@ def learn(mdp,
     l_2 = []
     l_inf = []
     fvals = []
+    episode_t = []
 
     # Create masks for ADAM and SGD
     adam_mask = pack(np.zeros(C), np.ones((C,K)) * alpha_adam, np.zeros((C,K,K)))  # ADAM learns only \mu
@@ -387,6 +388,7 @@ def learn(mdp,
             s = mdp.reset()
             h = 0
             Q._w = sample_posterior(params, C, K)
+            episode_t.append(i)
 
         # Evaluate model
         if i % eval_freq == 0:
@@ -434,7 +436,7 @@ def learn(mdp,
                 print("Iter {} Episodes {} Rew(G) {} Rew(L) {} Fval {} L2 {} L_inf {} time {:.1f} s".format(
                     i, episodes[-1], rew, learning_rew, fval, l_2_err, l_inf_err, elapsed_time))
 
-    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals]
+    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, fvals, episode_rewards[:len(episode_t)], episode_t]
     weights = np.array(mu)
 
     return [mdp.get_info(), weights, run_info]

### 2018-05-09 algorithms/nt.py

@@ -33,7 +33,7 @@ def learn(mdp,
 
     # Randomly initialize the weights in case an MLP is used
     if isinstance(Q, MLPQFunction):
-        Q.init_weights()
+        # Q.init_weights()
         if isinstance(operator, DQNOperator):
             operator._q_target._w = Q._w
 
@@ -65,6 +65,7 @@ def learn(mdp,
     evaluation_rewards = []
     learning_rewards = []
     episode_rewards = [0.0]
+    episode_t = []
     l_2 = []
     l_inf = []
 
@@ -106,6 +107,7 @@ def learn(mdp,
             episode_rewards.append(0.0)
             s = mdp.reset()
             h = 0
+            episode_t.append(i)
 
         # Evaluate model
         if i % eval_freq == 0:
@@ -137,8 +139,11 @@ def learn(mdp,
             if verbose:
                 print("Iter {} Episodes {} Rew(G) {} Rew(L) {} L2 {} L_inf {} time {:.1f} s".format(
                     i, episodes[-1], rew, learning_rew, l_2_err, l_inf_err, elapsed_time))
+        # if np.mean(episode_rewards[-mean_episodes - 1:-1]) > -80:
+        #     render=True
 
-    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf]
+
+    run_info = [iterations, episodes, n_samples, learning_rewards, evaluation_rewards, l_2, l_inf, episode_rewards[:len(episode_t)], episode_t]
     weights = np.array(Q._w)
 
     return [mdp.get_info(), weights, run_info]

### 2018-05-09 utils.py
added clipping in adam and sgd

@@ -255,7 +255,7 @@ def softmax(a, tau, axis=-1):
     return num / np.sum(num, axis=axis, keepdims=True)
 
 
-def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1e-8):
+def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1e-8, clip=1000.):
     """
     Applies a gradient step to the given parameters based on ADAM update rule
     :param params: a numpy array of parameters
@@ -269,6 +269,10 @@ def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1
     :param eps: small constant
     :return: the updated parameters, iteration number, first order momentum, and second order momentum
     """
+
+    grad[grad > clip] = clip
+    grad[grad < clip] = clip
+
     t += 1
     m_t = beta_1 * m_t + (1 - beta_1) * grad
     v_t = beta_2 * v_t + (1 - beta_2) * grad ** 2
@@ -277,7 +281,9 @@ def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1
     return params - alpha * m_t_hat / (np.sqrt(v_t_hat) + eps), t, m_t, v_t
 
 
-def sgd(params, grad, alpha=0.001):
+def sgd(params, grad, alpha=0.001, clip=1000.):
+    grad[grad > clip] = clip
+    grad[grad < clip] = clip
     """Applies a gradient step to the given parameters based on SGD update rule"""
     return params - alpha * grad
 

### 2018-05-09 utils.py
clipping in grads of sgd, adam

@@ -255,7 +255,7 @@ def softmax(a, tau, axis=-1):
     return num / np.sum(num, axis=axis, keepdims=True)
 
 
-def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1e-8, clip=1000.):
+def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1e-8, clip=1e3):
     """
     Applies a gradient step to the given parameters based on ADAM update rule
     :param params: a numpy array of parameters
@@ -271,7 +271,7 @@ def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1
     """
 
     grad[grad > clip] = clip
-    grad[grad < clip] = clip
+    grad[grad < -clip] = -clip
 
     t += 1
     m_t = beta_1 * m_t + (1 - beta_1) * grad
@@ -281,9 +281,9 @@ def adam(params, grad, t, m_t, v_t, alpha=0.001, beta_1=0.9, beta_2=0.999, eps=1
     return params - alpha * m_t_hat / (np.sqrt(v_t_hat) + eps), t, m_t, v_t
 
 
-def sgd(params, grad, alpha=0.001, clip=1000.):
+def sgd(params, grad, alpha=0.001, clip=1e3):
     grad[grad > clip] = clip
-    grad[grad < clip] = clip
+    grad[grad < -clip] = -clip
     """Applies a gradient step to the given parameters based on SGD update rule"""
     return params - alpha * grad
 

### 2018-05-09 scripts/run_mgvt_maze.py
mean episodes default to 100

@@ -30,7 +30,7 @@ parser.add_argument("--buffer_size", default=10000)
 parser.add_argument("--random_episodes", default=0)
 parser.add_argument("--train_freq", default=1)
 parser.add_argument("--eval_freq", default=100)
-parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--mean_episodes", default=100)
 parser.add_argument("--alpha_adam", default=0.001)
 parser.add_argument("--alpha_sgd", default=0.0001)
 parser.add_argument("--lambda_", default=0.00001)

### 2018-05-09 NIPS 2018/main.tex
Edits

@@
 Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
-This rarely represents a problem since typical value-based algorithm are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}).
-However, in our case ...
-\todo[inline]{What is a good motivation for the fact that we need a residual algorithm?} To solve this issue, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
+This rarely represents a problem since typical value-based algorithms are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}).
+However, our transfer settings are rather different than common RL.
+In fact, our algorithm is likely to always start from $Q$-functions that are very close to the optimum, and the only thing that needs to be done is to adapt the weights in a direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the task that is being solved.
+Unfortunately, this property cannot be guaranteed for most semi-gradient algorithms.
+Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching the optimum, and require a lot of tuning and tricks to work well.
+This is obviously an undesirable property in our case, as we only aim at adapting already good solutions.
+Thus, we consider using a residual gradient algorithm (after \cite{}\todo{Baird}).
+In order to differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
 \begin{equation}
@@
 where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
-We defer a theoretical analysis of the consequences of this approximation to Section \ref{sec:theory}.
 The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
@@
 the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
-\todo[inline]{Here we need to talk about residual algorithms and how to improve their gradient}
+Although residual algorithms have the sought guaranteed convergence, they are typically much slower than their semi-gradient counterpart.
+This problem was addressed in \cite{}\todo{Baird again}, where the authors proposed a simple remedy consisting in projecting the gradient in a direction that sill guarantees convergence but is also closer to the one of the semi-gradient, thus achieving higher learning speed.
+This can be easily done by including a parameter $\psi\in[0,1]$ in the TD error gradient such that:
+\begin{equation}
+\nabla_{\bm{w}}\norm{\wt{B}(\bm{w})}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right)
+\end{equation}
+where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$.
+Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$).
+A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee converge).
+Since in our case we are likely to start from this latter point, we consider only higher values (e.g., above $0.5$).
 

### 2018-05-10 scripts/run_gvt_maze.py
bug fixed for 1-job runs

@@ -47,7 +47,7 @@ parser.add_argument("--n_weights", default=10)
 parser.add_argument("--n_source", default=5)
 parser.add_argument("--sigma_reg", default=0.0001)
 parser.add_argument("--cholesky_clip", default=0.0001)
-parser.add_argument("--source_file", default="../scripts/mazes10x10_ns20_32x32nn_uniqueInit")
+parser.add_argument("--source_file", default="source_tasks/mazes10x10_ns20_32x32nn_sources")
 parser.add_argument("--time_coherent", default=False)
 
 parser.add_argument("--fixed_seed", default=-1)
@@ -155,7 +155,7 @@ if fixed_seed < 0:
 else:
     seeds = [fixed_seed for _ in range(n_runs)]
 if n_jobs == 1:
-    results = [run(mdp,seed) for (mdp,seed,source) in zip(mdps,seeds,sources)]
+    results = [run(mdp,seed) for (mdp,seed,source) in zip(envs,seeds,sources)]
 elif n_jobs > 1:
     results = Parallel(n_jobs=n_jobs)(delayed(run)(mdp,seed,source) for (mdp,seed,source) in zip(envs,seeds,sources))
 

### 2018-05-10 scripts/run_mgvt_maze.py

@@ -165,7 +165,7 @@ else:
     seeds = [fixed_seed for _ in range(n_runs)]
 # seeds = [np.random.randint(1000000) for _ in range(n_runs)]
 if n_jobs == 1:
-    results = [run(mdp,seed) for (mdp,seed,source) in zip(mdps,seeds,sources)]
+    results = [run(mdp,seed) for (mdp,seed,source) in zip(envs,seeds,sources)]
 elif n_jobs > 1:
     results = Parallel(n_jobs=n_jobs)(delayed(run)(mdp,seed,source) for (mdp,seed,source) in zip(envs,seeds,sources))
 

### 2018-05-10 NIPS 2018/main.tex

@@
 \newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
-\title{Formatting instructions for NIPS 2018}
+\title{What the hell is the title of this paper?}
 
@@
 \section{Introduction}
+
+Recent advances have allowed reinforcement learning (RL) \cite{}\todo{cite Sutton} to solve a wide variety complex tasks, ranging from playing Atari \cite{} and the game of Go \cite{} to the control of sophisticated robotics systems \cite{}.
+The main drawback is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
+One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
+In the typical settings of transfer in RL \cite{}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
+Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process.
+This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previously learned tasks.
+Several algorithms have been proposed in the literature to transfer experience samples \cite{}, policies/options \cite{}, rewards \cite{}, value functions \cite{}, features \cite{}, and so on.
+We refer the reader to \cite{} for a thorough survey on transfer in RL.
+
+One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks.
+Intuitively, assuming tasks in the family under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
+Appealing approaches for this problem are the Bayesian ones (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible, or the model-based ones (e.g., \cite{}), which typically transfer samples to improve the estimate of the current task model and adopt classic count-based exploration.
+However, we believe all this approaches to have several limitations that reduce their practical applicability.\todo{mention some}
+
+In this work, we tackle such limitations by taking a more general approach.
+Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
+Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
+Leveraging on recent ideas from randomized value functions (\cite{}), we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+(with respect to) the sampled value function.
+We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models.
+\todo[inline]{Maybe mention something about theory/experiments here}
+
+The rest of this document is organized as follows... \todo[inline]{Complete this when the structure is defined or simply remove it to save space.}
+
+Transfer approaches to mention:
+\begin{itemize}
+\item Taylor 2009: survey
+\item Konidaris and Barto transfer shaped reward functions PROs: this allows the agent to have a more goal-directed behavior, thus limiting unnecessary random exploration CONs: applicable only to simple problems, does not scale
+\item Wilson 2007 propose a hierarchical Bayesian model for the distribution over tasks PROs it explicitly models the uncertainty over which tasks are being solved, thus quickly adapting to new ones and allowing informed exploration decisions to be taken
+\item Lazaric 2008 transfer samples PROs select good samples, can scale to continuous domains CONs eps greedy is used
+\item Taylor 2008 transfer samples for model-based RL PROs good exploration via model-based RL CONs does not scale, can negatively transfer when tasks are very different
+\item Lazaric 2010 propose a hierarchical bayesian model for the distribution over value functions PROs quickly adapts to new tasks, non-parameteric (GP) models CONs scaling, strong assumptions (GPTD)
+\item Fernandez and veloso 2006 propose an exploration strategy based on probabilistic policy reuse PROs good exploration (?) CONs Do not try to figure out which policies are good or bad
+\item Brunskill propose a method to transfer in model based RL (E3) - PROs theory, exploration CONs scaling
+\item Barreto use successor features PROs simple, theory CONs eps-greedy exploration
+\end{itemize}
+
+Exploration approaches to mention:
+\begin{itemize}
+\item Osband 2014 propose a method to efficiently explore via randomized value functions
+\item Osband 2016 adapt such algorithm to DQNs
+\item Houthooft 2016 use variational inference to approximate the posterior distribution over parameters of the dynamics, and use that to drive exploration
+\item Azizzadenesheli 2018 extend Osband 2016 to use Bayesian DQN instead. Still makes Gaussian assumptions though
+\end{itemize}
 

### 2018-05-10 NIPS 2018/main.tex
Edits

@@
 
-Recent advances have allowed reinforcement learning (RL) \cite{}\todo{cite Sutton} to solve a wide variety complex tasks, ranging from playing Atari \cite{} and the game of Go \cite{} to the control of sophisticated robotics systems \cite{}.
-The main drawback is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
+Recent advances have allowed reinforcement learning (RL) \cite{} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{}, to the game of Go \cite{}, to the control of sophisticated robotics systems \cite{}.
+The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
 One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
@@
 One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks.
-Intuitively, assuming tasks in the family under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
-Appealing approaches for this problem are the Bayesian ones (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible, or the model-based ones (e.g., \cite{}), which typically transfer samples to improve the estimate of the current task model and adopt classic count-based exploration.
-However, we believe all this approaches to have several limitations that reduce their practical applicability.\todo{mention some}
+Intuitively, assuming the tasks under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
+Among the appealing approaches for this problem we find Bayesian methods (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible.
+Similarly, model-based algorithms (e.g., \cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain.
+However, all these approaches either require strong assumptions (for example, on the distribution involved in Bayesian methods) or do not scale well to large problems.
+This greatly limits their practical applicability.
 
-In this work, we tackle such limitations by taking a more general approach.
+In this work, we tackle such limitations by considering a more general approach.
 Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.

### 2018-05-11 algorithms/mgvt_torch.py
cache posterior in init_posterior

@@ -12,6 +12,7 @@ prior_eigen = None
 cholesky_mask = None
 prior_normal = None
 posterior_normal = None
+sigma_inv = None
 
 def unpack(params, C, K):
     """Unpacks a parameter vector into c, mu, L"""
@@ -190,7 +191,7 @@ def init_posterior(c, mu, L, c_bar, mu_bar, Sigma_bar, phi, psi, C, K, cholesky_
                                                             C, K, precision=precision, tight_bound=False)
         params = clip(params - eta * pack(grad_c, grad_mu, grad_L), cholesky_clip, C, K)
         c, mu, L = unpack(params, C, K)
-        ukl = UKL(c, mu, None, c_bar, mu_bar, Sigma_bar, phi, psi, L=L)
+        ukl = UKL(c, mu, None, c_bar, mu_bar, Sigma_bar, phi, psi, L=L, precision=precision)
         done = np.abs(ukl-ukl_prev) < eps
         ukl_prev = ukl
         i += 1
@@ -212,8 +213,8 @@ def gradient(samples, params, Q, c_bar, mu_bar, Sigma_bar, operator, n_samples, 
     ebe_grad_mu = np.average(be_grad, axis=1)
     # Gradient of the expected Bellman error wrt L.
     ebe_grad_L = np.average(np.matmul(be_grad[:, :, :, np.newaxis], vs.reshape(C, n_weights, K)[:,:,np.newaxis]), axis=1)
-    ebe_grad_mu = c[:, np.newaxis] * ebe_grad_mu
-    ebe_grad_L = c[:, np.newaxis, np.newaxis] * ebe_grad_L
+    # ebe_grad_mu = c[:, np.newaxis] * ebe_grad_mu
+    # ebe_grad_L = c[:, np.newaxis, np.newaxis] * ebe_grad_L
 
     kl_grad_c, kl_grad_mu, kl_grad_L, phi, psi = gradient_KL(c, mu, L, c_bar, mu_bar, Sigma_bar, phi, psi,
                                                              max_iter_ukl, C, K, precision=precision,
@@ -370,10 +371,11 @@ def learn(mdp,
             g = gradient(buffer.sample_batch(batch_size), params, Q, c_bar, mu_bar, Sigma_bar, operator,
                          i + 1, phi, psi, n_weights, lambda_, max_iter_ukl, C, K, precision=Sigma_bar_inv,
                          t_step=i, ukl_tight_freq=ukl_tight_freq)
+
             # Take a gradient step for \mu
[…]

### 2018-05-11 algorithms/mgvt_torch.py
cache posterior in init_posterior

@@ -213,8 +213,8 @@ def gradient(samples, params, Q, c_bar, mu_bar, Sigma_bar, operator, n_samples, 
     ebe_grad_mu = np.average(be_grad, axis=1)
     # Gradient of the expected Bellman error wrt L.
     ebe_grad_L = np.average(np.matmul(be_grad[:, :, :, np.newaxis], vs.reshape(C, n_weights, K)[:,:,np.newaxis]), axis=1)
-    # ebe_grad_mu = c[:, np.newaxis] * ebe_grad_mu
-    # ebe_grad_L = c[:, np.newaxis, np.newaxis] * ebe_grad_L
+    ebe_grad_mu = c[:, np.newaxis] * ebe_grad_mu
+    ebe_grad_L = c[:, np.newaxis, np.newaxis] * ebe_grad_L
 
     kl_grad_c, kl_grad_mu, kl_grad_L, phi, psi = gradient_KL(c, mu, L, c_bar, mu_bar, Sigma_bar, phi, psi,
                                                              max_iter_ukl, C, K, precision=precision,

### 2018-05-11 algorithms/mgvt_torch.py
cache posterior in init_posterior

@@ -373,9 +373,9 @@ def learn(mdp,
                          t_step=i, ukl_tight_freq=ukl_tight_freq)
 
             # Take a gradient step for \mu
-            params, t, m_t, v_t = utils.adam(params, g, t, m_t, v_t, alpha=adam_mask + sgd_mask)
+            params, t, m_t, v_t = utils.adam(params, g, t, m_t, v_t, alpha=adam_mask)
             # Take a gradient step for L
-            # params = utils.sgd(params, g, alpha=sgd_mask)
+            params = utils.sgd(params, g, alpha=sgd_mask)
             # Clip parameters
             params = clip(params, cholesky_clip, C, K)
 

### 2018-05-11 NIPS 2018/main.tex

@@
 Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process.
-This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previously learned tasks.
+This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previous learning experience.
 Several algorithms have been proposed in the literature to transfer experience samples \cite{}, policies/options \cite{}, rewards \cite{}, value functions \cite{}, features \cite{}, and so on.
@@
 
+\paragraph*{Exploration-based introduction}
 One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks.
@@
 
+\paragraph*{Transfer-based introduction}
+
+Under the assumption that tasks follow a certain distribution, an intuitive choice for designing a transfer algorithm is to attempt at charactering the uncertainty over the target task.
+Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task in such a way that this uncertainty is reduced as quickly as possible.
+This simple intuition makes Bayesian \todo{probabilistic?
+distributional?} methods appealing approaches for transfer in RL, and many previous works have been proposed in this direction.
+\cite{} assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of this two elements.
+Similarly, \cite{} assume tasks are similar in their value functions and design a different hierarchical Bayesian model.
+More recently, \cite{}, and its extension \cite{}, consider tasks that share structure in their dynamics which is governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
+However, all these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
+[Having more general algorithms that alleviate the need of strong assumptions and can be easily adapted to different contexts is one of the most relevant problems in current research.]
+
+In this work, we take a more general approach.
+Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
+Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
+Leveraging on recent ideas from randomized value functions (\cite{}), we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+(with respect to) the sampled value function.
+We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models.
+\todo[inline]{Maybe mention something about theory/experiments here}
+
 The rest of this document is organized as follows... \todo[inline]{Complete this when the structure is defined or simply remove it to save space.}
-
-Transfer approaches to mention:
-\begin{itemize}
-\item Taylor 2009: survey
-\item Konidaris and Barto transfer shaped reward functions PROs: this allows the agent to have a more goal-directed behavior, thus limiting unnecessary random exploration CONs: applicable only to simple problems, does not scale
-\item Wilson 2007 propose a hierarchical Bayesian model for the distribution over tasks PROs it explicitly models the uncertainty over which tasks are being solved, thus quickly adapting to new ones and allowing informed exploration decisions to be taken
-\item Lazaric 2008 transfer samples PROs select good samples, can scale to continuous domains CONs eps greedy is used
-\item Taylor 2008 transfer samples for model-based RL PROs good exploration via model-based RL CONs does not scale, can negatively transfer when tasks are very different
-\item Lazaric 2010 propose a hierarchical bayesian model for the distribution over value functions PROs quickly adapts to new tasks, non-parameteric (GP) models CONs scaling, strong assumptions (GPTD)
-\item Fernandez and veloso 2006 propose an exploration strategy based on probabilistic policy reuse PROs good exploration (?) CONs Do not try to figure out which policies are good or bad
-\item Brunskill propose a method to transfer in model based RL (E3) - PROs theory, exploration CONs scaling
-\item Barreto use successor features PROs simple, theory CONs eps-greedy exploration
-\end{itemize}
-
-Exploration approaches to mention:
-\begin{itemize}
-\item Osband 2014 propose a method to efficiently explore via randomized value functions
-\item Osband 2016 adapt such algorithm to DQNs
-\item Houthooft 2016 use variational inference to approximate the posterior distribution over parameters of the dynamics, and use that to drive exploration
-\item Azizzadenesheli 2018 extend Osband 2016 to use Bayesian DQN instead. Still makes Gaussian assumptions though
-\end{itemize}
 
@@
 
+Our approach is mostly related to \cite{}.
+Although we both assume the tasks to share similarities in their value functions, \cite{} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian.
+On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators.
+Furthermore, \cite{} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation of Sec.
+\ref{sec:mgvt} and proves again the importance of capturing more complicated task distributions.
+Another related approach is \cite{}, where the authors propose a hierarchical Bayesian model for the distribution over tasks.
+Differently from our approach and \cite{}, they consider a distribution over transition probabilities and rewards, rather than value functions.
+In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it, thus providing efficient exploration via the transferred knowledge.
+However, \cite{} consider only finite MDPs, which poses a severe limitation in the algorithm's applicability.
+On the contrary, our approach can handle high dimensional tasks by allowing powerful function approximators.
+\todo{Cite also HIP}
+
+\todo[inline]{Should we add more here or just leave a quick citation in the introduction?}
+
+The idea of exploration via value function randomization we build upon was first proposed in the RL community by \cite{}.
+The authors extend the well-known LSTD \cite{} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a Thompson sampling-like procedure.
+Such approach was recently extended by \cite{}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
+Both these algorithms rely on the Gaussian assumption and, since they work in plain RL settings, have no informative prior available.
+On the other hand, our variational approximation allows more complex distributions (e.g., mixtures) to be adopted, while knowledge from the source tasks allows us to learn very informative priors.
+Finally, the variational approximation technique we consider in this work has been previously adopted in \cite{} to approximate an intractable posterior over the transition dynamics, which is then used to drive efficient exploration via an information-maximizing procedure.
+
 \section{Experiments}
@@
 
+Transfer approaches to mention:
+\begin{itemize}
+\item Taylor 2009: survey
+\item Konidaris and Barto transfer shaped reward functions PROs: this allows the agent to have a more goal-directed behavior, thus limiting unnecessary random exploration CONs: applicable only to simple problems, does not scale
+\item Wilson 2007 propose a hierarchical Bayesian model for the distribution over tasks PROs it explicitly models the uncertainty over which tasks are being solved, thus quickly adapting to new ones and allowing informed exploration decisions to be taken
+\item Lazaric 2008 transfer samples PROs select good samples, can scale to continuous domains CONs eps greedy is used
+\item Taylor 2008 transfer samples for model-based RL PROs good exploration via model-based RL CONs does not scale, can negatively transfer when tasks are very different
+\item Lazaric 2010 propose a hierarchical bayesian model for the distribution over value functions PROs quickly adapts to new tasks, non-parameteric (GP) models CONs scaling, strong assumptions (GPTD)
+\item Fernandez and veloso 2006 propose an exploration strategy based on probabilistic policy reuse PROs good exploration (?) CONs Do not try to figure out which policies are good or bad
+\item Brunskill propose a method to transfer in model based RL (E3) - PROs theory, exploration CONs scaling
+\item Barreto use successor features PROs simple, theory CONs eps-greedy exploration
+\end{itemize}
+
+Exploration approaches to mention:
+\begin{itemize}
+\item Osband 2014 propose a method to efficiently explore via randomized value functions
+\item Osband 2016 adapt such algorithm to DQNs
+\item Houthooft 2016 use variational inference to approximate the posterior distribution over parameters of the dynamics, and use that to drive exploration
+\item Azizzadenesheli 2018 extend Osband 2016 to use Bayesian DQN instead. Still makes Gaussian assumptions though
+\end{itemize}
+
 \end{document}

### 2018-05-12 NIPS 2018/main.tex
Updated MM theorem

@@
 
-\begin{restatable}{theorem}{thmm} \label{th:mm}
+\begin{restatable}{theorem}{thmmv} \label{th:mmv}
 Let $V$ be the fixed-point of the optimal Bellman operator $T$, and $Q$ the corresponding action-value function.
@@
 \norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{(1-\gamma)^2}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
+\end{equation}
+\end{restatable}
+
+\begin{restatable}{theorem}{thmm} \label{th:mm}
+Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$.
+Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$.
+Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}).
+Let $\nu$ be a probability measure over the state-action space.
+Then, for any $p \geq 1$:
+\begin{equation}
+\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p
 \end{equation}
@@
 
-\thmm*
+\thmmv*
 \begin{proof}
@@
 \abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2R_{max}}{1-\gamma}\abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
+\end{align*}
+Taking the norm and plugging this into Eq. \eqref{eq:mm1} concludes the proof.
+\end{proof}
+
+\thmm*
+\begin{proof}
+We begin by noticing that:
+\begin{align*}
+\norm{Q^*-\wt{Q}}_{\nu,p}^p =\ & \norm{TQ^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ =\ &
+\norm{TQ^* - \wt{T}Q^* + \wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
+\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \norm{\wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
+\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \gamma\norm{Q^* - \wt{Q}}_{\nu,p}^p
+\end{align*}
+where the first inequality follows from Minkowsky's inequality and the second one from the contraction property of the mellow Bellman operator. This implies that:
+\begin{align} \label{eq:mm1}
+\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p
+\end{align}
+Let us bound the norm on the right-hand side separately.
+In order to do that, we will bound the function $\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)}$ point-wisely for any state $s,a$.
+By applying the definition of the optimal and mellow Bellman operators, we obtain:
+\begin{align} \label{eq:mm5}
+\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} =\ & \abs{R(s,a) + \gamma\mathbb{E}\left[\max_{a'}Q^*(s',a')\right] - R(s,a) - \gamma\mathbb{E}\left[\mm_{a'}Q^*(s',a')\right]}\notag \\ =\ & \gamma\abs{\mathbb{E}\left[\max_{a'}Q^*(s',a')\right] - \mathbb{E}\left[\mm_{a'}Q^*(s',a')\right]}\notag \\ \leq\ & \gamma\mathbb{E}\left[\abs{\max_{a'}Q^*(s',a') - \mm_{a'}Q^*(s',a')}\right]
+\end{align}
+Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$.
+Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}.
+Thus, we can write:
+\begin{align} \label{eq:mm2}
+\abs{\max_a Q(s,a) - \mm_a Q(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q(s,a)}\notag\\ =\ & \abs{\sum_a Q(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}
+\end{align}
+where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q$ and $\pi_{\beta_{\kappa}}$ is the Boltzmann distribution induced by $Q$ with inverse temperature $\beta_{\kappa}$:
+\begin{align*}
+\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q(s,a')}}
+\end{align*}
+Denote by $a_1(s)$ the optimal action for state $s$ under $Q$. We can then write:
+\begin{align} \label{eq:mm3}
+\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)} =\ & \abs{\pi^*(a_1(s)|s) - \pi_{\beta_{\kappa}}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ =\ & \abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi_{\beta_{\kappa}}(a|s)}\notag\\ =\ & 2\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)}
+\end{align}
+Finally, let us bound this last term:
+\begin{align} \label{eq:mm4}
+\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q(s,a_1(s)) - Q(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\end{align}
+Combining Eq. \eqref{eq:mm5}, \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:
+\begin{align*}
+\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
 \end{align*}

### 2018-05-12 NIPS 2018/main.tex
Fixed part of the proof

@@
 \begin{align} \label{eq:mm2}
-\abs{\max_a Q(s,a) - \mm_a Q(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q(s,a)}\notag\\ =\ & \abs{\sum_a Q(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}
+\abs{\max_a Q^*(s,a) - \mm_a Q^*(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q^*(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q^*(s,a)}\notag\\ =\ & \abs{\sum_a Q^*(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q^*(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}
 \end{align}
-where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q$ and $\pi_{\beta_{\kappa}}$ is the Boltzmann distribution induced by $Q$ with inverse temperature $\beta_{\kappa}$:
+where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q^*$ and $\pi_{\beta_{\kappa}}$ is the Boltzmann distribution induced by $Q^*$ with inverse temperature $\beta_{\kappa}$:
 \begin{align*}
-\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q(s,a')}}
+\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}
 \end{align*}
-Denote by $a_1(s)$ the optimal action for state $s$ under $Q$. We can then write:
+Denote by $a_1(s)$ the optimal action for state $s$ under $Q^*$. We can then write:
 \begin{align} \label{eq:mm3}
@@
 \begin{align} \label{eq:mm4}
-\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q(s,a_1(s)) - Q(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q^*(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q^*(s,a_1(s)) - Q^*(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
 \end{align}
-Combining Eq. \eqref{eq:mm5}, \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:
+Combining Eq. \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:
 \begin{align*}
-\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2 R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\end{align*}
+Finally, using Eq. \eqref{eq:mm5} we get:
+\begin{align*}
+\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} \leq \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
 \end{align*}

### 2018-05-12 NIPS 2018/main.tex
Added part of experiments

@@
 
-\subsection{Gridworld}
+In this section, we provide an experimental evaluation of our approach.
+We begin by analyzing the behavior of our algorithm on a toy problem in Sec.
+\ref{sec:gw}.
+Then, in Sec.
+\ref{sec:cc}, we consider two classic control benchmarks, namely cartpole and mountain car.
+We conclude with a complex maze navigation task in Sec.
+\ref{sec:mn}.
+In all experiments, we compare the behavior of our variational transfer algorithm with Gaussian distributions (GVT) and with mixture of Gaussians (MGVT).
+To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
+\todo{Any better motivation?}
 
-\subsection{Classic Control}
+\subsection{The Rooms Problem} \label{sec:gw}
 
-\subsection{Maze Navigation}
+We consider an agent navigating in the rooms environment depicted in Fig.
+\ref{}.
+The agent starts in the bottom-left corner and must move from one room to another to reach a goal position in the top-right corner.
+The rooms are connected by small doors whose positions are unknown to the agent.
+In particular, we consider two versions of the environment, with two rooms (Fig.
+\ref{} top) and three rooms (Fig.
+\ref{} bottom), respectively.
+The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
+After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise with $0.2$ standard deviation.
+In case the agent hits a wall, its position remains unchanged.
+The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
+We consider a distribution over tasks in which doors have a fixed width of $1$, while their positions are sampled uniformly in $[0.5,9.5]$.
+Since the agent does not know where the doors are located in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
+While this might be a complicated problem for plain RL, our transfer algorithm should be able to quickly figure out the door positions.
+In fact, notice that, although different, the optimal $Q$-functions for all tasks share some similarities.
+For example, once the agent has passed the last door before the goal, the $Q$-values are exactly the same in all tasks.
+This does not hold for positions nearby the start state, however it is clear that there should be a preference over actions up and right, rather than low and left.
+Thus, we expect our algorithm to efficiently explore any target task.
+
+\subsection{Classic Control} \label{sec:cc}
+
+\subsection{Maze Navigation} \label{sec:mn}
 

### 2018-05-12 NIPS 2018/main.tex
Updates to the figures

@@
 
+\begin{figure*}[t]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.5cm]{images/rooms.pdf} \hfill
+\includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
+\caption{Bla bla bla}
+    \label{fig:puddleworld}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room-gen/lrev.pdf} \hfill
+\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
+\caption{Bla bla bla}
+    \label{fig:acrobot}
+\end{minipage}
+\end{figure*}
+
 We consider an agent navigating in the rooms environment depicted in Fig.
 \ref{}.
-The agent starts in the bottom-left corner and must move from one room to another to reach a goal position in the top-right corner.
+The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
 The rooms are connected by small doors whose positions are unknown to the agent.
@@
 For example, once the agent has passed the last door before the goal, the $Q$-values are exactly the same in all tasks.
-This does not hold for positions nearby the start state, however it is clear that there should be a preference over actions up and right, rather than low and left.
+This does not hold for positions nearby the start state.
+However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).
 Thus, we expect our algorithm to efficiently explore any target task.
@@
 
+\section{Additional Details on the Experiments}
+
+\subsection{The Rooms Problem}
+
+\subsection{Classic Control}
+
+\subsection{Maze Navigation}
+
 Transfer approaches to mention:

### 2018-05-13 NIPS 2018/main.tex
added description of the maze navigation task

--- 2018-05-12 NIPS 2018/main.tex
@@
 
+For this setting we propose a maze environment, such as those in Fig.
+*, for a robotic agent to navigate.
+We created a set of 20 mazes of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze.
+In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance/angle each time an action is performed: \emph{move forward, rotate counter- and clockwise}.
+Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of 2 and a field of vision from -90º to 90º relative to its orientation.
+In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike.
+Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation.
+Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation.
+
+The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit  in different maze configurations leveraging its previous experience.
+Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is robust to negative transfer.
+
+These mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
+Finally, the MGVT algorithm, with one component for the posterior distribution, was used to solve the target tasks shown in Fig.
+*.
+
 \section{Conclusion}

### 2018-05-13 NIPS 2018/main.tex
New figures

--- 2018-05-12 NIPS 2018/main.tex
@@
 \ref{sec:mn}.
-In all experiments, we compare the behavior of our variational transfer algorithm with Gaussian distributions (GVT) and with mixture of Gaussians (MGVT).
+In all experiments, we compare our variational transfer algorithm with Gaussian distributions (GVT) and with mixture of Gaussians (MGVT) to plain no-transfer RL (NT).
 To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
@@
 \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room-gen/lrev.pdf} \hfill
-\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
+\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/likelihood/lrew.pdf}
 \caption{Bla bla bla}

### 2018-05-13 NIPS 2018/main.tex
Completed rooms section

--- 2018-05-12 NIPS 2018/main.tex
@@
 \usepackage{thmtools, thm-restate}
+\usepackage{subcaption}
 
@@
 
-\subsection{Optimizing the TD error}
+\subsection{Optimizing the TD error} \label{sec:td}
 
@@
 \ref{sec:mn}.
-In all experiments, we compare the behavior of our variational transfer algorithm with Gaussian distributions (GVT) and with mixture of Gaussians (MGVT).
+In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using mixture of Gaussians with $c$ components ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration.
 To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
@@
 \begin{figure*}[t] 
-\centering
-\begin{minipage}[t]{0.49\linewidth}
-\centering
-\includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.5cm]{images/rooms.pdf} \hfill
-\includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
-\caption{Bla bla bla}
-    \label{fig:puddleworld}
-\end{minipage}\hfill
-\begin{minipage}[t]{0.49\linewidth}
-\centering
-\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room-gen/lrev.pdf} \hfill
-\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
-\caption{Bla bla bla}
-    \label{fig:acrobot}
-\end{minipage}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.0cm]{images/rooms.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{(a) the rooms environment, (b) transfer from $10$ source tasks with both doors moving, (c) transfer from $10$ source tasks with only one door moving, and (d) transfer performance as a function of how likely the target task is according to the prior.}
+  \label{fig:dipfdbsgraphplots}
 \end{figure*}
@@
 The rooms are connected by small doors whose positions are unknown to the agent.
-In particular, we consider two versions of the environment, with two rooms (Fig.
-\ref{} top) and three rooms (Fig.
-\ref{} bottom), respectively.
 The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
@@
 Thus, we expect our algorithm to efficiently explore any target task.
+
+In order to prove that our guesses are correct, we generate a set of $50$ source tasks for the three-room environment of Fig.
+\ref{} by sampling both door positions uniformly, and solve all of them by directly minimizing the TD error as presented in Sec.
+\ref{sec:td}.
+In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until converge.
+Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
+The average return over the last $50$ learning episodes as a function of the number of iterations is shown in Fig.
+\ref{}.
+Each curve is the result of $20$ independent runs, each resampling the target and source tasks.
+$95\%$ confidence intervals are shown.
+Further details on the parameters adopted in this experiment are given in App.
+\ref{}.
+As expected, the no-transfer algorithm NT fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
+On the other hand, all our algorithms achieve a significant speed-up and are able to converge to the optimal performance in few iterations, with GVT being slightly slower.
+Interestingly, we notice that there is no advantage in adopting more than $1$ component for the posterior in MGVT.
+This is intuitive since, when the algorithm quickly figures out which task is being solved, it will move all components in the same direction.
+
+To better understand the differences between GVT and MGVT, we now consider transferring from a slightly different distribution than the one from which target tasks are drawn.
+We generate again $50$ source tasks but this time with the bottom door fixed in the center and the other one moving.
+Then, we repeat the previous experiment, allowing both doors to move when sampling target tasks.
+The results are shown in Fig.
+\ref{}.
+Interestingly, MGVT seems almost unaffected by this change, proving that is has sufficient representation power to generalize to slightly different task distributions.
+The same does not hold for GVT, which now is not able to solve many of the sampled target tasks (this is the reason for the very high variance).
+This proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
+
+Finally, we analyze the transfer performance as a function of how likely the target task is according to the prior.
+We consider a two-room version of the environment of Fig.
+\ref{}.
+Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is close to the sides are very unlikely.
+Fig.
+\ref{} shows the performance reached by GVT and MGVT with $1$ component at fixed iterations as a function of how likely the target task is according to such distribution.
+As expected GVT achieves poor performance on very unlikely tasks, even after many iterations.
+In fact, estimating a single Gaussian distribution definitely implies some information loss, especially about the unlikely tasks.
+On the other hand, MGVT keeps such information and, consequently, performs much better.
+Perhaps not surprisingly, MGVT reaches the optimal performance in $4k$ iterations no matter what task is being solved.
 

### 2018-05-13 scripts/run_nt_mountaincar.py
mountain car env modified

@@ -26,7 +26,7 @@ parser.add_argument("--batch_size", default=32)
 parser.add_argument("--max_iter", default=10000)
 parser.add_argument("--buffer_size", default=50000)
 parser.add_argument("--random_episodes", default=0)
-parser.add_argument("--exploration_fraction", default=0.5)
+parser.add_argument("--exploration_fraction", default=0.1)
 parser.add_argument("--eps_start", default=1.0)
 parser.add_argument("--eps_end", default=0.01)
 parser.add_argument("--train_freq", default=1)
@@ -69,11 +69,11 @@ file_name = str(args.file_name)
 dqn = bool(args.dqn)
 
 # Seed to get reproducible results
-np.random.seed(485)
+# np.random.seed(485)
 # torch.manual_seed(485)
 
 # Generate tasks
-vel = [np.random.uniform(0.001, 0.0025) if speed < 0 else speed for _ in range(n_runs)]
+vel = [np.random.uniform(0.0005, 0.0015) if speed < 0 else speed for _ in range(n_runs)]
 print(vel)
 mdps = [MountainCarEnv(vel[i]) for i in range(n_runs)]
 n_eval_episodes = 5

### 2018-05-13 NIPS 2018/main.tex

@@
 
+\section{Additional Details on the Algorithms}
+
+\subsection{Gaussian Variational Transfer}
+
+\subsection{Mixture of Gaussian Variational Transfer}
+
 \section{Additional Details on the Experiments}

### 2018-05-13 scripts/run_nt_mountaincar.py
modify range of speeds

@@ -73,7 +73,7 @@ dqn = bool(args.dqn)
 # torch.manual_seed(485)
 
 # Generate tasks
-vel = [np.random.uniform(0.0005, 0.0015) if speed < 0 else speed for _ in range(n_runs)]
+vel = [np.random.uniform(0.001, 0.0015) if speed < 0 else speed for _ in range(n_runs)]
 print(vel)
 mdps = [MountainCarEnv(vel[i]) for i in range(n_runs)]
 n_eval_episodes = 5

### 2018-05-13 NIPS 2018/main.tex
Updated intro + prelims

@@
 
-Recent advances have allowed reinforcement learning (RL) \cite{} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{}, to the game of Go \cite{}, to the control of sophisticated robotics systems \cite{}.
+Recent advances have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
 The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
 One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
-In the typical settings of transfer in RL \cite{}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
+In the typical settings of transfer in RL \cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
 Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process.
 This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previous learning experience.
-Several algorithms have been proposed in the literature to transfer experience samples \cite{}, policies/options \cite{}, rewards \cite{}, value functions \cite{}, features \cite{}, and so on.
-We refer the reader to \cite{} for a thorough survey on transfer in RL.
+Several algorithms have been proposed in the literature to transfer experience samples \cite{lazaric2008transfer,taylor2008transferring}, policies/options \cite{fernandez2006probabilistic,konidaris2007building}, rewards \cite{konidaris2006autonomous}, features \cite{barreto2017successor}, parameters \cite{doshi2016hidden,killian2017robust}, and so on.
+We refer the reader to \cite{taylor2009transfer} for a thorough survey on transfer in RL.
 
-\paragraph*{Exploration-based introduction}
-One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks.
+%\paragraph*{Exploration-based introduction}
+%One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks.
 Intuitively, assuming the tasks under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
@@
 
-In this work, we tackle such limitations by considering a more general approach.
+%In this work, we tackle such limitations by considering a more general approach.
 Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
@@
 
-\paragraph*{Transfer-based introduction}
-
-Under the assumption that tasks follow a certain distribution, an intuitive choice for designing a transfer algorithm is to attempt at charactering the uncertainty over the target task.
+Under the assumption that tasks follow a certain distribution, an intuitive choice for designing a transfer algorithm is to attempt at characterizing the uncertainty over the target task.
 Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task in such a way that this uncertainty is reduced as quickly as possible.
@@
 distributional?} methods appealing approaches for transfer in RL, and many previous works have been proposed in this direction.
-\cite{} assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of this two elements.
-Similarly, \cite{} assume tasks are similar in their value functions and design a different hierarchical Bayesian model.
-More recently, \cite{}, and its extension \cite{}, consider tasks that share structure in their dynamics which is governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
+\cite{wilson2007multi} assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of these two elements.
+Similarly, \cite{lazaric2010bayesian} assume tasks are similar in their value functions and design a different hierarchical Bayesian model for transferring such information.
+More recently, \cite{doshi2016hidden}, and its extension \cite{killian2017robust}, consider tasks whose dynamics are governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
 However, all these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
-[Having more general algorithms that alleviate the need of strong assumptions and can be easily adapted to different contexts is one of the most relevant problems in current research.]
+The importance of having transfer algorithms that alleviate the need of strong assumptions and can be easily adapted to different contexts motivates us to take a more general approach.
 
-In this work, we take a more general approach.
-Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
+Similarly to \cite{lazaric2010bayesian}, we assume tasks to share similarities in their value functions and use the given source tasks to learn a distribution over such functions.
 Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
-Leveraging on recent ideas from randomized value functions (\cite{}), we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
 (with respect to) the sampled value function.
 We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models.
-\todo[inline]{Maybe mention something about theory/experiments here}
-
-The rest of this document is organized as follows... \todo[inline]{Complete this when the structure is defined or simply remove it to save space.}
+We propose a finite-sample analysis that theoretically validates our approach, while empirically evaluating its performance on three domains with increasing level of difficulty.
 
@@
 
-We define a Markov decision process (MDP) as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
+We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov decision process (MDP).
+We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
 We assume the reward function to be uniformly bounded by a constant $R_{max}>0$.
@@
 
-When learning the optimal value function, a quantity of interest is how close a given $Q$-function is to the fixed-point of the Bellman operator.
-This is given by its Bellman residual, defined by $B(Q) \triangleq TQ - Q$.
-Notice that $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$.
-Furthermore, if we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, the squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\nu$, $\norm{B(Q)}_{\nu}^2=\mathbb{E}_{\mu}\left[ B^2(Q) \right]$.
-Although minimizing the empirical Bellman error is an appealing objective, it is well-known that an unbiased estimator requires two independent samples of the next state $s'$ of each $s,a$ (e.g., \cite{} \todo{cite Maillard}).
-In practice, the empirical Bellman error is typically replaced by the TD error, which approximates the former using a single transition sample.
-Given a dataset of $N$ samples, the TD error is computed as $\norm{B(Q)}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.
+We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$ and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
+When learning the optimal value function, a quantity of interest is how close a given function $Q_{\bm{w}}$ is to the fixed-point of the Bellman operator.
+A possible measure is its Bellman error (or Bellman residual), defined by $B(\bm{w}) \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$.
+Notice that $Q_{\bm{w}}$ is optimal if, and only if, $B(\bm{w})(s,a) = 0$ for all $s,a$.
+If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, an appealing objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B(\bm{w})}_{\nu}^2$\todo{Should we define norms before?}.
+Unfortunately, it is well-known that an unbiased estimator of this quanitity requires two independent samples of the next state $s'$ for each $s,a$ (e.g., \cite{maillard2010finite}).
+In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$.
+Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B(\bm{w})}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$.
+Whenever the distinction is clear from the context, with slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.
 

### 2018-05-13 scripts/run_gvt_mountaincar.py
mountain car gvt

@@ -1,0 +1,133 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.mountain_car import MountainCarEnv
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.gvt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=500)
+parser.add_argument("--max_iter", default=10000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=200)
+parser.add_argument("--mean_episodes", default=20)
+parser.add_argument("--l1", default=64)
+parser.add_argument("--l2", default=0)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.00001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--sigma_reg", default=0.0001)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Cartpole parameters (default = randomize
+parser.add_argument("--speed", default=-1)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="mountaincar_sources_64nn_200k")
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
+xi = float(args.xi)
+tau = float(args.tau)
+batch_size = int(args.batch_size)
+max_iter = int(args.max_iter)
+buffer_size = int(args.buffer_size)
+random_episodes = int(args.random_episodes)
[…]

### 2018-05-13 NIPS 2018/main.tex
Updates to Sec.3

@@
 We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov decision process (MDP).
-We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
+We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$\todo{Should we provide a more transfer-oriented definition?}, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
 We assume the reward function to be uniformly bounded by a constant $R_{max}>0$.
@@
 
-We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$ and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
+We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$, and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
 When learning the optimal value function, a quantity of interest is how close a given function $Q_{\bm{w}}$ is to the fixed-point of the Bellman operator.
@@
 In Section \ref{sec:alg}, we start by introducing our algorithm from a high-level perspective, in such a way that it can be used for any choice of prior and posterior distributions.
-Then, in Sections \ref{sec:gvt} and \ref{sec:mgvt}, we propose practical implementations based on Gaussian prior/posterior and mixture of Gaussian prior/posterior, respectively.
+Then, in Sections \ref{sec:gvt} and \ref{sec:mgvt}, we propose practical implementations based on Gaussians and mixtures of Gaussians, respectively.
+We conclude with some considerations on how to optimize the proposed objective in Sec.
+\ref{sec:td}.
 
@@
 Since, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
-Furthermore, assume we know such distribution and we are given a new task $\tau$ to solve.
-Our goal is to design an algorithm that efficiently explores $\tau$ so as to quickly adapt the prior distribution in a Bayesian fashion to put all probability mass over the optimal $Q$-function of $\tau$.
+In particular, we reduce the latter to a distribution $p(\bm{w})$ over weights.
 
-We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$.
-For simplicity, we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$\footnote{In practice, this is easily achieved by truncation.}.
-Then, we can reduce our prior distribution over $Q$-functions to a prior distribution over weights $p(\bm{w})$.
 Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
@@
 To prevent the covariance from going not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $L$ instead.
-Under Gaussian distributions, all quantity of interest for using Alg.
-\ref{alg:transfer} can be computed very easily.
-The KL divergence between the prior and approximate posterior can be computed in closed-form as:
-\begin{equation}
-KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
-\end{equation}
-for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are \cite{}\todo{Cite matrix cookboox}:
-\begin{equation}
-\nabla_{\bm{\mu}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p)
-\end{equation}
-\begin{equation}
-\nabla_{\bm{L}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1}\bm{L} - (\bm{L}^{-1})^T
-\end{equation}
-Finally, the gradients w.r.t.
-the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{}\todo{Cite deepmind and another}):
-\begin{equation}
-\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
-\end{equation}
-\begin{equation}
-\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
-\end{equation}
 
@@
 
+Under Gaussian distributions, all quantities of interest for using Alg.
+\ref{alg:transfer} can be computed very easily.
+The KL divergence between the prior and approximate posterior can be computed in closed-form as:
+\begin{equation}
+KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
+\end{equation}
+for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are \cite{}\todo{Cite matrix cookboox}:
+\begin{equation}
+\nabla_{\bm{\mu}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p)
+\end{equation}
+\begin{equation}
+\nabla_{\bm{L}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1}\bm{L} - (\bm{L}^{-1})^T
+\end{equation}
+Finally, the gradients w.r.t.
+the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{}\todo{Cite deepmind and another}):
+\begin{equation}
+\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\end{equation}
+\begin{equation}
+\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\end{equation}
+
 \subsection{Mixture of Gaussian Variational Transfer}

### 2018-05-13 NIPS 2018/main.tex
Changes

@@
 We begin with a simple consideration: the distribution $\mathcal{D}$ over tasks clearly induces a distribution over optimal $Q$-functions.
-Since, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
-In particular, we reduce the latter to a distribution $p(\bm{w})$ over weights.
+\todo{Should we just make the assumption that Q-functions share knowledge in their weights?} Moreover, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
+Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
+In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.
 
-Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
+Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
 Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$.
 Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$.
-In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors \cite{}\todo{Cite somebody}.
-However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability of the approach.
-Thus, we take a different approach to derive a more general and meaningful solution.
+In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors.
+However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability to specific problems.
+Thus, we take a different approach to derive a more general, but still well-grounded, solution.
 Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$.
-Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
+Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ takes the form (e.g., \cite{catoni2007pac}):
 \begin{equation}\label{eq:gibbs}
@@
 the Gibbs posterior $q$.
-From the theory of variational inference (e.g., \cite{}\todo{cite}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
+From the theory of variational inference (e.g., \cite{blei2017variational}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
 \begin{align} \label{eq:elbo}
@@
 \end{align}
-Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term).
+Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term).
 Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t.
-the variational parameters $\bm{\xi}$, our objective can be easily optimized with any stochastic optimization algorithm.
+the variational parameters $\bm{\xi}$, our objective can be easily optimized using any stochastic optimization algorithm.
+
+\begin{algorithm}[t]
+\begin{algorithmic}[1]
+\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch size $M$
+\\\hrulefill
+
+\STATE{Estimate prior $p(\bm{w})$ from $\mathcal{W}_s$}
+\STATE{Initialize variational parameters: $\bm{\xi} \leftarrow \argmin_{\bm{\xi}} KL(q_{\bm{\xi}}||p)$}
+\STATE{Initialize replay buffer: $D = \emptyset$}
+\REPEAT
+
+\STATE{Sample initial state: $s_0 \sim p_0^{(\tau)}$}
+
+\WHILE{$s_h$ is not terminal}
+\STATE{Sample weights: $\bm{w} \sim q_{\bm{\xi}}(\bm{w})$}
+\STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$}
+\STATE{Collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
+\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
+\STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M}$ from $D$}
+\STATE{Compute the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using $D'$}
+\STATE{Update $\bm{\xi}$ in the direction of $-\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using any stochastic optimizer (e.g., ADAM)}
+\ENDWHILE
+
+\UNTIL{forever}
+\end{algorithmic}
+\caption{Variational Transfer} \label{alg:transfer}
+\end{algorithm}
 
@@
 
-\begin{algorithm}[t]
-\begin{algorithmic}[1]
-\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch sizes $M_D$ and $M_{\mathcal{W}}$, prior weight $\lambda$
-\\\hrulefill
-
-\STATE{Estimate prior $p(\bm{w})$ from $\mathcal{W}_s$}
-\STATE{Initialize variational parameters: $\bm{\xi} \leftarrow \argmin_{\bm{\xi}} KL(q_{\bm{\xi}}||p)$}
-\STATE{Initialize replay buffer: $D = \emptyset$}
-\REPEAT
-
-\STATE{Sample initial state: $s_0 \sim p_0^{(\tau)}$}
-
-\WHILE{$s_h$ is not terminal}
-\STATE{Sample weights: $\bm{w} \sim q_{\bm{\xi}}(\bm{w})$}
-\STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
-\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$}
-\STATE{Collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
-\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
-\STATE{Sample batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M_D}$ from $D$ and $\mathcal{W} = \left\{ \bm{w}_1, \bm{w}_2, \dots, \bm{w}_{M_{\mathcal{W}}} \right\}$ from $q_{\bm{\xi}}$}
-\STATE{Approximate objective: $\mathcal{L}(\bm{\xi}) = \frac{1}{M_{\mathcal{W}}}\sum_{\bm{w}\in\mathcal{W}}\norm{B(\bm{w})}_{D'}^2 - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}\ ||\ p\right)$}
-\STATE{Compute the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$}
-\STATE{Update $\bm{\xi}$ in the direction of $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using any stochastic optimizer (e.g., ADAM)}
-\ENDWHILE
-
-\UNTIL{forever}
-\end{algorithmic}
-\caption{Variational Transfer} \label{alg:transfer}
-\end{algorithm}
-
 \subsection{Gaussian Variational Transfer}\label{sec:gvt}
 
-We now restrict ourselves to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement.
+We now restrict to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement.
 We assume that optimal $Q$-functions according to our task distribution (or better, their weights) follow a multivariate Gaussian law.

### 2018-05-13 NIPS 2018/main.tex
Updated up to GVT

@@
 for some parameter $\Lambda > 0$.
-Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
+\todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
 Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior.
@@
 \STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
-\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$}
-\STATE{Collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$ and collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
 \STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
 \STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M}$ from $D$}
-\STATE{Compute the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using $D'$}
+\STATE{Estimate the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using $D'$}
 \STATE{Update $\bm{\xi}$ in the direction of $-\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using any stochastic optimizer (e.g., ADAM)}
@@
 We now highlight our general transfer procedure in Alg.
-\ref{alg:transfer}, while deferring a description of practical implementations with specific choices for the distributions involved to the next two sections.
-Given a set of weights $\mathcal{W}_s$ from the source tasks, we start by estimating the prior distribution (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
-such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters, however this does not always hold in practice.} (line 2).
+\ref{alg:transfer}, while deferring a description of specific choices for the distributions involved to the next two sections.
+Given a set of weights $\mathcal{W}_s$ from the source tasks' optimal $Q$-functions, we start by estimating the prior distribution (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
+such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters.
+However, we are not making this assumption at this point.} (line 2).
 Then, at each time step of interaction, we re-sample the weights from the current approximate posterior and act greedily w.r.t.
 the corresponding $Q$-function (lines 7,8).
-This resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{}\todo{Cite} and allows our algorithm to efficiently explore the target task.
+After collecting and storing the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and, finally, update the variational parameters (line 13).
+
+The key property of our approach is the weight resampling at line 7.
+This resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
 In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
-After collecting and storing the new experience (lines 9-11), we draw a batch of samples from the replay buffer and a batch of weights from the posterior (line 12).
-We use these to approximate the negative ELBO, compute its gradient, and finally update the variational parameters (lines 13-15).
+This allows an efficient adaptive exploration of the target task.
+Intuitively, during the first steps of interaction, the agent is very uncertain about the current task and such uncertainty induces stochasticity in the chosen actions, allowing rather informed exploration to take place.
+Consider, for instance, that actions that are bad on average for all tasks are very unlikely to be sampled, while this cannot happen in uninformed exploration strategies, like $\epsilon$-greedy, before learning takes place.
+As the learning process goes on, the algorithm will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
+From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
 
-The main advantage of our approach is that it exploits knowledge from the source tasks to perform an efficient adaptive exploration.
-Intuitively, during the first steps of interaction, our algorithm has no idea about what is the current task.
-However, it can rely on the learned prior to take early informed decisions.
-As the learning process goes on, it will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
-From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
-Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any function approximator for the $Q$-functions and any family for the pior and posterior distributions can be adopted.
+Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any pior/posterior distributions can be adopted.
 For the latter, we describe two practical choices in the next two sections.
@@
 We now restrict to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement.
-We assume that optimal $Q$-functions according to our task distribution (or better, their weights) follow a multivariate Gaussian law.
-That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using, e.g., maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
+We assume that optimal $Q$-functions (or better, their weights) follow a multivariate Gaussian distribution.
+That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
 Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$.
-To prevent the covariance from going not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $L$ instead.
+To prevent the covariance from becoming not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $\bm{L}$ instead.
+In this case, deriving the gradient of the objective is very simple.
+Both the KL between two multivariate Gaussians and its gradients have a simple closed-form expression.
+The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}).
+Although these results are well-known in the literature, we report them in App.
+\ref{} to have a more self-contained description.
 

### 2018-05-13 NIPS 2018/main.tex
Updated up to MGVT

@@
 Although the Gaussian assumption of the previous section is very appealing as it allows for a simple and efficient way of computing the variational objective and its gradients, we believe that such assumption almost never holds in practice.
-In fact, even for families of tasks in which the reward and transition models follow a Gaussian law, the $Q$-values might be far from it.
+In fact, even for families of tasks in which the reward and transition models are Gaussian, the $Q$-values might be far from it.
 Depending on the family of tasks under consideration and, since we are learning a distribution over weights, on the chosen function approximator, the prior might have arbitrarily complex shapes.
-When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely too fail at transferring knowledge, thus reducing to almost random exploration.
+When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely too fail at capturing any similarities between the tasks.
 We now propose a variant to successfully solve this problem, while keeping the algorithm simple and efficient enough to be applied in practice.
-In order to capture arbitrarily complex distributions, we use a kernel estimator \cite{}\todo{} for learning our prior.
-Assume we are given a set $\mathcal{W}_s$ of weights from the source tasks.
-Then, our estimated prior places a single isotropic Gaussian over each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$\footnote{Notice that this is slightly different than the typical kernel estimator (e.g., \cite{})}.
-This takes the form of a mixture of Gaussians with equally weighted components.
+
+Given the source tasks' weights $\mathcal{W}_s$, we model our estimated prior as a mixture of Gaussians with one equally weighted isotropic Gaussian centered at each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$.
+This resembles a kernel density estimator \cite{scott2015multivariate} and, due to its nonparametric nature, it allows capturing arbitrarily complex distribution.
 Consistently with the prior, we model our approximate posterior as a mixture of Gaussians.
@@
 
-Although this new model has the potential to capture much more complex distributions, it poses a major complication: the KL divergence between two mixture of Gaussians is well-known to have no closed-form equation.
-To solve this issue, we can rely on an upper bound to such quantity, so that negative ELBO we are optimizing still represents an upper bound on the KL between the approximate and true posterior.
-However, this turns out to be non-trivial as well.
-In fact, it is very easy to bound the KL between two mixtures with the KLs between each couple of components.
-However, the loss of information is such that minimizing the upper bound via gradient methods converges to a local optimum in which all components tend to go to the same point, thus almost reducing to the single Gaussian case.
-To solve this issue, we adopt the variational upper bound proposed in \cite{}\todo{Cite UB}, which we found to be able to preserve the needed information.
-We report it here for the sake of completeness.
-See the original paper for the proof.
-\begin{theorem}
+Although this new model has the potential to capture much more complex distributions, it poses a major complication: the KL divergence between two mixture of Gaussians has no closed-form expression.
+To solve this issue, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and true posterior.
+Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report here for the sake of completeness.
+We refer the reader to the original paper for the proof.
+\begin{theorem}[\cite{hershey2007approximating}]
 Let $p = \sum_{i} c_i^{(p)} f_i^{(p)}$ and $q = \sum_{j} c_j^{(q)} f_j^{(q)}$ be two mixture of Gaussian distributions, where $f_i^{(p)} = \mathcal{N}(\bm{\mu}_i^{(p)},\bm{\Sigma}_i^{(p)})$ denotes the i-th component of $p$, $c_i^{(p)}$ denotes its weight, and similarly for $q$.
@@
 Each time we require its value, we have to recompute the parameters $\chi^{(1)}$ and $\chi^{(2)}$ that tighten the bound.
-As shown in \cite{}\todo{cite them again}, this can be achieved by a simple fixed-point procedure.
-Furthermore, both terms in the approximate negative ELBO are now linear combinations of functions of the variational parameters for different components, thus their gradients can be straightforwardly derived from the ones of the Gaussian case.
+As shown in \cite{hershey2007approximating}, this can be achieved by a simple fixed-point procedure.
+Finally, both terms in the objective are now linear combinations of functions of the variational parameters of different components, and their gradients are easily derived from the ones of the Gaussian case.
+We report the derivation in App.
+\ref{}.
 

### 2018-05-13 NIPS 2018/main.tex
Updated up to TD

@@
 Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
-This rarely represents a problem since typical value-based algorithms are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{}\todo{Cite Sutton}).
+This rarely represents a problem since typical value-based algorithms are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}).
 However, our transfer settings are rather different than common RL.
-In fact, our algorithm is likely to always start from $Q$-functions that are very close to the optimum, and the only thing that needs to be done is to adapt the weights in a direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the task that is being solved.
+In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum, and the only thing that needs to be done is to adapt the weights in a direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the task that is being solved.
 Unfortunately, this property cannot be guaranteed for most semi-gradient algorithms.
-Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching the optimum, and require a lot of tuning and tricks to work well.
+Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching an optimum, and require many tricks and tuning to work well \cite{schaul2015prioritized,van2016deep}.
 This is obviously an undesirable property in our case, as we only aim at adapting already good solutions.
-Thus, we consider using a residual gradient algorithm (after \cite{}\todo{Baird}).
-In order to differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{}\todo{Cite MM}, which adopts a softened version of max called \textit{mellowmax}:
+Thus, we consider using a residual gradient algorithm \cite{baird1995residual}.
+In order to differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{asadi2017alternative}, which adopts a softened version of max called \textit{mellowmax}:
 \begin{equation}
@@
 the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
-Although residual algorithms have the sought guaranteed convergence, they are typically much slower than their semi-gradient counterpart.
-This problem was addressed in \cite{}\todo{Baird again}, where the authors proposed a simple remedy consisting in projecting the gradient in a direction that sill guarantees convergence but is also closer to the one of the semi-gradient, thus achieving higher learning speed.
+Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart.
+\cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence.
 This can be easily done by including a parameter $\psi\in[0,1]$ in the TD error gradient such that:
@@
 A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee converge).
-Since in our case we are likely to start from this latter point, we consider only higher values (e.g., above $0.5$).
 

### 2018-05-14 NIPS 2018/main.tex
Updated up to RW

@@
 Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$.
-Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}).
+Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}).
 Let $\nu$ be a probability measure over the state-space.
@@
 Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$.
-Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{}\todo{Cite MM}).
+Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}).
 Let $\nu$ be a probability measure over the state-action space.
@@
 
-Our approach is mostly related to \cite{}.
-Although we both assume the tasks to share similarities in their value functions, \cite{} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian.
+Our approach is mostly related to \cite{lazaric2010bayesian}.
+Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian.
 On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators.
-Furthermore, \cite{} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation of Sec.
-\ref{sec:mgvt} and proves again the importance of capturing more complicated task distributions.
-Another related approach is \cite{}, where the authors propose a hierarchical Bayesian model for the distribution over tasks.
-Differently from our approach and \cite{}, they consider a distribution over transition probabilities and rewards, rather than value functions.
-In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it, thus providing efficient exploration via the transferred knowledge.
-However, \cite{} consider only finite MDPs, which poses a severe limitation in the algorithm's applicability.
-On the contrary, our approach can handle high dimensional tasks by allowing powerful function approximators.
-\todo{Cite also HIP}
+Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves again the importance of capturing more complicated task distributions.
+In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over tasks.
+Differently from our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
+In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it.
+However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability.
+On the contrary, our approach can handle high-dimensional tasks.
+In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
+This approach was recently extended in \cite{killian2017robust}, where the authors replace GPs with Bayesian neural networks to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
+Should we discuss more related works?}
 
-\todo[inline]{Should we add more here or just leave a quick citation in the introduction?}
-
-The idea of exploration via value function randomization we build upon was first proposed in the RL community by \cite{}.
-The authors extend the well-known LSTD \cite{} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a Thompson sampling-like procedure.
-Such approach was recently extended by \cite{}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
+In the RL community, our approach is related to value function randomization\cite{osband2014generalization}.
+The authors extend the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
+Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
 Both these algorithms rely on the Gaussian assumption and, since they work in plain RL settings, have no informative prior available.
 On the other hand, our variational approximation allows more complex distributions (e.g., mixtures) to be adopted, while knowledge from the source tasks allows us to learn very informative priors.
-Finally, the variational approximation technique we consider in this work has been previously adopted in \cite{} to approximate an intractable posterior over the transition dynamics, which is then used to drive efficient exploration via an information-maximizing procedure.
 

### 2018-05-14 NIPS 2018/main.tex
added cartpole, mazes and mountain car figures

--- 2018-05-13 NIPS 2018/main.tex
@@
 
-Recent advances have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
+Recent advancements have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
 The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
@@
 In the typical settings of transfer in RL \cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
-Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process.
+Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed up the learning process.
 This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previous learning experience.
@@
 However, all these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
-The importance of having transfer algorithms that alleviate the need of strong assumptions and can be easily adapted to different contexts motivates us to take a more general approach.
+The importance of having transfer algorithms that alleviate the need of strong assumptions and that can be easily adapted to different contexts motivates us to take a more general approach.
 
@@
 Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
-Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
 (with respect to) the sampled value function.
@@
 
-We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov decision process (MDP).
+We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov Decision Process (MDP).
 We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$\todo{Should we provide a more transfer-oriented definition?}, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
@@
 We begin with a simple consideration: the distribution $\mathcal{D}$ over tasks clearly induces a distribution over optimal $Q$-functions.
-\todo{Should we just make the assumption that Q-functions share knowledge in their weights?} Moreover, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
-Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
-In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.
+Since, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
+In particular, we reduce the latter to a distribution $p(\bm{w})$ over \todo{over the parameters of the function approximator, perhaps?} weights.
 
-Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
+Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
 Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$.
 Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$.
-In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors.
-However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability to specific problems.
-Thus, we take a different approach to derive a more general, but still well-grounded, solution.
-Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$.
-Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ takes the form (e.g., \cite{catoni2007pac}):
+In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors \cite{}\todo{Cite somebody}.
+However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability of the approach.
+Thus, we take a different approach to derive a more general and meaningful solution.
+Recall that our final goal is to move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$.
+Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
 \begin{equation}\label{eq:gibbs}
@@
 for some parameter $\Lambda > 0$.
-\todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
+Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
 Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior.
@@
 the Gibbs posterior $q$.
-From the theory of variational inference (e.g., \cite{blei2017variational}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
+From the theory of variational inference (e.g., \cite{}\todo{cite}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
 \begin{align} \label{eq:elbo}
@@
 \end{align}
-Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term).
+Intuitively, the approximate posterior balances the trade-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term).
 Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t.
-the variational parameters $\bm{\xi}$, our objective can be easily optimized using any stochastic optimization algorithm.
+the variational parameters $\bm{\xi}$, our objective can be easily optimized with any stochastic optimization algorithm.
+
+We now highlight our general transfer procedure in Alg.
+\ref{alg:transfer}, while deferring a description of practical implementations with specific choices for the distributions involved to the next two sections.
+Given a set of weights $\mathcal{W}_s$ from the source tasks, we start by estimating the prior distribution (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
+such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters, however this does not always hold in practice.} (line 2).
+Then, at each time step of interaction, we re-sample the weights from the current approximate posterior and act greedily w.r.t.
+the corresponding $Q$-function (lines 7,8).
+This resembles the well-known Thompson Sampling approach adopted in multi-armed bandits \cite{}\todo{Cite} and allows our algorithm to efficiently explore the target task.
+In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
+After collecting and storing the new experience (lines 9-11), we draw a batch of samples from the replay buffer and a batch of weights from the posterior (line 12).
+We use these to approximate the negative ELBO, compute its gradient, and finally update the variational parameters (lines 13-15).
+
+The main advantage of our approach is that it exploits knowledge from the source tasks to perform an efficient adaptive exploration.
+Intuitively, during the first steps of interaction, our algorithm has no idea about what is the current task.
+However, it can rely on the learned prior to take early informed decisions.
+As the learning process goes on, it will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
+From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
+Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any function approximator for the $Q$-functions and any family for the prior and posterior distributions can be adopted.
+For the latter, we describe two practical choices in the next two sections.
 
@@
 \begin{algorithmic}[1]
-\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch size $M$
+\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch sizes $M_D$ and $M_{\mathcal{W}}$, prior weight $\lambda$
 \\\hrulefill
@@
 \STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
-\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$ and collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$}
+\STATE{Collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
 \STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
-\STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M}$ from $D$}
-\STATE{Estimate the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using $D'$}
-\STATE{Update $\bm{\xi}$ in the direction of $-\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using any stochastic optimizer (e.g., ADAM)}
+\STATE{Sample batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M_D}$ from $D$ and $\mathcal{W} = \left\{ \bm{w}_1, \bm{w}_2, \dots, \bm{w}_{M_{\mathcal{W}}} \right\}$ from $q_{\bm{\xi}}$}
+\STATE{Approximate objective: $\mathcal{L}(\bm{\xi}) = \frac{1}{M_{\mathcal{W}}}\sum_{\bm{w}\in\mathcal{W}}\norm{B(\bm{w})}_{D'}^2 - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}\ ||\ p\right)$}
+\STATE{Compute the gradient $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$}
+\STATE{Update $\bm{\xi}$ in the direction of $\nabla_{\bm{\xi}}\mathcal{L}(\bm{\xi})$ using any stochastic optimizer (e.g., ADAM)}
 \ENDWHILE
@@
 
-We now highlight our general transfer procedure in Alg.
-\ref{alg:transfer}, while deferring a description of specific choices for the distributions involved to the next two sections.
-Given a set of weights $\mathcal{W}_s$ from the source tasks' optimal $Q$-functions, we start by estimating the prior distribution (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
-such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters.
-However, we are not making this assumption at this point.} (line 2).
-Then, at each time step of interaction, we re-sample the weights from the current approximate posterior and act greedily w.r.t.
-the corresponding $Q$-function (lines 7,8).
-After collecting and storing the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and, finally, update the variational parameters (line 13).
-
-The key property of our approach is the weight resampling at line 7.
-This resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
-In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
-This allows an efficient adaptive exploration of the target task.
-Intuitively, during the first steps of interaction, the agent is very uncertain about the current task and such uncertainty induces stochasticity in the chosen actions, allowing rather informed exploration to take place.
-Consider, for instance, that actions that are bad on average for all tasks are very unlikely to be sampled, while this cannot happen in uninformed exploration strategies, like $\epsilon$-greedy, before learning takes place.
-As the learning process goes on, the algorithm will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
-From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
-
-Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any pior/posterior distributions can be adopted.
-For the latter, we describe two practical choices in the next two sections.
-
 \subsection{Gaussian Variational Transfer}\label{sec:gvt}
 
-We now restrict to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement.
-We assume that optimal $Q$-functions (or better, their weights) follow a multivariate Gaussian distribution.
-That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
+We now restrict ourselves to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement.
+We assume that optimal $Q$-functions according to our task distribution (or better, their weights) follow a multivariate Gaussian law.
+That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using, e.g., maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
 Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$.
-To prevent the covariance from becoming not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $\bm{L}$ instead.
-In this case, deriving the gradient of the objective is very simple.
-Both the KL between two multivariate Gaussians and its gradients have a simple closed-form expression.
-The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}).
-Although these results are well-known in the literature, we report them in App.
-\ref{} to have a more self-contained description.
+Additionally, to prevent the covariance from going not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $L$ instead.
 
@@
 Although the Gaussian assumption of the previous section is very appealing as it allows for a simple and efficient way of computing the variational objective and its gradients, we believe that such assumption almost never holds in practice.
-In fact, even for families of tasks in which the reward and transition models are Gaussian, the $Q$-values might be far from it.
+In fact, even for families of tasks in which the reward and transition models follow a Gaussian law, the $Q$-values might be far from it.
 Depending on the family of tasks under consideration and, since we are learning a distribution over weights, on the chosen function approximator, the prior might have arbitrarily complex shapes.
-When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely too fail at capturing any similarities between the tasks.
+When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely too fail at transferring knowledge, thus reducing to almost random exploration.
 We now propose a variant to successfully solve this problem, while keeping the algorithm simple and efficient enough to be applied in practice.
-
-Given the source tasks' weights $\mathcal{W}_s$, we model our estimated prior as a mixture of Gaussians with one equally weighted isotropic Gaussian centered at each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$.
-This resembles a kernel density estimator \cite{scott2015multivariate} and, due to its nonparametric nature, it allows capturing arbitrarily complex distribution.
+In order to capture arbitrarily complex distributions, we use a kernel estimator \cite{}\todo{} for learning our prior.
+Assume we are given a set $\mathcal{W}_s$ of weights from the source tasks.
+Then, our estimated prior places a single isotropic Gaussian over each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$\footnote{Notice that this is slightly different than the typical kernel estimator (e.g., \cite{})}.
+This takes the form of a mixture of Gaussians with equally weighted components.
 Consistently with the prior, we model our approximate posterior as a mixture of Gaussians.
@@
 
-Although this new model has the potential to capture much more complex distributions, it poses a major complication: the KL divergence between two mixture of Gaussians has no closed-form expression.
-To solve this issue, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and true posterior.
-Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report here for the sake of completeness.
-We refer the reader to the original paper for the proof.
-\begin{theorem}[\cite{hershey2007approximating}]
+Although this new model has the potential to capture much more complex distributions, it poses a major complication: the KL divergence between two mixture of Gaussians is well-known to have no closed-form equation.
+To solve this issue, we can rely on an upper bound to such quantity, so that the negative ELBO we are optimizing still represents an upper bound on the KL between the approximate and true posterior.
+However, this turns out to be non-trivial as well.
+In fact, it is very easy to bound the KL between two mixtures with the KLs between each couple of components.
+However, the loss of information is such that minimizing the upper bound via gradient methods converges to a local optimum in which all components tend to go to the same point, thus almost reducing to the single Gaussian case.
+To solve this issue, we adopt the variational upper bound proposed in \cite{}\todo{Cite UB}, which we found to be able to preserve the needed information.
+We report it here for the sake of completeness.
+See the original paper for the proof.
+\begin{theorem}
 Let $p = \sum_{i} c_i^{(p)} f_i^{(p)}$ and $q = \sum_{j} c_j^{(q)} f_j^{(q)}$ be two mixture of Gaussian distributions, where $f_i^{(p)} = \mathcal{N}(\bm{\mu}_i^{(p)},\bm{\Sigma}_i^{(p)})$ denotes the i-th component of $p$, $c_i^{(p)}$ denotes its weight, and similarly for $q$.
@@
 Each time we require its value, we have to recompute the parameters $\chi^{(1)}$ and $\chi^{(2)}$ that tighten the bound.
-As shown in \cite{hershey2007approximating}, this can be achieved by a simple fixed-point procedure.
-Finally, both terms in the objective are now linear combinations of functions of the variational parameters of different components, and their gradients are easily derived from the ones of the Gaussian case.
-We report the derivation in App.
-\ref{}.
+As shown in \cite{}\todo{cite them again}, this can be achieved by a simple fixed-point procedure.
+Furthermore, both terms in the approximate negative ELBO are now linear combinations of functions of the variational parameters for different components, thus their gradients can be straightforwardly derived from the ones of the Gaussian case.
 
@@
 Then, in Sec.
-\ref{sec:cc}, we consider two classic control benchmarks, namely cartpole and mountain car.
+\ref{sec:cc}, we consider two classic control benchmarks, namely Cartpole and Mountain Car.
 We conclude with a complex maze navigation task in Sec.
@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.0cm]{images/rooms.pdf}
+    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=3cm, width=2.0cm]{images/rooms2.pdf}
     \caption{}
@@
 \ref{sec:td}.
-In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until converge.
+In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until convergence.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
@@
 \ref{}.
-As expected, the no-transfer algorithm NT fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
+As expected, the no-transfer (NT) algorithm fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
 On the other hand, all our algorithms achieve a significant speed-up and are able to converge to the optimal performance in few iterations, with GVT being slightly slower.
@@
 Interestingly, MGVT seems almost unaffected by this change, proving that is has sufficient representation power to generalize to slightly different task distributions.
-The same does not hold for GVT, which now is not able to solve many of the sampled target tasks (this is the reason for the very high variance).
+The same does not hold for GVT, which now is not able to solve many of the sampled target tasks,thus the very high variance.
 This proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
@@
 \ref{}.
-Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is close to the sides are very unlikely.
+Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
 Fig.
@@
 As expected GVT achieves poor performance on very unlikely tasks, even after many iterations.
-In fact, estimating a single Gaussian distribution definitely implies some information loss, especially about the unlikely tasks.
+In fact, estimating a single Gaussian distribution definitely entails some information loss, especially about the unlikely tasks.
 On the other hand, MGVT keeps such information and, consequently, performs much better.
@@
 
+\begin{figure*}[t] 
+  \begin{subfigure}[b]{0.15\textwidth}
+    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze13.png}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{(a) Sample Maze, (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 0, 6, 13---see App. \ref{}}
+  \label{fig:ccmazeplots}
+\end{figure*}
+
+To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
+In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
+Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
+We kept a discount factor of $\gamma=0.99$ for both environments.
+Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
+We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
+
+In Fig.
+\ref{}, we show the results of transfer in Cartpole from which it is easily noticed a near-optimal jump-start in both GVT and 1-MGVT that during the following iterations converges to the optimal performance.
+In the other hand, transfer in Mountain Car as shown in Fig.
+\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence within the same number of iterations to the optimal performances.
+
 \subsection{Maze Navigation} \label{sec:mn}
@@
 For this setting we propose a maze environment, such as those in Fig.
-*, for a robotic agent to navigate.
+\ref{}, for a robotic agent to navigate.
 We created a set of 20 mazes of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze.
-In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance/angle each time an action is performed: \emph{move forward, rotate counter- and clockwise}.
-Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of 2 and a field of vision from -90º to 90º relative to its orientation.
+In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}).
+Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision from $-90º$ to $90º$ relative to its orientation.
 In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike.
 Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation.
-Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation.
+Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.
 
 The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience.
-Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is robust to negative transfer.
+Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is to negative transfer.
 
-These mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
+In App \ref the mazes used are enumerated.
+These were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
 Finally, the MGVT algorithm, with one component for the posterior distribution, was used to solve the target tasks shown in Fig.

### 2018-05-14 NIPS 2018/main.tex

--- 2018-05-14 NIPS 2018/main.tex
@@
 
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.15\textwidth}
+    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze13.png}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.27\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{(a) Sample Maze, (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 0, 6, 13---see App. \ref{}}
+  \label{fig:ccmazeplots}
+\end{figure*}
+
+To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
+In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
+Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
+We kept a discount factor of $\gamma=0.99$ for both environments.
+Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
+We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
+
+In Fig.
+\ref{}, we show the results of transfer in Cartpole from which it is easily noticed a near-optimal jump-start in both GVT and 1-MGVT that during the following iterations converges to the optimal performance.
+In the other hand, transfer in Mountain Car as shown in Fig.
+\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence within the same number of iterations to the optimal performances.
+
 \subsection{Maze Navigation} \label{sec:mn}

### 2018-05-14 NIPS 2018/main.tex
added classic control results, mazes, images

@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze13.png}
+    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze6.png}
     \caption{}
@@
     \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
+    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev.pdf}
     \caption{}
   \end{subfigure}
-  \caption{(a) Sample Maze, (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 0, 6, 13---see App. \ref{}}
+  \caption{(a) Sample Maze (Maze 6), (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 6 and 13---see App.
+\ref{}.}
   \label{fig:ccmazeplots}
@@
 We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
-
+Analogously to Sec.
+\ref{sec:gw}, in Fig.
+\ref{} and \ref{} we show the expected return---as the average of the last $50$ episodes of lerning---of transfer for $20$ independent runs randomizing the sources and target tasks.
 In Fig.
-\ref{}, we show the results of transfer in Cartpole from which it is easily noticed a near-optimal jump-start in both GVT and 1-MGVT that during the following iterations converges to the optimal performance.
-In the other hand, transfer in Mountain Car as shown in Fig.
-\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence within the same number of iterations to the optimal performances.
+\ref{}, that corresponds to Cartpole, it is easily noticeable a near-optimal jump-start, in both GVT and 1-MGVT, that during the following iterations converges to the optimal performance.
+Furthermore, transfer in Mountain Car as shown in Fig.
+\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence, within the same number of iterations, to the optimal performances.
 
@@
 \ref{}, for a robotic agent to navigate.
-We created a set of 20 mazes of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze.
+We created a set of 20 mazes---see App \ref{}---of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze.
 In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}).
-Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision from $-90º$ to $90º$ relative to its orientation.
+Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measurements to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision of $9$ equally-spaced directions in $[-90,90º]$ relative to its orientation.
 In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike.
@@
 The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience.
-Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is to negative transfer.
+Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting suitable to assess how robust our algorithm is to negative transfer.
 
-In App \ref the mazes used are enumerated.
-These were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
-Finally, the MGVT algorithm, with one component for the posterior distribution, was used to solve the target tasks shown in Fig.
-*.
+The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
+Finally, the 1-MGVT algorithm was used to solve the target tasks---Mazes 6 and 13.
+As before, $20$ independent runs with randomized sources to transfer are averaged and shown in Fig.
+\ref{}, in this case $5$ source tasks were used for each trial.
+While these mazes pose a challenge for our algorithm, we can see that 1-MGVT is capable to still capture useful information from the sources and adapt to the target mazes which is demonstrated by the increased slope in the learning curve.
+\todo{actually, decide how to improve these results}
 

### 2018-05-14 NIPS 2018/main.tex
Small edits

--- 2018-05-14 NIPS 2018/main.tex
@@
 
-Recent advancements have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
+Recent advances have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
 The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
@@
 In the typical settings of transfer in RL \cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
-Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed up the learning process.
+Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process.
 This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previous learning experience.
@@
 However, all these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
-The importance of having transfer algorithms that alleviate the need of strong assumptions and that can be easily adapted to different contexts motivates us to take a more general approach.
+The importance of having transfer algorithms that alleviate the need of strong assumptions and can be easily adapted to different contexts motivates us to take a more general approach.
 
@@
 Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
-Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
 (with respect to) the sampled value function.
@@
 
-We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov Decision Process (MDP).
+We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov decision process (MDP).
 We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$\todo{Should we provide a more transfer-oriented definition?}, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
@@
 In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
-This approach was recently extended in \cite{killian2017robust}, where the authors replace GPs with Bayesian neural networks to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
+Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, so as to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
 Should we discuss more related works?}
 
-In the RL community, our approach is related to value function randomization\cite{osband2014generalization}.
-The authors extend the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
+In the RL community, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
 Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
@@
 
-In this section, we provide an experimental evaluation of our approach.
-We begin by analyzing the behavior of our algorithm on a toy problem in Sec.
-\ref{sec:gw}.
-Then, in Sec.
-\ref{sec:cc}, we consider two classic control benchmarks, namely Cartpole and Mountain Car.
-We conclude with a complex maze navigation task in Sec.
-\ref{sec:mn}.
-In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using mixture of Gaussians with $c$ components ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration.
+In this section, we provide an experimental evaluation of our approach in three different domains with increasing level of difficulty.
+In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using a $c$-component mixture of Gaussians ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration.
 To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=3cm, width=2.0cm]{images/rooms2.pdf}
+    \includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.0cm]{images/rooms.pdf}
     \caption{}
@@
 \ref{sec:td}.
-In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until convergence.
+In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until converge.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
@@
 \ref{}.
-As expected, the no-transfer (NT) algorithm fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
+As expected, the no-transfer algorithm NT fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
 On the other hand, all our algorithms achieve a significant speed-up and are able to converge to the optimal performance in few iterations, with GVT being slightly slower.
@@
 Interestingly, MGVT seems almost unaffected by this change, proving that is has sufficient representation power to generalize to slightly different task distributions.
-The same does not hold for GVT, which now is not able to solve many of the sampled target tasks,thus the very high variance.
+The same does not hold for GVT, which now is not able to solve many of the sampled target tasks (this is the reason for the very high variance).
 This proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
@@
 \ref{}.
-Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
+Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is close to the sides are very unlikely.
 Fig.
@@
 As expected GVT achieves poor performance on very unlikely tasks, even after many iterations.
-In fact, estimating a single Gaussian distribution definitely entails some information loss, especially about the unlikely tasks.
+In fact, estimating a single Gaussian distribution definitely implies some information loss, especially about the unlikely tasks.
 On the other hand, MGVT keeps such information and, consequently, performs much better.
@@
 
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze13.png}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-    \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-    \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{(a) Sample Maze, (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 0, 6, 13---see App. \ref{}}
-  \label{fig:ccmazeplots}
-\end{figure*}
-
-To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
-In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
-Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
-We kept a discount factor of $\gamma=0.99$ for both environments.
-Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
-We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
-
-In Fig.
-\ref{}, we show the results of transfer in Cartpole from which it is easily noticed a near-optimal jump-start in both GVT and 1-MGVT that during the following iterations converges to the optimal performance.
-In the other hand, transfer in Mountain Car as shown in Fig.
-\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence within the same number of iterations to the optimal performances.
-
 \subsection{Maze Navigation} \label{sec:mn}
@@
 For this setting we propose a maze environment, such as those in Fig.
-\ref{}, for a robotic agent to navigate.
+*, for a robotic agent to navigate.
 We created a set of 20 mazes of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze.
-In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}).
-Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision from $-90º$ to $90º$ relative to its orientation.
+In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance/angle each time an action is performed: \emph{move forward, rotate counter- and clockwise}.
+Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of 2 and a field of vision from -90º to 90º relative to its orientation.
 In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike.
 Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation.
-Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.
+Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation.
 
 The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit  in different maze configurations leveraging its previous experience.
-Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is to negative transfer.
+Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is robust to negative transfer.
 
-In App \ref the mazes used are enumerated.
-These were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
+These mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
 Finally, the MGVT algorithm, with one component for the posterior distribution, was used to solve the target tasks shown in Fig.
@@
 \end{equation}
-for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are \cite{}\todo{Cite matrix cookboox}:
+for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are:
 \begin{equation}
@@
 Finally, the gradients w.r.t.
-the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{}\todo{Cite deepmind and another}):
+the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}):
 \begin{equation}
@@
 
-Transfer approaches to mention:
-\begin{itemize}
-\item Taylor 2009: survey
-\item Konidaris and Barto transfer shaped reward functions PROs: this allows the agent to have a more goal-directed behavior, thus limiting unnecessary random exploration CONs: applicable only to simple problems, does not scale
-\item Wilson 2007 propose a hierarchical Bayesian model for the distribution over tasks PROs it explicitly models the uncertainty over which tasks are being solved, thus quickly adapting to new ones and allowing informed exploration decisions to be taken
-\item Lazaric 2008 transfer samples PROs select good samples, can scale to continuous domains CONs eps greedy is used
-\item Taylor 2008 transfer samples for model-based RL PROs good exploration via model-based RL CONs does not scale, can negatively transfer when tasks are very different
-\item Lazaric 2010 propose a hierarchical bayesian model for the distribution over value functions PROs quickly adapts to new tasks, non-parameteric (GP) models CONs scaling, strong assumptions (GPTD)
-\item Fernandez and veloso 2006 propose an exploration strategy based on probabilistic policy reuse PROs good exploration (?) CONs Do not try to figure out which policies are good or bad
-\item Brunskill propose a method to transfer in model based RL (E3) - PROs theory, exploration CONs scaling
-\item Barreto use successor features PROs simple, theory CONs eps-greedy exploration
-\end{itemize}
-
-Exploration approaches to mention:
-\begin{itemize}
-\item Osband 2014 propose a method to efficiently explore via randomized value functions
-\item Osband 2016 adapt such algorithm to DQNs
-\item Houthooft 2016 use variational inference to approximate the posterior distribution over parameters of the dynamics, and use that to drive exploration
-\item Azizzadenesheli 2018 extend Osband 2016 to use Bayesian DQN instead. Still makes Gaussian assumptions though
-\end{itemize}
-
 \end{document}

### 2018-05-14 NIPS 2018/main.tex

@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=3cm, width=2.0cm]{images/rooms2.pdf}
+    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze6.png}
+    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=2.6cm, width=2.0cm]{images/maze/maze6.png}
     \caption{}

### 2018-05-14 NIPS 2018/main.tex
Remove thm2 + moved RW

@@
 
-\begin{restatable}{theorem}{thmmv} \label{th:mmv}
-Let $V$ be the fixed-point of the optimal Bellman operator $T$, and $Q$ the corresponding action-value function.
-Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$.
-Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}).
-Let $\nu$ be a probability measure over the state-space.
-Then, for any $p \geq 1$:
-\begin{equation}
-\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{(1-\gamma)^2}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
-\end{equation}
-\end{restatable}
-
 \begin{restatable}{theorem}{thmm} \label{th:mm}
@@
 Let $\nu$ be a probability measure over the state-action space.
-Then, for any $p \geq 1$:
+Then, for any $p \geq 1$:\todo{Correct measure on the rhs}
 \begin{equation}
@@
 \end{restatable}
-
-\section{Related Works}
-
-Our approach is mostly related to \cite{lazaric2010bayesian}.
-Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian.
-On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators.
-Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves again the importance of capturing more complicated task distributions.
-In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over tasks.
-Differently from our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
-In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it.
-However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability.
-On the contrary, our approach can handle high-dimensional tasks.
-In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
-Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, so as to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
-Should we discuss more related works?}
-
-In the RL community, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
-Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
-Both these algorithms rely on the Gaussian assumption and, since they work in plain RL settings, have no informative prior available.
-On the other hand, our variational approximation allows more complex distributions (e.g., mixtures) to be adopted, while knowledge from the source tasks allows us to learn very informative priors.
 
@@
 \subsection{The Rooms Problem} \label{sec:gw}
+
+We consider an agent navigating in the rooms environment depicted in Fig.
+\ref{}.
+The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
+The rooms are connected by small doors whose positions are unknown to the agent.
+The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
+After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise with $0.2$ standard deviation.
+In case the agent hits a wall, its position remains unchanged.
+The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
+We consider a distribution over tasks in which doors have a fixed width of $1$, while their positions are sampled uniformly in $[0.5,9.5]$.
+Since the agent does not know where the doors are located in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
+While this might be a complicated problem for plain RL, our transfer algorithm should be able to quickly figure out the door positions.
+In fact, notice that, although different, the optimal $Q$-functions for all tasks share some similarities.
+For example, once the agent has passed the last door before the goal, the $Q$-values are exactly the same in all tasks.
+This does not hold for positions nearby the start state.
+However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).
+Thus, we expect our algorithm to efficiently explore any target task.
 
@@
 \end{figure*}
-
-We consider an agent navigating in the rooms environment depicted in Fig.
-\ref{}.
-The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
-The rooms are connected by small doors whose positions are unknown to the agent.
-The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
-After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise with $0.2$ standard deviation.
-In case the agent hits a wall, its position remains unchanged.
-The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
-We consider a distribution over tasks in which doors have a fixed width of $1$, while their positions are sampled uniformly in $[0.5,9.5]$.
-Since the agent does not know where the doors are located in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
-While this might be a complicated problem for plain RL, our transfer algorithm should be able to quickly figure out the door positions.
-In fact, notice that, although different, the optimal $Q$-functions for all tasks share some similarities.
-For example, once the agent has passed the last door before the goal, the $Q$-values are exactly the same in all tasks.
-This does not hold for positions nearby the start state.
-However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).
-Thus, we expect our algorithm to efficiently explore any target task.
 
@@
 
+To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
+In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
+Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
+We kept a discount factor of $\gamma=0.99$ for both environments.
+Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
+We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
+Analogously to Sec.
+\ref{sec:gw}, in Fig.
+\ref{} and \ref{} we show the expected return---as the average of the last $50$ episodes of lerning---of transfer for $20$ independent runs randomizing the sources and target tasks.
+In Fig.
+\ref{}, that corresponds to Cartpole, it is easily noticeable a near-optimal jump-start, in both GVT and 1-MGVT, that during the following iterations converges to the optimal performance.
+Furthermore, transfer in Mountain Car as shown in Fig.
+\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence, within the same number of iterations, to the optimal performances.
+
+\subsection{Maze Navigation} \label{sec:mn}
+
 \begin{figure*}[t]
@@
 
-To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
-In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
-Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
-We kept a discount factor of $\gamma=0.99$ for both environments.
-Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
-We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
-Analogously to Sec.
-\ref{sec:gw}, in Fig.
-\ref{} and \ref{} we show the expected return---as the average of the last $50$ episodes of lerning---of transfer for $20$ independent runs randomizing the sources and target tasks.
-In Fig.
-\ref{}, that corresponds to Cartpole, it is easily noticeable a near-optimal jump-start, in both GVT and 1-MGVT, that during the following iterations converges to the optimal performance.
-Furthermore, transfer in Mountain Car as shown in Fig.
-\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence, within the same number of iterations, to the optimal performances.
-
-\subsection{Maze Navigation} \label{sec:mn}
-
 For this setting we propose a maze environment, such as those in Fig.
@@
 
+\section{Related Works}
+
+Our approach is mostly related to \cite{lazaric2010bayesian}.
+Although we both assume the tasks to share similarities in their value functions, \cite{lazaric2010bayesian} consider only linear approximators and adopt a hierarchical Bayesian model of the corresponding weights' distribution, which is assumed Gaussian.
+On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators.
+Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves again the importance of capturing more complicated task distributions.
+In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over tasks.
+Differently from our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
+In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it.
+However, \cite{wilson2007multi} consider only finite MDPs, which poses a severe limitation on the algorithm's applicability.
+On the contrary, our approach can handle high-dimensional tasks.
+In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
+Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, so as to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
+Should we discuss more related works?}
+
+In the RL community, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
+Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
+Both these algorithms rely on the Gaussian assumption and, since they work in plain RL settings, have no informative prior available.
+On the other hand, our variational approximation allows more complex distributions (e.g., mixtures) to be adopted, while knowledge from the source tasks allows us to learn very informative priors.
+
 \section{Conclusion}
@@
 \section{Proofs}
-
-\thmmv*
-\begin{proof}
-We begin by noticing that:
-\begin{align*}
-\norm{V-\wt{V}}_{\nu,p}^p =\ & \norm{TV - \wt{T}\wt{V}}_{\nu,p}^p \\ =\ &
-\norm{TV - \wt{T}V + \wt{T}V - \wt{T}\wt{V}}_{\nu,p}^p \\ \leq\ &
-\norm{TV - \wt{T}V}_{\nu,p}^p + \norm{\wt{T}V - \wt{T}\wt{V}}_{\nu,p}^p \\ \leq\ &
-\norm{TV - \wt{T}V}_{\nu,p}^p + \gamma\norm{V - \wt{V}}_{\nu,p}^p
-\end{align*}
-where the first inequality follows from Minkowsky's inequality and the second one from the contraction property of the mellow Bellman operator. This implies that:
-\begin{align} \label{eq:mm1}
-\norm{V-\wt{V}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TV - \wt{T}V}_{\nu,p}^p
-\end{align}
-Let us bound the norm on the right-hand side separately.
-In order to do that, we will bound the function $\abs{TV(s) - \wt{T}V(s)}$ point-wisely for any state $s$.
-By applying the definition of the optimal and mellow Bellman operators, we obtain:
-\begin{align*}
-\abs{TV(s) - \wt{T}V(s)} =\ & \abs{\max_{a}\lbrace R(s,a) + \gamma\mathbb{E}\left[V(s')\right] \rbrace - \mm_{a}\lbrace R(s,a) + \gamma\mathbb{E}\left[V(s')\right] \rbrace}\\ =\ & \abs{\max_a Q(s,a) - \mm_a Q(s,a)}
-\end{align*}
-Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta$ induced by $\kappa$ \cite{}\todo{Cite MM}.
-Thus, we can write:
-\begin{align} \label{eq:mm2}
-\abs{\max_a Q(s,a) - \mm_a Q(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q(s,a) - \sum_a \pi_{\beta}(a|s)Q(s,a)}\notag\\ =\ & \abs{\sum_a Q(s,a) \left( \pi^*(a|s) - \pi_{\beta}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q(s,a)} \abs{\pi^*(a|s) - \pi_{\beta}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta}(a|s)}
-\end{align}
-where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q$ and $\pi_{\beta}$ is the Boltzmann distribution induced by $Q$ with inverse temperature $\beta$:
-\begin{align*}
-\pi_{\beta}(a|s) = \frac{e^{\beta Q(s,a)}}{\sum_{a'}e^{\beta Q(s,a')}}
-\end{align*}
-Denote by $a_1(s)$ the optimal action for state $s$ under $Q$. We can then write:
-\begin{align} \label{eq:mm3}
-\sum_a\abs{\pi^*(a|s) - \pi_{\beta}(a|s)} =\ & \abs{\pi^*(a_1(s)|s) - \pi_{\beta}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi^*(a|s) - \pi_{\beta}(a|s)}\notag\\ =\ & \abs{1 - \pi_{\beta}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi_{\beta}(a|s)}\notag\\ =\ & 2\abs{1 - \pi_{\beta}(a_1(s)|s)}
-\end{align}
-Finally, let us bound this last term:
-\begin{align} \label{eq:mm4}
-\abs{1 - \pi_{\beta}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta Q(s,a_1(s))}}{\sum_{a'}e^{\beta Q(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta \left( Q(s,a_1(s)) - Q(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta g(s)}}{\sum_{a'}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta g(s)}}{e^{\beta g(s)} + \sum_{a' \neq a_1(s)}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta g(s)}}{e^{\beta g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
-\end{align}
-Combining Eq. \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:
-\begin{align*}
-\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2R_{max}}{1-\gamma}\abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
-\end{align*}
-Taking the norm and plugging this into Eq. \eqref{eq:mm1} concludes the proof.
-\end{proof}
 

### 2018-05-14 NIPS 2018/main.tex
Added part of proof

@@
 \newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
-\title{What the hell is the title of this paper?}
+\title{Variational Approximations for Transfer in Reinforcement Learning}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:general-bound}
 Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
@@
 This concludes the proof.
+\end{proof}
+
+\begin{theorem}\label{th:main-gaussian}
+aaa
+\end{theorem}
+\begin{proof}
+Using Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}},\wh{\bm{\Sigma}})$, we have:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align*}
+where the second inequality is due to the fact, since Lemma \ref{lemma:general-bound} contains an infimum over the variational parameters, we can upper bound its right-hand side by choosing any specific $\bm{\xi}$ from $\Xi$.
+Here, we choose $\bm{\mu} = \bm{w}^*$ and $\bm{\Sigma} = c\bm{I}$, for some positive constant $c>0$.
+Let us now bound these terms separately.
+
+\paragraph*{Bounding the expected TD error}
+
+We have:
+\begin{align}\label{eq:thg-3}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
+\end{align}
+Let us bound these two terms point-wisely for each $s,a$. For the first expectation, we have:
+\begin{align}\label{eq:thg-1}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\notag\\ =\ & R(s,a) + \gamma\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] - \bm{w}^{*T}\bm{\phi}(s,a)
+\end{align}
+To bound the second term, we adopt Jensen's inequality:
+\begin{align}\label{eq:thg-2}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^T\bm{\phi}(s',a') }\right]\notag\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right]
+\end{align}
+Now, since we know that $\bm{w}^T\bm{\phi}(s',a') \sim \mathcal{N}(\bm{w}^{*T}\bm{\phi}(s',a'),c\ \bm{\phi}(s',a')^T\bm{\phi}(s',a'))$, $e^{\kappa\bm{w}^T\bm{\phi}(s',a')}$ follows a log-normal distribution with mean $e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}$.
+Thus:
+\begin{align*}
+\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right] =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}}\\ =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')} + \frac{1}{2}\kappa c\bm{\phi}_{max}\\ =\ & \mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa c\bm{\phi}_{max}
+\end{align*}
+Plugging this into \ref{eq:thg-2} and then into \ref{eq:thg-1}, we obtain:
+\begin{align*}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max} - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}(\bm{w}^{*}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}
+\end{align*}
+This implies:
+\begin{align*}
+\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2
+\end{align*}
+where the second inequality follows from Cauchy-Schwarz inequality. Going back to \ref{eq:thg-3}, the first term can now be upper bounded by:
+\begin{align*}
+\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2
+\end{align*}
+Let us now consider the variance term of \ref{eq:thg-3} and derive a bound that holds point-wisely for any $s,a$. We have:
+\begin{align*}
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}c\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]
+\end{align*}
+From Cauchy-Schwarz inequality:
+\begin{align*}
+c\abs{\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)} \leq\ & c\norm{\bm{w}}\norm{\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)}\\ \leq\ & c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}
+\end{align*}
+Then, the random variable over which the variance is computed is limited in $[-c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma},c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}]$ and the variance can be straightforwardly bounded using Popoviciu's inequality:
+\begin{align*}
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq \gamma^2 \frac{1}{4}\left(2c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}\right)^2 = \left(c\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+\end{align*}
+We can finally plug everything into \ref{eq:thg-3}, thus obtaining:
+\begin{align*}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + \left(c\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+\end{align*}
 \end{proof}
@@
 
+\paragraph*{Bounding the KL divergence}
+
+We have:
+
 \subsection{Mixture of Gaussian Variational Transfer}

### 2018-05-14 NIPS 2018/main.tex
added MGVT app

--- 2018-05-14 NIPS 2018/main.tex
@@
 We refer the reader to the original paper for the proof.
-\begin{theorem}[\cite{hershey2007approximating}]
+\begin{theorem}[\cite{hershey2007approximating}]\label{th:ukl}
 Let $p = \sum_{i} c_i^{(p)} f_i^{(p)}$ and $q = \sum_{j} c_j^{(q)} f_j^{(q)}$ be two mixture of Gaussian distributions, where $f_i^{(p)} = \mathcal{N}(\bm{\mu}_i^{(p)},\bm{\Sigma}_i^{(p)})$ denotes the i-th component of $p$, $c_i^{(p)}$ denotes its weight, and similarly for $q$.
@@
 for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are:
-\begin{equation}
+\begin{equation}\label{eq:klgradmu}
 \nabla_{\bm{\mu}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p)
 \end{equation}
-\begin{equation}
+\begin{equation}\label{eq:klgradL}
 \nabla_{\bm{L}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1}\bm{L} - (\bm{L}^{-1})^T 
@@
 the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}):
-\begin{equation}
+\begin{equation}\label{eq:tdgradmu}
 \nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
 \end{equation} 
-\begin{equation}
+\begin{equation}\label{eq:tdgradL}
 \nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
@@
 \subsection{Mixture of Gaussian Variational Transfer}
+
+For the implementation of the Mixture of Gaussian Variational Transfer, we use the upper bound on the KL divergence between two Mixtures of Gaussians, as in Theorem\ref{th:ukl}, to obtain an upper bound on the negative ELBO in Equation\ref{eq:elbo}.
+Consider we have $C$ components for the posterior family $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$ and a prior distribution, constructed from the set of weights $\mathcal{W}_s = \left\lbrace \bm{w}_1,..., \bm{w}_{|\mathcal{W}_s|} \right\rbrace$ of the sources' optimal $Q$-functions, $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{j=1}^{|\mathcal{W}_s|}\mathcal{N}(\bm{w}|\bm{w}_j,\sigma_p^2\bm{I})$.
+
+\begin{equation}\label{eq:ukl}
+KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{equation}
+
+And substituting \ref{eq:ukl} in the negative ELBO in \ref{eq:elbo} we get the following upper bound.
+
+\begin{equation}
+\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] + KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{equation}
+
+Finally, using this upper bound as objective of our optimization problem, we can then exploit the linearity of the expectation operator to obtain
+
+\begin{equation}
+\widetilde{\mathcal{L}}(\bm{\xi}) = \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] + KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{equation}
+
+that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Eq.
+\ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL}.
 

### 2018-05-14 NIPS 2018/main.tex
Completed proof

--- 2018-05-14 NIPS 2018/main.tex
@@
 Using Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}},\wh{\bm{\Sigma}})$, we have:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
-\end{align*}
-where the second inequality is due to the fact, since Lemma \ref{lemma:general-bound} contains an infimum over the variational parameters, we can upper bound its right-hand side by choosing any specific $\bm{\xi}$ from $\Xi$.
+\begin{align}\label{eq:thg-4}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align}
+where the second inequality is due to the fact that, since Lemma \ref{lemma:general-bound} contains an infimum over the variational parameters, we can upper bound its right-hand side by choosing any specific $\bm{\xi}$ from $\Xi$.
 Here, we choose $\bm{\mu} = \bm{w}^*$ and $\bm{\Sigma} = c\bm{I}$, for some positive constant $c>0$.
@@
 \begin{align*}
-Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}c\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}\sqrt{c}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]
 \end{align*}
@@
 \begin{align*}
-c\abs{\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)} \leq\ & c\norm{\bm{w}}\norm{\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)}\\ \leq\ & c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}
+\sqrt{c}\abs{\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)} \leq\ & \sqrt{c}\norm{\bm{w}}\norm{\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)}\\ \leq\ & \sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}
 \end{align*}
-Then, the random variable over which the variance is computed is limited in $[-c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma},c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}]$ and the variance can be straightforwardly bounded using Popoviciu's inequality:
+Then, the random variable over which the variance is computed is limited in $[-\sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma},\sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}]$ and the variance can be straightforwardly bounded using Popoviciu's inequality:
 \begin{align*}
-Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq \gamma^2 \frac{1}{4}\left(2c\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}\right)^2 = \left(c\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq \gamma^2 \frac{1}{4}\left(2\sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}\right)^2 = c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + \left(c\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+\end{align*}
+
+\paragraph*{Bounding the KL divergence}
+
+We have:
+\begin{align*}
+KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^K} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -K \right)\\ \leq\ & \frac{1}{2}K\log\frac{\sigma_{max}}{c} + \frac{1}{2}K\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}
+\end{align*}
+Now, putting all together into \ref{eq:thg-4}:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \upsilon(\bm{w}^*)\sqrt{c}\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align*}
+where $\upsilon(\bm{w}^*) = \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$. Since the bound holds for any $c>0$, we can set it to $1/N$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K \log(\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + \frac{1}{\sqrt{N}}\left(\upsilon(\bm{w}^*) + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\log\frac{2}{\delta}}\right)
+\end{align*}
+Finally, defining the constants $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda K}{\sigma_{min}}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K \log(\sigma_{max} + \log N)$\todo{$c_2$ actually contains $N$.
+Should we make this more explicit?}, and $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, we obtain:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}
 \end{align*}
@@
 
-\paragraph*{Bounding the KL divergence}
-
-We have:
-
 \subsection{Mixture of Gaussian Variational Transfer}

### 2018-05-14 NIPS 2018/main.tex
appendix C

--- 2018-05-14 NIPS 2018/main.tex
@@
 that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Eq.
-\ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL}.
+\ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL} derived for the Gaussian case.
 
 \section{Additional Details on the Experiments}
+
+In the present section we present the hyper-parameters and corresponding values that were used for the experiments presented in this paper.
+
+For all the algorithms implemented for the empirical evaluation, we used a Replay Buffer ($Buffer\_size$) with a fixed size and batches of a given size ($Batch\_size$) sampled randomly from it to perform the gradient steps.
+
+In the case of no-transfer-based algorithms we used a linearly scheduled $\epsilon$-greedy exploration for which we could specify the starting and final values of $\epsilon$, $\epsilon_s$ and $\epsilon_f$ respectively, and the \emph{Exploration Fraction} of the maximum number of iterations for which the linear schedule would be used.
+As the learning procedure is done by gradient descent, we also have $\alpha$ as the learning rate.
+Additionally, in the case of the DDQNs we have the \emph{Target Update Frequency} that specifies the number of iterations before setting the target neural network to the current parameters of the online network.
+
+As presented in Sec.
+\ref{sec:td}, for the minimization procedure of the TD error based on \emph{mellow-max} we also have to set $\kappa$ to control the approximation to the maximum operator and $\psi \in \left[0,1\right]$ to control the proportion between the full residual gradient and the semi-gradient approach used.
+
+For the transfer algorithms proposed here, namely, GVT and MGVT we have the following parameters.
+As presented in Sec.
+\ref{sec:alg}, we have $\lambda \geq 0$ to control the trade-off between the prior knowledge and the loss measure---i.e.
+the TD error---in the target task.
+Moreover, we allow to control the learning rates differently for the gradients related to the means and covariance matrices, the Cholesky factor L to be precise: $\alpha_{\mu}$ and $\alpha_L$.
+In order to approximate the expectation of the TD error, we used a fixed number of $weights$ sampled from the posterior distribution.
+Specifically, for MGVT it is necessary to specify the value of the variance $\sigma_p^2$ for the prior model and the number of components $C$ for the posterior family to be used.
+Furthermore, as explained in Sec.
+\ref{sec:mgvt}, to perform the initialization of the posterior by minimizing the KL divergence we set the a maximum number of iterations (\emph{UKL max iterations}) and the precision to reach during this optimization $\varepsilon$ and its learning rate $\eta$.
+Finally, to avoid problems with the positive-definiteness of the covariances being learned, we specify a hyper-parameter $\sigma_{min}$ as the minimum value the diagonal elements of the Cholesky factor can reach.
+
+In the following sections we present the configurations used for the experiments presented in this paper.
+For all our experiments we set $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$.
+Also, we used ADAM optimizer---with parameters $\beta_1=0.9$, $\beta_2=0.999$---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
+For the non-transfer algorithms only ADAM was used with the same mentioned parameters.
 
@@
 
+For the Cartpole environment, we generated tasks by uniformly sampling the cart mass in the range $\left[0.5,1.5\right]$, the pole mass in $\left[0.1,0.3\right]$ and the pole length in $\left[0.2,1.0\right]$.
+
+During the training of the source tasks, we used a $Batch\_size = 32$, $Buffer\_size = 50000$.
+For DDQN with a $Target\_Update\_Frequency = 500$ and $Exploration\_fraction = 0.35$ with $\epsilon_s=1$ and $\epsilon_f=0.1$.
+The function approximator was a Multilayer Perceptron (MLP) with ReLU as activation function and a hidden layer of $32$ neurons.
+For the transfer experiments we set $Batch\_size=500$ and $weights=5$, $\lambda=0.001$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$.
+In the case of MGVT we set $\sigma_p^2=10^{-5}$.
+
+In the case of Mountain Car, to generate tasks we sampled uniformly the base speed of the actions in the range $\left[0.001, 0.0015\right]$.
+We trained DDQN with $Target\_Update\_Frequency = 500$ and $Exploration\_fraction = 0.15$ with $\epsilon_s=1$ and $\epsilon_f=0.1$ and used  an MLP with single hidden layer of $64$ neurons with ReLU activation.
+For the transfer experiments we set the $Batch\_size=50$, $weights=10$, $\lambda=10^{-5}$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$.
+For MGVT we set $\sigma_p^2=10^{-5}$.
+
 \subsection{Maze Navigation}

### 2018-05-14 NIPS 2018/main.tex

--- 2018-05-14 NIPS 2018/main.tex
@@
 
+For the implementation of the Mixture of Gaussian Variational Transfer, we use the upper bound on the KL divergence between two Mixtures of Gaussians, as in Theorem\ref{th:ukl}, to obtain an upper bound on the negative ELBO in Equation\ref{eq:elbo}.
+Consider we have $C$ components for the posterior family $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$ and a prior distribution, constructed from the set of weights $\mathcal{W}_s = \left\lbrace \bm{w}_1,..., \bm{w}_{|\mathcal{W}_s|} \right\rbrace$ of the sources' optimal $Q$-functions, $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{j=1}^{|\mathcal{W}_s|}\mathcal{N}(\bm{w}|\bm{w}_j,\sigma_p^2\bm{I})$.
+
+\begin{equation}\label{eq:ukl}
+KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{equation}
+
+And substituting \ref{eq:ukl} in the negative ELBO in \ref{eq:elbo} we get the following upper bound.
+
+\begin{equation}
+\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] + KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{equation}
+
+Finally, using this upper bound as objective of our optimization problem, we can then exploit the linearity of the expectation operator to obtain
+
+\begin{equation}
+\widetilde{\mathcal{L}}(\bm{\xi}) = \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] + KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{equation}
+
+that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Eq.
+\ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL} derived for the Gaussian case.
+
 \section{Additional Details on the Experiments}
+
+In the present section we present the hyper-parameters and corresponding values that were used for the experiments presented in this paper.
+
+For all the algorithms implemented for the empirical evaluation, we used a Replay Buffer ($Buffer\_size$) with a fixed size and batches of a given size ($Batch\_size$) sampled randomly from it to perform the gradient steps.
+
+In the case of no-transfer-based algorithms we used a linearly scheduled $\epsilon$-greedy exploration for which we could specify the starting and final values of $\epsilon$, $\epsilon_s$ and $\epsilon_f$ respectively, and the \emph{Exploration Fraction} of the maximum number of iterations for which the linear schedule would be used.
+As the learning procedure is done by gradient descent, we also have $\alpha$ as the learning rate.
+Additionally, in the case of the DDQNs we have the \emph{Target Update Frequency} that specifies the number of iterations before setting the target neural network to the current parameters of the online network.
+
+As presented in Sec.
+\ref{sec:td}, for the minimization procedure of the TD error based on \emph{mellow-max} we also have to set $\kappa$ to control the approximation to the maximum operator and $\psi \in \left[0,1\right]$ to control the proportion between the full residual gradient and the semi-gradient approach used.
+
+For the transfer algorithms proposed here, namely, GVT and MGVT we have the following parameters.
+As presented in Sec.
+\ref{sec:alg}, we have $\lambda \geq 0$ to control the trade-off between the prior knowledge and the loss measure---i.e.
+the TD error---in the target task.
+Moreover, we allow to control the learning rates differently for the gradients related to the means and covariance matrices, the Cholesky factor L to be precise: $\alpha_{\mu}$ and $\alpha_L$.
+In order to approximate the expectation of the TD error, we used a fixed number of $weights$ sampled from the posterior distribution.
+Specifically, for MGVT it is necessary to specify the value of the variance $\sigma_p^2$ for the prior model and the number of components $C$ for the posterior family to be used.
+Furthermore, as explained in Sec.
+\ref{sec:mgvt}, to perform the initialization of the posterior by minimizing the KL divergence we set the a maximum number of iterations (\emph{UKL max iterations}) and the precision to reach during this optimization $\varepsilon$ and its learning rate $\eta$.
+Finally, to avoid problems with the positive-definiteness of the covariances being learned, we specify a hyper-parameter $\sigma_{min}$ as the minimum value the diagonal elements of the Cholesky factor can reach.
+
+In the following sections we present the configurations used for the experiments presented in this paper.
+For all our experiments we set $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$.
+Also, we used ADAM optimizer---with parameters $\beta_1=0.9$, $\beta_2=0.999$---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
+For the non-transfer algorithms only ADAM was used with the same mentioned parameters.
 

### 2018-05-15 NIPS 2018/main.tex
added tikz rooms figure

--- 2018-05-14 NIPS 2018/main.tex
@@
 \usepackage{subcaption}
+\usepackage{tikz}
 
@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
+
+\begin{tikzpicture}[scale=0.4]
+\draw [help lines] (0,0) grid (7,7);
+\begin{scope}[shift={(0,1.5)}]
+\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
+\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
+\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
+\path [fill=gray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);
+
+\node at (1.5,-0.5) {start};
+\node at (3.5,5.5) {goal};
+
+\draw [thick] (0,0) rectangle (5,5);
+\draw [line width=0.5mm] (1.5,5/3) -- (5,5/3);
+\draw [line width=0.5mm] (0,5/3) -- (0.5,5/3);
+\draw [line width=0.5mm] (0,10/3) -- (3,10/3);
+\draw [line width=0.5mm] (4,10/3) -- (5,10/3);
+\end{scope}
+\end{tikzpicture}
+
+    %\includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
     \caption{}
@@
 Furthermore, as explained in Sec.
-\ref{sec:mgvt}, to perform the initialization of the posterior by minimizing the KL divergence we set the a maximum number of iterations (\emph{UKL max iterations}) and the precision to reach during this optimization $\varepsilon$ and its learning rate $\eta$.
+\ref{sec:mgvt}, to perform the initialization of the posterior by minimizing the KL divergence we set a maximum number of iterations (\emph{UKL max iterations}) and the precision to reach during this optimization $\varepsilon$ and its learning rate $\eta$.
 Finally, to avoid problems with the positive-definiteness of the covariances being learned, we specify a hyper-parameter $\sigma_{min}$ as the minimum value the diagonal elements of the Cholesky factor can reach.
@@
 For all our experiments we set $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$.
-Also, we used ADAM optimizer---with parameters $\beta_1=0.9$, $\beta_2=0.999$---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
+Also, we used ADAM optimizer---with parameters $\beta_1=0.9$ for the decay of the first order momentum and $\beta_2=0.999$ for the second order momentum---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
 For the non-transfer algorithms only ADAM was used with the same mentioned parameters.
@@
 In the case of Mountain Car, to generate tasks we sampled uniformly the base speed of the actions in the range $\left[0.001, 0.0015\right]$.
-We trained DDQN with $Target\_Update\_Frequency = 500$ and $Exploration\_fraction = 0.15$ with $\epsilon_s=1$ and $\epsilon_f=0.1$ and used  an MLP with single hidden layer of $64$ neurons with ReLU activation.
+We trained DDQN with $Target\_Update\_Frequency = 500$ and a $Batch\_size = 32$, $Buffer\_size = 50000$.
+For the $Exploration\_fraction = 0.15$ with $\epsilon_s=1$ and $\epsilon_f=0.1$.
+We used an MLP with single hidden layer of $64$ neurons with ReLU activation.
 For the transfer experiments we set the $Batch\_size=50$, $weights=10$, $\lambda=10^{-5}$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$.
@@
 
+% add figures of convergent DDQN. Comparison for various exploration fractions.
+
 \subsection{Maze Navigation}
 
+%enumerate mazes. training parameters dqn. approximator. mgvt and gvt paramters
+
+For the maze navigation task presented in Sec.
+\ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
+In Fig.
+\ref{}, there $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
+Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.
+
+For the experiments we used as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the state of the MDP and an output layer that outputs the value of each action.
+For training the sources we, again, used DDQN with $Batch\_size = 70$, $Buffer\_size = 10000$ and $Target\_Update\_Frequency = 100$, setting the $Exploration\_fraction = 0.1$ with $\epsilon_s=1$ and $\epsilon_f=0.01$ and ran it for $200k$ to ensure convergence.
+
 \end{document}

### 2018-05-15 NIPS 2018/main.tex
Added Thm3

--- 2018-05-14 NIPS 2018/main.tex
@@
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newcommand{\arginf}{\operatornamewithlimits{arginf}}
+\newcommand{\argsup}{\operatornamewithlimits{argsup}}
 \newcommand{\mm}{\operatornamewithlimits{mm}}
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:diff-q}
 Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
@@
 \begin{theorem}\label{th:main-gaussian}
-aaa
+Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Consider the Gaussian version of Alg.
+\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+\begin{equation}
+\resizebox{0.93\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\end{equation}
 \end{theorem}
@@
 \mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}
+\end{align*}
+Let us now apply Corollary \ref{cor:diff-q}. We have that, with probability at least $1-\delta$:
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ]}{(1-\gamma)\delta}
+\end{align*}
+Thus, we probability at least $1-2\delta$:
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
 \end{align*}

### 2018-05-15 NIPS 2018/main.tex
Completed theory

@@
 
-In this section, we theoretically analyze our variational transfer algorithm...
-
 A first important question that we need to answer is whether replacing max with mellow-max in the Bellman operator constitutes a strong approximation or not.
-It has been proved \cite{} \todo{Cite MM} that the mellow Bellman operator is a contraction under the $L_{\infty}$-norm and, thus, has a unique fixed-point.
+It has been proved \cite{asadi2017alternative} that the mellow Bellman operator is a non-expansion under the $L_{\infty}$-norm and, thus, has a unique fixed-point.
 However, how such fixed-point differs from the one of the optimal Bellman operator remains an open question.
@@
 \end{restatable}
+
+The proof is provided in App.
+\ref{}.
+As expected, $\wt{Q}$ converges to $Q^*$ exponentially fast when either $\kappa$ (equivalently, $\beta_{\kappa}$) increases, or the action gaps are enlarged.
+Notice that this result is of interest even outside our specific settings.
+
+The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
+To address this point, we restrict to the case of linear approximators with Gaussian prior and posterior.
+We assume Alg.
+\ref{alg:transfer} is used with a finite dataset and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
+Our main results is given in the following theorem.
+
+\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
+Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Consider the Gaussian version of Alg.
+\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+\begin{equation}
+\resizebox{0.93\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
+\end{equation}
+\end{restatable}
+We refer the reader to App.
+\ref{} for the proof and a specific definition of the three constants.
+Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying very fast (as $\mathcal{O}(\frac{1}{N^2})$).
+Intuitively, our bound demonstrates that, if one starts very close the prior, the only error incurred, besides the irreducible approximation error, is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly.
+Furthermore, as $N\rightarrow\infty$ the only error term remaining is the irreducible approximation error.
+Notice that the variance term $\upsilon(\bm{w}^*)$ is due to the fact that we minimize a biased estimator of the Bellman error.
+As mentioned in the preliminaries, if double sampling of the next state is possible (e.g., in simulation), such term would disappear.
+Finally, we want to point out that the proof of this theorem relies on a very general result (Lemma \ref{lemma:general-bound} in App.
+\ref{}) that does not require any specific choice of distribution of approximator.
+Leveraging on such results, it is straightforward to provide a finite-sample analysis of the mixture version of our algorithm.
+For the sake of completeness, we report the derivation in App.
+\ref{}.
 
@@
 
-\begin{theorem}\label{th:main-gaussian}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the Gaussian version of Alg.
-\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
-\begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
-\end{equation}
-\end{theorem}
+\thg*
 \begin{proof}

### 2018-05-15 scripts/plot_results_like.py

@@ -1,0 +1,185 @@
+import utils
+import numpy as np
+import matplotlib.pyplot as plt
+
+MARKERS = ["o", "D", "s", "^", "v", "p", "*"]
+COLORS = ["#0e5ad3","#bc2d14", "#a011a3","#d67413","#22aa16", "#d1ba0e" ,"#14ccc2"]
+LINES = ["solid", "dashed", "dashdot", "dotted", "solid", "dashed", "dashdot", "dotted"]
+
+
+def plot_curves(x_data, y_mean_data, y_std_data=None, title="", x_label="Episodes", y_label="Performance", names=None,
+                file_name=None):
+    assert len(x_data) < 8
+
+    plt.style.use('ggplot')
+
+    plt.rcParams['font.family'] = 'serif'
+    plt.rcParams['font.serif'] = 'Ubuntu'
+    plt.rcParams['font.monospace'] = 'Ubuntu Mono'
+    plt.rcParams['font.size'] = 20
+    plt.rcParams['axes.labelsize'] = 20
+    # plt.rcParams['axes.labelweight'] = 'bold'
+    plt.rcParams['axes.titlesize'] = 20
+    plt.rcParams['xtick.labelsize'] = 16
+    plt.rcParams['ytick.labelsize'] = 16
+    plt.rcParams['legend.fontsize'] = 22
+    plt.rcParams['figure.titlesize'] = 20
+
+    fig, ax = plt.subplots()
+
+    plt.title(title)
+    plt.xlabel(x_label)
+    plt.ylabel(y_label)
+
+    X = np.array(x_data)
+    plt.xlim([X.min(), X.max()])
+    plt.ylim([0,0.85])
+
+    for i in range(len(x_data)):
+
+        ax.plot(x_data[i], y_mean_data[i], linewidth=3, color=COLORS[i], marker=None, markersize=8.0,
+                linestyle="solid", label=names[i] if names is not None else None)
+        if y_std_data is not None:
+            ax.fill_between(x_data[i], y_mean_data[i] - y_std_data[i], y_mean_data[i] + y_std_data[i],
+                            facecolor=COLORS[i], edgecolor=COLORS[i], alpha=0.3)
+
+    if names is not None:
+        ax.legend(loc='best', numpoints=1, fancybox=True, frameon=False)
+
+    if file_name is not None:
+        plt.savefig(file_name + ".pdf", format='pdf')
+
+    plt.show()
+
[…]

### 2018-05-15 scripts/ppp.py

@@ -1,0 +1,56 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import utils
+
+nt_states = np.array(utils.load_object("nt_states"))
+gvt_states = np.array(utils.load_object("gvt_states"))
+mgvt_states = np.array(utils.load_object("mgvt_states"))
+
+colors = ['#4EACC5', '#FF9C34', '#4E9A06']
+plt.figure()
+plt.hold(True)
+plt.plot(nt_states[:,0], nt_states[:,1], 'w', markerfacecolor=colors[0], marker='.', markersize=6, label="NT")
+plt.plot(gvt_states[:,0], gvt_states[:,1], 'w', markerfacecolor=colors[1], marker='.', markersize=6, label="GVT")
+plt.plot(mgvt_states[:,0], mgvt_states[:,1], 'w', markerfacecolor=colors[2], marker='.', markersize=6, label="1-MGVT")
+plt.plot([0,4.5],[5,5], color="#000000", linewidth=3)
+plt.plot([5.5,10],[5,5], color="#000000", linewidth=3)
+plt.plot([0,10],[0,0], color="#000000", linewidth=3)
+plt.plot([0,10],[10,10], color="#000000", linewidth=3)
+plt.plot([0,0],[0,10], color="#000000", linewidth=3)
+plt.plot([10,10],[0,10], color="#000000", linewidth=3)
+
+plt.legend(loc='best', numpoints=1, fancybox=True, frameon=False, markerscale=3)
+
+plt.grid(True)
+plt.savefig("exploration.png", format='png')
+plt.show()
+
+
+
+nt_transitions = utils.load_object("nt_transitions")
+gvt_transitions = utils.load_object("gvt_transitions")
+
+colors = ['#4EACC5', '#FF9C34', '#4E9A06']
+plt.figure()
+plt.hold(True)
+
+for i in range(len(nt_transitions)):
+    x = np.array(nt_transitions[i])
+    plt.plot(x[:,0], x[:,1], color=colors[0])
+
+for i in range(len(gvt_transitions)):
+    x = np.array(gvt_transitions[i])
+    plt.plot(x[:,0], x[:,1], color=colors[1])
+
+plt.plot([0,4.5],[5,5], color="#000000", linewidth=3)
+plt.plot([5.5,10],[5,5], color="#000000", linewidth=3)
+plt.plot([0,10],[0,0], color="#000000", linewidth=3)
[…]

### 2018-05-15 scripts/res/run_gvt_gw_torch.py

@@ -1,0 +1,140 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
+from features.agrbf import build_features_gw_state
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.gvt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=20000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.1)
+parser.add_argument("--lambda_", default=0.001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--sigma_reg", default=0.0001)
+parser.add_argument("--cholesky_clip", default=0.0001)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=10)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=11)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/gw10x10_torch")
+
+# Read arguments
+args = parser.parse_args()
[…]

### 2018-05-15 scripts/res/run_gvt_maze.py

@@ -1,0 +1,165 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.emaze import Maze
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.gvt_torch import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+from random import shuffle
+
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--render", default=False)
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=20000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=25)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+
+parser.add_argument("--maze", default=-1)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=32)
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--mazes_file", default="../scripts/mazes10")
+
+#GVT parameters
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.0001)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=5)
+parser.add_argument("--sigma_reg", default=0.0001)
+parser.add_argument("--cholesky_clip", default=0.0001)
+parser.add_argument("--source_file", default="source_tasks/mazes10x10_ns20_32x32nn_sources")
+parser.add_argument("--time_coherent", default=False)
+
+parser.add_argument("--fixed_seed", default=-1)
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
[…]

### 2018-05-15 scripts/res/run_mgvt_gw_likelihood.py

@@ -1,0 +1,154 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
+from features.agrbf import build_features_gw_state
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.mgvt_torch import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.1)
+parser.add_argument("--lambda_", default=0.000001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=10)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=11)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="mgvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/gw10x10_gaussian")
+parser.add_argument("--eta", default=1e-6)  # learning rate for
[…]

### 2018-05-15 scripts/res/run_nt_maze.py

@@ -1,0 +1,131 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.emaze import Maze
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.nt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+from random import shuffle
+from algorithms.dqn import DQN
+
+
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--render", default=False)
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=32)
+parser.add_argument("--max_iter", default=300000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--exploration_fraction", default=0.7)
+parser.add_argument("--eps_start", default=1.0)
+parser.add_argument("--eps_end", default=0.05)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=100)
+parser.add_argument("--alpha", default=0.001)
+parser.add_argument("--maze", default=-1)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=32)
+parser.add_argument("--file_name", default="nt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--mazes_file", default="../scripts/mazes10")
+parser.add_argument("--dqn", default=False)
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
+xi = float(args.xi)
+tau = float(args.tau)
+batch_size = int(args.batch_size)
+max_iter = int(args.max_iter)
+buffer_size = int(args.buffer_size)
+random_episodes = int(args.random_episodes)
+exploration_fraction = float(args.exploration_fraction)
+eps_start = float(args.eps_start)
+eps_end = float(args.eps_end)
[…]

### 2018-05-15 scripts/res/run_nt_mountaincar.py

@@ -1,0 +1,131 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.mountain_car import MountainCarEnv
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.nt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+from algorithms.dqn import DQN
+
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=32)
+parser.add_argument("--max_iter", default=10000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--exploration_fraction", default=0.5)
+parser.add_argument("--eps_start", default=1.0)
+parser.add_argument("--eps_end", default=0.01)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=20)
+parser.add_argument("--l1", default=64)
+parser.add_argument("--l2", default=0)
+parser.add_argument("--alpha", default=0.001)
+parser.add_argument("--env", default="cartpole")
+# Car parameters (default = randomize)
+parser.add_argument("--speed", default=-1)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="nt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--dqn", default=False)
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
+xi = float(args.xi)
+tau = float(args.tau)
+batch_size = int(args.batch_size)
+max_iter = int(args.max_iter)
+buffer_size = int(args.buffer_size)
+random_episodes = int(args.random_episodes)
+exploration_fraction = float(args.exploration_fraction)
+eps_start = float(args.eps_start)
+eps_end = float(args.eps_end)
+train_freq = int(args.train_freq)
[…]

### 2018-05-15 scripts/results/run_gvt_maze.py

@@ -1,0 +1,165 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.emaze import Maze
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.gvt_torch import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+from random import shuffle
+
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--render", default=False)
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=20000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=25)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+
+parser.add_argument("--maze", default=-1)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=32)
+parser.add_argument("--file_name", default="gvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--mazes_file", default="../scripts/mazes10")
+
+#GVT parameters
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.0001)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=5)
+parser.add_argument("--sigma_reg", default=0.0001)
+parser.add_argument("--cholesky_clip", default=0.0001)
+parser.add_argument("--source_file", default="../scripts/mazes10x10_ns20_32x32nn_uniqueInit")
+parser.add_argument("--time_coherent", default=False)
+
+parser.add_argument("--fixed_seed", default=-1)
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
[…]

### 2018-05-15 scripts/results/run_mgvt_cartpole.py

@@ -1,0 +1,150 @@
+import sys
+
+sys.path.append("../")
+
+import numpy as np
+from envs.cartpole import CartPoleEnv
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.mgvt_torch import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=500)
+parser.add_argument("--max_iter", default=10000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.0001)
+parser.add_argument("--lambda_", default=0.00001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Door at -1 means random positions over all runs
+parser.add_argument("--cart_mass", default=-1)
+parser.add_argument("--pole_mass", default=-1)
+parser.add_argument("--pole_length", default=-1)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=0)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="mgvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/")
+parser.add_argument("--eta", default=1e-6)  # learning rate for
+parser.add_argument("--eps", default=0.001)  # precision for the initial posterior approximation and upperbound tighting
[…]

### 2018-05-15 scripts/results/run_mgvt_gw.py

@@ -1,0 +1,164 @@
+import sys
+
+sys.path.append("../")
+
+import numpy as np
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
+from features.agrbf import build_features_gw_state
+from features.identity import Identity
+from approximators.linear import LinearQFunction
+from operators.mellow import MellowBellmanOperator
+from algorithms.mgvt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.1)
+parser.add_argument("--lambda_", default=0.000001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=5)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=6)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="mgvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/gw5x5")
+parser.add_argument("--eta", default=1e-6)  # learning rate for
[…]

### 2018-05-15 scripts/results/run_mgvt_gw_torch.py

@@ -1,0 +1,152 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.two_room_gw import TwoRoomGridworld
+from envs.three_room_gw import ThreeRoomGridworld
+from features.agrbf import build_features_gw_state
+from approximators.mlp_torch import MLPQFunction
+from operators.mellow_torch import MellowBellmanOperator
+from algorithms.mgvt_torch import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=20000)
+parser.add_argument("--buffer_size", default=50000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=50)
+parser.add_argument("--mean_episodes", default=50)
+parser.add_argument("--alpha_adam", default=0.001)
+parser.add_argument("--alpha_sgd", default=0.1)
+parser.add_argument("--lambda_", default=0.000001)
+parser.add_argument("--time_coherent", default=False)
+parser.add_argument("--n_weights", default=10)
+parser.add_argument("--n_source", default=10)
+parser.add_argument("--env", default="two-room-gw")
+parser.add_argument("--gw_size", default=10)
+parser.add_argument("--cholesky_clip", default=0.0001)
+# Door at -1 means random positions over all runs
+parser.add_argument("--door", default=-1)
+parser.add_argument("--door2", default=-1)
+parser.add_argument("--n_basis", default=11)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="mgvt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+parser.add_argument("--source_file", default="source_tasks/gw10x10_torch")
+parser.add_argument("--eta", default=1e-6)  # learning rate for
[…]

### 2018-05-15 scripts/results/run_nt_cartpole.py

@@ -1,0 +1,122 @@
+import sys
+sys.path.append("../")
+
+import numpy as np
+from envs.cartpole import CartPoleEnv
+from approximators.mlp import MLPQFunction
+from operators.mellow import MellowBellmanOperator
+from algorithms.nt import learn
+import utils
+import argparse
+from joblib import Parallel, delayed
+import datetime
+
+# Global parameters
+render = False
+verbose = True
+
+# Command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("--kappa", default=100.)
+parser.add_argument("--xi", default=0.5)
+parser.add_argument("--tau", default=0.0)
+parser.add_argument("--batch_size", default=50)
+parser.add_argument("--max_iter", default=5000)
+parser.add_argument("--buffer_size", default=10000)
+parser.add_argument("--random_episodes", default=0)
+parser.add_argument("--exploration_fraction", default=0.2)
+parser.add_argument("--eps_start", default=1.0)
+parser.add_argument("--eps_end", default=0.02)
+parser.add_argument("--train_freq", default=1)
+parser.add_argument("--eval_freq", default=100)
+parser.add_argument("--mean_episodes", default=20)
+parser.add_argument("--l1", default=32)
+parser.add_argument("--l2", default=0)
+parser.add_argument("--alpha", default=0.001)
+parser.add_argument("--env", default="cartpole")
+# Cartpole parameters (default = randomize)
+parser.add_argument("--cart_mass", default=-1)
+parser.add_argument("--pole_mass", default=-1)
+parser.add_argument("--pole_length", default=-1)
+parser.add_argument("--n_jobs", default=1)
+parser.add_argument("--n_runs", default=1)
+parser.add_argument("--file_name", default="nt_{}".format(datetime.datetime.now().strftime("%Y%m%d_%H%M%S")))
+
+# Read arguments
+args = parser.parse_args()
+kappa = float(args.kappa)
+xi = float(args.xi)
+tau = float(args.tau)
+batch_size = int(args.batch_size)
+max_iter = int(args.max_iter)
+buffer_size = int(args.buffer_size)
+random_episodes = int(args.random_episodes)
+exploration_fraction = float(args.exploration_fraction)
+eps_start = float(args.eps_start)
+eps_end = float(args.eps_end)
[…]

### 2018-05-15 NIPS 2018/main.tex
Merged with Marcello's edits

@@
 
-Recent advancements have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
-The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
-One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
-In the typical settings of transfer in RL \cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
-Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed up the learning process.
-This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previous learning experience.
-Several algorithms have been proposed in the literature to transfer experience samples \cite{lazaric2008transfer,taylor2008transferring}, policies/options \cite{fernandez2006probabilistic,konidaris2007building}, rewards \cite{konidaris2006autonomous}, features \cite{barreto2017successor}, parameters \cite{doshi2016hidden,killian2017robust}, and so on.
-We refer the reader to \cite{taylor2009transfer} for a thorough survey on transfer in RL.
+Recent advancements have allowed reinforcement learning (RL)~\cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari~\cite{mnih2015human} through the game of Go~\cite{silver2016mastering} to the control of sophisticated robotics systems~\cite{kober2009policy,lillicrap2015continuous,levine2016end}.
+The main limitation is that these RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
+One of the most promising solutions to reduce the need of samples is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
+In the typical settings of transfer in RL~\cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
+Then, given a \textit{target task} (which is drawn from the same distribution, or a slightly different one), the agent can rely on knowledge from the source tasks to speed up the learning process.
+This reuse of knowledge constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of any previous learning experience.
+Several algorithms have been proposed in the literature to transfer different elements involved in the learning process: experience samples~\cite{lazaric2008transfer,taylor2008transferring}, policies/options~\cite{fernandez2006probabilistic,konidaris2007building}, rewards~\cite{konidaris2006autonomous}, features~\cite{barreto2017successor}, parameters~\cite{doshi2016hidden,killian2017robust}, and so on.
+We refer the reader to~\cite{taylor2009transfer,lazaric2012transfer} for a thorough survey on transfer in RL.
 
@@
 Intuitively, assuming the tasks under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
-Among the appealing approaches for this problem we find Bayesian methods (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible.
-Similarly, model-based algorithms (e.g., \cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain.
+Among the appealing approaches for this problem we find Bayesian methods (e.g.,~\cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible.
+Similarly, model-based algorithms (e.g.,~\cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain.
 However, all these approaches either require strong assumptions (for example, on the distribution involved in Bayesian methods) or do not scale well to large problems.
@@
 %In this work, we tackle such limitations by considering a more general approach.
-Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
+Similarly to~\cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
 Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
@@
 
-Under the assumption that tasks follow a certain distribution, an intuitive choice for designing a transfer algorithm is to attempt at characterizing the uncertainty over the target task.
-Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task in such a way that this uncertainty is reduced as quickly as possible.
+Under the assumption that tasks follow a specific distribution, an intuitive choice for designing a transfer algorithm is to attempt at characterizing the uncertainty over the target task.
+Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task to reduce the uncertainty as quickly as possible.
 This simple intuition makes Bayesian \todo{probabilistic?
 distributional?} methods appealing approaches for transfer in RL, and many previous works have been proposed in this direction.
-\cite{wilson2007multi} assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of these two elements.
-Similarly, \cite{lazaric2010bayesian} assume tasks are similar in their value functions and design a different hierarchical Bayesian model for transferring such information.
-More recently, \cite{doshi2016hidden}, and its extension \cite{killian2017robust}, consider tasks whose dynamics are governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
-However, all these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
-The importance of having transfer algorithms that alleviate the need of strong assumptions and that can be easily adapted to different contexts motivates us to take a more general approach.
+In~\cite{wilson2007multi}, the authors assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of these two elements.
+Similarly, in~\cite{lazaric2010bayesian}, the authors assume that tasks are similar in their value functions and design a different hierarchical Bayesian model for transferring such information.
+More recently,~\cite{doshi2016hidden}, and its extension~\cite{killian2017robust}, consider tasks whose dynamics are governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
+However, most of these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
+The importance of having transfer algorithms that alleviate the need for strong assumptions and that easily adapt to different contexts motivates us to take a more general approach.
 
-Similarly to \cite{lazaric2010bayesian}, we assume tasks to share similarities in their value functions and use the given source tasks to learn a distribution over such functions.
-Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
-Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+Similarly to~\cite{lazaric2010bayesian}, we assume tasks to share similarities in their value functions and use the given source tasks to learn a distribution over such functions.
+Then, we use this distribution as a prior for learning the target task and we propose a variational approximation of the corresponding posterior that is computationally efficient.
+Leveraging on recent ideas from randomized value functions~\cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
 (with respect to) the sampled value function.
-We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models.
-We propose a finite-sample analysis that theoretically validates our approach, while empirically evaluating its performance on three domains with increasing level of difficulty.
+We show that our approach is very general, in the sense that it can work with any parametric function approximator and with any prior/posterior distribution models (in this paper we focus on the Gaussian and Gaussian mixture models).
+In addition to the algorithmic contribution, we give also a theoretical contribution by providing a finite-sample analysis of our approach and an experimental contribution showing its empirical performance on four domains with increasing level of difficulty.
 
@@
 
-We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov Decision Process (MDP).
-We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$\todo{Should we provide a more transfer-oriented definition?}, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
+We consider a distribution $\mathcal{D}$ over tasks, where each task $\mathcal{M}_\tau$ is modeled as a discounted Markov Decision Process (MDP).
+We define an MDP as a tuple $\mathcal{M}_\tau = \langle \mathcal{S},\mathcal{A},\mathcal{P}_\tau,\mathcal{R}_\tau,p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}_\tau(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}_\tau: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
 We assume the reward function to be uniformly bounded by a constant $R_{max}>0$.
@@
 At the beginning of each episode of interaction, the initial state $s_0$ is drawn from $p_0$.
-Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated.
-The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$.
-To this end, we define the optimal value function $Q^*(s,a)$ as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter.
-Then, an optimal policy $\pi^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi^*(s) = \argmax_a Q^*(s,a)$ for all states $s$.
-It can be shown (e.g., \cite{puterman1994markov}) that $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$ defined by $TQ(s,a) = \mathcal{R}(s,a) + \gamma\mathbb{E}_{\mathcal{P}}[\max_{a'}Q(s',a')]$ for any value function $Q$.
+Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}_\tau(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated.
+The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}_{\mathcal{M}_\tau,\pi}[\sum_{t=0}^{\infty} \gamma^t \mathcal{R}_\tau(s_t,a_t)]$.
+To this end, we define the optimal value function of task $\mathcal{M}_\tau$, $Q_\tau^*(s,a)$, as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter.
+Then, an optimal policy $\pi_\tau^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi_\tau^*(s) = \argmax_a Q_\tau^*(s,a)$ for all states $s$.
+It can be shown (e.g.,~\cite{puterman1994markov}) that $Q_\tau^*$ is the unique fixed-point of the optimal Bellman operator $T_\tau$ defined by $T_\tau Q(s,a) = \mathcal{R}_\tau(s,a) + \gamma\mathbb{E}_{s' \sim\mathcal{P}_\tau}[\max_{a'}Q(s',a')]$ for any value function $Q$.
 From now on, we adopt the term $Q$-function to denote any plausible value function, i.e., any function $Q : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R}$ uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
+In the following, to avoid cluttering the notation, we will drop the subscript $\tau$ when there is no ambiguity.
 
-We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$, and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
+We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^d\right\}$, and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
 When learning the optimal value function, a quantity of interest is how close a given function $Q_{\bm{w}}$ is to the fixed-point of the Bellman operator.
-A possible measure is its Bellman error (or Bellman residual), defined by $B(\bm{w}) \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$.
-Notice that $Q_{\bm{w}}$ is optimal if, and only if, $B(\bm{w})(s,a) = 0$ for all $s,a$.
-If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, an appealing objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B(\bm{w})}_{\nu}^2$\todo{Should we define norms before?}.
-Unfortunately, it is well-known that an unbiased estimator of this quanitity requires two independent samples of the next state $s'$ for each $s,a$ (e.g., \cite{maillard2010finite}).
-In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$.
-Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B(\bm{w})}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$.
+A possible measure is its Bellman error (or Bellman residual), defined by $B_{\bm{w}} \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$.
+Notice that $Q_{\bm{w}}$ is optimal if and only if $B_{\bm{w}}(s,a) = 0$ for all $s,a$.
+If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, a sound objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B_{\bm{w}}}_{\nu}^2$.
+Unfortunately, it is well-known that an unbiased estimator of this quantity requires two independent samples of the next state $s'$ for each $s,a$ (e.g.,~\cite{maillard2010finite}).
+In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample $\langle s,a,s',r \rangle$, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$.
+Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B_{\bm{w}}}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$.
 Whenever the distinction is clear from the context, with slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.
@@
 \eqref{eq:bayes}.
-The main intuition behind variational inference \cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$.
+The main intuition behind variational inference~\cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$.
 The latter is chosen in a parametric family, with variational parameters $\bm{\xi}$, as the minimizer of the Kullback-Leibler (KL) divergence w.r.t.

### 2018-05-15 NIPS 2018/main.tex
Minor changes to section 3.1

@@
 In this section, we describe our variational approach to transfer in RL.
-In Section \ref{sec:alg}, we start by introducing our algorithm from a high-level perspective, in such a way that it can be used for any choice of prior and posterior distributions.
-Then, in Sections \ref{sec:gvt} and \ref{sec:mgvt}, we propose practical implementations based on Gaussians and mixtures of Gaussians, respectively.
-We conclude with some considerations on how to optimize the proposed objective in Sec.
-\ref{sec:td}.
+In Section~\ref{sec:alg}, we start by introducing our algorithm from a high-level perspective, in such a way that any choice of prior and posterior distributions is possible.
+Then, in Sections~\ref{sec:gvt} and~\ref{sec:mgvt}, we propose practical implementations based on Gaussians and mixtures of Gaussians, respectively.
+We conclude with some considerations on how to optimize the proposed objective in Section~\ref{sec:td}.
 
@@
 
-We begin with a simple consideration: the distribution $\mathcal{D}$ over tasks clearly induces a distribution over optimal $Q$-functions.
-\todo{Should we just make the assumption that Q-functions share knowledge in their weights?} Moreover, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
+Let us observe that the distribution $\mathcal{D}$ over tasks induces a distribution over optimal $Q$-functions.
+\todo{Should we just make the assumption that Q-functions share knowledge in their weights?} Furthermore, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
 Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
@@
 
-Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve.
-Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$.
+Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve.
+Then, we can compute the posterior distribution over weights given such dataset by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$.
 Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$.
-In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors.
-However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability to specific problems.
+In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions to get tractable posteriors.
+However, in our transfer settings, all distributions involved depend on the family of tasks under consideration and making such assumptions is likely to limit the applicability to specific problems.
 Thus, we take a different approach to derive a more general, but still well-grounded, solution.
-Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$.
+Recall that our final goal is to move the total probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B_{\bm{w}}}_D^2$.
 Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ takes the form (e.g., \cite{catoni2007pac}):
 \begin{equation}\label{eq:gibbs}
-q(\bm{w}) = \frac{e^{-\Lambda\norm{B(\bm{w})}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B(\bm{w}')}_D^2}p(d\bm{w}')}
+q(\bm{w}) = \frac{e^{-\Lambda\norm{B_{\bm{w}}}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B_{\bm{w}'}}_D^2}p(d\bm{w}')},
 \end{equation}
 for some parameter $\Lambda > 0$.
-\todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
-Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior.
+\todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
+Notice that, whenever the term $e^{-\Lambda\norm{B_{\bm{w}}}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior.
 Although we now have an appealing distribution, the integral at the denominator of \eqref{eq:gibbs} is intractable to compute even for simple $Q$-function models.
@@
 \begin{align} \label{eq:elbo}
-\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
+\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
 \end{align}
-Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term).
-Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t.
-the variational parameters $\bm{\xi}$, our objective can be easily optimized using any stochastic optimization algorithm.
+The approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term).
+Assuming that we can compute the gradients of \eqref{eq:elbo} w.r.t.
+the variational parameters $\bm{\xi}$, our objective can be optimized using any stochastic optimization algorithm, as shown in the next subsections.
 
@@
 
-We now highlight our general transfer procedure in Alg.
-\ref{alg:transfer}, while deferring a description of specific choices for the distributions involved to the next two sections.
-Given a set of weights $\mathcal{W}_s$ from the source tasks' optimal $Q$-functions, we start by estimating the prior distribution (line 1) and we initialize the variational parameters by minimizing the KL divergence w.r.t.
-such distribution\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters.
-However, we are not making this assumption at this point.} (line 2).
-Then, at each time step of interaction, we re-sample the weights from the current approximate posterior and act greedily w.r.t.
+We now highlight our general transfer procedure in Algorithm~\ref{alg:transfer}, while deferring a description of specific choices for the involved distributions to the next two subsections.
+Given a set of weights $\mathcal{W}_s$ from the source tasks' optimal $Q$-functions, we start by estimating the prior distribution (line 1), and we initialize the variational parameters by minimizing the KL divergence w.r.t.
+such distribution (line 2).\footnote{If the prior and approximate posterior were in the same family of distributions we could simply set $\bm{\xi}$ to the prior parameters.
+However, we are not making this assumption at this point.} Then, at each time step of interaction, we re-sample the weights from the current approximate posterior and act greedily w.r.t.
 the corresponding $Q$-function (lines 7,8).
@@
 
-The key property of our approach is the weight resampling at line 7.
-This resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
-In some sense, at each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were actually true.
-This allows an efficient adaptive exploration of the target task.
-Intuitively, during the first steps of interaction, the agent is very uncertain about the current task and such uncertainty induces stochasticity in the chosen actions, allowing rather informed exploration to take place.
-Consider, for instance, that actions that are bad on average for all tasks are very unlikely to be sampled, while this cannot happen in uninformed exploration strategies, like $\epsilon$-greedy, before learning takes place.
-As the learning process goes on, the algorithm will quickly figure out which task is being solved, thus moving all probability mass over the weights minimizing the TD error.
+The key property of our approach is the weight resampling at line 7, which resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
+At each time we guess what the task we are trying to solve based on our current belief is and we act as if such guess were true.
+This mechanism allows an efficient adaptive exploration of the target task.
+Intuitively, during the first steps of interaction, the agent is very uncertain about the current task, and such uncertainty induces stochasticity in the chosen actions, allowing rather informed exploration to take place.
+Consider, for instance, that actions that are bad on average for all tasks are improbable to be sampled, while this cannot happen in uninformed exploration strategies, like $\epsilon$-greedy, before learning takes place.
+As the learning process goes on, the algorithm will quickly figure out which task is being faced, thus moving all the probability mass over the weights minimizing the TD error.
 From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
 
-Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any pior/posterior distributions can be adopted.
+Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any prior/posterior distributions can be adopted.
 For the latter, we describe two practical choices in the next two sections.

### 2018-05-15 NIPS 2018/main.tex
Update up to Sec. 5.2

--- 2018-05-15 NIPS 2018/main.tex
@@
 
-In this section, we provide an experimental evaluation of our approach in three different domains with increasing level of difficulty.
+In this section, we provide an experimental evaluation of our approach in four different domains with increasing level of difficulty.
 In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using a $c$-component mixture of Gaussians ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration.
 To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
+Thus, we provide a discussion of related works in the next section.
 \todo{Any better motivation?}
@@
 The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
-We consider a distribution over tasks in which doors have a fixed width of $1$, while their positions are sampled uniformly in $[0.5,9.5]$.
+In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.
+
 Since the agent does not know where the doors are located in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
@@
 This does not hold for positions nearby the start state.
-However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).
-Thus, we expect our algorithm to efficiently explore any target task.
+However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).\todo{Good candidate to be removed}
 
@@
 In order to prove that our guesses are correct, we generate a set of $50$ source tasks for the three-room environment of Fig.
-\ref{} by sampling both door positions uniformly, and solve all of them by directly minimizing the TD error as presented in Sec.
+\ref{} by sampling both door positions uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Sec.
 \ref{sec:td}.
-In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until convergence.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
@@
 \ref{}.
-Each curve is the result of $20$ independent runs, each resampling the target and source tasks.
-$95\%$ confidence intervals are shown.
+Each curve is the result of $20$ independent runs, each resampling the target and source tasks, with $95\%$ confidence intervals.
 Further details on the parameters adopted in this experiment are given in App.
@@
 To better understand the differences between GVT and MGVT, we now consider transferring from a slightly different distribution than the one from which target tasks are drawn.
-We generate again $50$ source tasks but this time with the bottom door fixed in the center and the other one moving.
+We generate again $50$ source tasks but this time with the bottom door fixed at the center and the other one moving.
 Then, we repeat the previous experiment, allowing both doors to move when sampling target tasks.
@@
 Interestingly, MGVT seems almost unaffected by this change, proving that is has sufficient representation power to generalize to slightly different task distributions.
-The same does not hold for GVT, which now is not able to solve many of the sampled target tasks,thus the very high variance.
+The same does not hold for GVT, which now is not able to solve many of the sampled target tasks, as can be noticed from the higher variance.
 This proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
@@
 \ref{}.
-Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
+Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
 Fig.
-\ref{} shows the performance reached by GVT and MGVT with $1$ component at fixed iterations as a function of how likely the target task is according to such distribution.
+\ref{} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
 As expected GVT achieves poor performance on very unlikely tasks, even after many iterations.
@@
 
-To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
-In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
-Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
-We kept a discount factor of $\gamma=0.99$ for both environments.
-Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
-We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
-Analogously to Sec.
-\ref{sec:gw}, in Fig.
-\ref{} and \ref{} we show the expected return---as the average of the last $50$ episodes of lerning---of transfer for $20$ independent runs randomizing the sources and target tasks.
-In Fig.
-\ref{}, that corresponds to Cartpole, it is easily noticeable a near-optimal jump-start, in both GVT and 1-MGVT, that during the following iterations converges to the optimal performance.
-Furthermore, transfer in Mountain Car as shown in Fig.
-\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence, within the same number of iterations, to the optimal performances.
+We now consider two well-known classic control environments: Cartpole and Mountain Car \citep{sutton1998reinforcement}.
+For both, we generate $20$ source tasks by uniformly sampling their physical parameters (cart mass, pole mass, pole length for Cartpole and car speed for Mountain Car).
+We parameterize $Q$-functions using neural networks with $1$-layer of $32$ hidden units for Cartpole and $64$ for Mountain Car.
+A better description of these two environments and their parameters is given in App.
+\ref{}.
+In this experiment, we use a Double Deep Q-Network \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
+The results (same settings of Sec.
+\ref{sec:gw}) are shown in Fig.
+\ref{} and \ref{}.
+For Cartpole (Fig.
+\ref{}), all transfer algorithms are almost zero-shot.
+This is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are almost the same for all tasks.
+On the contrary, in Mountain Car (Fig.
+\ref{}) the optimal $Q$-functions become really different when changing the car speed.
+This causes GVT to struggle to solve the target task, while 1-MGVT achieves a good jump-start and convergences in less iterations.
 

### 2018-05-15 NIPS 2018/main.tex
app c

--- 2018-05-15 NIPS 2018/main.tex
@@
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newcommand{\arginf}{\operatornamewithlimits{arginf}}
-\newcommand{\argsup}{\operatornamewithlimits{argsup}}
 \newcommand{\mm}{\operatornamewithlimits{mm}}
@@
 
-Recent advancements have allowed reinforcement learning (RL)~\cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari~\cite{mnih2015human} through the game of Go~\cite{silver2016mastering} to the control of sophisticated robotics systems~\cite{kober2009policy,lillicrap2015continuous,levine2016end}.
-The main limitation is that these RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
-One of the most promising solutions to reduce the need of samples is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
-In the typical settings of transfer in RL~\cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
-Then, given a \textit{target task} (which is drawn from the same distribution, or a slightly different one), the agent can rely on knowledge from the source tasks to speed up the learning process.
-This reuse of knowledge constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of any previous learning experience.
-Several algorithms have been proposed in the literature to transfer different elements involved in the learning process: experience samples~\cite{lazaric2008transfer,taylor2008transferring}, policies/options~\cite{fernandez2006probabilistic,konidaris2007building}, rewards~\cite{konidaris2006autonomous}, features~\cite{barreto2017successor}, parameters~\cite{doshi2016hidden,killian2017robust}, and so on.
-We refer the reader to~\cite{taylor2009transfer,lazaric2012transfer} for a thorough survey on transfer in RL.
+Recent advancements have allowed reinforcement learning (RL) \cite{sutton1998reinforcement} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{mnih2015human}, to the game of Go \cite{silver2016mastering}, to the control of sophisticated robotics systems \cite{kober2009policy,lillicrap2015continuous,levine2016end}.
+The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
+One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
+In the typical settings of transfer in RL \cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
+Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed up the learning process.
+This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previous learning experience.
+Several algorithms have been proposed in the literature to transfer experience samples \cite{lazaric2008transfer,taylor2008transferring}, policies/options \cite{fernandez2006probabilistic,konidaris2007building}, rewards \cite{konidaris2006autonomous}, features \cite{barreto2017successor}, parameters \cite{doshi2016hidden,killian2017robust}, and so on.
+We refer the reader to \cite{taylor2009transfer} for a thorough survey on transfer in RL.
 
@@
 Intuitively, assuming the tasks under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
-Among the appealing approaches for this problem we find Bayesian methods (e.g.,~\cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible.
-Similarly, model-based algorithms (e.g.,~\cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain.
+Among the appealing approaches for this problem we find Bayesian methods (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible.
+Similarly, model-based algorithms (e.g., \cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain.
 However, all these approaches either require strong assumptions (for example, on the distribution involved in Bayesian methods) or do not scale well to large problems.
@@
 %In this work, we tackle such limitations by considering a more general approach.
-Similarly to~\cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
+Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
 Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
@@
 
-Under the assumption that tasks follow a specific distribution, an intuitive choice for designing a transfer algorithm is to attempt at characterizing the uncertainty over the target task.
-Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task to reduce the uncertainty as quickly as possible.
+Under the assumption that tasks follow a certain distribution, an intuitive choice for designing a transfer algorithm is to attempt at characterizing the uncertainty over the target task.
+Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task in such a way that this uncertainty is reduced as quickly as possible.
 This simple intuition makes Bayesian \todo{probabilistic?
 distributional?} methods appealing approaches for transfer in RL, and many previous works have been proposed in this direction.
-In~\cite{wilson2007multi}, the authors assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of these two elements.
-Similarly, in~\cite{lazaric2010bayesian}, the authors assume that tasks are similar in their value functions and design a different hierarchical Bayesian model for transferring such information.
-More recently,~\cite{doshi2016hidden}, and its extension~\cite{killian2017robust}, consider tasks whose dynamics are governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
-However, most of these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
-The importance of having transfer algorithms that alleviate the need for strong assumptions and that easily adapt to different contexts motivates us to take a more general approach.
+\cite{wilson2007multi} assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of these two elements.
+Similarly, \cite{lazaric2010bayesian} assume tasks are similar in their value functions and design a different hierarchical Bayesian model for transferring such information.
+More recently, \cite{doshi2016hidden}, and its extension \cite{killian2017robust}, consider tasks whose dynamics are governed by some hidden parameters, and propose efficient Bayesian models for quickly learning such parameters in new tasks.
+However, all these algorithms require specific, and sometimes restrictive, assumptions (e.g., on the distributions involved or the function approximators adopted), which might limit their practical applicability.
+The importance of having transfer algorithms that alleviate the need of strong assumptions and that can be easily adapted to different contexts motivates us to take a more general approach.
 
-Similarly to~\cite{lazaric2010bayesian}, we assume tasks to share similarities in their value functions and use the given source tasks to learn a distribution over such functions.
-Then, we use this distribution as a prior for learning the target task and we propose a variational approximation of the corresponding posterior that is computationally efficient.
-Leveraging on recent ideas from randomized value functions~\cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+Similarly to \cite{lazaric2010bayesian}, we assume tasks to share similarities in their value functions and use the given source tasks to learn a distribution over such functions.
+Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
+Leveraging on recent ideas from randomized value functions \cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
 (with respect to) the sampled value function.
-We show that our approach is very general, in the sense that it can work with any parametric function approximator and with any prior/posterior distribution models (in this paper we focus on the Gaussian and Gaussian mixture models).
-In addition to the algorithmic contribution, we give also a theoretical contribution by providing a finite-sample analysis of our approach and an experimental contribution showing its empirical performance on four domains with increasing level of difficulty.
+We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models.
+We propose a finite-sample analysis that theoretically validates our approach, while empirically evaluating its performance on three domains with increasing level of difficulty.
 
@@
 
-We consider a distribution $\mathcal{D}$ over tasks, where each task $\mathcal{M}_\tau$ is modeled as a discounted Markov Decision Process (MDP).
-We define an MDP as a tuple $\mathcal{M}_\tau = \langle \mathcal{S},\mathcal{A},\mathcal{P}_\tau,\mathcal{R}_\tau,p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}_\tau(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}_\tau: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
+We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov Decision Process (MDP).
+We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$\todo{Should we provide a more transfer-oriented definition?}, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor.
 We assume the reward function to be uniformly bounded by a constant $R_{max}>0$.
@@
 At the beginning of each episode of interaction, the initial state $s_0$ is drawn from $p_0$.
-Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}_\tau(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated.
-The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}_{\mathcal{M}_\tau,\pi}[\sum_{t=0}^{\infty} \gamma^t \mathcal{R}_\tau(s_t,a_t)]$.
-To this end, we define the optimal value function of task $\mathcal{M}_\tau$, $Q_\tau^*(s,a)$, as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter.
-Then, an optimal policy $\pi_\tau^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi_\tau^*(s) = \argmax_a Q_\tau^*(s,a)$ for all states $s$.
-It can be shown (e.g.,~\cite{puterman1994markov}) that $Q_\tau^*$ is the unique fixed-point of the optimal Bellman operator $T_\tau$ defined by $T_\tau Q(s,a) = \mathcal{R}_\tau(s,a) + \gamma\mathbb{E}_{s' \sim\mathcal{P}_\tau}[\max_{a'}Q(s',a')]$ for any value function $Q$.
+Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated.
+The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$.
+To this end, we define the optimal value function $Q^*(s,a)$ as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter.
+Then, an optimal policy $\pi^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi^*(s) = \argmax_a Q^*(s,a)$ for all states $s$.
+It can be shown (e.g., \cite{puterman1994markov}) that $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$ defined by $TQ(s,a) = \mathcal{R}(s,a) + \gamma\mathbb{E}_{\mathcal{P}}[\max_{a'}Q(s',a')]$ for any value function $Q$.
 From now on, we adopt the term $Q$-function to denote any plausible value function, i.e., any function $Q : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R}$ uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
-In the following, to avoid cluttering the notation, we will drop the subscript $\tau$ when there is no ambiguity.
 
-We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^d\right\}$, and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
+We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$, and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
 When learning the optimal value function, a quantity of interest is how close a given function $Q_{\bm{w}}$ is to the fixed-point of the Bellman operator.
-A possible measure is its Bellman error (or Bellman residual), defined by $B_{\bm{w}} \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$.
-Notice that $Q_{\bm{w}}$ is optimal if and only if $B_{\bm{w}}(s,a) = 0$ for all $s,a$.
-If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, a sound objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B_{\bm{w}}}_{\nu}^2$.
-Unfortunately, it is well-known that an unbiased estimator of this quantity requires two independent samples of the next state $s'$ for each $s,a$ (e.g.,~\cite{maillard2010finite}).
-In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample $\langle s,a,s',r \rangle$, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$.
-Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B_{\bm{w}}}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$.
+A possible measure is its Bellman error (or Bellman residual), defined by $B(\bm{w}) \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$.
+Notice that $Q_{\bm{w}}$ is optimal if, and only if, $B(\bm{w})(s,a) = 0$ for all $s,a$.
+If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, an appealing objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B(\bm{w})}_{\nu}^2$\todo{Should we define norms before?}.
+Unfortunately, it is well-known that an unbiased estimator of this quanitity requires two independent samples of the next state $s'$ for each $s,a$ (e.g., \cite{maillard2010finite}).
+In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$.
+Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B(\bm{w})}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$.
 Whenever the distinction is clear from the context, with slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.
@@
 \eqref{eq:bayes}.
-The main intuition behind variational inference~\cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$.
+The main intuition behind variational inference \cite{} \todo{CITE} is to approximate the intractable posterior $p(\bm{w} | D)$ with a simpler distribution $q_{\bm{\xi}}(\bm{w})$.
 The latter is chosen in a parametric family, with variational parameters $\bm{\xi}$, as the minimizer of the Kullback-Leibler (KL) divergence w.r.t.
@@
 
+In this section, we theoretically analyze our variational transfer algorithm...
+
 A first important question that we need to answer is whether replacing max with mellow-max in the Bellman operator constitutes a strong approximation or not.
-It has been proved \cite{asadi2017alternative} that the mellow Bellman operator is a non-expansion under the $L_{\infty}$-norm and, thus, has a unique fixed-point.
+It has been proved \cite{} \todo{Cite MM} that the mellow Bellman operator is a contraction under the $L_{\infty}$-norm and, thus, has a unique fixed-point.
 However, how such fixed-point differs from the one of the optimal Bellman operator remains an open question.
@@
 
-The proof is provided in App.
-\ref{}.
-As expected, $\wt{Q}$ converges to $Q^*$ exponentially fast when either $\kappa$ (equivalently, $\beta_{\kappa}$) increases, or the action gaps are enlarged.
-Notice that this result is of interest even outside our specific settings.
-
-The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we restrict to the case of linear approximators with Gaussian prior and posterior.
-We assume Alg.
-\ref{alg:transfer} is used with a finite dataset and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
-Our main results is given in the following theorem.
-
-\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the Gaussian version of Alg.
-\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
-\begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
-\end{equation}
-\end{restatable}
-We refer the reader to App.
-\ref{} for the proof and a specific definition of the three constants.
-Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying very fast (as $\mathcal{O}(\frac{1}{N^2})$).
-Intuitively, our bound demonstrates that, if one starts very close the prior, the only error incurred, besides the irreducible approximation error, is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly.
-Furthermore, as $N\rightarrow\infty$ the only error term remaining is the irreducible approximation error.
-Notice that the variance term $\upsilon(\bm{w}^*)$ is due to the fact that we minimize a biased estimator of the Bellman error.
-As mentioned in the preliminaries, if double sampling of the next state is possible (e.g., in simulation), such term would disappear.
-Finally, we want to point out that the proof of this theorem relies on a very general result (Lemma \ref{lemma:general-bound} in App.
-\ref{}) that does not require any specific choice of distribution of approximator.
-Leveraging on such results, it is straightforward to provide a finite-sample analysis of the mixture version of our algorithm.
-For the sake of completeness, we report the derivation in App.
-\ref{}.
-
 \section{Experiments}
 
-In this section, we provide an experimental evaluation of our approach in four different domains with increasing level of difficulty.
+In this section, we provide an experimental evaluation of our approach in three different domains with increasing level of difficulty.
 In all experiments, we compare our Gaussian variational transfer algorithm (GVT) and the version using a $c$-component mixture of Gaussians ($c$-MGVT) to plain no-transfer RL (NT) with $\epsilon$-greedy exploration.
 To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
-Thus, we provide a discussion of related works in the next section.
 \todo{Any better motivation?}
@@
 The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
-In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.
-
+We consider a distribution over tasks in which doors have a fixed width of $1$, while their positions are sampled uniformly in $[0.5,9.5]$.
 Since the agent does not know where the doors are located in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
@@
 This does not hold for positions nearby the start state.
-However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).\todo{Good candidate to be removed}
+However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).
+Thus, we expect our algorithm to efficiently explore any target task.
 
@@
 In order to prove that our guesses are correct, we generate a set of $50$ source tasks for the three-room environment of Fig.
-\ref{} by sampling both door positions uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Sec.
+\ref{} by sampling both door positions uniformly, and solve all of them by directly minimizing the TD error as presented in Sec.
 \ref{sec:td}.
+In order to make sure that their solutions are accurate enough, we allow sampling the initial state uniformly in the environment and run until convergence.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
@@
 \ref{}.
-Each curve is the result of $20$ independent runs, each resampling the target and source tasks, with $95\%$ confidence intervals.
+Each curve is the result of $20$ independent runs, each resampling the target and source tasks.
+$95\%$ confidence intervals are shown.
 Further details on the parameters adopted in this experiment are given in App.
@@
 To better understand the differences between GVT and MGVT, we now consider transferring from a slightly different distribution than the one from which target tasks are drawn.
-We generate again $50$ source tasks but this time with the bottom door fixed at the center and the other one moving.
+We generate again $50$ source tasks but this time with the bottom door fixed in the center and the other one moving.
 Then, we repeat the previous experiment, allowing both doors to move when sampling target tasks.
@@
 Interestingly, MGVT seems almost unaffected by this change, proving that is has sufficient representation power to generalize to slightly different task distributions.
-The same does not hold for GVT, which now is not able to solve many of the sampled target tasks, as can be noticed from the higher variance.
+The same does not hold for GVT, which now is not able to solve many of the sampled target tasks,thus the very high variance.
 This proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
@@
 \ref{}.
-Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
+Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$, and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
 Fig.
-\ref{} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
+\ref{} shows the performance reached by GVT and MGVT with $1$ component at fixed iterations as a function of how likely the target task is according to such distribution.
 As expected GVT achieves poor performance on very unlikely tasks, even after many iterations.
@@
 
-We now consider two well-known classic control environments: Cartpole and Mountain Car \citep{sutton1998reinforcement}.
-For both, we generate $20$ source tasks by uniformly sampling their physical parameters (cart mass, pole mass, pole length for Cartpole and car speed for Mountain Car).
-We parameterize $Q$-functions using neural networks with $1$-layer of $32$ hidden units for Cartpole and $64$ for Mountain Car.
-A better description of these two environments and their parameters is given in App.
-\ref{}.
-In this experiment, we use a Double Deep Q-Network \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
-The results (same settings of Sec.
-\ref{sec:gw}) are shown in Fig.
-\ref{} and \ref{}.
-For Cartpole (Fig.
-\ref{}), all transfer algorithms are almost zero-shot.
-This is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are almost the same for all tasks.
-On the contrary, in Mountain Car (Fig.
-\ref{}) the optimal $Q$-functions become really different when changing the car speed.
-This causes GVT to struggle to solve the target task, while 1-MGVT achieves a good jump-start and convergences in less iterations.
+To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}.
+In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length.
+Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car.
+We kept a discount factor of $\gamma=0.99$ for both environments.
+Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator.
+We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.
+Analogously to Sec.
+\ref{sec:gw}, in Fig.
+\ref{} and \ref{} we show the expected return---as the average of the last $50$ episodes of lerning---of transfer for $20$ independent runs randomizing the sources and target tasks.
+In Fig.
+\ref{}, that corresponds to Cartpole, it is easily noticeable a near-optimal jump-start, in both GVT and 1-MGVT, that during the following iterations converges to the optimal performance.
+Furthermore, transfer in Mountain Car as shown in Fig.
+\ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence, within the same number of iterations, to the optimal performances.
 
@@
 
-\begin{corollary}\label{cor:diff-q}
+\begin{corollary}
 Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
@@
 
-\thg*
+\begin{theorem}\label{th:main-gaussian}
+aaa
+\end{theorem}
 \begin{proof}
@@
 \end{align*}
-Let us now apply Corollary \ref{cor:diff-q}. We have that, with probability at least $1-\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ]}{(1-\gamma)\delta}
-\end{align*}
-Thus, we probability at least $1-2\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
-\end{align*}
 \end{proof}
@@
 
-\begin{equation}
-\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] + KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
-\end{equation}
+\begin{align}
+\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\&+ KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{align}
 
@@
 
-\begin{equation}
-\widetilde{\mathcal{L}}(\bm{\xi}) = \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] + KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
-\end{equation}
+\begin{align}
+\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\ &+\ KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\end{align}
 
@@
 In the following sections we present the configurations used for the experiments presented in this paper.
-For all our experiments we set $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$.
-Also, we used ADAM optimizer---with parameters $\beta_1=0.9$, $\beta_2=0.999$---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
+For all our experiments we set $\kappa=100$, $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$.
+Also, we used ADAM optimizer---with parameters $\beta_1=0.9$ for the decay of the first order momentum and $\beta_2=0.999$ for the second order momentum---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
 For the non-transfer algorithms only ADAM was used with the same mentioned parameters.
@@
 
+% add figures of convergent DDQN. Comparison for various exploration fractions.
+
 \subsection{Maze Navigation}
 
+%enumerate mazes. training parameters dqn. approximator. mgvt and gvt paramters
+
+For the maze navigation task presented in Sec.
+\ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
+In Fig.
+\ref{}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
+Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.
+
+For the experiments we used as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the state of the MDP and an output layer that outputs the value of each action.
+For training the sources we, again, used DDQN with $Batch\_size = 70$, $Buffer\_size = 10000$ and $Target\_Update\_Frequency = 100$, setting the $Exploration\_fraction = 0.1$ with $\epsilon_s=1$ and $\epsilon_f=0.01$ and ran it for $200k$ to ensure convergence.
+
+\begin{tikzpicture}[scale=0.4]
+\draw [line width=0cm, white] (0,0) grid (7,7);
+\begin{scope}[shift={(0,1.5)}]
+\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
+\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
+\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
+\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);
+
+\draw [fill=black!50] (1,1) circle [radius=0.1cm];
+
+\node at (1.7,-0.5)[left] {start};
+\node at (3.3,5.5) [right]{goal};
+%\node at (1,1) [ right] {$A$};
+
+\draw [thick] (0,0) rectangle (5,5);
+\draw [line width=0.5mm] (1.5,5/3) -- (5,5/3);
+\draw [line width=0.5mm] (0,5/3) -- (0.5,5/3);
+\draw [line width=0.5mm] (0,10/3) -- (3,10/3);
+\draw [line width=0.5mm] (4,10/3) -- (5,10/3);
+\end{scope}
+\end{tikzpicture}
+
 \end{document}

### 2018-05-16 NIPS 2018/main.tex
descriptions of the experiments in appendix C

@@
   \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
+    %\includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
+    \begin{tikzpicture}[scale=0.4]
+\draw [white] (0,0) grid (7,7);
+\begin{scope}[shift={(0,1.5)}]
+\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
+\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
+\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
+\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);
+
+%\draw [fill=black!50] (1,1) circle [radius=0.1cm];
+%\node at (1,1) [ right] {$A$};
+
+\node at (1.7,-0.5)[left] {start};
+\node at (3.3,5.5) [right]{goal};
+
+\draw [thick] (0,0) rectangle (5,5);
+\draw [line width=0.5mm] (1.25,5/3) -- (5,5/3);
+\draw [line width=0.5mm] (0,5/3) -- (0.75,5/3);
+\draw [line width=0.5mm] (0,10/3) -- (3.25,10/3);
+\draw [line width=0.5mm] (3.75,10/3) -- (5,10/3);
+\end{scope}
+\end{tikzpicture} 
     \caption{}
@@
 
-In the present section we present the hyper-parameters and corresponding values that were used for the experiments presented in this paper.
-
-For all the algorithms implemented for the empirical evaluation, we used a Replay Buffer ($Buffer\_size$) with a fixed size and batches of a given size ($Batch\_size$) sampled randomly from it to perform the gradient steps.
-
-In the case of no-transfer-based algorithms we used a linearly scheduled $\epsilon$-greedy exploration for which we could specify the starting and final values of $\epsilon$, $\epsilon_s$ and $\epsilon_f$ respectively, and the \emph{Exploration Fraction} of the maximum number of iterations for which the linear schedule would be used.
-As the learning procedure is done by gradient descent, we also have $\alpha$ as the learning rate.
-Additionally, in the case of the DDQNs we have the \emph{Target Update Frequency} that specifies the number of iterations before setting the target neural network to the current parameters of the online network.
-
-As presented in Sec.
-\ref{sec:td}, for the minimization procedure of the TD error based on \emph{mellow-max} we also have to set $\kappa$ to control the approximation to the maximum operator and $\psi \in \left[0,1\right]$ to control the proportion between the full residual gradient and the semi-gradient approach used.
-
-For the transfer algorithms proposed here, namely, GVT and MGVT we have the following parameters.
-As presented in Sec.
-\ref{sec:alg}, we have $\lambda \geq 0$ to control the trade-off between the prior knowledge and the loss measure---i.e.
-the TD error---in the target task.
-Moreover, we allow to control the learning rates differently for the gradients related to the means and covariance matrices, the Cholesky factor L to be precise: $\alpha_{\mu}$ and $\alpha_L$.
-In order to approximate the expectation of the TD error, we used a fixed number of $weights$ sampled from the posterior distribution.
-Specifically, for MGVT it is necessary to specify the value of the variance $\sigma_p^2$ for the prior model and the number of components $C$ for the posterior family to be used.
-Furthermore, as explained in Sec.
-\ref{sec:mgvt}, to perform the initialization of the posterior by minimizing the KL divergence we set a maximum number of iterations (\emph{UKL max iterations}) and the precision to reach during this optimization $\varepsilon$ and its learning rate $\eta$.
-Finally, to avoid problems with the positive-definiteness of the covariances being learned, we specify a hyper-parameter $\sigma_{min}$ as the minimum value the diagonal elements of the Cholesky factor can reach.
-
-In the following sections we present the configurations used for the experiments presented in this paper.
-For all our experiments we set $\kappa=100$, $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$.
-Also, we used ADAM optimizer---with parameters $\beta_1=0.9$ for the decay of the first order momentum and $\beta_2=0.999$ for the second order momentum---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT.
-For the non-transfer algorithms only ADAM was used with the same mentioned parameters.
+In the present section we present the values of the hyper-parameters that we use for the experiments presented in this paper.
+
+It is important to notice that for the implementation of the algorithms we used a Replay Buffer with a fixed size and batches of a given size sampled randomly from it to perform the gradient steps and used ADAM as optimizer with the default parameters.
 
@@
 
+For these experiments, in order to train the source tasks for the Rooms Problem, we directly minimize the expected TD error based on the \textit{mellow} Bellman operator by stochastic gradient descent.
+.
+We set to use a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$, $\psi=0.5$ and a learning rate $\alpha=0.001$.
+Additionally, for exploration we use an \textit{Exploration Fraction} of $0.7$.
+
+For the transfer algorithm GVT, we set a \textit{Batch Size} of 50 and a \textit{Buffer Size} of 10000.
+We use $\psi=0.5$, $\lambda=10^{-4}$ and 10 \textit{weights} for approximating the expected TD error.
+For the learning rates we use $\alpha_{\mu}=0.001$ for the mean and $\alpha_{L}=0.0001$ to learn the Cholesky factor L.
+Furthermore, we restrict the minimum value reachable for the eigenvalues of these factors to be $\sigma_{min}^2=0.0001$.
+In the case of MGVT we use, instead, $\lambda=10^{-6}$, $\alpha_{\mu}=0.001$ and $\alpha_{L}=0.1$.
+Finally, for the prior's covariances we set $\sigma_p^2=10^{-5}$.
+
+Besides the results that we show in Sec. \ref{sec:gw}, we present in this section further empirical evaluation.
+
+Firstly, we show the results of the evaluation performance.
+We compute this as the average reward gotten when the agent acts using the greedy policy using the parameters at the moment of evaluation.
+In the case of GVT, we take the mean of the posterior Gaussian and, in MGVT, we compute the mean of the posterior by averaging the means of its components and use it for evaluation.
+
+In Fig.
+\ref{fig:3r-rew} we show the results when evaluating for the Rooms Problem when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
+It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer algorithm and shows that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
+
+In Fig.\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled sources have a door fixed and the target task is generated by sampling both doors' positions.
+From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution is this more complicated setting, whereas GVT fails to adapt as MGVT.
+In this scenario, using a Gaussian to model the prior over-constrains the algorithm to stay close to part of the function space that cannot solve optimally the target tasks sampled from the modified distribution.
+
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room/erew.pdf}
+    \caption{}
+    \label{fig:3r-erew}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-gen/erew.pdf}
+    \caption{}
+    \label{fig:3rg-erew}
+  \end{subfigure}
+  \caption{(a) Rooms Problem: Evaluation Reward, (b) Rooms Problem: Evaluation Reward in the generalization experiment}
+  \label{fig:rooms-erew}
+\end{figure*}
+
+Furthermore, we investigate how is the exploratory behavior of our transfer algorithms  and how they differ.
+In Fig.
+\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2k$ iterations and we represent in the plot the positions visited by the agent.
+
+Observing Fig.
+\ref{fig:nt-vs-gvt}, it is possible to understand the difference between the $\epsilon$-greedy exploration and the resulting behavior from GVT.
+It is noticeable that NT is not capable to lead the agent to the goal within the given iterations as most of the states visited are sparse within the first room, whereas GVT is able to concentrate more of its effort in looking for the door around the middle of the wall.
+After finding it, in the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
+This is not surprising as the value function should be equal for all tasks after crossing the door.
+
+In the other case, we have Fig.
+\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of MGVT is with respect to GVT.
+MGVT is able to actually explore the right part of the first room within these iterations, which might be seen as the result of the prior model being able to capture more information that the Gaussian, hence the higher speed-up in convergence and robustness to changes in the distribution from which target tasks are drawn.
+Indeed, as MGVT is able to allow for more flexible exploration, it is capable to discover how to best solve the task much faster than GVT.
+
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_gvt.pdf}
+    \caption{}
+    \label{fig:nt-vs-gvt}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_mgvt.pdf}
+    \caption{}
+    \label{fig:nt-vs-mgvt}
+  \end{subfigure}
+  \caption{(a) Rooms Problem: Evaluation Reward, (b) Rooms Problem: Evaluation Reward in the generalization experiment}
+  \label{fig:rooms-expl}
+\end{figure*}
+
 \subsection{Classic Control}
 
-For the Cartpole environment, we generated tasks by uniformly sampling the cart mass in the range $\left[0.5,1.5\right]$, the pole mass in $\left[0.1,0.3\right]$ and the pole length in $\left[0.2,1.0\right]$.
-
-During the training of the source tasks, we used a $Batch\_size = 32$, $Buffer\_size = 50000$.
-For DDQN with a $Target\_Update\_Frequency = 500$ and $Exploration\_fraction = 0.35$ with $\epsilon_s=1$ and $\epsilon_f=0.1$.
-The function approximator was a Multilayer Perceptron (MLP) with ReLU as activation function and a hidden layer of $32$ neurons.
-For the transfer experiments we set $Batch\_size=500$ and $weights=5$, $\lambda=0.001$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$.
-In the case of MGVT we set $\sigma_p^2=10^{-5}$.
-
-In the case of Mountain Car, to generate tasks we sampled uniformly the base speed of the actions in the range $\left[0.001, 0.0015\right]$.
-We trained DDQN with $Target\_Update\_Frequency = 500$ and a $Batch\_size = 32$, $Buffer\_size = 50000$.
-For the $Exploration\_fraction = 0.15$ with $\epsilon_s=1$ and $\epsilon_f=0.1$.
-We used an MLP with single hidden layer of $64$ neurons with ReLU activation.
-For the transfer experiments we set the $Batch\_size=50$, $weights=10$, $\lambda=10^{-5}$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$.
-For MGVT we set $\sigma_p^2=10^{-5}$.
-
-% add figures of convergent DDQN. Comparison for various exploration fractions.
+\subsubsection{Cartpole}
+
+For this environment we generate tasks by uniformly sampling the cart mass in the range $\left[0.5,1.5\right]$, the pole mass in $\left[0.1,0.3\right]$ and the pole length in $\left[0.2,1.0\right]$.
+
+During the training of the source tasks, we use a \textit{Batch Size} of $150$ and \textit{Buffer Size} of $50000$.
+Specifically, for DDQN we use a \textit{Target Update Frequency} of $500$ and and \textit{Exploration Fraction} of $0.35$.
+We use a Multilayer Perceptron (MLP) with ReLU as activation function and a hidden layer of $32$ neurons, an input layer of $4$ and the value of the $2$ actions as the output layer.
+
+For the transfer experiments, we set the \textit{Batch Size} to $500$, the number of \textit{weights} sampled to approximate the expected gradient of the TD error to $5$, $\lambda=0.001$ and $\psi=0.5\ $.
+We use $\alpha_{\mu}=0.001$ as the learning rate for the means.
+For the Cholesky factor L we use $\alpha_L=0.0001$ and set the a limit that the minimum eigenvalue may reach $\sigma_{min}^2=0.0001\ $.
+Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$.
+
+In Fig.
+\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters of the Q function.
+In the case of GVT, we use the mean of the Gaussian posterior for the greedy policy and for MGVT corresponds to the mean of the Mixture of Gaussians for the posterior, that reduces to the average of the components' means.
+
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/cartpole/erew.pdf}
+    \caption{}
+    \label{fig:cp-erew}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/mountaincar/erew.pdf}
+    \caption{}
+    \label{fig:mc-erew}
+  \end{subfigure}
+  \caption{(a) Cartpole: Evaluation Reward, (b) Mountain Car: Evaluation Reward}
+  \label{fig:ccerew}
+\end{figure*}
+
+\subsubsection{Mountain Car}
+
+We generate tasks sampling uniformly the base speed of the actions in the range $\left[0.001, 0.0015\right]$.
+
+For the sources, we train the tasks using DDQN with a \textit{Target Update Frequency} of $500$, a \textit{Batch Size} of $32$, a  \textit{Buffer Size} of $50000$.
+Moreover, we set the \textit{Exploration Fraction} to $0.15$.
+We use an MLP with single hidden layer of $64$ neurons with ReLU activation function, an input layer of $4$ neurons and as output the value of each of the $2$ actions.
+
+For the transfer experiments, we set the \textit{Batch Size} to $500$, and use $10$ \textit{weights} to approximate the expected TD error, $\lambda=10^{-5}$ and $\psi=0.5$.
+For the learning rates, we use $\alpha_{\mu}=0.001$ for learning the means of the Gaussians.
+In the case of the Cholesky factors L, we use $\alpha_L=0.0001$ and allow the eigenvalues to reach a minimum value of $\sigma_{min}^2=0.0001$.
+In the case of MGVT, additionally, we set $\sigma_p^2=10^{-5}$.
+
+In Fig.
+\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the current parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT.
 
 \subsection{Maze Navigation}
-
-%enumerate mazes. training parameters dqn. approximator. mgvt and gvt paramters
 
@@
 In Fig.
-\ref{}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
+\ref{fig:mazes}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
 Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.
@@
 For the experiments we used as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the state of the MDP and an output layer that outputs the value of each action.
-For training the sources we, again, used DDQN with $Batch\_size = 70$, $Buffer\_size = 10000$ and $Target\_Update\_Frequency = 100$, setting the $Exploration\_fraction = 0.1$ with $\epsilon_s=1$ and $\epsilon_f=0.01$ and ran it for $200k$ to ensure convergence.
-
-\begin{tikzpicture}[scale=0.4]
-\draw [line width=0cm, white] (0,0) grid (7,7);
-\begin{scope}[shift={(0,1.5)}]
-\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
-\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
-\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
-\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);
-
-\draw [fill=black!50] (1,1) circle [radius=0.1cm];
-
-\node at (1.7,-0.5)[left] {start};
-\node at (3.3,5.5) [right]{goal};
-%\node at (1,1) [ right] {$A$};
-
-\draw [thick] (0,0) rectangle (5,5);
-\draw [line width=0.5mm] (1.5,5/3) -- (5,5/3);
-\draw [line width=0.5mm] (0,5/3) -- (0.5,5/3);
-\draw [line width=0.5mm] (0,10/3) -- (3,10/3);
-\draw [line width=0.5mm] (4,10/3) -- (5,10/3);
-\end{scope}
-\end{tikzpicture}
+For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$.
+
+\begin{figure*}[t]
+\centering
+\begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze0.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze1.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze2.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze3.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze4.pdf}
+    \caption{}
+  \end{subfigure}
+
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze5.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze6.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze7.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze8.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze9.pdf}
+    \caption{}
+  \end{subfigure}
+
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze10.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze11.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze12.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze13.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze14.pdf}
+    \caption{}
+  \end{subfigure}
+
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze15.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze16.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze17.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze18.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.18\textwidth}
+    \includegraphics[width=\textwidth]{images/maze/maze19.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{Set of mazes for the Maze Navigation task}
+  \label{fig:mazes}
+\end{figure*}
 

### 2018-05-16 NIPS 2018/main.tex
Added MGVT theorem

@@
 
+\begin{restatable}{theorem}{thmg} \label{th:main-mixture}
+Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Consider the mixture version of Alg.
+\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and prior $p(\bm{w}) =\frac{1}{\abs{\mathcal{W}_s}}\sum_j\mathcal{N}(\bm{w}_j,\sigma^2_p\bm{I})$.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+\begin{equation}
+\resizebox{0.93\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\end{equation}
+\end{restatable}
+\begin{proof}
+Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
+Then, we obtain:
+\begin{align}\label{eq:thmg-1}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align}
+The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+\begin{align}\label{eq:thmg-2}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
+\end{align}
+where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
+\ref{th:ukl}.
+Notice that, since we reduced the posterior to one component, the can get rid of the index $i$.
+Using the definitions of these two vectors from Sec.
+8 of \cite{hershey2007approximating}, we have:
+\begin{align*}
+\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+\begin{align}\label{eq:chi2}
+\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align}
+Since the KL divergence is:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
+\end{align*}
+Eq. \ref{eq:chi2} can be rewritten as:
+\begin{align*}
+\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
+\begin{align*}
+KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
+\end{align*}
+where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
+\begin{align*}
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
+\end{align*}
+Putting it all together:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
+\end{align*}
+Notice that, from now on, one can simply apply the proof of Thm.
+\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
+Thus, by changing the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log(\sigma^2_p + \log N)$\todo{$c_2$ actually contains $N$.
+Should we make this more explicit?}, $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, and setting $c_4 = \frac{2\lambda}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+\end{align*}
+\end{proof}
+
 \section{Additional Details on the Algorithms}

### 2018-05-16 NIPS 2018/main.tex
Updated main paper with MGVT theorem instead of GVT

@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we restrict to the case of linear approximators with Gaussian prior and posterior.
+To address this point, we consider Alg.
+\ref{alg:transfer} with mixture of Gaussians and linear approximators.
 We assume Alg.
@@
 
-\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
+\begin{restatable}{theorem}{thmg} \label{th:main-mixture}
 Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
 Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the Gaussian version of Alg.
-\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
+Consider the mixture version of Alg.
+\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and prior $p(\bm{w}) =\frac{1}{\abs{\mathcal{W}_s}}\sum_j\mathcal{N}(\bm{w}_j,\sigma^2_p\bm{I})$.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
 \ref{eq:elbo} on a dataset $D$ of $N$ samples.
@@
 Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
 \end{equation}
 \end{restatable}
+
 We refer the reader to App.
 \ref{} for the proof and a specific definition of the three constants.
-Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying very fast (as $\mathcal{O}(\frac{1}{N^2})$).
-Intuitively, our bound demonstrates that, if one starts very close the prior, the only error incurred, besides the irreducible approximation error, is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly.
-Furthermore, as $N\rightarrow\infty$ the only error term remaining is the irreducible approximation error.
+Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(\frac{1}{N^2})$.
+Intuitively, the bound is tighten when the source tasks' $Q$-functions are, on average, close to the optimal ones for the target task.
+In such case, the dominating error is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly, as new data is collected.
+Furthermore, as $N\rightarrow\infty$ the only error term remaining is, as usual, the irreducible approximation error.
 Notice that the variance term $\upsilon(\bm{w}^*)$ is due to the fact that we minimize a biased estimator of the Bellman error.
-As mentioned in the preliminaries, if double sampling of the next state is possible (e.g., in simulation), such term would disappear.
+If double sampling of the next state were possible (e.g., in simulation), such term could be removed.
 Finally, we want to point out that the proof of this theorem relies on a very general result (Lemma \ref{lemma:general-bound} in App.
 \ref{}) that does not require any specific choice of distribution of approximator.
-Leveraging on such results, it is straightforward to provide a finite-sample analysis of the mixture version of our algorithm.
+Leveraging on such results, it is straightforward to provide a finite-sample analysis of the Gaussian version of our algorithm.
 For the sake of completeness, we report the derivation in App.
-\ref{}.
+\ref{}.\todo{Should we discuss the main difference between the MGVT and GVT bounds here?}
 
@@
 
-\thg*
+\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
+Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Consider the Gaussian version of Alg.
+\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+\begin{equation}
+\resizebox{0.93\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
+\end{equation}
+\end{restatable}
 \begin{proof}
@@
 
-\begin{restatable}{theorem}{thmg} \label{th:main-mixture}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the mixture version of Alg.
-\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and prior $p(\bm{w}) =\frac{1}{\abs{\mathcal{W}_s}}\sum_j\mathcal{N}(\bm{w}_j,\sigma^2_p\bm{I})$.
-Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
-\begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
-\end{equation}
-\end{restatable}
+\thmg*
 \begin{proof}

### 2018-05-16 NIPS 2018/main.tex
Minor changes to Sec.4

@@
 \ref{alg:transfer} with mixture of Gaussians and linear approximators.
-We assume Alg.
-\ref{alg:transfer} is used with a finite dataset and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
+We assume only a finite dataset is available and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
 Our main results is given in the following theorem.
@@
 Consider the mixture version of Alg.
-\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and prior $p(\bm{w}) =\frac{1}{\abs{\mathcal{W}_s}}\sum_j\mathcal{N}(\bm{w}_j,\sigma^2_p\bm{I})$.
+\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
 Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
@@
 We refer the reader to App.
-\ref{} for the proof and a specific definition of the three constants.
-Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(\frac{1}{N^2})$.
+\ref{} for the proof and a specific definition of the constants.
+Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(N^2)$.
 Intuitively, the bound is tighten when the source tasks' $Q$-functions are, on average, close to the optimal ones for the target task.
 In such case, the dominating error is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly, as new data is collected.
-Furthermore, as $N\rightarrow\infty$ the only error term remaining is, as usual, the irreducible approximation error.
+Furthermore, as $N\rightarrow\infty$ the only error term remaining is, as usual, the irreducible approximation error due to the limited functional space.
 Notice that the variance term $\upsilon(\bm{w}^*)$ is due to the fact that we minimize a biased estimator of the Bellman error.

### 2018-05-16 NIPS 2018/main.tex
added further results to appendix C

--- 2018-05-16 NIPS 2018/main.tex
@@
 
-\begin{restatable}{theorem}{thmg} \label{th:main-mixture}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the mixture version of Alg.
-\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and prior $p(\bm{w}) =\frac{1}{\abs{\mathcal{W}_s}}\sum_j\mathcal{N}(\bm{w}_j,\sigma^2_p\bm{I})$.
-Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
-\begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
-\end{equation}
-\end{restatable}
-\begin{proof}
-Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
-Then, we obtain:
-\begin{align}\label{eq:thmg-1}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
-\end{align}
-The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
-\begin{align}\label{eq:thmg-2}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
-\end{align}
-where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
-\ref{th:ukl}.
-Notice that, since we reduced the posterior to one component, the can get rid of the index $i$.
-Using the definitions of these two vectors from Sec.
-8 of \cite{hershey2007approximating}, we have:
-\begin{align*}
-\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-\end{align*}
-\begin{align}\label{eq:chi2}
-\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-\end{align}
-Since the KL divergence is:
-\begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
-\end{align*}
-Eq. \ref{eq:chi2} can be rewritten as:
-\begin{align*}
-\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-\end{align*}
-Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
-\begin{align*}
-KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
-\end{align*}
-where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
-\begin{align*}
-\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
-\end{align*}
-Putting it all together:
-\begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
-\end{align*}
-Notice that, from now on, one can simply apply the proof of Thm.
-\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
-Thus, by changing the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log(\sigma^2_p + \log N)$\todo{$c_2$ actually contains $N$.
-Should we make this more explicit?}, $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, and setting $c_4 = \frac{2\lambda}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
-\end{align*}
-\end{proof}
-
 \section{Additional Details on the Algorithms}
@@
 
-And substituting \ref{eq:ukl} in the negative ELBO in \ref{eq:elbo} we get the following upper bound.
+And substituting (\ref{eq:ukl}) in the negative ELBO in \ref{eq:elbo} we get the following upper bound.
 
 \begin{align}
-\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\&+ KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\&+ \frac{\lambda}{N} KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
 \end{align}
@@
 \begin{align}
-\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\ &+\ KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\ &+\ \frac{\lambda}{N}KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
 \end{align}
@@
 
-In the present section we present the values of the hyper-parameters that we use for the experiments presented in this paper.
-
-It is important to notice that for the implementation of the algorithms we used a Replay Buffer with a fixed size and batches of a given size sampled randomly from it to perform the gradient steps and used ADAM as optimizer with the default parameters.
+In the present section we present the values of the hyper-parameters that we use for the experiments in this paper.
+
+It is important to notice that for the implementation of the algorithms we use a Replay Buffer with a fixed size and batches of a given size sampled randomly from it to perform the gradient steps and use ADAM as the optimizer with the default parameters.
 
@@
 For these experiments, in order to train the source tasks for the Rooms Problem, we directly minimize the expected TD error based on the \textit{mellow} Bellman operator by stochastic gradient descent.
-.
 We set to use a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$, $\psi=0.5$ and a learning rate $\alpha=0.001$.
@@
 
-For the transfer algorithm GVT, we set a \textit{Batch Size} of 50 and a \textit{Buffer Size} of 10000.
-We use $\psi=0.5$, $\lambda=10^{-4}$ and 10 \textit{weights} for approximating the expected TD error.
-For the learning rates we use $\alpha_{\mu}=0.001$ for the mean and $\alpha_{L}=0.0001$ to learn the Cholesky factor L.
-Furthermore, we restrict the minimum value reachable for the eigenvalues of these factors to be $\sigma_{min}^2=0.0001$.
+For the transfer algorithm GVT, we set a \textit{Batch Size} of $50$ and a \textit{Buffer Size} of $10000$.
+We use $\psi=0.5$, $\lambda=10^{-4}$ and $10$ \textit{weights} to estimate the expected TD error.
+For the learning rates we use $\alpha_{\mu}=0.001$ for the mean of the posterior Gaussian and $\alpha_{L}=0.0001$ to learn its Cholesky factor L.
+Furthermore, we restrict the minimum value reachable for the eigenvalues of these factor to be $\sigma_{min}^2=0.0001$.
 In the case of MGVT we use, instead, $\lambda=10^{-6}$, $\alpha_{\mu}=0.001$ and $\alpha_{L}=0.1$.
@@
 Firstly, we show the results of the evaluation performance.
-We compute this as the average reward gotten when the agent acts using the greedy policy using the parameters at the moment of evaluation.
+We compute this as the average reward gotten when the agent acts using the greedy policy using the parameters at the iteration of evaluation.
 In the case of GVT, we take the mean of the posterior Gaussian and, in MGVT, we compute the mean of the posterior by averaging the means of its components and use it for evaluation.
@@
 In Fig.
-\ref{fig:3r-rew} we show the results when evaluating for the Rooms Problem when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
-It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer algorithm and shows that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
-
-In Fig.\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled sources have a door fixed and the target task is generated by sampling both doors' positions.
-From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution is this more complicated setting, whereas GVT fails to adapt as MGVT.
+\ref{fig:3r-rew} we show the results when evaluating the Rooms Problem performance when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
+It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer performance and shows that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
+
+In Fig.\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled source tasks have a door fixed and the target task is generated by sampling both doors' positions.
+From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution in this more complicated setting, whereas GVT fails to adapt as consistently as MGVT, thus the higher variance and distance to the optimal value.
 In this scenario, using a Gaussian to model the prior over-constrains the algorithm to stay close to part of the function space that cannot solve optimally the target tasks sampled from the modified distribution.
@@
 
-Furthermore, we investigate how is the exploratory behavior of our transfer algorithms  and how they differ.
+Furthermore, we investigate the exploratory behavior induced by our transfer algorithms and how they differ between each other and in comparison with $\epsilon$-greedy exploration.
 In Fig.
@@
 It is noticeable that NT is not capable to lead the agent to the goal within the given iterations as most of the states visited are sparse within the first room, whereas GVT is able to concentrate more of its effort in looking for the door around the middle of the wall.
-After finding it, in the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
+After finding it, already in the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
 This is not surprising as the value function should be equal for all tasks after crossing the door.
@@
 In the other case, we have Fig.
-\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of MGVT is with respect to GVT.
-MGVT is able to actually explore the right part of the first room within these iterations, which might be seen as the result of the prior model being able to capture more information that the Gaussian, hence the higher speed-up in convergence and robustness to changes in the distribution from which target tasks are drawn.
-Indeed, as MGVT is able to allow for more flexible exploration, it is capable to discover how to best solve the task much faster than GVT.
+\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
+Indeed, 1-MGVT is able to actually explore the right part of the first room within these iterations, which might be seen as the result of the prior model being able to capture more information than the Gaussian; hence, the higher speed-up in convergence and robustness to changes in the distribution from which target tasks are drawn.
+Indeed, as 1-MGVT is able to allow for more flexible exploration, it is capable to discover how to best solve the task much faster than GVT.
 
@@
   \end{subfigure}
-  \caption{(a) Rooms Problem: Evaluation Reward, (b) Rooms Problem: Evaluation Reward in the generalization experiment}
+  \caption{(a) Two-Rooms Problem: $\epsilon$-greedy vs. GVT, (b) Two-Rooms Problem: $\epsilon$-greedy vs. 1-MGVT experiment}
   \label{fig:rooms-expl}
@@
 
+Finally, in Fig.
+\ref{fig:sequential} we present the expected return as a function of the number of source tasks used for GVT and MGVT.
+In particular, we show the resulting curves after $1000$ iterations in Fig.
+\ref{fig:seq-1000} and after $1950$ iterations in Fig.
+\ref{fig:seq-1950}.
+It is interesting to notice the difference on performance between MGVT and GVT whenever there is a small number of source tasks.
+MGVT clearly provides faster adaptation in the presence of low prior knowledge as it can be discern from the gap seen in nearly a $1000$ iterations between the plots.
+It is as expected because approximating the prior Gaussian distribution using maximum likelihood estimations with a low number of samples does not provide enough precision.
+As the number of source tasks increases, as seen more clearly from Fig.
+\ref{fig:seq-1950}, the performances become closer for this environment.
+
+Finally, among the MGVT curves in Fig.
+\ref{fig:sequential}, we see that, even if more components lead to slightly better performances, the advantage is not quite significant in this environment.
+As seen before, the actual performances will converge to optimality in all the MGVT cases.
+Clearly, as we expect all components to converge to the optimal parameters, the initial performance difference will, indeed, reduce fast.
+
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/sequential/lrew_1000.pdf}
+    \caption{}
+    \label{fig:seq-1000}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/sequential/lrew_1950.pdf}
+    \caption{}
+    \label{fig:seq-1950}
+  \end{subfigure}
+  \caption{Expected return w.r.t. to the number of source tasks (a) $1000$ iterations, (b) $1950$ iterations}
+  \label{fig:sequential}
+\end{figure*}
+
 \subsection{Classic Control}
@@
 During the training of the source tasks, we use a \textit{Batch Size} of $150$ and \textit{Buffer Size} of $50000$.
-Specifically, for DDQN we use a \textit{Target Update Frequency} of $500$ and and \textit{Exploration Fraction} of $0.35$.
+Specifically, for DDQN we use a \textit{Target Update Frequency} of $500$ and and \textit{Exploration Fraction} of $0.35$ and a learning rate $\alpha=0.001$.
 We use a Multilayer Perceptron (MLP) with ReLU as activation function and a hidden layer of $32$ neurons, an input layer of $4$ and the value of the $2$ actions as the output layer.
 
-For the transfer experiments, we set the \textit{Batch Size} to $500$, the number of \textit{weights} sampled to approximate the expected gradient of the TD error to $5$, $\lambda=0.001$ and $\psi=0.5\ $.
-We use $\alpha_{\mu}=0.001$ as the learning rate for the means.
-For the Cholesky factor L we use $\alpha_L=0.0001$ and set the a limit that the minimum eigenvalue may reach $\sigma_{min}^2=0.0001\ $.
-Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$.
+For the transfer experiments, we set the \textit{Batch Size} to $500$, the number of \textit{weights} sampled to approximate the expected TD error to $5$, $\lambda=0.001$ and $\psi=0.5\ $.
+We use $\alpha_{\mu}=0.001$ as the learning rate for the mean of the Gaussian posterior.
+For its the Cholesky factor L we use $\alpha_L=0.0001$ and set the limit that the minimum eigenvalue may reach to $\sigma_{min}^2=0.0001\ $.
+Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$and leave the learning rates of the posterior components' means and Cholesky factor the same as GVT.
 
 In Fig.
-\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters of the Q function.
+\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters in the iteration of evaluation.
 In the case of GVT, we use the mean of the Gaussian posterior for the greedy policy and for MGVT corresponds to the mean of the Mixture of Gaussians for the posterior, that reduces to the average of the components' means.
+From the figure we can see how the transfer methods provide a significant jump-start w.r.t.
+the DDQN evaluation.
+Although, a slight performance drop is seen as the algorithm adapts to the optimal Q-function, the algorithm quickly reaches optimality and converges to the actual optimal performance while DDQN, within these iterations, remains on average slightly suboptimal.
+\todo{improve this}
 
@@
 
-For the sources, we train the tasks using DDQN with a \textit{Target Update Frequency} of $500$, a \textit{Batch Size} of $32$, a  \textit{Buffer Size} of $50000$.
+For the sources, we train the tasks using DDQN with a \textit{Target Update Frequency} of $500$, a \textit{Batch Size} of $32$, a  \textit{Buffer Size} of $50000$ and learning rate $\alpha=0.001$.
 Moreover, we set the \textit{Exploration Fraction} to $0.15$.
-We use an MLP with single hidden layer of $64$ neurons with ReLU activation function, an input layer of $4$ neurons and as output the value of each of the $2$ actions.
+We use an MLP with single hidden layer of $64$ neurons with ReLU activation function, an input layer of $4$ neurons and as output the value of each of the $3$ actions.
 
@@
 In the case of the Cholesky factors L, we use $\alpha_L=0.0001$ and allow the eigenvalues to reach a minimum value of $\sigma_{min}^2=0.0001$.
-In the case of MGVT, additionally, we set $\sigma_p^2=10^{-5}$.
-
-In Fig.
-\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the current parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT.
+In the case of MGVT, additionally, we set the prior covariance to be $\sigma_p^2=10^{-5}$.
+
+Finally, in Fig.
+\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT in the iteration of evaluation.
+In this plot, we can observe directly how fast is MGVT able to converge its mean to the actual optimal performance and that even if GVT struggles to find learn in comparison with MGVT, still provides a clear advantage w.r.t.
+DDQN.
+Also, it is worth noting that the variances seen are result that different speeds of the car result in different time to reach the goal and, thus, different optimal performances.
+
+Clearly, this variation in the values among tasks allows MGVT to excel w.r.t.
+to the other methods.
+The richer prior of MGVT allows to exploit efficiently the previous knowledge on the possible values attainable from the tasks and, therefore, quickly resolve how to best optimize for the target.
+This fact is a clear contrast with GVT as the search is  more likely constrained to the mean values and moving away from that is, in fact, slower.
 
@@
 
-For the maze navigation task presented in Sec.
+For the maze navigation task in Sec.
 \ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
@@
 
-For the experiments we used as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the state of the MDP and an output layer that outputs the value of each action.
-For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$.
+For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the $22$-dimensional state of the MDP and an output layer that produces the value of each of the $3$ action.
+For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate $\alpha=0.001$ .
+
+In transfer experiments we use $\psi=0.5$, a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$ and use $10$ sampled \textit{weights} from the posterior to approximate the TD error.
+Moreover, we use $\lambda=10^{-6}$.
+For GVT, in particular, we use $\alpha_{\mu}=0.001$ as the rate to learn the mean parameters of our Gaussian posterior.
+For the Cholesky factor L, instead, we use $\alpha_{L}=10^{-7}$ and set the minimum value reachable by its eigenvalues to be $\sigma_{min}=0.0001$.
+In the case of MGVT experiments we set $\alpha_{\mu}=0.001$ to learn the mean of the different Gaussian components of our posterior and set $\alpha_{L}=10^{-6}$ for the Cholesky factors of its covariances.
+Finally, we use $\sigma_p^2=10^{-5}$ as the prior variance.
 
@@
     \includegraphics[width=\textwidth]{images/maze/maze0.pdf}
-    \caption{}
+    \caption{} \label{fig:maze0}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{images/maze/maze6.pdf}
-    \caption{}
+    \caption{}\label{fig:maze6}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{images/maze/maze8.pdf}
-    \caption{}
+    \caption{}\label{fig:maze8}
   \end{subfigure}
@@
     \includegraphics[width=\textwidth]{images/maze/maze13.pdf}
-    \caption{}
+    \caption{}\label{fig:maze13}
   \end{subfigure}
@@
 
+In Fig.
+\ref{}, we present the results of transferring from $5$ source tasks to the mazes shown in Fig.
+\ref{fig:maze0}, Fig.
+\ref{fig:maze6}, Fig.
+\ref{fig:maze8} and Fig.
+\ref{fig:maze13} using \todo{also GVT?} GVT and MGVT.
+We show both the evaluation reward, i.e.
+the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t.
+those parameters, and the expected return.
+All the curves result from averaging $20$ independent runs and randomly sampled sources.
+
+% Placer-holder to actual plots. Add analyses
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{Maze \ref{fig:maze0} (a) Expected Return (b) Evaluation Reward}
+\end{figure*}
+
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{Maze \ref{fig:maze6} (a) Expected Return (b) Evaluation Reward}
+\end{figure*}
+
+\begin{figure*}[t]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
+    \caption{}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
+    \caption{}
+  \end{subfigure}
+  \caption{Maze \ref{fig:maze13} (a) Expected Return (b) Evaluation Reward}
+  \label{fig:mazes-plots}
+\end{figure*}
+
 \end{document}

### 2018-05-16 NIPS 2018/main.tex

@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we restrict to the case of linear approximators with Gaussian prior and posterior.
-We assume Alg.
-\ref{alg:transfer} is used with a finite dataset and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
+To address this point, we consider Alg.
+\ref{alg:transfer} with mixture of Gaussians and linear approximators.
+We assume only a finite dataset is available and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
 Our main results is given in the following theorem.
 
-\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
+\begin{restatable}{theorem}{thmg} \label{th:main-mixture}
 Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
 Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the Gaussian version of Alg.
-\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
+Consider the mixture version of Alg.
+\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
 \ref{eq:elbo} on a dataset $D$ of $N$ samples.
@@
 Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
 \end{equation}
 \end{restatable}
+
 We refer the reader to App.
-\ref{} for the proof and a specific definition of the three constants.
-Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying very fast (as $\mathcal{O}(\frac{1}{N^2})$).
-Intuitively, our bound demonstrates that, if one starts very close the prior, the only error incurred, besides the irreducible approximation error, is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly.
-Furthermore, as $N\rightarrow\infty$ the only error term remaining is the irreducible approximation error.
+\ref{} for the proof and a specific definition of the constants.
+Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(N^2)$.
+Intuitively, the bound is tighten when the source tasks' $Q$-functions are, on average, close to the optimal ones for the target task.
+In such case, the dominating error is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly, as new data is collected.
+Furthermore, as $N\rightarrow\infty$ the only error term remaining is, as usual, the irreducible approximation error due to the limited functional space.
 Notice that the variance term $\upsilon(\bm{w}^*)$ is due to the fact that we minimize a biased estimator of the Bellman error.
-As mentioned in the preliminaries, if double sampling of the next state is possible (e.g., in simulation), such term would disappear.
+If double sampling of the next state were possible (e.g., in simulation), such term could be removed.
 Finally, we want to point out that the proof of this theorem relies on a very general result (Lemma \ref{lemma:general-bound} in App.
 \ref{}) that does not require any specific choice of distribution of approximator.
-Leveraging on such results, it is straightforward to provide a finite-sample analysis of the mixture version of our algorithm.
+Leveraging on such results, it is straightforward to provide a finite-sample analysis of the Gaussian version of our algorithm.
 For the sake of completeness, we report the derivation in App.
-\ref{}.
+\ref{}.\todo{Should we discuss the main difference between the MGVT and GVT bounds here?}
 
@@
 \norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+\end{align*}
+\end{proof}
+
+\thmg*
+\begin{proof}
+Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
+Then, we obtain:
+\begin{align}\label{eq:thmg-1}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align}
+The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+\begin{align}\label{eq:thmg-2}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
+\end{align}
+where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
+\ref{th:ukl}.
+Notice that, since we reduced the posterior to one component, the can get rid of the index $i$.
+Using the definitions of these two vectors from Sec.
+8 of \cite{hershey2007approximating}, we have:
+\begin{align*}
+\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+\begin{align}\label{eq:chi2}
+\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align}
+Since the KL divergence is:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
+\end{align*}
+Eq. \ref{eq:chi2} can be rewritten as:
+\begin{align*}
+\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
+\begin{align*}
+KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
+\end{align*}
+where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
+\begin{align*}
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
+\end{align*}
+Putting it all together:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
+\end{align*}
+Notice that, from now on, one can simply apply the proof of Thm.
+\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
+Thus, by changing the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log(\sigma^2_p + \log N)$\todo{$c_2$ actually contains $N$.
+Should we make this more explicit?}, $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, and setting $c_4 = \frac{2\lambda}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
 \end{align*}

### 2018-05-16 NIPS 2018/main.tex
Softmin is back!

--- 2018-05-16 NIPS 2018/main.tex
@@
 \newcommand{\mm}{\operatornamewithlimits{mm}}
+\newcommand{\softmin}{\operatornamewithlimits{softmin}}
 \newcommand{\wt}[1]{\widetilde{#1}}
@@
 
+\begin{restatable}{theorem}{thmgsoft} \label{th:main-mixture-soft}
+Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Consider the mixture version of Alg.
+\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+\begin{equation}
+\resizebox{0.93\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\end{equation}
+\end{restatable}
+\begin{proof}
+Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
+Then, we obtain:
+\begin{align}\label{eq:thmg-1}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align}
+The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+\begin{align}\label{eq:thmg-2}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
+\end{align}
+where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
+\ref{th:ukl}.
+Notice that, since we reduced the posterior to one component, we can get rid of the index $i$.
+Using the definitions of these two vectors from Sec.
+8 of \cite{hershey2007approximating}, we have:
+\begin{align*}
+\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+\begin{align}\label{eq:chi2}
+\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align}
+Since the KL divergence is:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
+\end{align*}
+Eq. \ref{eq:chi2} can be rewritten as:
+\begin{align*}
+\chi^{(2)}_j = \frac{e^{-\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
+\begin{align*}
+KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ \leq\ & \log\abs{\mathcal{W}_s}
+\end{align*}
+where the inequality holds since the first term is negative. For the second one:
+\begin{align*}
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace
+\end{align*}
+Putting the two terms together:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace
+\end{align*}
+Notice that, from now on, one can simply apply the proof of Thm.
+\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace$.
+Thus, by redefining the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma^2_p + \log N) + 2\lambda\log\abs{\mathcal{W}_s}$\todo{$c_2$ actually contains $N$.
+Should we make this more explicit?}, and $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, we can write that, with probability at least $1-2\delta$:
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+\end{align*}
+\end{proof}
+
 \section{Additional Details on the Algorithms}

### 2018-05-17 NIPS 2018/main.tex
Minor fixes in Thm. 5
Added abstract + conclusion

@@
 \newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
-\title{Variational Approximations for Transfer in Reinforcement Learning}
+\title{Transferring Value Functions by Variational Methods}
 
@@
 \begin{abstract}
-  The abstract paragraph should be indented \nicefrac{1}{2}~inch
-  (3~picas) on both the left- and right-hand margins. Use 10~point
-  type, with a vertical spacing (leading) of 11~points.  The word
-  \textbf{Abstract} must be centered, bold, and in point size 12. Two
-  line spaces precede the abstract. The abstract must be limited to
-  one paragraph.
+We consider the problem of transferring of value functions in reinforcement learning.
+We propose an approach that uses the given source tasks to learn a prior distribution over optimal value functions and provide an efficient variational approximation of the corresponding posterior in a new target task.
+We show our approach to be general, in the sense that it can be combined with complex parametric function approximators and distribution models, while providing two practical algorithms based on Gaussians and Gaussian mixtures.
+We theoretically analyze both by providing a finite-sample analysis and evaluate them empirically in four different domains.\todo{Say something more about the advantages of our method}
 \end{abstract}
@@
 
+In this work, we presented a variational method for transferring value functions in RL.
+We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators, and we provided two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
+We analyzed both from a theoretical and empirical perspective, proving that the Gaussian one has severe limitations, while the mixture version is much more suitable for our transfer settings.
+
+Since our algorithm effectively models the uncertainty over tasks, a relevant future work is to design an algorithm that explicitly explores the target task to reduce such uncertainty (e.g., \cite{houthooft2016vime}).
+Furthermore, our variation approach could be extended to model a distribution over optimal policies instead of value functions (e.g., \cite{liu2017stein}), which might allow better transferred behavior.
+
 {\small 
@@
 Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
@@
 \end{equation}
+where $\softmin_i x \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$.
 \end{restatable}

### 2018-05-17 NIPS 2018/main.tex
Minor changes to Section 3

@@
 
-Although the Gaussian assumption of the previous section is very appealing as it allows for a simple and efficient way of computing the variational objective and its gradients, we believe that such assumption almost never holds in practice.
-In fact, even for families of tasks in which the reward and transition models are Gaussian, the $Q$-values might be far from it.
+Although the Gaussian assumption of the previous section is very appealing as it allows for a simple and efficient way of computing the variational objective and its gradients, in practice it rarely allows us to describe the prior distribution accurately.
+In fact, even for families of tasks in which the reward and transition models are Gaussian, the $Q$-values might be far from being normally distributed.
 Depending on the family of tasks under consideration and, since we are learning a distribution over weights, on the chosen function approximator, the prior might have arbitrarily complex shapes.
-When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely too fail at capturing any similarities between the tasks.
-We now propose a variant to successfully solve this problem, while keeping the algorithm simple and efficient enough to be applied in practice.
+When the information loss due to the Gaussian approximation becomes too severe, the algorithm is likely to fail at capturing any similarities between the tasks.
+We now propose a variant to successfully solve this problem, while keeping the algorithm efficient and simple enough to be applied in practice.
 
 Given the source tasks' weights $\mathcal{W}_s$, we model our estimated prior as a mixture of Gaussians with one equally weighted isotropic Gaussian centered at each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$.
-This resembles a kernel density estimator \cite{scott2015multivariate} and, due to its nonparametric nature, it allows capturing arbitrarily complex distribution.
+This model resembles a kernel density estimator \cite{scott2015multivariate} and, due to its nonparametric nature, it allows capturing arbitrarily complex distributions.
 Consistently with the prior, we model our approximate posterior as a mixture of Gaussians.
-However, we allow a different number of components (typically much less than the prior's) and we adopt full covariances instead of only diagonals, so that our posterior has the potential to match complex distributions with less components.
+However, we allow a different number of components \todo{questo dettaglio si potrebbe spostare nella parte sperimentale o togliere del tutto} (typically much less than the prior's), and we adopt full covariances instead of only diagonals so that our posterior has the potential to match complex distributions with fewer components.
 Using $C$ components, our posterior is $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$, with variational parameters $\bm{\xi} = (\bm{\mu}_1,\dots,\bm{\mu}_C,\bm{\Sigma}_1,\dots,\bm{\Sigma}_C)$.
@@
 
-Although this new model has the potential to capture much more complex distributions, it poses a major complication: the KL divergence between two mixture of Gaussians has no closed-form expression.
-To solve this issue, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and true posterior.
+Although this new model has the potential to capture much more complicated distributions, it poses a significant complication: the KL divergence between two mixtures of Gaussians has no closed-form expression.
+To solve this issue, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and the exact posterior.
 Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report here for the sake of completeness.
@@
 Each time we require its value, we have to recompute the parameters $\chi^{(1)}$ and $\chi^{(2)}$ that tighten the bound.
-As shown in \cite{hershey2007approximating}, this can be achieved by a simple fixed-point procedure.
-Finally, both terms in the objective are now linear combinations of functions of the variational parameters of different components, and their gradients are easily derived from the ones of the Gaussian case.
+As shown in \cite{hershey2007approximating}, we can use a simple fixed-point procedure for this purpose.
+Finally, both terms in the objective are now linear combinations of functions of the variational parameters of different components, and their gradients easily derive from the ones of the Gaussian case.
 We report the derivation in App.
@@
 Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
-This rarely represents a problem since typical value-based algorithms are actually semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}).
-However, our transfer settings are rather different than common RL.
-In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum, and the only thing that needs to be done is to adapt the weights in a direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the task that is being solved.
-Unfortunately, this property cannot be guaranteed for most semi-gradient algorithms.
+This issue rarely is a problem since typical value-based algorithms are semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}).
+However, our transfer settings are quite different from common RL.
+In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum and aims only to adapt the weights in some direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the target task.
+Unfortunately, this property does not hold for most semi-gradient algorithms.
 Even worse, many online RL algorithms combined with complex function approximators (e.g., DQNs) are well-known to be unstable, especially when approaching an optimum, and require many tricks and tuning to work well \cite{schaul2015prioritized,van2016deep}.
-This is obviously an undesirable property in our case, as we only aim at adapting already good solutions.
+This property is clearly undesirable in our case, as we only aim at adapting already good solutions.
 Thus, we consider using a residual gradient algorithm \cite{baird1995residual}.
-In order to differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{asadi2017alternative}, which adopts a softened version of max called \textit{mellowmax}:
+To differentiate the targets, we replace the optimal Bellman operator with the mellow Bellman operator introduced in \cite{asadi2017alternative}, which adopts a softened version of max called \textit{mellowmax}:
 \begin{equation}
@@
 Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
-the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable with respect to $\bm{w}$.
+the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable w.r.t.
+$\bm{w}$.
 Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart.
 \cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence.
-This can be easily done by including a parameter $\psi\in[0,1]$ in the TD error gradient such that:
+This projection is obtained by including a parameter $\psi\in[0,1]$ in the TD error gradient:
 \begin{equation}
-\nabla_{\bm{w}}\norm{\wt{B}(\bm{w})}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right)
+\nabla_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right),
 \end{equation}
@@
 Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$).
-A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee converge).
+A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee convergence).
 

### 2018-05-17 NIPS 2018/main.tex
Minor fixes to Section 4

@@
 However, how such fixed-point differs from the one of the optimal Bellman operator remains an open question.
-Since mellow-max monotonically converges to max as $\kappa \rightarrow \infty$, it would be desirable if the corresponding operator also monotonically converged to the optimal one.
+Since mellow-max monotonically converges to max as $\kappa \rightarrow \infty$, it would be desirable if the fixed point of the corresponding operator also monotonically converged to the fixed point of the optimal one.
 We confirm that this property actually holds in the following theorem.
@@
 \begin{equation}
-\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p
+\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p.
 \end{equation}
@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we consider Alg.
-\ref{alg:transfer} with mixture of Gaussians and linear approximators.
+To address this point, we consider Algorithm~\ref{alg:transfer} with a mixture of Gaussians and linear approximators.
 We assume only a finite dataset is available and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
-Our main results is given in the following theorem.
+Our main result is given in the following theorem.
 
 \begin{restatable}{theorem}{thmg} \label{th:main-mixture}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the mixture version of Alg.
-\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
-Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with uniformly bounded weights $|\bm{w}|\leq w_{max}$ and uniformly bounded features $|\bm{\phi}(s,a)|\leq \phi_{\max}$.
+Consider the mixture version of Algorithm~\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Equation \eqref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$.
 Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+Then, there exist constants $c_1$, $c_2$, $c_3$, $c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}.
 \end{equation}

### 2018-05-17 NIPS 2018/main.tex
Minor changes to Section 5

@@
 
-We consider an agent navigating in the rooms environment depicted in Fig.
-\ref{}.
+We consider an agent navigating in the environment depicted in Figure~\ref{f:rooms}.
 The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
-The rooms are connected by small doors whose positions are unknown to the agent.
+The rooms are connected by small doors whose locations are unknown to the agent.
 The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
-After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise with $0.2$ standard deviation.
+After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise $\mathcal{N}(0,0.2)$.
 In case the agent hits a wall, its position remains unchanged.
@@
 
-Since the agent does not know where the doors are located in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
-While this might be a complicated problem for plain RL, our transfer algorithm should be able to quickly figure out the door positions.
+Since the agent does not know the locations of the doors in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
+While this might be a complicated problem for plain RL, our transfer algorithm should be able to figure out the door positions quickly.
 In fact, notice that, although different, the optimal $Q$-functions for all tasks share some similarities.
 For example, once the agent has passed the last door before the goal, the $Q$-values are exactly the same in all tasks.
-This does not hold for positions nearby the start state.
-However, it is clear that there should be a preference over actions up and right, rather than down and left (which are worse in all tasks).\todo{Good candidate to be removed}
+The same does not hold for positions nearby the starting state.
+However, it is clear that there should be a preference over actions \textit{up} and \textit{right}, rather than \textit{down} and \textit{left} (which are worse in all tasks).\todo{Good candidate to be removed}
 
@@
 \end{tikzpicture} 
-    \caption{}
+    \caption{}\label{f:rooms}
   \end{subfigure}
@@
     \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
-    \caption{}
+    \caption{}\label{f:two_doors}
   \end{subfigure}
@@
     \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
-    \caption{}
+    \caption{}\label{f:one_door}
   \end{subfigure}
@@
     \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
-    \caption{}
+    \caption{}\label{f:likelihood}
   \end{subfigure}
@@
 
-In order to prove that our guesses are correct, we generate a set of $50$ source tasks for the three-room environment of Fig.
-\ref{} by sampling both door positions uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Sec.
-\ref{sec:td}.
+To prove that our guesses are correct, we generate a set of $50$ source tasks for the three-room environment of Figure~\ref{f:rooms} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
-The average return over the last $50$ learning episodes as a function of the number of iterations is shown in Fig.
-\ref{}.
-Each curve is the result of $20$ independent runs, each resampling the target and source tasks, with $95\%$ confidence intervals.
+The average return over the last $50$ learning episodes as a function of the number of iterations is shown in Figure~\ref{f:two_doors}.
+Each curve is the result of $20$ independent runs, each one resampling the target and source tasks, with $95\%$ confidence intervals.
 Further details on the parameters adopted in this experiment are given in App.
@@
 As expected, the no-transfer (NT) algorithm fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
-On the other hand, all our algorithms achieve a significant speed-up and are able to converge to the optimal performance in few iterations, with GVT being slightly slower.
+On the other hand, all our algorithms achieve a significant speed-up and converge to the optimal performance in few iterations, with GVT being slightly slower.
 Interestingly, we notice that there is no advantage in adopting more than $1$ component for the posterior in MGVT.
-This is intuitive since, when the algorithm quickly figures out which task is being solved, it will move all components in the same direction.
+This result is intuitive since, as soon as the algorithm figures out which is the target task, all the components move towards the same region.
 
 To better understand the differences between GVT and MGVT, we now consider transferring from a slightly different distribution than the one from which target tasks are drawn.
-We generate again $50$ source tasks but this time with the bottom door fixed at the center and the other one moving.
+We generate $50$ source tasks again but this time with the bottom door fixed at the center and the other one moving.
 Then, we repeat the previous experiment, allowing both doors to move when sampling target tasks.
-The results are shown in Fig.
-\ref{}.
-Interestingly, MGVT seems almost unaffected by this change, proving that is has sufficient representation power to generalize to slightly different task distributions.
+The results are shown in Figure~\ref{f:one_door}.
+Interestingly, MGVT seems almost unaffected by this change, proving that it has sufficient representation power to generalize to slightly different task distributions.
 The same does not hold for GVT, which now is not able to solve many of the sampled target tasks, as can be noticed from the higher variance.
-This proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
+This result proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
 
 Finally, we analyze the transfer performance as a function of how likely the target task is according to the prior.
-We consider a two-room version of the environment of Fig.
-\ref{}.
-Differently from before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks where the door is near the sides are very unlikely.
-Fig.
-\ref{} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
-As expected GVT achieves poor performance on very unlikely tasks, even after many iterations.
+We consider a two-room version of the environment of Figure~\ref{f:rooms}.
+Unlike before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks with the door near the sides are very unlikely.
+Figure~\ref{f:likelihood} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
+As expected, GVT achieves poor performance on very unlikely tasks, even after many iterations.
 In fact, estimating a single Gaussian distribution definitely entails some information loss, especially about the unlikely tasks.
@@
 In this experiment, we use a Double Deep Q-Network \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
-The results (same settings of Sec.
-\ref{sec:gw}) are shown in Fig.
-\ref{} and \ref{}.
-For Cartpole (Fig.
-\ref{}), all transfer algorithms are almost zero-shot.
-This is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are almost the same for all tasks.
-On the contrary, in Mountain Car (Fig.
-\ref{}) the optimal $Q$-functions become really different when changing the car speed.
-This causes GVT to struggle to solve the target task, while 1-MGVT achieves a good jump-start and convergences in less iterations.
+The results (same settings of Section~\ref{sec:gw}) are shown in Figures~\ref{f:cartpole} and~\ref{f:mountaincar}.
+For Cartpole (Figure~\ref{f:cartpole}), all transfer algorithms are almost zero-shot.
+This result is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are almost the same for all tasks.
+On the contrary, in Mountain Car (Figure~\ref{f:mountaincar}) the optimal $Q$-functions become very different when changing the car speed.
+This phenomenon hinders the learning of GVT in the target task, while 1-MGVT achieves a good jump-start and converges in fewer iterations.
 
@@
     \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=2.6cm, width=2.0cm]{images/maze/maze6.png}
-    \caption{}
+    \caption{}\label{f:maze}
   \end{subfigure}
@@
     \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
-    \caption{}
+    \caption{}\label{f:cartpole}
   \end{subfigure}
@@
     \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
-    \caption{}
+    \caption{}\label{f:mountaincar}
   \end{subfigure}
@@
     \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev.pdf}
-    \caption{}
+    \caption{}\label{f:maze_results}
   \end{subfigure}

### 2018-05-17 NIPS 2018/main.tex
Corrected appendix

--- 2018-05-17 NIPS 2018/main.tex
@@
 
+\subsection{Proof of Theorem 2}
+
 \thmm*
@@
 Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$.
-Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}.
+Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}.
 Thus, we can write:
@@
 \begin{align*}
-\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}
+\pi_{\beta_{\kappa}}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}
 \end{align*}
@@
 
-\begin{lemma}
-Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
+\subsection{Proof of Theorem 3}
+
+We begin by proving some important lemmas.
+Then, we use them to derive a finite-sample analysis of Alg.
+\ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Thm.
+\ref{th:main-gaussian}) and Gaussian mixture models (Thm.
+\ref{th:main-mixture}).
+
+\begin{lemma}\label{lemma:l1}
+Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively.
 Assume $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$.
-Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
+Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
 \begin{equation}
-\norm{Q - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
 \end{equation}
@@
 \begin{align*}
-\norm{Q - Q^*} =\ & \norm{Q + TQ - TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \norm{TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \gamma\norm{Q - Q^*}\\ =\ & \norm{B(Q)} + \gamma\norm{Q - Q^*}
+\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 =\ & \norm{Q_{\bm{w}} + TQ_{\bm{w}} - TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \norm{TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2\\ =\ & \norm{B_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2
 \end{align*}
@@
 \begin{align*}
-\norm{Q - Q^*} \leq\ \frac{1}{1-\gamma}\norm{B(Q)}
+\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq\ \frac{1}{1-\gamma}\norm{B_{\bm{w}}}_{\nu}^2
 \end{align*}
@@
 \begin{align*}
-P\left( \norm{Q - Q^*} > \epsilon \right) \leq P\left(\norm{B(Q)} > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
+P\left( \norm{Q_{\bm{w}} - Q^*}_{\nu}^2 > \epsilon \right) \leq P\left(\norm{B_{\bm{w}}}_{\nu}^2 > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
 \end{align*}
@@
 
+Lemma \ref{lemma:l1} can be straightforwardly extended to the case where the mellow Bellman operator is used instead of the optimal one. This is given in the following corollary.
+
 \begin{corollary}\label{cor:diff-q}
-Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
+Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively.
 Assume $\wt{Q}$ is the unique fixed-point of the mellow Bellman operator $\wt{T}$.
-Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
+Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
 \begin{equation}
-\norm{Q - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
 \end{equation}
@@
 
+We now prove some important properties of the variational approximation introduced in Sec.
+\ref{sec:alg}.
+Our results generalize those of existing works that consider variational approximations of intractable Gibbs posteriors \cite{alquier2016properties,cottet20181}.
+From now on, we consider only $Q$-functions parameterized by weights $\bm{w}$ and assume them to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
+
 \begin{lemma}\label{lemma:l2}
-Assume $Q$-functions belong to a parametric space of functions bounded by $\frac{R_{max}}{1-\gamma}$.
-Let $p$ and $q$ be arbitrary distributions over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
-Consider a dataset $D$ of $N$ samples and define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Let $p$ and $q$ be arbitrary distributions over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
+Consider a dataset $D$ of $N$ i.i.d.
+samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
 \begin{equation}\label{eq:lemma2-1}
-\mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_q\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
 \begin{equation}\label{eq:lemma2-2}
-\mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_q\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
@@
 \end{align}
-From the change of measure inequality \cite{}\todo{Find a reference for this}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
+From the change of measure inequality \cite{seldin2012pac}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
 \begin{align*}
@@
 \end{proof}
+
+From Lemma \ref{lemma:l2} we can straightforwardly prove the following result which will be of fundamental importance in the remaining.
 
@@
 Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, for any $\delta > 0$, with probability at least $1-\delta$:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 
+It is worth noting the generality of Lemma \ref{lemma:general-bound}: in bounding the expected Bellman error we did not need to assume any particular distribution, nor did we have to assume any particular function approximator.
+
+We are now ready to state our main result. We start from the Gaussian case and then straightforwardly extend the proof to the mixture one.
+
 \begin{restatable}{theorem}{thg} \label{th:main-gaussian}
 Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
 Consider the Gaussian version of Alg.
 \ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+\ref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
+samples distributed according to $\tau$ and $\nu$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}
 \end{equation}
@@
 \begin{align}\label{eq:thg-4}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align}
@@
 \begin{align}\label{eq:thg-3}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w})}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
 \end{align}
@@
 \begin{align*}
-\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right] =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}}\\ =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')} + \frac{1}{2}\kappa c\bm{\phi}_{max}\\ =\ & \mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa c\bm{\phi}_{max}
+\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right] =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}^2}\\ =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')} + \frac{1}{2}\kappa c\bm{\phi}_{max}^2\\ =\ & \mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa c\bm{\phi}_{max}^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max} - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}(\bm{w}^{*}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2 - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}(\bm{w}^{*}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2
+\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2
+\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \upsilon(\bm{w}^*)\sqrt{c}\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
-\end{align*}
-where $\upsilon(\bm{w}^*) = \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$. Since the bound holds for any $c>0$, we can set it to $1/N$, thus obtaining:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K \log(\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + \frac{1}{\sqrt{N}}\left(\upsilon(\bm{w}^*) + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\log\frac{2}{\delta}}\right)
-\end{align*}
-Finally, defining the constants $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda K}{\sigma_{min}}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K \log(\sigma_{max} + \log N)$\todo{$c_2$ actually contains $N$.
-Should we make this more explicit?}, and $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, we obtain:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+Since the bound holds for any $c>0$, we can set it to $1/N$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+Finally, defining the constants $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K (\log\sigma_{max} + \log N)$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda K}{\sigma_{min}}$, we obtain:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)
 \end{align*}
@@
 
-\thmg*
-\begin{proof}
-Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
+%\thmg*
+%\begin{proof}
+%Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
 Then, we obtain:
-\begin{align}\label{eq:thmg-1}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
-\end{align}
-The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
-\begin{align}\label{eq:thmg-2}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
-\end{align}
-where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
+%\begin{align}\label{eq:thmg-1}
+%\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+%\end{align}
+%The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+%\begin{align}\label{eq:thmg-2}
+%KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
+%\end{align}
+%where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
 \ref{th:ukl}.
@@
 8 of \cite{hershey2007approximating}, we have:
-\begin{align*}
-\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-\end{align*}
-\begin{align}\label{eq:chi2}
-\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-\end{align}
-Since the KL divergence is:
-\begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
-\end{align*}
-Eq. \ref{eq:chi2} can be rewritten as:
-\begin{align*}
-\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-\end{align*}
-Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
-\begin{align*}
-KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
-\end{align*}
-where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
-\begin{align*}
-\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
-\end{align*}
-Putting it all together:
-\begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
-\end{align*}
-Notice that, from now on, one can simply apply the proof of Thm.
+%\begin{align*}
+%\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+%\end{align*}
+%\begin{align}\label{eq:chi2}
+%\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+%\end{align}
+%Since the KL divergence is:
+%\begin{align*}
+%KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
+%\end{align*}
+%Eq. \ref{eq:chi2} can be rewritten as:
+%\begin{align*}
+%\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+%\end{align*}
+%Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
+%\begin{align*}
+%KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
+%\end{align*}
+%where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
+%\begin{align*}
+%\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
+%\end{align*}
+%Putting it all together:
+%\begin{align*}
+%KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
+%\end{align*}
+%Notice that, from now on, one can simply apply the proof of Thm.
 \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
@@
 Should we make this more explicit?}, $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, and setting $c_4 = \frac{2\lambda}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
-\end{align*}
-\end{proof}
+%\begin{align*}
+%\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+%\end{align*}
+%\end{proof}
 
@@
 Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
 Consider the mixture version of Alg.
@@
 Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+\ref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
+samples distributed according to $\tau$ and $\nu$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
 \end{equation}
@@
 \begin{align}\label{eq:thmg-1}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align}
@@
 \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace$.
-Thus, by redefining the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma^2_p + \log N) + 2\lambda\log\abs{\mathcal{W}_s}$\todo{$c_2$ actually contains $N$.
-Should we make this more explicit?}, and $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, we can write that, with probability at least $1-2\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma^2_p + \log N) + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
+\begin{align*}
+\resizebox{0.93\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
 \end{align*}

### 2018-05-17 NIPS 2018/main.tex
Fixes in appendix

@@
 \begin{align} \label{eq:elbo}
-\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
+\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
 \end{align}
@@
 From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t.
-$\bm{\xi}$ requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t.
+$\bm{\xi}$ requires differentiating $\norm{B_{\bm{w}}}_D^2$ w.r.t.
 $\bm{w}$.
@@
 The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
-Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
-the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable w.r.t.
+Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
+the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}_{\bm{w}}}_D^2$, is now differentiable w.r.t.
 $\bm{w}$.
@@
 \ref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
 \end{equation}
@@
 Consider a dataset $D$ of $N$ i.i.d.
-samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
 \begin{equation}\label{eq:lemma2-1}
-\mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B_{\bm{w}}}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
 \begin{equation}\label{eq:lemma2-2}
-\mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{B_{\bm{w}}}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
@@
 \begin{align*}
-P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] - \norm{B(\bm{w})}_D^2} > \epsilon \right) \leq 2exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
+P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] - \norm{B_{\bm{w}}}_D^2} > \epsilon \right) \leq 2exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
 \end{align*}
@@
 \begin{align*}
-\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] - \norm{B(\bm{w})}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] - \norm{B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[b(\bm{w})^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right] + \mathbb{E}_{\mathcal{P}}\left[b(\bm{w})\right]^2\right]\\ =\ & v(\bm{w}) + \norm{B(\bm{w})}_{\nu}^2
-\end{align*}
-where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$. Thus:
+\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{B_{\bm{w}}}_{\nu}^2
+\end{align*}
+where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$. Thus:
 \begin{align}\label{eq:hoeff}
-\abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align}
@@
 \end{align*}
-Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2}$, we obtain:
+Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2}$, we obtain:
 \begin{align*}
@@
 \begin{align*}
-\mathbb{E}_q\left[ \abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
-Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
-Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
+Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
 \begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 We can now use Eq.
-\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right]$, thus obtaining:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right]$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}
 \end{equation}
@@
 \begin{align}\label{eq:thg-4}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align}
@@
 \begin{align}\label{eq:thg-3}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w})}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}}}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
 \end{align}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2 - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}(\bm{w}^{*}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2 - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}_{\bm{w}^{*}} + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
+\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ]}{(1-\gamma)\delta}
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)
 \end{align*}
@@
 %\begin{align}\label{eq:thmg-1}
-%\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+%\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
 %\end{align}
@@
 %\begin{align*}
-%\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+%\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
 %\end{align*}
@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
 \end{equation}
@@
 \begin{align}\label{eq:thmg-1}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align}
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
 \end{align*}
@@
 \begin{equation}\label{eq:tdgradmu}
-\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B_{\bm{w}}||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B_{\bm{w}}||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
 \end{equation} 
 \begin{equation}\label{eq:tdgradL}
-\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B_{\bm{w}}||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B_{\bm{w}}||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
 \end{equation}
@@
 \begin{align}
-\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\&+ \frac{\lambda}{N} KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] \nonumber \\&+ \frac{\lambda}{N} KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
 \end{align}
@@
 \begin{align}
-\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\ &+\ \frac{\lambda}{N}KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B_{\bm{w}}}_D^2\right] \nonumber \\ &+\ \frac{\lambda}{N}KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
 \end{align}

### 2018-05-17 NIPS 2018/main.tex
Updated proofs

@@
 %
-%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
+%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^d$ given data $D$,
 %\begin{equation}\label{eq:bayes}
@@
 That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
-Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$.
+Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^d, \bm{\Sigma}\in\mathbb{R}^{d\times d}, \bm{\Sigma}\succ 0 \right\}$.
 To prevent the covariance from becoming not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $\bm{L}$ instead.
@@
 \begin{align*}
-KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^K} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -K \right)\\ \leq\ & \frac{1}{2}K\log\frac{\sigma_{max}}{c} + \frac{1}{2}K\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}
+KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^d} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -d \right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma_{max}}{c} + \frac{1}{2}d\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}d\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}d\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
-\end{align*}
-Finally, defining the constants $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K (\log\sigma_{max} + \log N)$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda K}{\sigma_{min}}$, we obtain:
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align*}
+Finally, defining the constants $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N)$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}$, we obtain:
 \begin{align*}
@@
 \begin{equation}
-KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
+KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -d \right)
 \end{equation}

### 2018-05-17 NIPS 2018/main.tex

@@
 \begin{abstract}
-We consider the problem of transferring of value functions in reinforcement learning.
+We consider the problem of transferring value functions in reinforcement learning.
 We propose an approach that uses the given source tasks to learn a prior distribution over optimal value functions and provide an efficient variational approximation of the corresponding posterior in a new target task.
@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we consider Alg.
-\ref{alg:transfer} with mixture of Gaussians and linear approximators.
+To address this point, we consider Algorithm~\ref{alg:transfer} with a mixture of Gaussians and linear approximators.
 We assume only a finite dataset is available and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
-Our main results is given in the following theorem.
+Our main result is given in the following theorem.
 
 \begin{restatable}{theorem}{thmg} \label{th:main-mixture}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
-Consider the mixture version of Alg.
-\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
-Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with uniformly bounded weights $|\bm{w}|\leq w_{max}$ and uniformly bounded features $|\bm{\phi}(s,a)|\leq \phi_{\max}$.
+Consider the mixture version of Algorithm~\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Equation \eqref{eq:elbo} on a dataset $D$ of $N$ samples.
 Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3,c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, there exist constants $c_1$, $c_2$, $c_3$, $c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}.
 \end{equation}

### 2018-05-17 NIPS 2018/main.tex
Minor changes to Related Works

@@
 \begin{abstract}
-We consider the problem of transferring value functions in reinforcement learning.
+We consider the problem of transferring of value functions in reinforcement learning.
 We propose an approach that uses the given source tasks to learn a prior distribution over optimal value functions and provide an efficient variational approximation of the corresponding posterior in a new target task.
@@
 %
-%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^d$ given data $D$,
+%When working with Bayesian approaches, the posterior distribution of hidden variables $\bm{w} \in \mathbb{R}^K$ given data $D$,
 %\begin{equation}\label{eq:bayes}
@@
 \begin{align} \label{eq:elbo}
-\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
+\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
 \end{align}
@@
 That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using maximum likelihood estimation (with small regularization to make sure the covariance is positive definite).
-Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^d, \bm{\Sigma}\in\mathbb{R}^{d\times d}, \bm{\Sigma}\succ 0 \right\}$.
+Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$.
 To prevent the covariance from becoming not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $\bm{L}$ instead.
@@
 From Sections \ref{sec:gvt} and \ref{sec:mgvt}, we know that differentiating the negative ELBO $\mathcal{L}$ w.r.t.
-$\bm{\xi}$ requires differentiating $\norm{B_{\bm{w}}}_D^2$ w.r.t.
+$\bm{\xi}$ requires differentiating $\norm{B(\bm{w})}_D^2$ w.r.t.
 $\bm{w}$.
@@
 The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
-Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
-the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}_{\bm{w}}}_D^2$, is now differentiable w.r.t.
+Denoting by $\wt{B}(\bm{w}) = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
+the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}(\bm{w})}_D^2$, is now differentiable w.r.t.
 $\bm{w}$.
@@
 On the other hand, our variational approximation allows for more general distribution families and can be combined with non-linear approximators.
-Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves again the importance of capturing more complicated task distributions.
-In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over tasks.
-Differently from our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
+Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves the importance of capturing more complicated task distributions again.
+In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over MDPs.
+unlike our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
 In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it.
@@
 In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
-Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, so as to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
+Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
 Should we discuss more related works?}
@@
 \section{Proofs}
-
-\subsection{Proof of Theorem 2}
 
@@
 Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$.
-Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}.
+Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}.
 Thus, we can write:
@@
 \begin{align*}
-\pi_{\beta_{\kappa}}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}
+\pi_{\beta}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}
 \end{align*}
@@
 
-\subsection{Proof of Theorem 3}
-
-We begin by proving some important lemmas.
-Then, we use them to derive a finite-sample analysis of Alg.
-\ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Thm.
-\ref{th:main-gaussian}) and Gaussian mixture models (Thm.
-\ref{th:main-mixture}).
-
-\begin{lemma}\label{lemma:l1}
-Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively.
+\begin{lemma}
+Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
 Assume $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$.
-Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
+Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
 \begin{equation}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\norm{Q - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
 \end{equation}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 =\ & \norm{Q_{\bm{w}} + TQ_{\bm{w}} - TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \norm{TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2\\ =\ & \norm{B_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2
+\norm{Q - Q^*} =\ & \norm{Q + TQ - TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \norm{TQ - TQ^*}\\ \leq\ & \norm{Q - TQ} + \gamma\norm{Q - Q^*}\\ =\ & \norm{B(Q)} + \gamma\norm{Q - Q^*}
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq\ \frac{1}{1-\gamma}\norm{B_{\bm{w}}}_{\nu}^2
+\norm{Q - Q^*} \leq\ \frac{1}{1-\gamma}\norm{B(Q)}
 \end{align*}
@@
 \begin{align*}
-P\left( \norm{Q_{\bm{w}} - Q^*}_{\nu}^2 > \epsilon \right) \leq P\left(\norm{B_{\bm{w}}}_{\nu}^2 > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
+P\left( \norm{Q - Q^*} > \epsilon \right) \leq P\left(\norm{B(Q)} > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B(Q)}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
 \end{align*}
@@
 
-Lemma \ref{lemma:l1} can be straightforwardly extended to the case where the mellow Bellman operator is used instead of the optimal one. This is given in the following corollary.
-
 \begin{corollary}\label{cor:diff-q}
-Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively.
+Let $p$ and $\nu$ denote probability measures over $Q$-functions and state-action pairs, respectively.
 Assume $\wt{Q}$ is the unique fixed-point of the mellow Bellman operator $\wt{T}$.
-Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
+Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of a $Q$-function $Q$, the following holds:
 \begin{equation}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\norm{Q - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}(Q)}_{\nu}^2 \right]}{(1-\gamma)\delta}
 \end{equation}
@@
 
-We now prove some important properties of the variational approximation introduced in Sec.
-\ref{sec:alg}.
-Our results generalize those of existing works that consider variational approximations of intractable Gibbs posteriors \cite{alquier2016properties,cottet20181}.
-From now on, we consider only $Q$-functions parameterized by weights $\bm{w}$ and assume them to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
-
 \begin{lemma}\label{lemma:l2}
-Let $p$ and $q$ be arbitrary distributions over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
-Consider a dataset $D$ of $N$ i.i.d.
-samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+Assume $Q$-functions belong to a parametric space of functions bounded by $\frac{R_{max}}{1-\gamma}$.
+Let $p$ and $q$ be arbitrary distributions over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
+Consider a dataset $D$ of $N$ samples and define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
 \begin{equation}\label{eq:lemma2-1}
-\mathbb{E}_q\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B_{\bm{w}}}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_q\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
 \begin{equation}\label{eq:lemma2-2}
-\mathbb{E}_q\left[ \norm{B_{\bm{w}}}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{B(\bm{w})}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_q\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
@@
 \begin{align*}
-P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] - \norm{B_{\bm{w}}}_D^2} > \epsilon \right) \leq 2exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
+P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] - \norm{B(\bm{w})}_D^2} > \epsilon \right) \leq 2exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
 \end{align*}
@@
 \begin{align*}
-\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] - \norm{B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] - \norm{B(\bm{w})}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{B_{\bm{w}}}_{\nu}^2
-\end{align*}
-where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$. Thus:
+\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B(\bm{w})}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[b(\bm{w})^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right] + \mathbb{E}_{\mathcal{P}}\left[b(\bm{w})\right]^2\right]\\ =\ & v(\bm{w}) + \norm{B(\bm{w})}_{\nu}^2
+\end{align*}
+where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$. Thus:
 \begin{align}\label{eq:hoeff}
-\abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
-\end{align}
-From the change of measure inequality \cite{seldin2012pac}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
+\abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\end{align}
+From the change of measure inequality \cite{}\todo{Find a reference for this}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
 \begin{align*}
@@
 \end{align*}
-Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2}$, we obtain:
+Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2}$, we obtain:
 \begin{align*}
@@
 \begin{align*}
-\mathbb{E}_q\left[ \abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \abs{\norm{B(\bm{w})}_{\nu}^2 + v(\bm{w}) - \norm{B(\bm{w})}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 
-From Lemma \ref{lemma:l2} we can straightforwardly prove the following result which will be of fundamental importance in the remaining.
-
 \begin{lemma}\label{lemma:general-bound}
 Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
-Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
-Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
-Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
-\begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
+Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
+Then, for any $\delta > 0$, with probability at least $1-\delta$:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 We can now use Eq.
-\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right]$, thus obtaining:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_D^2 \right]$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
 \end{align*}
@@
 
-It is worth noting the generality of Lemma \ref{lemma:general-bound}: in bounding the expected Bellman error we did not need to assume any particular distribution, nor did we have to assume any particular function approximator.
-
-We are now ready to state our main result. We start from the Gaussian case and then straightforwardly extend the proof to the mixture one.
-
 \begin{restatable}{theorem}{thg} \label{th:main-gaussian}
 Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
 Consider the Gaussian version of Alg.
 \ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
-samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_1}{N^2}\right)$}
 \end{equation}
@@
 \begin{align}\label{eq:thg-4}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
 \end{align}
@@
 \begin{align}\label{eq:thg-3}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}}}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
 \end{align}
@@
 \begin{align*}
-\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right] =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}^2}\\ =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')} + \frac{1}{2}\kappa c\bm{\phi}_{max}^2\\ =\ & \mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa c\bm{\phi}_{max}^2
+\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right] =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}}\\ =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')} + \frac{1}{2}\kappa c\bm{\phi}_{max}\\ =\ & \mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa c\bm{\phi}_{max}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2 - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}_{\bm{w}^{*}} + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max} - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}(\bm{w}^{*}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
+\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
+\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}(\bm{w}^*)}_{\nu}^2\right] \leq 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
 \end{align*}
@@
 \begin{align*}
-KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^d} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -d \right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma_{max}}{c} + \frac{1}{2}d\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}
+KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^K} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -K \right)\\ \leq\ & \frac{1}{2}K\log\frac{\sigma_{max}}{c} + \frac{1}{2}K\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}d\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}d\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
-\end{align*}
-Since the bound holds for any $c>0$, we can set it to $1/N$, thus obtaining:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
-\end{align*}
-Finally, defining the constants $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N)$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}$, we obtain:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \upsilon(\bm{w}^*)\sqrt{c}\\ &\ + \frac{\lambda}{N}K\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}K\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align*}
+where $\upsilon(\bm{w}^*) = \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$. Since the bound holds for any $c>0$, we can set it to $1/N$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda K}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K \log(\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + \frac{1}{\sqrt{N}}\left(\upsilon(\bm{w}^*) + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\log\frac{2}{\delta}}\right)
+\end{align*}
+Finally, defining the constants $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda K}{\sigma_{min}}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda K \log(\sigma_{max} + \log N)$\todo{$c_2$ actually contains $N$.
+Should we make this more explicit?}, and $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, we obtain:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ]}{(1-\gamma)\delta}
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
 \end{align*}
@@
 
-%\thmg*
-%\begin{proof}
-%Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
+\thmg*
+\begin{proof}
+Similarly to the previous proof, we can apply Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$, while choosing the same specific parameters for the right-hand side: $\bm{\mu}_i = \bm{w}^*$ and $\bm{\Sigma}_i = c\bm{I}$ for all $i=1,\dots,C$.
 Then, we obtain:
-%\begin{align}\label{eq:thmg-1}
-%\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
-%\end{align}
-%The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
-%\begin{align}\label{eq:thmg-2}
-%KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
-%\end{align}
-%where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
+\begin{align}\label{eq:thmg-1}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
+\end{align}
+The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+\begin{align}\label{eq:thmg-2}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
+\end{align}
+where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
 \ref{th:ukl}.
@@
 8 of \cite{hershey2007approximating}, we have:
-%\begin{align*}
-%\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-%\end{align*}
-%\begin{align}\label{eq:chi2}
-%\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-%\end{align}
-%Since the KL divergence is:
-%\begin{align*}
-%KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
-%\end{align*}
-%Eq. \ref{eq:chi2} can be rewritten as:
-%\begin{align*}
-%\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
-%\end{align*}
-%Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
-%\begin{align*}
-%KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
-%\end{align*}
-%where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
-%\begin{align*}
-%\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
-%\end{align*}
-%Putting it all together:
-%\begin{align*}
-%KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
-%\end{align*}
-%Notice that, from now on, one can simply apply the proof of Thm.
+\begin{align*}
+\chi^{(1)}_j = \frac{1}{\abs{\mathcal{W}_s}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+\begin{align}\label{eq:chi2}
+\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align}
+Since the KL divergence is:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
+\end{align*}
+Eq. \ref{eq:chi2} can be rewritten as:
+\begin{align*}
+\chi^{(2)}_j = \frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\end{align*}
+Let us bound the two terms of \eqref{eq:thmg-2} separately. For the first one, we have:
+\begin{align*}
+KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & \sum_j \chi^{(2)}_j \log\frac{e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \sum_j \chi^{(2)}_j \log\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}} - \log\frac{1}{\abs{\mathcal{W}_s}}\\ =\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - \log\frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}e^{-\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}\\ \leq\ & -\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{\abs{\mathcal{W}_s}}\sum_{j'}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}
+\end{align*}
+where we applied Jensen's inequality in the last step ($-\log$ is a convex function). The second term of \eqref{eq:thmg-2} is:
+\begin{align*}
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}
+\end{align*}
+Putting it all together:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq\ & \frac{1}{\abs{\mathcal{W}_s}}\sum_{j}\frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j}} -\frac{1}{2}\sum_j \chi^{(2)}_j \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}\\ \leq\ & \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}} + \frac{1}{2}d\log\frac{\sigma^2_p}{c}  + \frac{1}{2}d\frac{c}{\sigma^2_p}
+\end{align*}
+Notice that, from now on, one can simply apply the proof of Thm.
 \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
@@
 Should we make this more explicit?}, $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, and setting $c_4 = \frac{2\lambda}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
-%\begin{align*}
-%\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
-%\end{align*}
-%\end{proof}
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
+\end{align*}
+\end{proof}
 
@@
 Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\bm{w}\leq w_{max}$ and uniformly bounded features $\bm{\phi}(s,a)\leq \phi_{\max}$.
 Consider the mixture version of Alg.
@@
 Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
-samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+\ref{eq:elbo} on a dataset $D$ of $N$ samples.
+Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}(\bm{w})}_{\nu}^2$.
+Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}
 \end{equation}
@@
 \begin{align}\label{eq:thmg-1}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B(\bm{w})}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 2\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{N}}
 \end{align}
@@
 \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace$.
-Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma^2_p + \log N) + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
-\begin{align*}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
+Thus, by redefining the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma^2_p + \log N) + 2\lambda\log\abs{\mathcal{W}_s}$\todo{$c_2$ actually contains $N$.
+Should we make this more explicit?}, and $c_3 = 2\frac{R_{max}^2}{(1-\gamma)^2}$, we can write that, with probability at least $1-2\delta$:
+\begin{align*}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}(\bm{w}^{*})}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)
 \end{align*}
@@
 \begin{equation}
-KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -d \right)
+KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
 \end{equation}
@@
 \begin{equation}\label{eq:tdgradmu}
-\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B_{\bm{w}}||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B_{\bm{w}}||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
 \end{equation} 
 \begin{equation}\label{eq:tdgradL}
-\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B_{\bm{w}}||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B_{\bm{w}}||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
+\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
 \end{equation}
@@
 \begin{align}
-\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] \nonumber \\&+ \frac{\lambda}{N} KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\mathcal{L}(\bm{\xi}) \leq  \widetilde{\mathcal{L}}(\bm{\xi}) &= \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\&+ \frac{\lambda}{N} KL(\chi^{(2)}||\chi^{(1)}) +\  \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)}KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
 \end{align}
@@
 \begin{align}
-\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B_{\bm{w}}}_D^2\right] \nonumber \\ &+\ \frac{\lambda}{N}KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
+\widetilde{\mathcal{L}}(\bm{\xi}) &= \frac{1}{C}\sum_{i=1}^C \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)}\left[\norm{B(\bm{w})}_D^2\right] \nonumber \\ &+\ \frac{\lambda}{N}KL(\chi^{(2)}||\chi^{(1)}) + \frac{\lambda}{N}\sum_{i=1}^C\sum_{j=1}^{|\mathcal{W}_s|} \chi_{j,i}^{(2)} KL(\mathcal{N}(\bm{w}|\bm{\mu}_i, \bm{\Sigma}_i)\ ||\ \mathcal{N}(\bm{w}|\bm{w}_j, \sigma_p^2\bm{I}))
 \end{align}

### 2018-05-17 NIPS 2018/main.tex
added new plots, minor corrections to appendix C

--- 2018-05-17 NIPS 2018/main.tex
@@
 \begin{align} \label{eq:elbo}
-\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
+\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B_{\bm{w}}}_D^2\right] + \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right).
 \end{align}
@@
     %\includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
-    \begin{tikzpicture}[scale=0.4]
+    \begin{tikzpicture}[scale=0.37]
 \draw [white] (0,0) grid (7,7);
-\begin{scope}[shift={(0,1.5)}]
+\begin{scope}[shift={(0,2)}]
 \draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
@@
 
-\node at (1.7,-0.5)[left] {start};
-\node at (3.3,5.5) [right]{goal};
-
-\draw [thick] (0,0) rectangle (5,5);
-\draw [line width=0.5mm] (1.25,5/3) -- (5,5/3);
-\draw [line width=0.5mm] (0,5/3) -- (0.75,5/3);
-\draw [line width=0.5mm] (0,10/3) -- (3.25,10/3);
-\draw [line width=0.5mm] (3.75,10/3) -- (5,10/3);
+\node at (1.8,-0.5)[left] {\color{darkgray}\small Start};
+\node at (3.1,5.5) [right]{\color{darkgray}\small Goal};
+
+\draw [thick, gray] (0,0) rectangle (5,5);
+\draw [line width=0.5mm, gray] (1.25,5/3) -- (5,5/3);
+\draw [line width=0.5mm, gray] (0,5/3) -- (0.75,5/3);
+\draw [line width=0.5mm, gray] (0,10/3) -- (3.25,10/3);
+\draw [line width=0.5mm, gray] (3.75,10/3) -- (5,10/3);
 \end{scope}
@@
   \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
+    \includegraphics[trim=0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
     \caption{}\label{f:two_doors}
@@
     \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
+    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
     \caption{}\label{f:one_door}
@@
     \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
+    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
     \caption{}\label{f:likelihood}
@@
 \begin{figure*}[t]
-  \begin{subfigure}[b]{0.15\textwidth}
-    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=2.6cm, width=2.0cm]{images/maze/maze6.png}
-    \caption{}\label{f:maze}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
+  \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
     \caption{}\label{f:cartpole}
   \end{subfigure}
-    \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
+    \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
     \caption{}\label{f:mountaincar}
   \end{subfigure}
-    \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev.pdf}
+    \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
     \caption{}\label{f:maze_results}
   \end{subfigure}
-  \caption{(a) Sample Maze (Maze 6), (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 6 and 13---see App.
-\ref{}.}
+  \caption{(a) transfer from $10$ sources in Cartpole, (b) transfer from $10$ source tasks in Mountain Car, and (c) transfer from $10$ sources in Maze \ref{fig:maze6}---see App. \ref{}.}
   \label{fig:ccmazeplots}
@@
 
-It is important to notice that for the implementation of the algorithms we use a Replay Buffer with a fixed size and batches of a given size sampled randomly from it to perform the gradient steps and use ADAM as the optimizer with the default parameters.
+It is worth noting that for the implementation of the algorithms we use a Replay Buffer with a fixed size and batches sampled randomly from it to perform the gradient steps using ADAM, with the default parameters, as the optimizer.
 
@@
 For these experiments, in order to train the source tasks for the Rooms Problem, we directly minimize the expected TD error based on the \textit{mellow} Bellman operator by stochastic gradient descent.
-We set to use a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$, $\psi=0.5$ and a learning rate $\alpha=0.001$.
+We use a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$, $\psi=0.5$ and a learning rate $\alpha=0.001$.
 Additionally, for exploration we use an \textit{Exploration Fraction} of $0.7$.
@@
 We use $\psi=0.5$, $\lambda=10^{-4}$ and $10$ \textit{weights} to estimate the expected TD error.
-For the learning rates we use $\alpha_{\mu}=0.001$ for the mean of the posterior Gaussian and $\alpha_{L}=0.0001$ to learn its Cholesky factor L.
-Furthermore, we restrict the minimum value reachable for the eigenvalues of these factor to be $\sigma_{min}^2=0.0001$.
+For the learning rates, $\alpha_{\mu}=0.001$ for the mean of the posterior Gaussian and $\alpha_{L}=0.0001$ to learn its Cholesky factor L.
+Furthermore, we restrict the minimum value reachable by the eigenvalues of these factors to be $\sigma_{min}^2=0.0001$.
 In the case of MGVT we use, instead, $\lambda=10^{-6}$, $\alpha_{\mu}=0.001$ and $\alpha_{L}=0.1$.
-Finally, for the prior's covariances we set $\sigma_p^2=10^{-5}$.
+Finally, for the prior's covariances we set it to $\sigma_p^2=10^{-5}$.
 
@@
 
-Firstly, we show the results of the evaluation performance.
+Firstly, we show the results of the evaluation of the greedy performance.
 We compute this as the average reward gotten when the agent acts using the greedy policy using the parameters at the iteration of evaluation.
@@
 In Fig.
-\ref{fig:3r-rew} we show the results when evaluating the Rooms Problem performance when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
+\ref{fig:3r-rew} we show the results when evaluating the Rooms Problem performance when the sources used to transfer have sample tasks resulting when both doors are sampled uniformly.
 It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer performance and shows that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
@@
 In Fig.\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled source tasks have a door fixed and the target task is generated by sampling both doors' positions.
-From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution in this more complicated setting, whereas GVT fails to adapt as consistently as MGVT, thus the higher variance and distance to the optimal value.
+From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution in this more complicated setting, whereas GVT fails to adapt as consistently as MGVT; thus the higher variance and distance to the optimal value.
 In this scenario, using a Gaussian to model the prior over-constrains the algorithm to stay close to part of the function space that cannot solve optimally the target tasks sampled from the modified distribution.
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room/erew.pdf}
+    \includegraphics[trim=0.3cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room/erew.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-gen/erew.pdf}
+    \includegraphics[trim=0.3cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-gen/erew.pdf}
     \caption{}
@@
   \end{subfigure}
-  \caption{(a) Rooms Problem: Evaluation Reward, (b) Rooms Problem: Evaluation Reward in the generalization experiment}
+  \caption{(a) Rooms Problem: Expected Return w.r.t. Greedy Policy, (b) Rooms Problem: Expected Return w.r.t. Greedy Policy in the generalization experiment}
   \label{fig:rooms-erew}
@@
 In Fig.
-\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2k$ iterations and we represent in the plot the positions visited by the agent.
+\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2000$ iterations and we represent as a scatter plot the positions visited by the agent.
 
@@
 It is noticeable that NT is not capable to lead the agent to the goal within the given iterations as most of the states visited are sparse within the first room, whereas GVT is able to concentrate more of its effort in looking for the door around the middle of the wall.
-After finding it, already in the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
+After finding it, within the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
 This is not surprising as the value function should be equal for all tasks after crossing the door.
@@
 In the other case, we have Fig.
-\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
+\ref{fig:nt-vs-mgvt} that shows a similar situation to that of GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
 Indeed, 1-MGVT is able to actually explore the right part of the first room within these iterations, which might be seen as the result of the prior model being able to capture more information than the Gaussian; hence, the higher speed-up in convergence and robustness to changes in the distribution from which target tasks are drawn.
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_gvt.pdf}
+    \includegraphics[trim=0.5cm 0.5cm 1.5cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_gvt.png}
     \caption{}
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_mgvt.pdf}
+    \includegraphics[trim=0.5cm 0.5cm 1.5cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_mgvt.png}
     \caption{}
@@
 It is interesting to notice the difference on performance between MGVT and GVT whenever there is a small number of source tasks.
-MGVT clearly provides faster adaptation in the presence of low prior knowledge as it can be discern from the gap seen in nearly a $1000$ iterations between the plots.
-It is as expected because approximating the prior Gaussian distribution using maximum likelihood estimations with a low number of samples does not provide enough precision.
+MGVT clearly provides faster adaptation in the presence of low prior knowledge as it can be discerned from the gap created after nearly a $1000$ iterations between the plots.
+This, however, is as expected because approximating the prior Gaussian distribution using maximum likelihood estimations with a low number of samples does not provide enough precision.
 As the number of source tasks increases, as seen more clearly from Fig.
-\ref{fig:seq-1950}, the performances become closer for this environment.
+\ref{fig:seq-1950}, the performances between the algorithms become closer for this environment.
 
@@
 \ref{fig:sequential}, we see that, even if more components lead to slightly better performances, the advantage is not quite significant in this environment.
-As seen before, the actual performances will converge to optimality in all the MGVT cases.
+As seen above, the actual performances will converge to optimality in all the MGVT cases.
 Clearly, as we expect all components to converge to the optimal parameters, the initial performance difference will, indeed, reduce fast.
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/sequential/lrew_1000.pdf}
+    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=4.5cm]{images/sequential/lrew_1000.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/sequential/lrew_1950.pdf}
+    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=4.5cm]{images/sequential/lrew_1950.pdf}
     \caption{}
@@
 
-During the training of the source tasks, we use a \textit{Batch Size} of $150$ and \textit{Buffer Size} of $50000$.
-Specifically, for DDQN we use a \textit{Target Update Frequency} of $500$ and and \textit{Exploration Fraction} of $0.35$ and a learning rate $\alpha=0.001$.
-We use a Multilayer Perceptron (MLP) with ReLU as activation function and a hidden layer of $32$ neurons, an input layer of $4$ and the value of the $2$ actions as the output layer.
+During the training of the source tasks, we use a \textit{Batch Size} of $150$ and a \textit{Buffer Size} of $50000$.
+Specifically, for DDQN we use a \textit{Target Update Frequency} of $500$,\textit{Exploration Fraction} of $0.35$ and a learning rate $\alpha=0.001$.
+We use a Multilayer Perceptron (MLP) with ReLU as activation function and a single hidden layer of $32$ neurons.
 
@@
 For its the Cholesky factor L we use $\alpha_L=0.0001$ and set the limit that the minimum eigenvalue may reach to $\sigma_{min}^2=0.0001\ $.
-Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$and leave the learning rates of the posterior components' means and Cholesky factor the same as GVT.
+Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$ and leave the learning rates of the posterior components' means and Cholesky factor the same as GVT.
 
 In Fig.
-\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters in the iteration of evaluation.
+\ref{fig:cp-erew}, we show the evaluation performance for DDQN, GVT, 1-MGVT and 3-MGVT, which consists of the average performance of the greedy policy using the parameters in the iteration of evaluation.
 In the case of GVT, we use the mean of the Gaussian posterior for the greedy policy and for MGVT corresponds to the mean of the Mixture of Gaussians for the posterior, that reduces to the average of the components' means.
@@
 the DDQN evaluation.
-Although, a slight performance drop is seen as the algorithm adapts to the optimal Q-function, the algorithm quickly reaches optimality and converges to the actual optimal performance while DDQN, within these iterations, remains on average slightly suboptimal.
-\todo{improve this}
+Also, in this tasks is possible to still observe an improved performance from using MGVT as within fewer iterations, the mean parameters converges to the optimal $Q$-function.
 
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/cartpole/erew.pdf}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/cartpole/erew.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/mountaincar/erew.pdf}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/mountaincar/erew.pdf}
     \caption{}
@@
   \end{subfigure}
-  \caption{(a) Cartpole: Evaluation Reward, (b) Mountain Car: Evaluation Reward}
+  \caption{(a) Cartpole: Expected Return w.r.t. Greedy Policy, (b) Mountain Car: Expected Return w.r.t. Greedy Policy}
   \label{fig:ccerew}
@@
 Moreover, we set the \textit{Exploration Fraction} to $0.15$.
-We use an MLP with single hidden layer of $64$ neurons with ReLU activation function, an input layer of $4$ neurons and as output the value of each of the $3$ actions.
+We use an MLP with single hidden layer of $64$ neurons with ReLU activation function.
 
 For the transfer experiments, we set the \textit{Batch Size} to $500$, and use $10$ \textit{weights} to approximate the expected TD error, $\lambda=10^{-5}$ and $\psi=0.5$.
-For the learning rates, we use $\alpha_{\mu}=0.001$ for learning the means of the Gaussians.
+For the learning rates, we use $\alpha_{\mu}=0.001$ for the means of the Gaussians.
 In the case of the Cholesky factors L, we use $\alpha_L=0.0001$ and allow the eigenvalues to reach a minimum value of $\sigma_{min}^2=0.0001$.
@@
 Finally, in Fig.
-\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT in the iteration of evaluation.
-In this plot, we can observe directly how fast is MGVT able to converge its mean to the actual optimal performance and that even if GVT struggles to find learn in comparison with MGVT, still provides a clear advantage w.r.t.
+\ref{fig:mc-erew}, we show the evaluation performance obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT in the iteration of evaluation.
+In this plot, we can observe directly how fast is MGVT able to make its mean converge to the actual optimal performance.
+Also, even though GVT struggles to learn in comparison with MGVT, still provides a clear advantage w.r.t.
 DDQN.
-Also, it is worth noting that the variances seen are result that different speeds of the car result in different time to reach the goal and, thus, different optimal performances.
+It is worth noting that the variances seen are caused by different speeds of the car resulting in different time to reach the goal and, thus, different optimal return.
 
@@
 
-For the maze navigation task in Sec.
+For the maze navigation task presented in Sec.
 \ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
@@
 
-For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the $22$-dimensional state of the MDP and an output layer that produces the value of each of the $3$ action.
-For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate $\alpha=0.001$ .
+For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions..For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate to $\alpha=0.001$ .
 
@@
 
+\begin{figure*}[h]
+	\begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze0.pdf}
+    \caption{Expected Return during learning}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze0.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze0}}
+  \label{fig:rew-maze0}
+
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze6.pdf}
+    \caption{Expected Return during learning}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze6.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze6}}
+  \label{fig:rew-maze6}
+
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze13.pdf}
+    \caption{Expected Return during learning}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze13.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze13} }
+  \label{fig:rew-maze13}
+\end{figure*}
+
+Hereafter, we present additional results of transferring from $5$ source tasks to the mazes shown in Fig.
+\ref{fig:maze0}, Fig.
+\ref{fig:maze6} and Fig.
+\ref{fig:maze13} using both GVT and MGVT.
+We show both the evaluation performance, i.e.
+the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t.
+those parameters, and the expected return during the learning process.
+All the curves result from averaging $20$ independent runs and randomly sampled sources.
+
 In Fig.
-\ref{}, we present the results of transferring from $5$ source tasks to the mazes shown in Fig.
-\ref{fig:maze0}, Fig.
-\ref{fig:maze6}, Fig.
-\ref{fig:maze8} and Fig.
-\ref{fig:maze13} using \todo{also GVT?} GVT and MGVT.
-We show both the evaluation reward, i.e.
-the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t.
-those parameters, and the expected return.
-All the curves result from averaging $20$ independent runs and randomly sampled sources.
-
-% Placer-holder to actual plots. Add analyses
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{Maze \ref{fig:maze0} (a) Expected Return (b) Evaluation Reward}
-\end{figure*}
-
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{Maze \ref{fig:maze6} (a) Expected Return (b) Evaluation Reward}
-\end{figure*}
-
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{Maze \ref{fig:maze13} (a) Expected Return (b) Evaluation Reward}
-  \label{fig:mazes-plots}
-\end{figure*}
+\ref{fig:maze0}, \ref{fig:maze6}, \ref{fig:maze13}, we can appreciate that in this more complex transfer setting, MGVT is able to provide significant speed-up in a consistent manner in this subset of mazes.
+It is also noticeable the bad performance obtained with GVT in all cases.
+The Gaussian prior model clearly fails to capture enough information to transfer in this setting that result in a negative transfer effect.
 

### 2018-05-18 NIPS 2018/main.tex
Minor fixes to the Appendix

--- 2018-05-17 NIPS 2018/main.tex
@@
 \norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \norm{\wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
-\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \gamma\norm{Q^* - \wt{Q}}_{\nu,p}^p
+\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \gamma\norm{Q^* - \wt{Q}}_{\nu,p}^p,
 \end{align*}
@@
 \begin{align} \label{eq:mm1}
-\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p
+\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p.
 \end{align}
 Let us bound the norm on the right-hand side separately.
-In order to do that, we will bound the function $\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)}$ point-wisely for any state $s,a$.
+In order to do that, we will bound the function $\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)}$ point-wisely for any pair $\langle s,a\rangle$.
 By applying the definition of the optimal and mellow Bellman operators, we obtain:
 \begin{align} \label{eq:mm5}
-\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} =\ & \abs{R(s,a) + \gamma\mathbb{E}\left[\max_{a'}Q^*(s',a')\right] - R(s,a) - \gamma\mathbb{E}\left[\mm_{a'}Q^*(s',a')\right]}\notag \\ =\ & \gamma\abs{\mathbb{E}\left[\max_{a'}Q^*(s',a')\right] - \mathbb{E}\left[\mm_{a'}Q^*(s',a')\right]}\notag \\ \leq\ & \gamma\mathbb{E}\left[\abs{\max_{a'}Q^*(s',a') - \mm_{a'}Q^*(s',a')}\right]
+\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} =\ & \abs{R(s,a) + \gamma\mathbb{E}\left[\max_{a'}Q^*(s',a')\right] - R(s,a) - \gamma\mathbb{E}\left[\mm_{a'}Q^*(s',a')\right]}\notag \\ =\ & \gamma\abs{\mathbb{E}\left[\max_{a'}Q^*(s',a')\right] - \mathbb{E}\left[\mm_{a'}Q^*(s',a')\right]}\notag \\ \leq\ & \gamma\mathbb{E}\left[\abs{\max_{a'}Q^*(s',a') - \mm_{a'}Q^*(s',a')}\right].
 \end{align}
@@
 \begin{align} \label{eq:mm2}
-\abs{\max_a Q^*(s,a) - \mm_a Q^*(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q^*(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q^*(s,a)}\notag\\ =\ & \abs{\sum_a Q^*(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q^*(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}
+\abs{\max_a Q^*(s,a) - \mm_a Q^*(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q^*(s,a) - \sum_a \pi_{\beta_{\kappa}}(a|s)Q^*(s,a)}\notag\\ =\ & \abs{\sum_a Q^*(s,a) \left( \pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q^*(s,a)} \abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)},
 \end{align}
@@
 \begin{align*}
-\pi_{\beta_{\kappa}}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}
+\pi_{\beta_{\kappa}}(a|s) = \frac{e^{\beta_{\kappa} Q^*(s,a)}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}.
 \end{align*}
@@
 \begin{align} \label{eq:mm3}
-\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)} =\ & \abs{\pi^*(a_1(s)|s) - \pi_{\beta_{\kappa}}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ =\ & \abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi_{\beta_{\kappa}}(a|s)}\notag\\ =\ & 2\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)}
-\end{align}
-Finally, let us bound this last term:
+\sum_a\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)} =\ & \abs{\pi^*(a_1(s)|s) - \pi_{\beta_{\kappa}}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi^*(a|s) - \pi_{\beta_{\kappa}}(a|s)}\notag\\ =\ & \abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi_{\beta_{\kappa}}(a|s)}\notag\\ =\ & 2\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)}.
+\end{align}
+Finally, denoting with $a_2(s)$ the second-best action in state $s$, let us bound this last term:
 \begin{align} \label{eq:mm4}
-\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q^*(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q^*(s,a_1(s)) - Q^*(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\abs{1 - \pi_{\beta_{\kappa}}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta_{\kappa} Q^*(s,a_1(s))}}{\sum_{a'}e^{\beta_{\kappa} Q^*(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} \left( Q^*(s,a_1(s)) - Q^*(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{\sum_{a'}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \sum_{a' \neq a_1(s)}e^{\beta_{\kappa} \left( Q^*(s,a') - Q^*(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta_{\kappa} g(s)}}{e^{\beta_{\kappa} g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}.
 \end{align}
@@
 \begin{align*}
-\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2 R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2 R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}.
 \end{align*}
@@
 \begin{align*}
-\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} \leq \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}
+\abs{TQ^*(s,a) - \wt{T}Q^*(s,a)} \leq \frac{2\gamma R_{max}}{1-\gamma}\abs{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g(s)}}}.
 \end{align*}
@@
 We begin by proving some important lemmas.
-Then, we use them to derive a finite-sample analysis of Alg.
-\ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Thm.
+Then, we use them to derive a finite-sample analysis of Algorithm~\ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Thm.
 \ref{th:main-gaussian}) and Gaussian mixture models (Thm.
@@
 \begin{equation}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}.
 \end{equation}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 =\ & \norm{Q_{\bm{w}} + TQ_{\bm{w}} - TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \norm{TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2\\ =\ & \norm{B_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2
+\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 =\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}} + TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \norm{TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2\\ =\ & \norm{B_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq\ \frac{1}{1-\gamma}\norm{B_{\bm{w}}}_{\nu}^2
-\end{align*}
-Then we can write:
-\begin{align*}
-P\left( \norm{Q_{\bm{w}} - Q^*}_{\nu}^2 > \epsilon \right) \leq P\left(\norm{B_{\bm{w}}}_{\nu}^2 > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\epsilon}
-\end{align*}
-Settings the right-hand side equal to $\delta$ and solving for $\epsilon$ concludes the proof.
+\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq\ \frac{1}{1-\gamma}\norm{B_{\bm{w}}}_{\nu}^2.
+\end{align*}
+Then, using Markov inequality, we can write:
+\begin{align*}
+P\left( \norm{Q_{\bm{w}} - Q^*}_{\nu}^2 > \epsilon \right) \leq P\left(\norm{B_{\bm{w}}}_{\nu}^2 > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\epsilon}.
+\end{align*}
+By setting the right-hand side equal to $\delta$ and solving for $\epsilon$ concludes the proof.
 \end{proof}
@@
 \begin{equation}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}.
 \end{equation}
@@
 
-We now prove some important properties of the variational approximation introduced in Sec.
-\ref{sec:alg}.
+We now prove some important properties of the variational approximation introduced in Section~\ref{sec:alg}.
 Our results generalize those of existing works that consider variational approximations of intractable Gibbs posteriors \cite{alquier2016properties,cottet20181}.
@@
 Consider a dataset $D$ of $N$ i.i.d.
-samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
 \begin{equation}\label{eq:lemma2-1}
-\mathbb{E}_q\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{B_{\bm{w}}}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{equation}
 \begin{equation}\label{eq:lemma2-2}
-\mathbb{E}_q\left[ \norm{B_{\bm{w}}}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{equation}
@@
 \begin{align*}
-P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] - \norm{B_{\bm{w}}}_D^2} > \epsilon \right) \leq 2exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
+P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] - \norm{\wt B_{\bm{w}}}_D^2} > \epsilon \right) \leq 2\exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
 \end{align*}
@@
 \begin{align*}
-\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] - \norm{B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] - \norm{\wt B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{B_{\bm{w}}}_{\nu}^2
-\end{align*}
-where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$. Thus:
+\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{\wt B_{\bm{w}}}_{\nu}^2,
+\end{align*}
+where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Thus:
 \begin{align}\label{eq:hoeff}
-\abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{align}
@@
 \begin{align*}
-\log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \geq \mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p)
-\end{align*}
-Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2}$, we obtain:
-\begin{align*}
-\mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p) \leq \log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \leq 4\frac{R_{max}^2 \lambda^{-1}N}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \geq \mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p).
+\end{align*}
+Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2}$, we obtain:
+\begin{align*}
+\mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p) \leq \log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \leq 4\frac{R_{max}^2 \lambda^{-1}N}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_q\left[ \abs{\norm{B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{B_{\bm{w}}}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_q\left[ \abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
-Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
-Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
+Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
 \begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
 \end{align*}
@@
 We can now use Eq.
-\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_D^2 \right]$, thus obtaining:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right]$, thus obtaining:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{align*}
@@
 
-It is worth noting the generality of Lemma \ref{lemma:general-bound}: in bounding the expected Bellman error we did not need to assume any particular distribution, nor did we have to assume any particular function approximator.
+It is worth noting the generality of Lemma \ref{lemma:general-bound}: in bounding the expected Bellman error we do not need to assume any particular distribution, nor we have to assume any particular function approximator.
 
@@
 \begin{restatable}{theorem}{thg} \label{th:main-gaussian}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
 Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
-Consider the Gaussian version of Alg.
-\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
+Consider the Gaussian version of Algorithm~\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.~\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}.
 \end{equation}
@@
 \begin{align}\label{eq:thg-4}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
 \end{align}
@@
 \begin{align}\label{eq:thg-3}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}}}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]
-\end{align}
-Let us bound these two terms point-wisely for each $s,a$. For the first expectation, we have:
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}}}_{\nu}^2\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{\nu}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[(\wt{T}Q_{\bm{w}}-Q_{\bm{w}})^2\right]\right]\notag\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right]+ \mathbb{E}_{\nu}\left[Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right].
+\end{align}
+Let us bound these two terms point-wisely for each pair $\langle s,a\rangle$. For the first expectation, we have:
 \begin{align}\label{eq:thg-1}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\notag\\ =\ & R(s,a) + \gamma\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] - \bm{w}^{*T}\bm{\phi}(s,a)
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] - \bm{w}^T\bm{\phi}(s,a)\right]\notag\\ =\ & R(s,a) + \gamma\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right]\right] - \bm{w}^{*T}\bm{\phi}(s,a).
 \end{align}
@@
 \begin{align}\label{eq:thg-2}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^T\bm{\phi}(s',a') }\right]\notag\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right]
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right]\right] =\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\mathbb{E}_{s'}\left[\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^T\bm{\phi}(s',a') }\right]\right]\notag\\ \leq\ & \mathbb{E}_{s'}\left[\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right]\right].
 \end{align}
@@
 Thus:
-\begin{align*}
-\mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right] =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\\ \leq\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}^2}\\ =\ & \mathbb{E}_{s'}\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')} + \frac{1}{2}\kappa c\bm{\phi}_{max}^2\\ =\ & \mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa c\bm{\phi}_{max}^2
-\end{align*}
-Plugging this into \ref{eq:thg-2} and then into \ref{eq:thg-1}, we obtain:
-\begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2 - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}_{\bm{w}^{*}} + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2
+\begin{small}
+\begin{align*}
+\mathbb{E}_{s'}\left[\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[e^{\kappa\bm{w}^T\bm{\phi}(s',a')}\right]\right] =\ & \mathbb{E}_{s'}\left[\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a') + \frac{1}{2}\kappa^2c\bm{\phi}(s',a')^T\bm{\phi}(s',a')}\right]\\ \leq\ & \mathbb{E}_{s'}\left[\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}e^{\frac{1}{2}\kappa^2c\bm{\phi}_{max}^2}\right]\\ =\ & \mathbb{E}_{s'}\left[\frac{1}{\kappa} \log \frac{1}{|\mathcal{A}|}\sum_{a'} e^{\kappa\bm{w}^{*T}\bm{\phi}(s',a')}\right] + \frac{1}{2}\kappa c\bm{\phi}_{max}^2\\ =\ & \mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a')\right] + \frac{1}{2}\kappa c\bm{\phi}_{max}^2.
+\end{align*}
+\end{small}
+Plugging this into \eqref{eq:thg-2} and then into \eqref{eq:thg-1}, we obtain:
+\begin{align*}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & R(s,a) + \gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^{*T}\bm{\phi}(s',a')\right] + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2 - \bm{w}^{*T}\bm{\phi}(s,a)\\ =\ & \wt{B}_{\bm{w}^{*}} + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
-\end{align*}
-where the second inequality follows from Cauchy-Schwarz inequality. Going back to \ref{eq:thg-3}, the first term can now be upper bounded by:
-\begin{align*}
-\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4
-\end{align*}
-Let us now consider the variance term of \ref{eq:thg-3} and derive a bound that holds point-wisely for any $s,a$. We have:
-\begin{align*}
-Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\mm_{a'}\sqrt{c}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]
+\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4,
+\end{align*}
+where the second inequality follows from Cauchy-Schwarz inequality. Going back to \eqref{eq:thg-3}, the first term can now be upper bounded by:
+\begin{align*}
+\mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}^2\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right]\right] \leq 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4.
+\end{align*}
+Let us now consider the variance term of \eqref{eq:thg-3} and derive a bound that holds point-wisely for any $s,a$. We have:
+\begin{align*}
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\left[\mm_{a'}\sqrt{c}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\right].
 \end{align*}
@@
 \begin{align*}
-\sqrt{c}\abs{\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)} \leq\ & \sqrt{c}\norm{\bm{w}}\norm{\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)}\\ \leq\ & \sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}
+\sqrt{c}\abs{\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)} \leq\ & \sqrt{c}\norm{\bm{w}}\norm{\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)}\\ \leq\ & \sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}.
 \end{align*}
@@
 \begin{align*}
-Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq \gamma^2 \frac{1}{4}\left(2\sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}\right)^2 = c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
-\end{align*}
-We can finally plug everything into \ref{eq:thg-3}, thus obtaining:
-\begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq \gamma^2 \frac{1}{4}\left(2\sqrt{c}\bm{w}_{max}\bm{\phi}_{max}\frac{1 + \gamma}{\gamma}\right)^2 = c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2.
+\end{align*}
+We can finally plug everything into \eqref{eq:thg-3}, thus obtaining:
+\begin{align*}
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2.
 \end{align*}
@@
 \begin{align*}
-KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^d} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -d \right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma_{max}}{c} + \frac{1}{2}d\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}
-\end{align*}
-Now, putting all together into \ref{eq:thg-4}:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}d\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}d\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right) =\ & KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)\right)\\ =\ & \frac{1}{2}\left( \log\frac{\abs{\bm{\Sigma}_p}}{c^d} + c\text{Tr}\left( \bm{\Sigma}_p^{-1}\right) + \norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} -d \right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma_{max}}{c} + \frac{1}{2}d\frac{c}{\sigma_{min}} + \frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}.
+\end{align*}
+Now, putting all together into \eqref{eq:thg-4}:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2 + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right]\\ &\ + \frac{\lambda}{N}d\log\frac{\sigma_{max}}{c} + \frac{\lambda}{N}d\frac{c}{\sigma_{min}} + \frac{\lambda}{N}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + \frac{1}{N^2}\left(\frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}\right)\\ &\ + \frac{1}{N}\left(\bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N) + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} \right)\\ &\ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}.
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ]}{(1-\gamma)\delta}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ]}{(1-\gamma)\delta}.
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right).
 \end{align*}
@@
 \begin{restatable}{theorem}{thmgsoft} \label{th:main-mixture-soft}
-Fix a target task $\tau$ a let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
 Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
-Consider the mixture version of Alg.
-\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
+Consider the mixture version of Algorithm~ \ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
 Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\ref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
+\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[B_{\bm{w}}\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$},
 \end{equation}
@@
 \begin{align}\label{eq:thmg-1}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
 \end{align}
@@
 \begin{align}\label{eq:thmg-2}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})),
 \end{align}
@@
 \begin{align}\label{eq:chi2}
-\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+\chi^{(2)}_j = \frac{e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I}))}}{\sum_{j'}e^{-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_{j'}, \sigma_p^2\bm{I}))}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}.
 \end{align}
@@
 \begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)
-\end{align*}
-Eq. \ref{eq:chi2} can be rewritten as:
-\begin{align*}
-\chi^{(2)}_j = \frac{e^{-\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) = \frac{1}{2}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right),
+\end{align*}
+Eq. \eqref{eq:chi2} can be rewritten as:
+\begin{align*}
+\chi^{(2)}_j = \frac{e^{-\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}}}{\sum_{j'}e^{-\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_{j'}}}}\ \forall j = 1,\dots,\abs{\mathcal{W}_s}.
 \end{align*}
@@
 \begin{align*}
-KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ \leq\ & \log\abs{\mathcal{W}_s}
+KL(\chi^{(2)}||\chi^{(1)}) =\ & \sum_j \chi^{(2)}_j \log\frac{\chi^{(2)}_j}{\chi^{(1)}_j}\\ =\ & \sum_j \chi^{(2)}_j \log\chi^{(2)}_j - \sum_j \chi^{(2)}_j \log\frac{1}{\abs{\mathcal{W}_s}}\\ \leq\ & \log\abs{\mathcal{W}_s},
 \end{align*}
@@
 \begin{align*}
-\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace.
 \end{align*}
@@
 \begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace.
 \end{align*}
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}.
 \end{align*}
@@
 
-Under Gaussian distributions, all quantities of interest for using Alg.
-\ref{alg:transfer} can be computed very easily.
+Under Gaussian distributions, all quantities of interest for using Algorithm \ref{alg:transfer} can be computed very easily.
 The KL divergence between the prior and approximate posterior can be computed in closed-form as:
@@
 
-For the implementation of the Mixture of Gaussian Variational Transfer, we use the upper bound on the KL divergence between two Mixtures of Gaussians, as in Theorem\ref{th:ukl}, to obtain an upper bound on the negative ELBO in Equation\ref{eq:elbo}.
+For the implementation of the Mixture of Gaussian Variational Transfer, we use the upper bound on the KL divergence between two Mixtures of Gaussians, as in Theorem~\ref{th:ukl}, to obtain an upper bound on the negative ELBO in Equation~\eqref{eq:elbo}.
 Consider we have $C$ components for the posterior family $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$ and a prior distribution, constructed from the set of weights $\mathcal{W}_s = \left\lbrace \bm{w}_1,..., \bm{w}_{|\mathcal{W}_s|} \right\rbrace$ of the sources' optimal $Q$-functions, $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{j=1}^{|\mathcal{W}_s|}\mathcal{N}(\bm{w}|\bm{w}_j,\sigma_p^2\bm{I})$.
@@
 
-And substituting (\ref{eq:ukl}) in the negative ELBO in \ref{eq:elbo} we get the following upper bound.
+And substituting \eqref{eq:ukl} in the negative ELBO in \eqref{eq:elbo} we get the following upper bound.
 
@@
 
-that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Eq.
-\ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL} derived for the Gaussian case.
+that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Equations~\eqref{eq:klgradmu}, \eqref{eq:klgradL}, \eqref{eq:tdgradmu}, \eqref{eq:tdgradL} derived for the Gaussian case.
 
@@
 
-Besides the results that we show in Sec. \ref{sec:gw}, we present in this section further empirical evaluation.
+Besides the results that we show in Section~\ref{sec:gw}, we present in this section further empirical evaluation.
 
@@
 
-In Fig.
-\ref{fig:3r-rew} we show the results when evaluating the Rooms Problem performance when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
+In Figure~\ref{fig:3r-rew} we show the results when evaluating the Rooms Problem performance when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
 It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer performance and shows that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
 
-In Fig.\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled source tasks have a door fixed and the target task is generated by sampling both doors' positions.
+In Figure~\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled source tasks have a door fixed and the target task is generated by sampling both doors' positions.
 From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution in this more complicated setting, whereas GVT fails to adapt as consistently as MGVT, thus the higher variance and distance to the optimal value.
@@
 Furthermore, we investigate the exploratory behavior induced by our transfer algorithms and how they differ between each other and in comparison with $\epsilon$-greedy exploration.
-In Fig.
-\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2k$ iterations and we represent in the plot the positions visited by the agent.
-
-Observing Fig.
-\ref{fig:nt-vs-gvt}, it is possible to understand the difference between the $\epsilon$-greedy exploration and the resulting behavior from GVT.
+In Figure~\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2k$ iterations and we represent in the plot the positions visited by the agent.
+
+Observing Figure~\ref{fig:nt-vs-gvt}, it is possible to understand the difference between the $\epsilon$-greedy exploration and the resulting behavior from GVT.
 It is noticeable that NT is not capable to lead the agent to the goal within the given iterations as most of the states visited are sparse within the first room, whereas GVT is able to concentrate more of its effort in looking for the door around the middle of the wall.
@@
 
-In the other case, we have Fig.
-\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
+In the other case, we have Figure~\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
 Indeed, 1-MGVT is able to actually explore the right part of the first room within these iterations, which might be seen as the result of the prior model being able to capture more information than the Gaussian; hence, the higher speed-up in convergence and robustness to changes in the distribution from which target tasks are drawn.
@@
 
-Finally, in Fig.
-\ref{fig:sequential} we present the expected return as a function of the number of source tasks used for GVT and MGVT.
-In particular, we show the resulting curves after $1000$ iterations in Fig.
-\ref{fig:seq-1000} and after $1950$ iterations in Fig.
-\ref{fig:seq-1950}.
+Finally, in Figure~\ref{fig:sequential} we present the expected return as a function of the number of source tasks used for GVT and MGVT.
+In particular, we show the resulting curves after $1000$ iterations in Figure~\ref{fig:seq-1000} and after $1950$ iterations in Figure~\ref{fig:seq-1950}.
 It is interesting to notice the difference on performance between MGVT and GVT whenever there is a small number of source tasks.
@@
 It is as expected because approximating the prior Gaussian distribution using maximum likelihood estimations with a low number of samples does not provide enough precision.
-As the number of source tasks increases, as seen more clearly from Fig.
-\ref{fig:seq-1950}, the performances become closer for this environment.
-
-Finally, among the MGVT curves in Fig.
-\ref{fig:sequential}, we see that, even if more components lead to slightly better performances, the advantage is not quite significant in this environment.
+As the number of source tasks increases, as seen more clearly from Figure~\ref{fig:seq-1950}, the performances become closer for this environment.
+
+Finally, among the MGVT curves in Figure~\ref{fig:sequential}, we see that, even if more components lead to slightly better performances, the advantage is not quite significant in this environment.
 As seen before, the actual performances will converge to optimality in all the MGVT cases.
@@
 
-In Fig.
-\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters in the iteration of evaluation.
+In Figure~\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters in the iteration of evaluation.
 In the case of GVT, we use the mean of the Gaussian posterior for the greedy policy and for MGVT corresponds to the mean of the Mixture of Gaussians for the posterior, that reduces to the average of the components' means.
@@
 
-Finally, in Fig.
-\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT in the iteration of evaluation.
+Finally, in Figure~\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT in the iteration of evaluation.
 In this plot, we can observe directly how fast is MGVT able to converge its mean to the actual optimal performance and that even if GVT struggles to find learn in comparison with MGVT, still provides a clear advantage w.r.t.
@@
 
-For the maze navigation task in Sec.
-\ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
-In Fig.
-\ref{fig:mazes}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
+For the maze navigation task in Section~\ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
+In Figure~\ref{fig:mazes}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
 Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.
@@
 
-In Fig.
-\ref{}, we present the results of transferring from $5$ source tasks to the mazes shown in Fig.
-\ref{fig:maze0}, Fig.
-\ref{fig:maze6}, Fig.
-\ref{fig:maze8} and Fig.
-\ref{fig:maze13} using \todo{also GVT?} GVT and MGVT.
+In Figure~\ref{}, we present the results of transferring from $5$ source tasks to the mazes shown in Figure~\ref{fig:maze0}, Figure~\ref{fig:maze6}, Figure~\ref{fig:maze8} and Figure~\ref{fig:maze13} using \todo{also GVT?} GVT and MGVT.
 We show both the evaluation reward, i.e.

### 2018-05-18 NIPS 2018/main.tex
Completed Sec 5.3

--- 2018-05-17 NIPS 2018/main.tex
@@
 \ref{}.
-In this experiment, we use a Double Deep Q-Network \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
+In this experiment, we use a Double Deep Q-Network (DDQN) \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
 The results (same settings of Section~\ref{sec:gw}) are shown in Figures~\ref{f:cartpole} and~\ref{f:mountaincar}.
@@
 On the contrary, in Mountain Car (Figure~\ref{f:mountaincar}) the optimal $Q$-functions become very different when changing the car speed.
-This phenomenon hinders the learning of GVT in the target task, while 1-MGVT achieves a good jump-start and converges in fewer iterations.
+This phenomenon hinders the learning of GVT in the target task, while MGVT achieves a good jump-start and converges in fewer iterations.
 
@@
 
-For this setting we propose a maze environment, such as those in Fig.
+In our last experiment, we consider a robotic agent navigating mazes.
+At the beginning of each episode, the agent is dropped to a random position in a $10m^2$ maze and must reach a goal area in the smallest time possible.
+The robot is equipped with sensors detecting its absolute position, its orientation, the distance to any obstacle within $2m$ in $9$ equally-spaced directions, and whether the goal is detected in the same range.
+The only actions available are \textit{move forward} with speed $0.5m/s$ or \textit{rotate} (in either direction) with speed of $\pi/8 rad/s$.
+Each time step corresponds to $1s$ of simulation.
+The reward is $1$ for reaching the goal and $0$ otherwise, while the discount factor is $\gamma=0.99$.
+For this experiment, we design a set of $20$ different mazes and solve them using a DDQN with two layers of $32$ neurons and ReLU activations.
+Then, we fix a target maze and transfer from $5$ source mazes uniformly sampled from such set (excluding the chosen target).
+To further asses the robustness of our method, we now consider transferring from the $Q$-functions learned by DDQNs instead of those obtained by minimizing the TD error as in the previous domains.
+From our considerations of Sec.
+\ref{sec:td} and \ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
+We show the results for a fixed target maze in Fig.
+\ref{}, while referring the reader to App.
+\ref{} for the illustration of our mazes and additional results.
+Once again, MGVT achieves a remarkable speed-up over (no-transfer) DDQN.
+This time, using $3$ components achieves slightly better performance than using only $1$, which is likely due to the fact that the task distribution is much more complicated than in the previous domains.
+For the same reason, GVT shows negative transfer and performs even worse than no-transfer.
+
+%For this setting we propose a maze environment, such as those in Fig.
 \ref{}, for a robotic agent to navigate.
@@
 
-The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience.
+%The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience.
 Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting suitable to assess how robust our algorithm is to negative transfer.
 
-The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
+%The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
 Finally, the 1-MGVT algorithm was used to solve the target tasks---Mazes 6 and 13.

### 2018-05-18 NIPS 2018/main.tex
Changed title

--- 2018-05-18 NIPS 2018/main.tex
@@
 Furthermore, we investigate the exploratory behavior induced by our transfer algorithms and how they differ between each other and in comparison with $\epsilon$-greedy exploration.
-In Figure~\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2k$ iterations and we represent in the plot the positions visited by the agent.
-
-Observing Figure~\ref{fig:nt-vs-gvt}, it is possible to understand the difference between the $\epsilon$-greedy exploration and the resulting behavior from GVT.
+In Fig.
+\ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2000$ iterations and we represent as a scatter plot the positions visited by the agent.
+
+Observing Fig.
+\ref{fig:nt-vs-gvt}, it is possible to understand the difference between the $\epsilon$-greedy exploration and the resulting behavior from GVT.
 It is noticeable that NT is not capable to lead the agent to the goal within the given iterations as most of the states visited are sparse within the first room, whereas GVT is able to concentrate more of its effort in looking for the door around the middle of the wall.
-After finding it, already in the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
+After finding it, within the second room, the positions concentrate in the path leading to the goal given that the need for the exploration is less.
 This is not surprising as the value function should be equal for all tasks after crossing the door.
 
-In the other case, we have Figure~\ref{fig:nt-vs-mgvt} that shows the same situation as with GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
+In the other case, we have Fig.
+\ref{fig:nt-vs-mgvt} that shows a similar situation to that of GVT, but it is quite interesting to notice how sparser the exploration of 1-MGVT is with respect to GVT.
 Indeed, 1-MGVT is able to actually explore the right part of the first room within these iterations, which might be seen as the result of the prior model being able to capture more information than the Gaussian; hence, the higher speed-up in convergence and robustness to changes in the distribution from which target tasks are drawn.
@@
 For its the Cholesky factor L we use $\alpha_L=0.0001$ and set the limit that the minimum eigenvalue may reach to $\sigma_{min}^2=0.0001\ $.
-Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$and leave the learning rates of the posterior components' means and Cholesky factor the same as GVT.
+Additionally, for MGVT we set the variance of the prior components $\sigma_p^2=10^{-5}$ and leave the learning rates of the posterior components' means and Cholesky factor the same as GVT.
 
@@
 
-For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions, an input layer receiving the $22$-dimensional state of the MDP and an output layer that produces the value of each of the $3$ action.
-For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate $\alpha=0.001$ .
+For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions..For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate to $\alpha=0.001$.
 
@@
 % Placer-holder to actual plots. Add analyses
-\begin{figure*}[t]
+\begin{figure*}[h]
 	\begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
-    \caption{}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze0.pdf}
+    \caption{Expected Return during learning}
   \end{subfigure}
   \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{Maze \ref{fig:maze0} (a) Expected Return (b) Evaluation Reward}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze0.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze0}}
+  \label{fig:rew-maze0}
+
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze6.pdf}
+    \caption{Expected Return during learning}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze6.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze6}}
+  \label{fig:rew-maze6}
+
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze13.pdf}
+    \caption{Expected Return during learning}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze13.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze13} }
+  \label{fig:rew-maze13}
 \end{figure*}
 
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{Maze \ref{fig:maze6} (a) Expected Return (b) Evaluation Reward}
-\end{figure*}
-
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev.pdf}
-    \caption{}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew.pdf}
-    \caption{}
-  \end{subfigure}
-  \caption{Maze \ref{fig:maze13} (a) Expected Return (b) Evaluation Reward}
-  \label{fig:mazes-plots}
-\end{figure*}
+Hereafter, we present additional results of transferring from $5$ source tasks to the mazes shown in Fig.
+\ref{fig:maze0}, Fig.
+\ref{fig:maze6} and Fig.
+\ref{fig:maze13} using both GVT and MGVT.
+We show both the evaluation performance, i.e.
+the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t.
+those parameters, and the expected return during the learning process.
+All the curves result from averaging $20$ independent runs and randomly sampled sources.
+
+In Fig.
+\ref{fig:maze0}, \ref{fig:maze6}, \ref{fig:maze13}, we can appreciate that in this more complex transfer setting, MGVT is able to provide significant speed-up in a consistent manner in this subset of mazes.
+It is also noticeable the bad performance obtained with GVT in all cases.
+The Gaussian prior model clearly fails to capture enough information to transfer in this setting that result in a negative transfer effect.
 

### 2018-05-18 NIPS 2018/main.tex
Changes

--- 2018-05-18 NIPS 2018/main.tex
@@
 \newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
-\title{Transferring Value Functions by Variational Methods}
+\title{Transfer of Value Functions via Variational Methods}
 
@@
   \end{subfigure}
-  \caption{(a) transfer from $10$ sources in Cartpole, (b) transfer from $10$ source tasks in Mountain Car, and (c) transfer from $10$ sources in Maze \ref{fig:maze6}---see App. \ref{}.}
+  \caption{(a) Cartpole, (b) Mountain Car, and (c) Maze Navigation}
   \label{fig:ccmazeplots}

### 2018-05-18 NIPS 2018/main.tex
Corrected proofs

@@
 samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
-Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
+Then, for any $\lambda > 0$ and $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
 \begin{equation}\label{eq:lemma2-1}
@@
 \begin{lemma}\label{lemma:general-bound}
-Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
-Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples.
-Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
+Fix a task $\mathcal{M}_{\tau}$.
+Let $p$ be a prior distribution over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$.
+Assume $\wh{\xi}$ is the minimizer of \eqref{eq:elbo} for a dataset $D$ of $N$ i.i.d.
+samples where state-action couples are distributed according to $\nu$.
+Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
@@
 \begin{restatable}{theorem}{thg} \label{th:main-gaussian}
-Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
+Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_{2}\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_{2}\leq \phi_{\max}$.
 Consider the Gaussian version of Algorithm~\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.~\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
@@
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}.
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}.
 \end{equation}
@@
 \begin{align*}
-\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2.
+\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2.
 \end{align*}
@@
 \end{align*}
-Finally, defining the constants $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma_{max} + \log N)$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}$, we obtain:
-\begin{align*}
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}.
+Finally, defining the constants $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log\sigma_{max}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma_{min}}$, we obtain:
+\begin{align*}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}.
 \end{align*}
@@
 \begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right).
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right).
 \end{align*}
@@
 \begin{restatable}{theorem}{thmgsoft} \label{th:main-mixture-soft}
-Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$.
+Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_2\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_2\leq \phi_{\max}$.
 Consider the mixture version of Algorithm~ \ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$},
-\end{equation}
-where $\softmin_i x \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$.
+\resizebox{0.92\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$},
+\end{equation}
+where, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( x_j\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
 \end{restatable}
@@
 \end{align*}
-where the inequality holds since the first term is negative. For the second one:
-\begin{align*}
-\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace.
+where the inequality holds since the first term is negative. For the second term of \eqref{eq:thmg-2}:
+\begin{align*}
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right).
 \end{align*}
@@
 \begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace.
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right).
 \end{align*}
 Notice that, from now on, one can simply apply the proof of Thm.
-\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace$.
-Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d (\log\sigma^2_p + \log N) + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
+\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)$.
+Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log\sigma^2_p + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
 \begin{align*}
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$}.
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$}.
 \end{align*}

### 2018-05-18 NIPS 2018/main.tex
Edited sec 4

@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we consider Algorithm~\ref{alg:transfer} with a mixture of Gaussians and linear approximators.
+To address this point, we consider the two versions Algorithm~\ref{alg:transfer} of Sec.
+\ref{sec:gvt} and \ref{sec:mgvt} with linear approximators.
 We assume only a finite dataset is available and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
-Our main result is given in the following theorem.
+Due to space constraints, we provide only the result for mixtures of Gaussians, while referring the reader to App.
+\ref{} for the Gaussian case.
 
 \begin{restatable}{theorem}{thmg} \label{th:main-mixture}
-Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with uniformly bounded weights $|\bm{w}|\leq w_{max}$ and uniformly bounded features $|\bm{\phi}(s,a)|\leq \phi_{\max}$.
-Consider the mixture version of Algorithm~\ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
-Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Equation \eqref{eq:elbo} on a dataset $D$ of $N$ samples.
-Let $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$ and $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$.
-Define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[ v(\bm{w}) \right]$, with $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1$, $c_2$, $c_3$, $c_4$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_2\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_2\leq \phi_{\max}$.
+Consider the mixture version of Algorithm~ \ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
+Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
+\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
+samples distributed according to $\tau$ and $\nu$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \frac{c_1}{N^2} + \frac{c_2 + \frac{c_4}{\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}}{N} + \frac{\upsilon(\bm{w}^*) + c_3\sqrt{\log\frac{2}{\delta}}}{\sqrt{N}}\right)$}.
-\end{equation}
+\resizebox{0.92\textwidth}{!}{$
+\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$},
+\end{equation}
+where, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( x_j\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
 \end{restatable}
@@
 \ref{} for the proof and a specific definition of the constants.
-Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second term), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(N^2)$.
-Intuitively, the bound is tighten when the source tasks' $Q$-functions are, on average, close to the optimal ones for the target task.
+Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second and third terms), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(N^2)$.
+Our main result shows a remarkable property of using Alg.
+\ref{alg:transfer} with mixtures of Gaussians: in order to tighten the bound, it is enough to have at least one source task that is close to the optimal solution of the target task.
 In such case, the dominating error is due to the variance of the estimates, and, thus, the algorithm is expected to achieve good performance rather quickly, as new data is collected.
-Furthermore, as $N\rightarrow\infty$ the only error term remaining is, as usual, the irreducible approximation error due to the limited functional space.
-Notice that the variance term $\upsilon(\bm{w}^*)$ is due to the fact that we minimize a biased estimator of the Bellman error.
-If double sampling of the next state were possible (e.g., in simulation), such term could be removed.
-Finally, we want to point out that the proof of this theorem relies on a very general result (Lemma \ref{lemma:general-bound} in App.
-\ref{}) that does not require any specific choice of distribution of approximator.
-Leveraging on such results, it is straightforward to provide a finite-sample analysis of the Gaussian version of our algorithm.
-For the sake of completeness, we report the derivation in App.
-\ref{}.\todo{Should we discuss the main difference between the MGVT and GVT bounds here?}
+Furthermore, as $N\rightarrow\infty$ the only error terms remaining are the irreducible approximation error due to the limited functional space and the  variance term $\upsilon(\bm{w}^*)$.
+The latter is due to the fact that we minimize a biased estimator of the Bellman error and can be removed in cases where double sampling of the next state is possible (e.g., in simulation).
+Finally, we want to point out that the only difference between the bound of Thm.
+\ref{th:main-mixture} and the one for the Gaussian version of Alg.
+\ref{alg:transfer} (Thm.
+\ref{th:main-gaussian} in App.
+\ref{}) is, as expected, in the term bounding the distance to the prior.
+While in Thm.
+\ref{th:main-mixture} we have the (smoothened) minimum distance to the source tasks' weights, in the Gaussian case we have the distance to the mean of such weights, $\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$.
+This proves a remarkable advantage of using mixtures.
+In fact, the Gaussian version requires the source tasks to be, on average, similar to the target task in order to perform well, while the mixture version only requires this property for one of them.
+We verify this consideration from an empirical perspective in the next section.
 
@@
 
-\begin{restatable}{theorem}{thmgsoft} \label{th:main-mixture-soft}
-Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
-Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_2\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_2\leq \phi_{\max}$.
-Consider the mixture version of Algorithm~ \ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior.
-Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq.
-\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d.
-samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
-\begin{equation}
-\resizebox{0.92\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$},
-\end{equation}
-where, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( x_j\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
-\end{restatable}
+\thmg*
 \begin{proof}

### 2018-05-18 NIPS 2018/main.tex
Reformatting

@@
 \begin{document}
+\setlength{\abovedisplayskip}{1.5pt}
+\setlength{\belowdisplayskip}{1.5pt} 
 % \nipsfinalcopy is no longer used
@@
 Consistently with the prior, we model our approximate posterior as a mixture of Gaussians.
-However, we allow a different number of components \todo{questo dettaglio si potrebbe spostare nella parte sperimentale o togliere del tutto} (typically much less than the prior's), and we adopt full covariances instead of only diagonals so that our posterior has the potential to match complex distributions with fewer components.
 Using $C$ components, our posterior is $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$, with variational parameters $\bm{\xi} = (\bm{\mu}_1,\dots,\bm{\mu}_C,\bm{\Sigma}_1,\dots,\bm{\Sigma}_C)$.
 Once again, we learn Cholesky factors instead of full covariances.
-
-Although this new model has the potential to capture much more complicated distributions, it poses a significant complication: the KL divergence between two mixtures of Gaussians has no closed-form expression.
-To solve this issue, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and the exact posterior.
-Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report here for the sake of completeness.
-We refer the reader to the original paper for the proof.
-\begin{theorem}[\cite{hershey2007approximating}]\label{th:ukl}
-Let $p = \sum_{i} c_i^{(p)} f_i^{(p)}$ and $q = \sum_{j} c_j^{(q)} f_j^{(q)}$ be two mixture of Gaussian distributions, where $f_i^{(p)} = \mathcal{N}(\bm{\mu}_i^{(p)},\bm{\Sigma}_i^{(p)})$ denotes the i-th component of $p$, $c_i^{(p)}$ denotes its weight, and similarly for $q$.
-Introduce two vectors $\chi^{(1)}$ and $\chi^{(2)}$ such that $c_i^{(p)} = \sum_j \chi^{(2)}_{j,i}$ and $c_j^{(q)} = \sum_i \chi^{(1)}_{i,j}$.
-Then:
-\begin{equation}
-KL(p||q) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{i,j} \chi^{(2)}_{j,i}KL(f_i^{(p)}||f_j^{(q)})
-\end{equation}
-%\begin{equation}
-%\chi^{(2)}_{i,j} = \frac{c_j^{(q)}\chi^{(1)}_{j,i}}{\sum_{i'} \chi^{(1)}%_{j,i'}},\ \ \ \ \chi^{(1)}_{j,i} = \frac{c_i^{(p)}\chi^{(2)}_{i,j}e^{-%KL(f_i^{(p)}||f_j^{(q)})}}{\sum_{j'}\chi^{(2)}_{i,j'}e^{-KL(f_i^{(p)}||f_{j'}%^{(q)})}}
-%\end{equation}
-\end{theorem}
-Our new algorithm replaces the KL with the above-mentioned upper bound.
-Each time we require its value, we have to recompute the parameters $\chi^{(1)}$ and $\chi^{(2)}$ that tighten the bound.
-As shown in \cite{hershey2007approximating}, we can use a simple fixed-point procedure for this purpose.
-Finally, both terms in the objective are now linear combinations of functions of the variational parameters of different components, and their gradients easily derive from the ones of the Gaussian case.
-We report the derivation in App.
-\ref{}.
-
-\subsection{Optimizing the TD error} \label{sec:td}
+Finally, since the KL divergence between two mixtures of Gaussians has no closed-form expression, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and the exact posterior.
+Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report in App.
+\ref{} for the sake of completeness.
+
+\subsection{Optimizing the TD Error} \label{sec:td}
 
@@
 However, our transfer settings are quite different from common RL.
-In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum and aims only to adapt the weights in some direction of lower error (i.e., higher likelihood) so as to quickly converge to the solution of the target task.
+In fact, our algorithm is likely to start from $Q$-functions that are very close to an optimum and aims only to adapt the weights in some direction of lower error so as to quickly converge to the solution of the target task.
 Unfortunately, this property does not hold for most semi-gradient algorithms.
@@
 $\bm{w}$.
-Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart.
-\cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence.
-This projection is obtained by including a parameter $\psi\in[0,1]$ in the TD error gradient:
-\begin{equation}
-\nabla_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right),
-\end{equation}
-where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$.
-Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$).
-A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee convergence).
+Further considerations on how to better optimize it are given in App.
+\ref{}.
 
@@
 
-Since the agent does not know the locations of the doors in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
+%Since the agent does not know the locations of the doors in advance and receives only very sparse feedback, it must efficiently explore the environment to figure out (i) their positions, and (ii) how to reach the goal.
 While this might be a complicated problem for plain RL, our transfer algorithm should be able to figure out the door positions quickly.
@@
 
-To prove that our guesses are correct, we generate a set of $50$ source tasks for the three-room environment of Figure~\ref{f:rooms} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
+We generate a set of $50$ source tasks for the three-room environment of Figure~\ref{f:rooms} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
@@
 This result proves again that assuming Gaussian distributions can pose severe limitations in our transfer settings.
-
-Finally, we analyze the transfer performance as a function of how likely the target task is according to the prior.
-We consider a two-room version of the environment of Figure~\ref{f:rooms}.
-Unlike before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks with the door near the sides are very unlikely.
-Figure~\ref{f:likelihood} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
-As expected, GVT achieves poor performance on very unlikely tasks, even after many iterations.
-In fact, estimating a single Gaussian distribution definitely entails some information loss, especially about the unlikely tasks.
-On the other hand, MGVT keeps such information and, consequently, performs much better.
-Perhaps not surprisingly, MGVT reaches the optimal performance in $4k$ iterations no matter what task is being solved.
 
@@
 In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
-Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.\todo{More comments about HiP-MDPs?
-Should we discuss more related works?}
+Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.
 
@@
 
+\subsection{Optimizing the TD Error}
+
+Although residual algorithms have guaranteed convergence, they are typically much slower than their semi-gradient counterpart.
+\cite{baird1995residual} proposed to project the gradient in a direction that achieves higher learning speed, while preserving convergence.
+This projection is obtained by including a parameter $\psi\in[0,1]$ in the TD error gradient:
+\begin{equation}
+\nabla_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{D}^2 = \frac{2}{N}\sum_{i=1}^N b_i(\bm{w})\left( \gamma\psi\nabla_{\bm{w}}\mm_{a'}Q_{\bm{w}}(s_i',a') - \nabla_{\bm{w}}Q_{\bm{w}}(s_i,a_i)) \right),
+\end{equation}
+where $b_i(\bm{w}) = r_i + \gamma\mm_{a'}Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i)$.
+Notice that $\psi$ trades-off between the semi-gradient ($\psi = 0$) and the full residual gradient ($\psi = 1$).
+A good criterion for choosing such parameter is to start with values close to zero (to have faster learning) and move to higher values when approaching the optimum (to guarantee convergence).
+
 \subsection{Gaussian Variational Transfer}
@@
 
-For the implementation of the Mixture of Gaussian Variational Transfer, we use the upper bound on the KL divergence between two Mixtures of Gaussians, as in Theorem~\ref{th:ukl}, to obtain an upper bound on the negative ELBO in Equation~\eqref{eq:elbo}.
+As mentioned in the main paper, for the mixture version of Alg.
+\ref{alg:transfer} we rely on the upper bound on the KL divergence between two mixture of Gaussians presented in \cite{hershey2007approximating}.
+We report it here for the sake of completeness.
+
+\begin{theorem}[\cite{hershey2007approximating}]\label{th:ukl}
+Let $p = \sum_{i} c_i^{(p)} f_i^{(p)}$ and $q = \sum_{j} c_j^{(q)} f_j^{(q)}$ be two mixture of Gaussian distributions, where $f_i^{(p)} = \mathcal{N}(\bm{\mu}_i^{(p)},\bm{\Sigma}_i^{(p)})$ denotes the i-th component of $p$, $c_i^{(p)}$ denotes its weight, and similarly for $q$.
+Introduce two vectors $\chi^{(1)}$ and $\chi^{(2)}$ such that $c_i^{(p)} = \sum_j \chi^{(2)}_{j,i}$ and $c_j^{(q)} = \sum_i \chi^{(1)}_{i,j}$.
+Then:
+\begin{equation}
+KL(p||q) \leq KL(\chi^{(2)}||\chi^{(1)}) + \sum_{i,j} \chi^{(2)}_{j,i}KL(f_i^{(p)}||f_j^{(q)})
+\end{equation}
+%\begin{equation}
+%\chi^{(2)}_{i,j} = \frac{c_j^{(q)}\chi^{(1)}_{j,i}}{\sum_{i'} \chi^{(1)}%_{j,i'}},\ \ \ \ \chi^{(1)}_{j,i} = \frac{c_i^{(p)}\chi^{(2)}_{i,j}e^{-%KL(f_i^{(p)}||f_j^{(q)})}}{\sum_{j'}\chi^{(2)}_{i,j'}e^{-KL(f_i^{(p)}||f_{j'}%^{(q)})}}
+%\end{equation}
+\end{theorem}
+Our new algorithm replaces the KL with the above-mentioned upper bound.
+Each time we require its value, we have to recompute the parameters $\chi^{(1)}$ and $\chi^{(2)}$ that tighten the bound.
+As shown in \cite{hershey2007approximating}, we can use a simple fixed-point procedure for this purpose.
+Finally, both terms in the objective are now linear combinations of functions of the variational parameters of different components, and their gradients easily derive from the ones of the Gaussian case.
+
 Consider we have $C$ components for the posterior family $q_{\bm{\xi}}(\bm{w}) = \frac{1}{C}\sum_{i=1}^C\mathcal{N}(\bm{w}|\bm{\mu}_i,\bm{\Sigma}_i)$ and a prior distribution, constructed from the set of weights $\mathcal{W}_s = \left\lbrace \bm{w}_1,..., \bm{w}_{|\mathcal{W}_s|} \right\rbrace$ of the sources' optimal $Q$-functions, $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{j=1}^{|\mathcal{W}_s|}\mathcal{N}(\bm{w}|\bm{w}_j,\sigma_p^2\bm{I})$.
+Then:
 
@@
   \label{fig:sequential}
+\end{figure*}
+
+Finally, we analyze the transfer performance as a function of how likely the target task is according to the prior.
+We consider a two-room version of the environment of Figure~\ref{f:rooms}.
+Unlike before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks with the door near the sides are very unlikely.
+Figure~\ref{f:likelihood} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
+As expected, GVT achieves poor performance on very unlikely tasks, even after many iterations.
+In fact, estimating a single Gaussian distribution definitely entails some information loss, especially about the unlikely tasks.
+On the other hand, MGVT keeps such information and, consequently, performs much better.
+Perhaps not surprisingly, MGVT reaches the optimal performance in $4k$ iterations no matter what task is being solved.
+
+\begin{figure*}[t]
+\centering
+    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=4.5cm]{images/likelihood/lrew.pdf}
+    \caption{Expected return as a function of the task likelihood.}
+  \label{fig:likelihood}
 \end{figure*}

### 2018-05-18 NIPS 2018/main.tex
Corrected up to C2

@@
 
-In the present section we present the values of the hyper-parameters that we use for the experiments in this paper.
-
-It is worth noting that for the implementation of the algorithms we use a Replay Buffer with a fixed size and batches sampled randomly from it to perform the gradient steps using ADAM, with the default parameters, as the optimizer.
+In the present section we provide details on the parameters adopted in all experiments and discuss further results.
 
@@
 
-For these experiments, in order to train the source tasks for the Rooms Problem, we directly minimize the expected TD error based on the \textit{mellow} Bellman operator by stochastic gradient descent.
-We use a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$, $\psi=0.5$ and a learning rate $\alpha=0.001$.
-Additionally, for exploration we use an \textit{Exploration Fraction} of $0.7$.
-
-For the transfer algorithm GVT, we set a \textit{Batch Size} of $50$ and a \textit{Buffer Size} of $10000$.
+In order to train the source tasks, we directly minimize the TD error based on the \textit{mellow} Bellman operator by stochastic gradient descent.
+We use a \textit{batch size} of $50$, a \textit{buffer size} of $50000$, $\psi=0.5$ and a learning rate $\alpha=0.001$.
+Additionally, we use an $\epsilon$-greedy policy for exploration, with $\epsilon$ linearly decaying from $1$ to $0.02$ in a fraction of $0.7$ the maximum number of iterations.
+
+For the transfer algorithm GVT, we set a \textit{batch size} of $50$ and a \textit{buffer size} of $10000$.
 We use $\psi=0.5$, $\lambda=10^{-4}$ and $10$ \textit{weights} to estimate the expected TD error.
-For the learning rates, $\alpha_{\mu}=0.001$ for the mean of the posterior Gaussian and $\alpha_{L}=0.0001$ to learn its Cholesky factor L.
+For the learning rates, $\alpha_{\mu}=0.001$ for the mean of the posterior and $\alpha_{L}=0.1$ to learn its Cholesky factor L.
 Furthermore, we restrict the minimum value reachable by the eigenvalues of these factors to be $\sigma_{min}^2=0.0001$.
 In the case of MGVT we use, instead, $\lambda=10^{-6}$, $\alpha_{\mu}=0.001$ and $\alpha_{L}=0.1$.
-Finally, for the prior's covariances we set it to $\sigma_p^2=10^{-5}$.
+Finally, we use a bandwidth $\sigma_p^2=10^{-5}$ for the prior.
 
@@
 Firstly, we show the results of the evaluation of the greedy performance.
-We compute this as the average reward gotten when the agent acts using the greedy policy using the parameters at the iteration of evaluation.
-In the case of GVT, we take the mean of the posterior Gaussian and, in MGVT, we compute the mean of the posterior by averaging the means of its components and use it for evaluation.
-
-In Figure~\ref{fig:3r-rew} we show the results when evaluating the Rooms Problem performance when the sources used to transfer have sample tasks resulting of both doors being sampled uniformly.
-It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer performance and shows that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
-
-In Figure~\ref{fig:3rg-erew} we show the evaluation for the generalization experiment when the sampled source tasks have a door fixed and the target task is generated by sampling both doors' positions.
-From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution in this more complicated setting, whereas GVT fails to adapt as consistently as MGVT, thus the higher variance and distance to the optimal value.
+We compute this as the expected return obtained when the agent acts using the greedy policy w.r.t.
+to the estimated $Q$-function.
+In the case of GVT, we take the mean of the posterior as the estimated $Q$-function, while for MGVT, we compute the greedy expected return under all components' means and average them.
+
+In Figure~\ref{fig:3r-erew} we show the results when transferring from the prior with both doors moving.
+It is easily noticeable that both GVT and MGVT perform much better in comparison with the no transfer performance and that the mean behavior of our posterior distribution, indeed, converges to the actual optimal solution.
+
+In Figure~\ref{fig:3rg-erew} we show the results when transferring from the prior with only one door moving.
+From this we can clearly appreciate that MGVT is able to quickly converge to the optimal solution in this more complicated setting, whereas GVT fails to adapt as consistently, thus the higher variance and distance to the optimal value.
 In this scenario, using a Gaussian to model the prior over-constrains the algorithm to stay close to part of the function space that cannot solve optimally the target tasks sampled from the modified distribution.
@@
 \ref{fig:rooms-expl}, we show the results of running the no transfer (NT) algorithm, GVT and 1-MGVT for $2000$ iterations and we represent as a scatter plot the positions visited by the agent.
+
+\begin{figure*}[b]
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0.5cm 1.5cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_gvt.png}
+    \caption{}
+    \label{fig:nt-vs-gvt}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.5cm 0.5cm 1.5cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_mgvt.png}
+    \caption{}
+    \label{fig:nt-vs-mgvt}
+  \end{subfigure}
+  \caption{Two-Rooms Problem: (a)  $\epsilon$-greedy vs. GVT, and (b) $\epsilon$-greedy vs. 1-MGVT}
+  \label{fig:rooms-expl}
+\end{figure*}
 
@@
 
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0.5cm 1.5cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_gvt.png}
-    \caption{}
-    \label{fig:nt-vs-gvt}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \includegraphics[trim=0.5cm 0.5cm 1.5cm 1.3cm,clip=true,height=4.5cm]{images/three-room-app/nt_vs_mgvt.png}
-    \caption{}
-    \label{fig:nt-vs-mgvt}
-  \end{subfigure}
-  \caption{(a) Two-Rooms Problem: $\epsilon$-greedy vs. GVT, (b) Two-Rooms Problem: $\epsilon$-greedy vs. 1-MGVT experiment}
-  \label{fig:rooms-expl}
-\end{figure*}
-
-Finally, in Figure~\ref{fig:sequential} we present the expected return as a function of the number of source tasks used for GVT and MGVT.
+In Figure~\ref{fig:sequential} we present the expected return as a function of the number of source tasks used for GVT and MGVT.
 In particular, we show the resulting curves after $1000$ iterations in Figure~\ref{fig:seq-1000} and after $1950$ iterations in Figure~\ref{fig:seq-1950}.
@@
 As the number of source tasks increases, as seen more clearly from Figure~\ref{fig:seq-1950}, the performances become closer for this environment.
-
-Finally, among the MGVT curves in Figure~\ref{fig:sequential}, we see that, even if more components lead to slightly better performances, the advantage is not quite significant in this environment.
-As seen before, the actual performances will converge to optimality in all the MGVT cases.
-Clearly, as we expect all components to converge to the optimal parameters, the initial performance difference will, indeed, reduce fast.
 
@@
 
-During the training of the source tasks, we use a \textit{Batch Size} of $150$ and a \textit{Buffer Size} of $50000$.
-Specifically, for DDQN we use a \textit{Target Update Frequency} of $500$,\textit{Exploration Fraction} of $0.35$ and a learning rate $\alpha=0.001$.
+During the training of the source tasks, we use a \textit{batch size} of $150$ and a \textit{buffer size} of $50000$.
+Specifically, for DDQN we use a \textit{target update frequency} of $500$,\textit{exploration fraction} of $0.35$ and a learning rate $\alpha=0.001$.
 We use a Multilayer Perceptron (MLP) with ReLU as activation function and a single hidden layer of $32$ neurons.
 
-For the transfer experiments, we set the \textit{Batch Size} to $500$, the number of \textit{weights} sampled to approximate the expected TD error to $5$, $\lambda=0.001$ and $\psi=0.5\ $.
+For the transfer experiments, we set the \textit{batch size} to $500$, the number of \textit{weights} sampled to approximate the expected TD error to $5$, $\lambda=0.001$ and $\psi=0.5\ $.
 We use $\alpha_{\mu}=0.001$ as the learning rate for the mean of the Gaussian posterior.
@@
 
-In Figure~\ref{fig:cp-erew}, we show the evaluation reward for DDQN, GVT, 1-MGVT and 3-MGVT, which consist of the average performance of the greedy policy using the parameters in the iteration of evaluation.
-In the case of GVT, we use the mean of the Gaussian posterior for the greedy policy and for MGVT corresponds to the mean of the Mixture of Gaussians for the posterior, that reduces to the average of the components' means.
-From the figure we can see how the transfer methods provide a significant jump-start w.r.t.
+In Figure~\ref{fig:cp-erew}, we show the greedy performance of DDQN, GVT, 1-MGVT and 3-MGVT, as in the previous section.
+Once again, we can see how the transfer methods provide a significant jump-start w.r.t.
 the DDQN evaluation.
-Although, a slight performance drop is seen as the algorithm adapts to the optimal Q-function, the algorithm quickly reaches optimality and converges to the actual optimal performance while DDQN, within these iterations, remains on average slightly suboptimal.
-\todo{improve this}
 
@@
 
-For the sources, we train the tasks using DDQN with a \textit{Target Update Frequency} of $500$, a \textit{Batch Size} of $32$, a  \textit{Buffer Size} of $50000$ and learning rate $\alpha=0.001$.
-Moreover, we set the \textit{Exploration Fraction} to $0.15$.
+For the sources, we train the tasks using DDQN with a \textit{target update frequency} of $500$, a \textit{batch size} of $32$, a  \textit{buffer size} of $50000$ and learning rate $\alpha=0.001$.
+Moreover, we set the \textit{exploration fraction} to $0.15$.
 We use an MLP with single hidden layer of $64$ neurons with ReLU activation function.
 
-For the transfer experiments, we set the \textit{Batch Size} to $500$, and use $10$ \textit{weights} to approximate the expected TD error, $\lambda=10^{-5}$ and $\psi=0.5$.
+For the transfer experiments, we set the \textit{batch size} to $500$, and use $10$ \textit{weights} to approximate the expected TD error, $\lambda=10^{-5}$ and $\psi=0.5$.
 For the learning rates, we use $\alpha_{\mu}=0.001$ for the means of the Gaussians.
@@
 
-Finally, in Figure~\ref{fig:mc-erew}, we show the evaluation reward obtained during the executions, which, as before, corresponds to the average reward gotten acting with a greedy policy with the parameters of the network in the case of DDQN and the mean value of the posterior in the cases of GVT and MGVT in the iteration of evaluation.
-In this plot, we can observe directly how fast is MGVT able to converge its mean to the actual optimal performance and that even if GVT struggles to find learn in comparison with MGVT, still provides a clear advantage w.r.t.
+In Figure~\ref{fig:mc-erew}, we show the greedy performance obtained during the executions, as in the previous sections.
+In this plot, we can observe directly how fast is MGVT able to converge its mean to the actual optimal performance and that even if GVT struggles to learn in comparison with MGVT, still provides a clear advantage w.r.t.
 DDQN.

### 2018-05-18 scripts/adasd.py

@@ -1,0 +1,24 @@
+ax = plot_ci(100 * _filter, EpRewMean_cb_pois[:, _filter], conf, n_runs, xlabel='trajectories', ylabel='average return', label='CB-POIS', linewidth=2.0, linestyle='-', color='b')
+ax = plot_ci(100 * _filter, EpRewMean_pb_pois[:, _filter], conf, n_runs, label='PB-POIS', ax=ax, linewidth=2.0, linestyle=':', color='r')
+ax = plot_ci(100 * _filter, EpRewMean_trpo[:, _filter], conf, n_runs, label='TRPO', ax=ax, linewidth=2.0, linestyle='--', color='g')
+#ax = plot_ci(100 * _filter, EpRewMean_cb_pois_pdis[:, _filter], conf, n_runs, label='PDIS', ax=ax, linewidth=2.0, linestyle='--', color='y')
+
+#ax.legend(loc='lower right', fontsize=LEGEND_FONT_SIZE)
+ax.xaxis.label.set_color('k')
+ax.yaxis.label.set_color('k')
+ax.tick_params(axis='x', colors='k', labelsize=TICKS_FONT_SIZE)
+ax.tick_params(axis='y', colors='k', labelsize=TICKS_FONT_SIZE)
+plt.ticklabel_format(style='sci', axis='x', scilimits=(0,0))
+
+plt.tight_layout()
+plt.savefig('pdfs/inverted-pendulum_linear.pdf')
+
+
+figLegend = plt.figure()
+legend = plt.figlegend(*ax.get_legend_handles_labels(), loc = 'upper left', fontsize=LEGEND_FONT_SIZE, ncol=2)
+legend.get_frame().set_facecolor('none')
+legend.get_frame().set_linewidth(0.0)
+figLegend.canvas.draw()
+bbox  = legend.get_window_extent().transformed(figLegend.dpi_scale_trans.inverted())
+figLegend.savefig('pdfs/legend.pdf',
+   bbox_inches=bbox)

### 2018-05-18 NIPS 2018/main.tex
Completed appendix revision

@@
 
-For the maze navigation task in Section~\ref{sec:mn}, here we enumerate the mazes that were designed to realize the experiments.
-In Figure~\ref{fig:mazes}, there are $20$ mazes with varying degree of difficulty and that were designed to hold some similarities that would be useful for transferring.
+The mazes adopted in the experiments of Sec.
+\ref{} are shown in Fig.~\ref{fig:mazes}.
+Our $20$ mazes have with varying degree of difficulty and are designed to hold few similarities that would be useful for transferring.
 Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.
 
-For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU as activation functions..For training the sources we use DDQN with a \textit{Batch size} of $70$, a \textit{Buffer Size} of $10000$ and a \textit{Target Update Frequency} of $100$, setting the \textit{Exploration Fraction} to $0.1$ and learning rate to $\alpha=0.001$.
-
-In transfer experiments we use $\psi=0.5$, a \textit{Batch Size} of $50$, a \textit{Buffer Size} of $50000$ and use $10$ sampled \textit{weights} from the posterior to approximate the TD error.
+For the experiments we use as an approximator an MLP with two hidden layers of $32$ neurons with ReLU activation functions.
+For training the sources we use a DDQN with a \textit{batch size} of $70$, a \textit{buffer size} of $10000$ and a \textit{target update frequency} of $100$, setting the \textit{exploration fraction} to $0.1$ and learning rate to $\alpha=0.001$.
+
+In the transfer experiments we use $\psi=0.5$, a \textit{batch size} of $50$, a \textit{buffer size} of $50000$ and use $10$ sampled \textit{weights} from the posterior to approximate the TD error.
 Moreover, we use $\lambda=10^{-6}$.
-For GVT, in particular, we use $\alpha_{\mu}=0.001$ as the rate to learn the mean parameters of our Gaussian posterior.
-For the Cholesky factor L, instead, we use $\alpha_{L}=10^{-7}$ and set the minimum value reachable by its eigenvalues to be $\sigma_{min}=0.0001$.
-In the case of MGVT experiments we set $\alpha_{\mu}=0.001$ to learn the mean of the different Gaussian components of our posterior and set $\alpha_{L}=10^{-6}$ for the Cholesky factors of its covariances.
-Finally, we use $\sigma_p^2=10^{-5}$ as the prior variance.
+For GVT, in particular, we use $\alpha_{\mu}=0.001$, $\alpha_{L}=10^{-7}$, and set the minimum value reachable by its eigenvalues to be $\sigma_{min}=0.0001$.
+In the case of MGVT, we set $\alpha_{\mu}=0.001$ and $\alpha_{L}=10^{-6}$.
+Finally, we use $\sigma_p^2=10^{-5}$ as the prior bandwidth.
 
@@
 \end{figure*}
-
-In Figure~\ref{}, we present the results of transferring from $5$ source tasks to the mazes shown in Figure~\ref{fig:maze0}, Figure~\ref{fig:maze6}, Figure~\ref{fig:maze8} and Figure~\ref{fig:maze13} using \todo{also GVT?} GVT and MGVT.
-We show both the evaluation reward, i.e.
-the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t.
-those parameters, and the expected return.
-All the curves result from averaging $20$ independent runs and randomly sampled sources.
 
@@
 \ref{fig:maze13} using both GVT and MGVT.
-We show both the evaluation performance, i.e.
-the average performance obtained evaluating the mean parameters of the posterior in a given iteration of the algorithm by following a greedy policy w.r.t.
-those parameters, and the expected return during the learning process.
+We show both the greedy and online performances.
 All the curves result from averaging $20$ independent runs and randomly sampled sources.

### 2018-05-18 NIPS 2018/main.tex
new plots, added common legend

--- 2018-05-18 NIPS 2018/main.tex
@@
 \usepackage{tikz}
+\usepackage{color}
 
@@
 \title{Transfer of Value Functions via Variational Methods}
+
+\definecolor{nt}{RGB}{14, 90, 211}
+\definecolor{gvt}{RGB}{188, 45, 20}
+\definecolor{mgvt1}{RGB}{34, 170, 22}
+\definecolor{mgvt3}{RGB}{160, 17, 163}
 
@@
 \begin{figure*}[t] 
-  \begin{subfigure}[b]{0.15\textwidth}
+  \begin{subfigure}[b]{0.32\textwidth}
     %\includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
     \begin{tikzpicture}[scale=0.37]
-\draw [white] (0,0) grid (7,7);
-\begin{scope}[shift={(0,2)}]
+\draw [white] (0,0) grid (11,8);
+%\begin{scope}[shift={(0,2)}]
+%\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
+%\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
+%\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
+%\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);
+%
+%%\draw [fill=black!50] (1,1) circle [radius=0.1cm];
+%%\node at (1,1) [ right] {$A$};
+%
+%\node at (1.8,-0.5)[left] {\color{darkgray}\small Start};
+%\node at (3.1,5.5) [right]{\color{darkgray}\small Goal};
+%
+%\draw [thick, gray] (0,0) rectangle (5,5);
+%\draw [line width=0.5mm, gray] (1.25,5/3) -- (5,5/3);
+%\draw [line width=0.5mm, gray] (0,5/3) -- (0.75,5/3);
+%\draw [line width=0.5mm, gray] (0,10/3) -- (3.25,10/3);
+%\draw [line width=0.5mm, gray] (3.75,10/3) -- (5,10/3);
+
+%\draw [thick, line width=0.6mm, dotted, nt] (5.5,4) -- (7,4);
+%\node at (7,4) [right] {NT};
+%\draw [thick, line width=0.6mm, dashed,gvt] (5.5,3) -- (7,3);
+%\node at (7,3) [right] {GVT};
+%\draw [thick, line width=0.6mm, mgvt1] (5.5,2) -- (7,2);
+%\node at (7,2) [right] {1-MGVT};
+%\draw [thick, line width=0.6mm, mgvt3] (5.5,1) -- (7,1);
+%\node at (7,1) [right] {3-MGVT};
+
+\begin{scope}[shift={(0,3)}]
+\begin{scope}[shift={(3,0)}]
 \draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
@@
 \draw [line width=0.5mm, gray] (3.75,10/3) -- (5,10/3);
+
+\end{scope}
+
+\draw [thick, line width=0.6mm, dotted, nt] (0,-1.5) -- (1,-1.5);
+\node at (1.5,-1.5) [right] {NT};
+\draw [thick, line width=0.6mm, dashed,gvt] (6, -1.5) -- (7,-1.5);
+\node at (7,-1.5) [right] {GVT};
+\draw [thick, line width=0.6mm, mgvt1] (0,-2.5) -- (1,-2.5);
+\node at (1.5,-2.5) [right] {1-MGVT};
+\draw [thick, line width=0.6mm, mgvt3] (6, -2.5) -- (7,-2.5);
+\node at (11.2,-2.5) [left] {3-MGVT};
+
 \end{scope}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
-    \caption{}\label{f:two_doors}
-  \end{subfigure}
-    \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
-    \caption{}\label{f:one_door}
-  \end{subfigure}
-    \begin{subfigure}[b]{0.27\textwidth}
-    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
-    \caption{}\label{f:likelihood}
-  \end{subfigure}
-  \caption{(a) the rooms environment, (b) transfer from $10$ source tasks with both doors moving, (c) transfer from $10$ source tasks with only one door moving, and (d) transfer performance as a function of how likely the target task is according to the prior.}
+  \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
+    \caption{Rooms Problem}\label{f:two_doors}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
+    \caption{Rooms Problem: Generalization}\label{f:one_door}
+  \end{subfigure}
+%    \begin{subfigure}[b]{0.27\textwidth}
+%    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
+%    \caption{}\label{f:likelihood}
+%  \end{subfigure}
+
+	\begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
+    \caption{Cartpole}\label{f:cartpole}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
+    \caption{Mountain Car}\label{f:mountaincar}
+  \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
+    \caption{Maze Navigation}\label{f:maze_results}
+  \end{subfigure}
+  \caption{Expected Return}
+  \label{fig:ccmazeplots}
+
   \label{fig:dipfdbsgraphplots}
@@
 
-\begin{figure*}[t]
-  \begin{subfigure}[b]{0.32\textwidth}
-    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
-    \caption{}\label{f:cartpole}
-  \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
-    \caption{}\label{f:mountaincar}
-  \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
-    \caption{}\label{f:maze_results}
-  \end{subfigure}
-  \caption{(a) Cartpole, (b) Mountain Car, and (c) Maze Navigation}
-  \label{fig:ccmazeplots}
-\end{figure*}
+%\begin{figure*}[t]
+%  \begin{subfigure}[b]{0.32\textwidth}
+%    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
+%    \caption{}\label{f:cartpole}
+%  \end{subfigure}
+%    \begin{subfigure}[b]{0.32\textwidth}
+%    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
+%    \caption{}\label{f:mountaincar}
+%  \end{subfigure}
+%    \begin{subfigure}[b]{0.32\textwidth}
+%    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
+%    \caption{}\label{f:maze_results}
+%  \end{subfigure}
+%  \caption{(a) Cartpole, (b) Mountain Car, and (c) Maze Navigation}
+%  \label{fig:ccmazeplots}
+%\end{figure*}
 

### 2018-05-18 NIPS 2018/main.tex
Modified Related Works

@@
 To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective.
-Thus, we provide a discussion of related works in the next section.
-\todo{Any better motivation?}
+A comparative discussion of related works motivating this statement is provided in the next section.
 
@@
 Furthermore, \cite{lazaric2010bayesian} propose a Dirichlet process model for the case where weights cluster into different classes, which relates to our mixture formulation and proves the importance of capturing more complicated task distributions again.
+Finally, \cite{lazaric2010bayesian} considers the problem of jointly learning all given tasks, while we focus on transferring information from a set of source tasks to the target task.
 In \cite{wilson2007multi}, the authors propose a hierarchical Bayesian model for the distribution over MDPs.
-unlike our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
+Unlike our approach and \cite{lazaric2010bayesian}, they consider a distribution over transition probabilities and rewards, rather than value functions.
 In the same spirit of our method, they consider a Thompson sampling-based procedure which, at each iteration, samples a new task from the posterior and solves it.
@@
 Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.
+Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.
 

### 2018-05-18 NIPS 2018/main.tex
Corrected captions
Squeezing in 8 pages

@@
 \begin{document}
-\setlength{\abovedisplayskip}{1.5pt}
-\setlength{\belowdisplayskip}{1.5pt} 
+\setlength{\abovedisplayskip}{0.5pt}
+\setlength{\belowdisplayskip}{0.5pt} 
 % \nipsfinalcopy is no longer used
@@
 Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
-In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.
-
+In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.\\
 Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve.
@@
 \begin{algorithmic}[1]
-\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch size $M$
-\\\hrulefill
+\REQUIRE Target task $\mathcal{M}_\tau$, source $Q$-function weights $\mathcal{W}_s$, batch size $M$
+% \\\hrulefill
 
@@
 
-\STATE{Sample initial state: $s_0 \sim p_0^{(\tau)}$}
+\STATE{Sample initial state: $s_0 \sim p_0$}
 
@@
 \STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
-\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$ and collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
-\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}_{\tau}(\cdot | s_h,a_h)$ and collect reward $r_{h+1} = \mathcal{R}_{\tau}(s_h,a_h)$}
+\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_{h+1},s_{h+1} \rangle$}
 \STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M}$ from $D$}
@@
 \ENDWHILE
-
 \UNTIL{forever}
@@
 \end{algorithm}
-
 We now highlight our general transfer procedure in Algorithm~\ref{alg:transfer}, while deferring a description of specific choices for the involved distributions to the next two subsections.
@@
 the corresponding $Q$-function (lines 7,8).
-After collecting and storing the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and, finally, update the variational parameters (line 13).
-
+After collecting the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and update the variational parameters (line 13).\\
 The key property of our approach is the weight resampling at line 7, which resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
@@
 As the learning process goes on, the algorithm will quickly figure out which task is being faced, thus moving all the probability mass over the weights minimizing the TD error.
-From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
-
+From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.\\
 Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any prior/posterior distributions can be adopted.
@@
 The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}).
-Although these results are well-known in the literature, we report them in App.
-\ref{} to have a more self-contained description.
+We report these results in App.
+\ref{}.
 
@@
 Finally, since the KL divergence between two mixtures of Gaussians has no closed-form expression, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and the exact posterior.
-Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report in App.
-\ref{} for the sake of completeness.
+Among the many upper bounds available, we adopt the one proposed in \cite{hershey2007approximating} (see App.
+\ref{}).
 
@@
 where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
-The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
+The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
 Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
@@
 
-\subsection{The Rooms Problem} \label{sec:gw}
-
-We consider an agent navigating in the environment depicted in Figure~\ref{f:rooms}.
-The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
-The rooms are connected by small doors whose locations are unknown to the agent.
-The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
-After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise $\mathcal{N}(0,0.2)$.
-In case the agent hits a wall, its position remains unchanged.
-The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
-In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.
+\paragraph{The Rooms Problem} \label{sec:gw}
 
@@
 \end{tikzpicture} 
-    \caption{}\label{f:rooms}
+    \caption{The rooms problem}\label{f:rooms}
   \end{subfigure}
@@
     \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
-    \caption{Rooms Problem}\label{f:two_doors}
+    \caption{Rooms: two doors moving}\label{f:two_doors}
   \end{subfigure}
@@
     \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
-    \caption{Rooms Problem: Generalization}\label{f:one_door}
+    \caption{Rooms: one door moving}\label{f:one_door}
   \end{subfigure}
@@
   \end{subfigure}
-  \caption{Expected Return}
+  \caption{Expected Return as a function of the number of iterations averaged over $20$ independent runs. $95\%$ confidence intervals are shown.}
   \label{fig:ccmazeplots}
-
   \label{fig:dipfdbsgraphplots}
 \end{figure*}
-
+We consider an agent navigating in the environment depicted in Figure~\ref{f:rooms}.
+The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
+The rooms are connected by small doors whose locations are unknown to the agent.
+The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
+After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise $\mathcal{N}(0,0.2)$.
+In case the agent hits a wall, its position remains unchanged.
+The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
+In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.\\
 We generate a set of $50$ source tasks for the three-room environment of Figure~\ref{f:rooms} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
@@
 Interestingly, we notice that there is no advantage in adopting more than $1$ component for the posterior in MGVT.
-This result is intuitive since, as soon as the algorithm figures out which is the target task, all the components move towards the same region.
-
+This result is intuitive since, as soon as the algorithm figures out which is the target task, all the components move towards the same region.\\
 To better understand the differences between GVT and MGVT, we now consider transferring from a slightly different distribution than the one from which target tasks are drawn.
@@
 
-\subsection{Classic Control} \label{sec:cc}
+\paragraph{Classic Control} \label{sec:cc}
 
@@
 For Cartpole (Figure~\ref{f:cartpole}), all transfer algorithms are almost zero-shot.
-This result is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are almost the same for all tasks.
+This result is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are similar for all tasks.
 On the contrary, in Mountain Car (Figure~\ref{f:mountaincar}) the optimal $Q$-functions become very different when changing the car speed.
@@
 
-\subsection{Maze Navigation} \label{sec:mn}
+\paragraph{Maze Navigation} \label{sec:mn}
 
@@
 To further asses the robustness of our method, we now consider transferring from the $Q$-functions learned by DDQNs instead of those obtained by minimizing the TD error as in the previous domains.
-From our considerations of Sec.
-\ref{sec:td} and \ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
-We show the results for a fixed target maze in Fig.
-\ref{}, while referring the reader to App.
+From our considerations of Sections~\ref{sec:td} and~\ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
+We show the results for a fixed target maze in Figure~\ref{f:maze_results}, while referring the reader to App.
 \ref{} for the illustration of our mazes and additional results.
@@
 Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.
-Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.
-
-In the RL community, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
+Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.\\
+In RL, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
 Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
@@
 
-In this work, we presented a variational method for transferring value functions in RL.
-We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators, and we provided two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
-We analyzed both from a theoretical and empirical perspective, proving that the Gaussian one has severe limitations, while the mixture version is much more suitable for our transfer settings.
-
+We presented a variational method for transferring value functions in RL.
+We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators.
+We provided two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
+We analyzed both from a theoretical and empirical perspectives, proving that the Gaussian version has severe limitations, while the mixture one is much better for our transfer settings.\\
 Since our algorithm effectively models the uncertainty over tasks, a relevant future work is to design an algorithm that explicitly explores the target task to reduce such uncertainty (e.g., \cite{houthooft2016vime}).

### 2018-05-18 NIPS 2018/main.tex
Ready for first submission

@@
 We show our approach to be general, in the sense that it can be combined with complex parametric function approximators and distribution models, while providing two practical algorithms based on Gaussians and Gaussian mixtures.
-We theoretically analyze both by providing a finite-sample analysis and evaluate them empirically in four different domains.\todo{Say something more about the advantages of our method}
+We theoretically analyze both by providing a finite-sample analysis and evaluate them empirically in four different domains.
 \end{abstract}
@@
 
-%\paragraph*{Exploration-based introduction}
-%One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks.
-Intuitively, assuming the tasks under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task.
-Among the appealing approaches for this problem we find Bayesian methods (e.g.,~\cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible.
-Similarly, model-based algorithms (e.g.,~\cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain.
-However, all these approaches either require strong assumptions (for example, on the distribution involved in Bayesian methods) or do not scale well to large problems.
-This greatly limits their practical applicability.
-
-%In this work, we tackle such limitations by considering a more general approach.
-Similarly to~\cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions.
-Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior.
-Leveraging on recent ideas from randomized value functions (\cite{}), we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
-(with respect to) the sampled value function.
-We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models.
-\todo[inline]{Maybe mention something about theory/experiments here}
-
 Under the assumption that tasks follow a specific distribution, an intuitive choice for designing a transfer algorithm is to attempt at characterizing the uncertainty over the target task.
 Then, an ideal algorithm would leverage prior knowledge from the source tasks to interact with the target task to reduce the uncertainty as quickly as possible.
-This simple intuition makes Bayesian \todo{probabilistic?
-distributional?} methods appealing approaches for transfer in RL, and many previous works have been proposed in this direction.
+This simple intuition makes Bayesian methods appealing approaches for transfer in RL, and many previous works have been proposed in this direction.
 In~\cite{wilson2007multi}, the authors assume tasks share similarities in their dynamics and rewards and propose a hierarchical Bayesian model for the distribution of these two elements.
@@
 Let us observe that the distribution $\mathcal{D}$ over tasks induces a distribution over optimal $Q$-functions.
-\todo{Should we just make the assumption that Q-functions share knowledge in their weights?} Furthermore, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
+Furthermore, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
 Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
@@
 Recall that our final goal is to move the total probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B_{\bm{w}}}_D^2$.
-Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ takes the form (e.g., \cite{catoni2007pac}):
+Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ minimizing an oracle upper bound on the expected loss takes the form (e.g., \cite{catoni2007pac}):
 \begin{equation}\label{eq:gibbs}
@@
 for some parameter $\Lambda > 0$.
-\todo{Maybe say how this is obtained} Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
+Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining, we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$.
 Notice that, whenever the term $e^{-\Lambda\norm{B_{\bm{w}}}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior.
@@
 We report these results in App.
-\ref{}.
+\ref{app:b2}.
 
@@
 Among the many upper bounds available, we adopt the one proposed in \cite{hershey2007approximating} (see App.
-\ref{}).
+\ref{app:b3}).
 
@@
 Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
-the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $\norm{\wt{B}_{\bm{w}}}_D^2$, is now differentiable w.r.t.
+the mellow Bellman operator $\wt{T}$, we have that the corresponding TD error, $||\wt{B}_{\bm{w}}||_D^2$, is now differentiable w.r.t.
 $\bm{w}$.
 Further considerations on how to better optimize it are given in App.
-\ref{}.
+\ref{app:b1}.
 
@@
 Let $\nu$ be a probability measure over the state-action space.
-Then, for any $p \geq 1$:\todo{Correct measure on the rhs}
+Then, for any $p \geq 1$:
 \begin{equation}
@@
 The proof is provided in App.
-\ref{}.
+\ref{app:a1}.
 As expected, $\wt{Q}$ converges to $Q^*$ exponentially fast when either $\kappa$ (equivalently, $\beta_{\kappa}$) increases, or the action gaps are enlarged.
@@
 Due to space constraints, we provide only the result for mixtures of Gaussians, while referring the reader to App.
-\ref{} for the Gaussian case.
+\ref{app:a2} for the Gaussian case.
 
@@
 We refer the reader to App.
-\ref{} for the proof and a specific definition of the constants.
+\ref{app:a2} for the proof and a specific definition of the constants.
 Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second and third terms), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(N^2)$.
@@
 \ref{th:main-gaussian} in App.
-\ref{}) is, as expected, in the term bounding the distance to the prior.
+\ref{app:a2}) is, as expected, in the term bounding the distance to the prior.
 While in Thm.
@@
 
-\section{Experiments}
+\section{Experiments} \label{sec:exp}
 
@@
   \end{subfigure}
-  \caption{Expected Return as a function of the number of iterations averaged over $20$ independent runs. $95\%$ confidence intervals are shown.}
+  \caption{Expected return as a function of the number of iterations averaged over $20$ independent runs. $95\%$ confidence intervals are shown.}
   \label{fig:ccmazeplots}
@@
 Further details on the parameters adopted in this experiment are given in App.
-\ref{}.
+\ref{app:c1}.
 As expected, the no-transfer (NT) algorithm fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
@@
 A better description of these two environments and their parameters is given in App.
-\ref{}.
+\ref{app:c2}.
 In this experiment, we use a Double Deep Q-Network (DDQN) \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
@@
 We show the results for a fixed target maze in Figure~\ref{f:maze_results}, while referring the reader to App.
-\ref{} for the illustration of our mazes and additional results.
+\ref{app:c3} for the illustration of our mazes and additional results.
 Once again, MGVT achieves a remarkable speed-up over (no-transfer) DDQN.
@@
 For the same reason, GVT shows negative transfer and performs even worse than no-transfer.
-
-%For this setting we propose a maze environment, such as those in Fig.
-\ref{}, for a robotic agent to navigate.
-We created a set of 20 mazes---see App \ref{}---of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze.
-In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}).
-Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measurements to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision of $9$ equally-spaced directions in $[-90,90º]$ relative to its orientation.
-In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike.
-Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation.
-Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.
-
-%The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience.
-Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting suitable to assess how robust our algorithm is to negative transfer.
-
-%The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm.
-Finally, the 1-MGVT algorithm was used to solve the target tasks---Mazes 6 and 13.
-As before, $20$ independent runs with randomized sources to transfer are averaged and shown in Fig.
-\ref{}, in this case $5$ source tasks were used for each trial.
-While these mazes pose a challenge for our algorithm, we can see that 1-MGVT is capable to still capture useful information from the sources and adapt to the target mazes which is demonstrated by the increased slope in the learning curve.
-\todo{actually, decide how to improve these results}
 
@@
 
-\subsection{Proof of Theorem 2}
+\subsection{Proof of Theorem 1}\label{app:a1}
 
@@
 
-\subsection{Proof of Theorem 3}
+\subsection{Proof of Theorem 2}\label{app:a2}
 
@@
 
-\subsection{Optimizing the TD Error}
+\subsection{Optimizing the TD Error}\label{app:b1}
 
@@
 
-\subsection{Gaussian Variational Transfer}
+\subsection{Gaussian Variational Transfer}\label{app:b2}
 
@@
 
-\subsection{Mixture of Gaussian Variational Transfer}
+\subsection{Mixture of Gaussian Variational Transfer}\label{app:b3}
 
@@
 
-\subsection{The Rooms Problem}
+\subsection{The Rooms Problem}\label{app:c1}
 
@@
 
-\subsection{Classic Control}
+\subsection{Classic Control}\label{app:c2}
 
@@
 
-\subsection{Maze Navigation}
+\subsection{Maze Navigation}\label{app:c3}
 
 The mazes adopted in the experiments of Sec.
-\ref{} are shown in Fig.~\ref{fig:mazes}.
+\ref{sec:exp} are shown in Fig.~\ref{fig:mazes}.
 Our $20$ mazes have with varying degree of difficulty and are designed to hold few similarities that would be useful for transferring.

### 2018-05-18 NIPS 2018/main.tex
Removed todos

@@
 Thus, bounding this quantity reduces to bounding $\abs{\max_{a}Q^*(s,a) - \mm_{a}Q^*(s,a)}$ point-wisely for any $s$.
-Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{}\todo{Cite MM}.
+Recall that applying the mellow Bellman operator is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta_{\kappa}$ induced by $\kappa$ \cite{asadi2017alternative}.
 Thus, we can write:
@@
 Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
-Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
+Then, for any $\delta > 0$, with probability at least $1-\delta$:
 \begin{align*}

### 2018-05-18 NIPS 2018/main.tex
centered rooms image and legend

--- 2018-05-18 NIPS 2018/main.tex
@@
 \begin{document}
-\setlength{\abovedisplayskip}{0.5pt}
-\setlength{\belowdisplayskip}{0.5pt} 
+\setlength{\abovedisplayskip}{1.5pt}
+\setlength{\belowdisplayskip}{1.5pt} 
 % \nipsfinalcopy is no longer used
@@
 Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
-In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.\\
+In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.
+
 Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve.
@@
 \begin{algorithmic}[1]
-\REQUIRE Target task $\mathcal{M}_\tau$, source $Q$-function weights $\mathcal{W}_s$, batch size $M$
-% \\\hrulefill
+\REQUIRE Target task $\tau$, source $Q$-function weights $\mathcal{W}_s$, batch size $M$
+\\\hrulefill
 
@@
 
-\STATE{Sample initial state: $s_0 \sim p_0$}
+\STATE{Sample initial state: $s_0 \sim p_0^{(\tau)}$}
 
@@
 \STATE{Take action $a_h = \argmax_a Q_{\bm{w}}(s_h,a)$}
-\STATE{Observe transition $s_{h+1} \sim \mathcal{P}_{\tau}(\cdot | s_h,a_h)$ and collect reward $r_{h+1} = \mathcal{R}_{\tau}(s_h,a_h)$}
-\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_{h+1},s_{h+1} \rangle$}
+\STATE{Observe transition $s_{h+1} \sim \mathcal{P}^{(\tau)}(\cdot | s_h,a_h)$ and collect reward $r_h = \mathcal{R}^{(\tau)}(s_h,a_h)$}
+\STATE{Add sample to the replay buffer: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
 \STATE{Sample mini-batch $D' = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{M}$ from $D$}
@@
 \ENDWHILE
+
 \UNTIL{forever}
@@
 \end{algorithm}
+
 We now highlight our general transfer procedure in Algorithm~\ref{alg:transfer}, while deferring a description of specific choices for the involved distributions to the next two subsections.
@@
 the corresponding $Q$-function (lines 7,8).
-After collecting the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and update the variational parameters (line 13).\\
+After collecting and storing the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and, finally, update the variational parameters (line 13).
+
 The key property of our approach is the weight resampling at line 7, which resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
@@
 As the learning process goes on, the algorithm will quickly figure out which task is being faced, thus moving all the probability mass over the weights minimizing the TD error.
-From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.\\
+From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
+
 Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any prior/posterior distributions can be adopted.
@@
 The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}).
-We report these results in App.
-\ref{}.
+Although these results are well-known in the literature, we report them in App.
+\ref{} to have a more self-contained description.
 
@@
 Finally, since the KL divergence between two mixtures of Gaussians has no closed-form expression, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and the exact posterior.
-Among the many upper bounds available, we adopt the one proposed in \cite{hershey2007approximating} (see App.
-\ref{}).
+Among the many upper bounds available in the literature, we adopt the one proposed in \cite{hershey2007approximating}, which we report in App.
+\ref{} for the sake of completeness.
 
@@
 where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
-The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
+The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties that make it suitable for our settings: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
 Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
@@
 
-\paragraph{The Rooms Problem} \label{sec:gw}
+\subsection{The Rooms Problem} \label{sec:gw}
+
+We consider an agent navigating in the environment depicted in Figure~\ref{f:rooms}.
+The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
+The rooms are connected by small doors whose locations are unknown to the agent.
+The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
+After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise $\mathcal{N}(0,0.2)$.
+In case the agent hits a wall, its position remains unchanged.
+The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
+In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.
 
@@
     \begin{tikzpicture}[scale=0.37]
-\draw [white] (0,0) grid (11,8);
+\draw [white] (0,0) grid (12,9);
 %\begin{scope}[shift={(0,2)}]
@@
 
-\begin{scope}[shift={(0,3)}]
-\begin{scope}[shift={(3,0)}]
+\begin{scope}[shift={(0,3.8)}]
+\begin{scope}[shift={(4,0)}]
 \draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
@@
 \end{scope}
-
+\begin{scope}[shift={(1,0)}]
 \draw [thick, line width=0.6mm, dotted, nt] (0,-1.5) -- (1,-1.5);
-\node at (1.5,-1.5) [right] {NT};
+\node at (1.5,-1.5) [right] {\small NT};
 \draw [thick, line width=0.6mm, dashed,gvt] (6, -1.5) -- (7,-1.5);
-\node at (7,-1.5) [right] {GVT};
+\node at (7,-1.5) [right] {\small GVT};
 \draw [thick, line width=0.6mm, mgvt1] (0,-2.5) -- (1,-2.5);
-\node at (1.5,-2.5) [right] {1-MGVT};
+\node at (1.5,-2.5) [right] {\small 1-MGVT};
 \draw [thick, line width=0.6mm, mgvt3] (6, -2.5) -- (7,-2.5);
-\node at (11.2,-2.5) [left] {3-MGVT};
-
+\node at (10.9,-2.5) [left] {\small 3-MGVT};
+\end{scope}
 \end{scope}
 \end{tikzpicture} 
-    \caption{The rooms problem}\label{f:rooms}
+    %\caption{The rooms problem}\label{f:rooms}
   \end{subfigure}
@@
   \label{fig:ccmazeplots}
+
   \label{fig:dipfdbsgraphplots}
 \end{figure*}
-We consider an agent navigating in the environment depicted in Figure~\ref{f:rooms}.
-The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
-The rooms are connected by small doors whose locations are unknown to the agent.
-The state-space is modeled as a $10 \times 10$ continuous grid, while the action-space is the set of $4$ movement directions (up, right, down, left).
-After each action, the agent moves by $1$ in the chosen direction and the final position is corrupted by Gaussian noise $\mathcal{N}(0,0.2)$.
-In case the agent hits a wall, its position remains unchanged.
-The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
-In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.\\
+
 We generate a set of $50$ source tasks for the three-room environment of Figure~\ref{f:rooms} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
@@
 Interestingly, we notice that there is no advantage in adopting more than $1$ component for the posterior in MGVT.
-This result is intuitive since, as soon as the algorithm figures out which is the target task, all the components move towards the same region.\\
+This result is intuitive since, as soon as the algorithm figures out which is the target task, all the components move towards the same region.
+
 To better understand the differences between GVT and MGVT, we now consider transferring from a slightly different distribution than the one from which target tasks are drawn.
@@
 
-\paragraph{Classic Control} \label{sec:cc}
+\subsection{Classic Control} \label{sec:cc}
 
@@
 For Cartpole (Figure~\ref{f:cartpole}), all transfer algorithms are almost zero-shot.
-This result is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are similar for all tasks.
+This result is expected since, although we vary the system parameters in a wide range, the optimal $Q$-values of states near the balanced position are almost the same for all tasks.
 On the contrary, in Mountain Car (Figure~\ref{f:mountaincar}) the optimal $Q$-functions become very different when changing the car speed.
@@
 
-\paragraph{Maze Navigation} \label{sec:mn}
+\subsection{Maze Navigation} \label{sec:mn}
 
@@
 To further asses the robustness of our method, we now consider transferring from the $Q$-functions learned by DDQNs instead of those obtained by minimizing the TD error as in the previous domains.
-From our considerations of Sections~\ref{sec:td} and~\ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
-We show the results for a fixed target maze in Figure~\ref{f:maze_results}, while referring the reader to App.
+From our considerations of Sec.
+\ref{sec:td} and \ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
+We show the results for a fixed target maze in Fig.
+\ref{}, while referring the reader to App.
 \ref{} for the illustration of our mazes and additional results.
@@
 Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.
-Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.\\
-In RL, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
+Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.
+
+In the RL community, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
 Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
@@
 
-We presented a variational method for transferring value functions in RL.
-We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators.
-We provided two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
-We analyzed both from a theoretical and empirical perspectives, proving that the Gaussian version has severe limitations, while the mixture one is much better for our transfer settings.\\
+In this work, we presented a variational method for transferring value functions in RL.
+We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators, and we provided two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
+We analyzed both from a theoretical and empirical perspective, proving that the Gaussian one has severe limitations, while the mixture version is much more suitable for our transfer settings.
+
 Since our algorithm effectively models the uncertainty over tasks, a relevant future work is to design an algorithm that explicitly explores the target task to reduce such uncertainty (e.g., \cite{houthooft2016vime}).

### 2018-05-18 NIPS 2018/main.tex
corrections to the paper

--- 2018-05-18 NIPS 2018/main.tex
@@
 The main limitation is that these RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks.
-One of the most promising solutions to reduce the need of samples is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
+One of the most promising solutions to alleviate this problem is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks.
 In the typical settings of transfer in RL~\cite{taylor2009transfer}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution.
@@
 Then, we use this distribution as a prior for learning the target task and we propose a variational approximation of the corresponding posterior that is computationally efficient.
-Leveraging on recent ideas from randomized value functions~\cite{osband2014generalization}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
+Leveraging on recent ideas from randomized value functions~\cite{osband2014generalization,azizzadenesheli2018efficient}, we design a Thompson Sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t.
 (with respect to) the sampled value function.
 We show that our approach is very general, in the sense that it can work with any parametric function approximator and with any prior/posterior distribution models (in this paper we focus on the Gaussian and Gaussian mixture models).
-In addition to the algorithmic contribution, we give also a theoretical contribution by providing a finite-sample analysis of our approach and an experimental contribution showing its empirical performance on four domains with increasing level of difficulty.
+In addition to the algorithmic contribution, we also give a theoretical contribution by providing a finite-sample analysis of our approach and an experimental contribution showing its empirical performance on four domains with increasing level of difficulty.
 
@@
 At the beginning of each episode of interaction, the initial state $s_0$ is drawn from $p_0$.
-Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}_\tau(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated.
+Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}_\tau(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}_{\tau}(\cdot | s_0,a_0)$, and the process is repeated.
 The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}_{\mathcal{M}_\tau,\pi}[\sum_{t=0}^{\infty} \gamma^t \mathcal{R}_\tau(s_t,a_t)]$.
@@
 From now on, we adopt the term $Q$-function to denote any plausible value function, i.e., any function $Q : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R}$ uniformly bounded by $\frac{R_{max}}{1-\gamma}$.
-In the following, to avoid cluttering the notation, we will drop the subscript $\tau$ when there is no ambiguity.
+In the following, to avoid cluttering the notation, we will drop the subscript $\tau$ whenever there is no ambiguity.
 
@@
 Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B_{\bm{w}}}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$.
-Whenever the distinction is clear from the context, with slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.
+Whenever the distinction is clear from the context, with a slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.
 
@@
 Furthermore, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem.
-Thus, one can safely replace the distribution over tasks with the distribution over their optimal value functions.
+Thus, we can safely replace the distribution over tasks with the distribution over their optimal value functions.
 In our parametric settings, we reduce the latter to a distribution $p(\bm{w})$ over weights.\\
-Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve.
+Assume, for the moment, that we know the distribution $p(\bm{w})$ and consider a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of samples from some task $\mathcal{M}_\tau \sim \mathcal{D}$ that we want to solve.
 Then, we can compute the posterior distribution over weights given such dataset by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$.
@@
 Thus, we take a different approach to derive a more general, but still well-grounded, solution.
-Recall that our final goal is to move the total probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B_{\bm{w}}}_D^2$.
+Notice that our final goal is to move the total probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B_{\bm{w}}}_D^2$.
 Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior $q$ minimizing an oracle upper bound on the expected loss takes the form (e.g., \cite{catoni2007pac}):
@@
 \end{align}
-The approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term).
+The approximate posterior balances between placing probability mass over those weights $\bm{w}$ that have low expected TD error (first term), and staying close to the prior distribution (second term).
 Assuming that we can compute the gradients of \eqref{eq:elbo} w.r.t.
@@
 After collecting the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and update the variational parameters (line 13).\\
-The key property of our approach is the weight resampling at line 7, which resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization}.
-At each time we guess what the task we are trying to solve based on our current belief is and we act as if such guess were true.
+The key property of our approach is the weight resampling at line 7, which resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization,azizzadenesheli2018efficient}.
+At each time we guess what is the task we are trying to solve based on our current belief and we act as if such guess were true.
 This mechanism allows an efficient adaptive exploration of the target task.
-Intuitively, during the first steps of interaction, the agent is very uncertain about the current task, and such uncertainty induces stochasticity in the chosen actions, allowing rather informed exploration to take place.
+Intuitively, during the first steps of interaction, the agent is very uncertain about the current task, and such uncertainty induces stochasticity in the chosen actions, allowing a rather informed exploration to take place.
 Consider, for instance, that actions that are bad on average for all tasks are improbable to be sampled, while this cannot happen in uninformed exploration strategies, like $\epsilon$-greedy, before learning takes place.
-As the learning process goes on, the algorithm will quickly figure out which task is being faced, thus moving all the probability mass over the weights minimizing the TD error.
+As the learning process goes on, the algorithm will quickly figure out which task is solving, thus moving all the probability mass over the weights minimizing the TD error.
 From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.\\
@@
 
-Given the source tasks' weights $\mathcal{W}_s$, we model our estimated prior as a mixture of Gaussians with one equally weighted isotropic Gaussian centered at each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$.
-This model resembles a kernel density estimator \cite{scott2015multivariate} and, due to its nonparametric nature, it allows capturing arbitrarily complex distributions.
+Given the source tasks' weights $\mathcal{W}_s$, we model our estimated prior as a mixture with equally weighted isotropic Gaussians centered at each weight: $p(\bm{w}) = \frac{1}{\abs{\mathcal{W}_s}}\sum_{\bm{w}_s \in \mathcal{W}_s}\mathcal{N}(\bm{w}|\bm{w}_s,\sigma_p^2\bm{I})$.
+This model resembles a kernel density estimator \cite{scott2015multivariate} with bandwidth $\sigma_p^2$ and, due to its nonparametric nature, it allows capturing arbitrarily complex distributions.
 Consistently with the prior, we model our approximate posterior as a mixture of Gaussians.
@@
 Once again, we learn Cholesky factors instead of full covariances.
-Finally, since the KL divergence between two mixtures of Gaussians has no closed-form expression, we rely on an upper bound to such quantity, so that negative ELBO still upper bounds the KL between the approximate and the exact posterior.
+Finally, since the KL divergence between two mixtures of Gaussians has no closed-form expression, we rely on an upper bound to such quantity, so that the negative ELBO still upper bounds the KL between the approximate and the exact posterior.
 Among the many upper bounds available, we adopt the one proposed in \cite{hershey2007approximating} (see App.
@@
 
-\subsection{Optimizing the TD Error} \label{sec:td}
+\subsection{Minimizing the TD Error} \label{sec:td}
 
@@
 Unfortunately, the TD error is well-known to be non-differentiable due to the presence of the max operator.
-This issue rarely is a problem since typical value-based algorithms are semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}).
+This issue is rarely a problem since typical value-based algorithms are semi-gradient methods, i.e., they do not differentiate the targets (see, e.g., Chapter 11 of \cite{sutton1998reinforcement}).
 However, our transfer settings are quite different from common RL.
@@
 where $\kappa$ is a hyperparameter and $|\mathcal{A}|$ is the number of actions.
-The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed point, and (iii) it is \textit{differentiable}.
+The mellow Bellman operator, which we denote as $\wt{T}$, has several appealing properties: (i) it converges to the maximum as $\kappa \rightarrow \infty$, (ii) it has a unique fixed-point, and (iii) it is \textit{differentiable}.
 Denoting by $\wt{B}_{\bm{w}} = \wt{T}Q_{\bm{w}} - Q_{\bm{w}}$ the Bellman residual w.r.t.
@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we consider the two versions Algorithm~\ref{alg:transfer} of Sec.
+To address this point, we consider the two variants of Algorithm~\ref{alg:transfer} from Sec.
 \ref{sec:gvt} and \ref{sec:mgvt} with linear approximators.
@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}||\wt{B}_{\bm{w}}||_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b_{\bm{w}}\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
   \caption{Expected return as a function of the number of iterations averaged over $20$ independent runs. $95\%$ confidence intervals are shown.}
-  \label{fig:ccmazeplots}
-  \label{fig:dipfdbsgraphplots}
+  \label{fig:main}
 \end{figure*}
-We consider an agent navigating in the environment depicted in Figure~\ref{f:rooms}.
+We consider an agent navigating in the environment depicted in Figure~\ref{fig:main}.
 The agent starts in the bottom-left corner and must move from one room to another to reach the goal position in the top-right corner.
@@
 In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.\\
-We generate a set of $50$ source tasks for the three-room environment of Figure~\ref{f:rooms} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
+We generate a set of $50$ source tasks for the three-room environment of Figure~\ref{fig:main} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
 Then, we use our algorithms to transfer from $10$ source tasks sampled from the previously generated set.
@@
 We now consider two well-known classic control environments: Cartpole and Mountain Car \citep{sutton1998reinforcement}.
-For both, we generate $20$ source tasks by uniformly sampling their physical parameters (cart mass, pole mass, pole length for Cartpole and car speed for Mountain Car).
-We parameterize $Q$-functions using neural networks with $1$-layer of $32$ hidden units for Cartpole and $64$ for Mountain Car.
+For both, we generate $20$ source tasks by uniformly sampling their physical parameters (cart mass, pole mass, pole length for Cartpole and car speed for Mountain Car) and solve them by directly minimizing the TD error as in the previous experiment.
+We parameterize $Q$-functions using neural networks with one layer of $32$ hidden units for Cartpole and $64$ for Mountain Car.
 A better description of these two environments and their parameters is given in App.
@@
 At the beginning of each episode, the agent is dropped to a random position in a $10m^2$ maze and must reach a goal area in the smallest time possible.
-The robot is equipped with sensors detecting its absolute position, its orientation, the distance to any obstacle within $2m$ in $9$ equally-spaced directions, and whether the goal is detected in the same range.
-The only actions available are \textit{move forward} with speed $0.5m/s$ or \textit{rotate} (in either direction) with speed of $\pi/8 rad/s$.
+The robot is equipped with sensors detecting its absolute position, its orientation, the distance to any obstacle within $2m$ in $9$ equally-spaced directions, and whether the goal is present in the same range.
+The only actions available are \textit{move forward} with speed $0.5m/s$ or \textit{rotate} (in either direction) with speed of $\pi/8\ rad/s$.
 Each time step corresponds to $1s$ of simulation.
@@
 Then, we fix a target maze and transfer from $5$ source mazes uniformly sampled from such set (excluding the chosen target).
-To further asses the robustness of our method, we now consider transferring from the $Q$-functions learned by DDQNs instead of those obtained by minimizing the TD error as in the previous domains.
+To further assess the robustness of our method, we now consider transferring from the $Q$-functions learned by DDQNs instead of those obtained by minimizing the TD error as in the previous domains.
 From our considerations of Sections~\ref{sec:td} and~\ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
@@
 This time, using $3$ components achieves slightly better performance than using only $1$, which is likely due to the fact that the task distribution is much more complicated than in the previous domains.
-For the same reason, GVT shows negative transfer and performs even worse than no-transfer.
+For the same reason, GVT shows negative transfer and performs even worse than DDQN.
 
@@
 In \cite{doshi2016hidden}, the authors consider a family of tasks whose dynamics are governed by some hidden parameters and use Gaussian processes (GPs) to model such dynamics across tasks.
-Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks, to obtain a more scalable approach.
-Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.\\
-In RL, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
+Recently, \cite{killian2017robust} extended this approach by replacing GPs with Bayesian neural networks to obtain a more scalable approach.
+Both approaches result in a model-based algorithm that quickly adapts to new tasks by estimating their hidden parameters, while we propose a model-free method which does not require such assumptions.
+
+%In RL, our approach is related to value function randomization\cite{osband2014generalization}, which extends the well-known LSTD \cite{boyan1999least} by adopting Bayesian linear regression to model the uncertainty over the predicted value function weights, and use that to perform a form of Thompson sampling.
 Such approach was recently extended by \cite{azizzadenesheli2018efficient}, where the approximator is replaced by a Bayesian neural network, leading to an algorithm capable of solving much more complicated problems.
@@
 We presented a variational method for transferring value functions in RL.
-We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators.
-We provided two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
-We analyzed both from a theoretical and empirical perspectives, proving that the Gaussian version has severe limitations, while the mixture one is much better for our transfer settings.\\
+We showed our approach to be general, in the sense that it can be combined with several distributions and function approximators, while providing two practical algorithms based on Gaussians and mixtures of Gaussians, respectively.
+We analyzed both from a theoretical and empirical perspectives, proving that the Gaussian version has severe limitations, while the mixture one is much better for our transfer settings.
+
 Since our algorithm effectively models the uncertainty over tasks, a relevant future work is to design an algorithm that explicitly explores the target task to reduce such uncertainty (e.g., \cite{houthooft2016vime}).
-Furthermore, our variation approach could be extended to model a distribution over optimal policies instead of value functions (e.g., \cite{liu2017stein}), which might allow better transferred behavior.
+Furthermore, our variational approach could be extended to model a distribution over optimal policies instead of value functions (e.g., \cite{sehnke2008policy,liu2017stein}), which might allow better transferred behavior.
 

### 2018-05-18 NIPS 2018/main.tex
Fixing to Theorem 1

--- 2018-05-18 NIPS 2018/main.tex
@@
 Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}).
-Let $\nu$ be a probability measure over the state-action space.
-Then, for any $p \geq 1$:
+% Let $\nu$ be a probability measure over the state-action space. 
+Then:
 \begin{equation}
-\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p.
+\norm{Q^*-\wt{Q}}_{\infty} \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\infty}.
 \end{equation}
@@
 \ref{app:a1}.
-As expected, $\wt{Q}$ converges to $Q^*$ exponentially fast when either $\kappa$ (equivalently, $\beta_{\kappa}$) increases, or the action gaps are enlarged.
+Notice that $\wt{Q}$ converges to $Q^*$ exponentially fast as $\kappa$ (equivalently, $\beta_{\kappa}$) increases and the action gaps are all larger than zero.
 Notice that this result is of interest even outside our specific settings.
@@
 \begin{align*}
-\norm{Q^*-\wt{Q}}_{\nu,p}^p =\ & \norm{TQ^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ =\ &
-\norm{TQ^* - \wt{T}Q^* + \wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
-\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \norm{\wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
-\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \gamma\norm{Q^* - \wt{Q}}_{\nu,p}^p,
+\norm{Q^*-\wt{Q}}_{\infty} =\ & \norm{TQ^* - \wt{T}\wt{Q}}_{\infty} \\ =\ &
+\norm{TQ^* - \wt{T}Q^* + \wt{T}Q^* - \wt{T}\wt{Q}}_{\infty} \\ \leq\ &
+\norm{TQ^* - \wt{T}Q^*}_{\infty} + \norm{\wt{T}Q^* - \wt{T}\wt{Q}}_{\infty} \\ \leq\ &
+\norm{TQ^* - \wt{T}Q^*}_{\infty} + \gamma\norm{Q^* - \wt{Q}}_{\infty},
 \end{align*}
@@
 \begin{align} \label{eq:mm1}
-\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p.
+\norm{Q^*-\wt{Q}}_{\infty} \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\infty}.
 \end{align}

### 2018-05-18 NIPS 2018/main.tex
Fixed Thm 2 and 3

--- 2018-05-18 NIPS 2018/main.tex
@@
 \ref{sec:gvt} and \ref{sec:mgvt} with linear approximators.
-We assume only a finite dataset is available and provide a finite-sample analysis bounding the distance between the fixed-point of the mellow Bellman operator and $Q$-functions sampled from the variational distribution minimizing the objective \eqref{eq:elbo}.
+We assume only a finite dataset is available and provide a finite-sample analysis bounding the expected (mellow) Bellman error under the variational distribution minimizing the objective \eqref{eq:elbo}.
 Due to space constraints, we provide only the result for mixtures of Gaussians, while referring the reader to App.
@@
 Let $\bm{w}^* = \arginf_{\bm{w}}||\wt{B}_{\bm{w}}||_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b_{\bm{w}}\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
 \begin{equation}
-\resizebox{0.92\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$},
+\resizebox{0.93\textwidth}{!}{$
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}$},
 \end{equation}
@@
 \ref{th:main-mixture}).
-
-\begin{lemma}\label{lemma:l1}
-Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively.
-Assume $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$.
-Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
-\begin{equation}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}.
-\end{equation}
-\end{lemma}
-\begin{proof}
-First notice that:
-\begin{align*}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 =\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}} + TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \norm{TQ_{\bm{w}} - TQ^*}_{\nu}^2\\ \leq\ & \norm{Q_{\bm{w}} - TQ_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2\\ =\ & \norm{B_{\bm{w}}}_{\nu}^2 + \gamma\norm{Q_{\bm{w}} - Q^*}_{\nu}^2
-\end{align*}
-which implies that:
-\begin{align*}
-\norm{Q_{\bm{w}} - Q^*}_{\nu}^2 \leq\ \frac{1}{1-\gamma}\norm{B_{\bm{w}}}_{\nu}^2.
-\end{align*}
-Then, using Markov inequality, we can write:
-\begin{align*}
-P\left( \norm{Q_{\bm{w}} - Q^*}_{\nu}^2 > \epsilon \right) \leq P\left(\norm{B_{\bm{w}}}_{\nu}^2 > \epsilon (1-\gamma)\right) \leq \frac{\mathbb{E}_p\left[ \norm{B_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\epsilon}.
-\end{align*}
-By setting the right-hand side equal to $\delta$ and solving for $\epsilon$ concludes the proof.
-\end{proof}
-
-Lemma \ref{lemma:l1} can be straightforwardly extended to the case where the mellow Bellman operator is used instead of the optimal one. This is given in the following corollary.
-
-\begin{corollary}\label{cor:diff-q}
-Let $p$ and $\nu$ denote probability measures over weights and state-action pairs, respectively.
-Assume $\wt{Q}$ is the unique fixed-point of the mellow Bellman operator $\wt{T}$.
-Then, for any $\delta > 0$, with probability at least $1 - \delta$ over the choice of weights $\bm{w} \sim p$, the following holds:
-\begin{equation}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_p\left[ \norm{\wt{B}_{\bm{w}}}_{\nu}^2 \right]}{(1-\gamma)\delta}.
-\end{equation}
-\end{corollary}
-
-We now prove some important properties of the variational approximation introduced in Section~\ref{sec:alg}.
+We start by proving some important properties of the variational approximation introduced in Section~\ref{sec:alg}.
 Our results generalize those of existing works that consider variational approximations of intractable Gibbs posteriors \cite{alquier2016properties,cottet20181}.
@@
 Consider a dataset $D$ of $N$ i.i.d.
-samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
+samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b_{\bm{w}}\right]\right]$.
 Then, for any $\lambda > 0$ and $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
@@
 \end{align*}
-where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Thus:
+where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b_{\bm{w}}\right]\right]$. Thus:
 \begin{align}\label{eq:hoeff}
@@
 samples where state-action couples are distributed according to $\nu$.
-Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$.
+Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b_{\bm{w}}\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$:
@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b_{\bm{w}}\right]\right]$.
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
 \begin{equation}
-\resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}.
+\resizebox{0.92\textwidth}{!}{$
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}$}.
 \end{equation}
@@
 \mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & 2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}.
-\end{align*}
-Let us now apply Corollary \ref{cor:diff-q}. We have that, with probability at least $1-\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ]}{(1-\gamma)\delta}.
-\end{align*}
-Thus, we probability at least $1-2\delta$:
-\begin{align*}
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right).
 \end{align*}
@@
 \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)$.
-Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log\sigma^2_p + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-2\delta$:
+Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log\sigma^2_p + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-\delta$:
 \begin{align*}
 \resizebox{0.93\textwidth}{!}{$
-\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$}.
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}.$}
 \end{align*}

### 2018-05-18 NIPS 2018/main.tex
aaa

@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}||\wt{B}_{\bm{w}}||_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b_{\bm{w}}\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}||\wt{B}_{\bm{w}}||_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b(\bm{w})\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
@@
 Consider a dataset $D$ of $N$ i.i.d.
-samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b_{\bm{w}}\right]\right]$.
+samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b(\bm{w})\right]\right]$.
 Then, for any $\lambda > 0$ and $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
@@
 \begin{align*}
-\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{\wt B_{\bm{w}}}_{\nu}^2,
-\end{align*}
-where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b_{\bm{w}}\right]\right]$. Thus:
+\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[\wt b(\bm{w})^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b(\bm{w})\right] + \mathbb{E}_{\mathcal{P}}\left[\wt b(\bm{w})\right]^2\right]\\ =\ & v(\bm{w}) + \norm{\wt B_{\bm{w}}}_{\nu}^2,
+\end{align*}
+where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b(\bm{w})\right]\right]$. Thus:
 \begin{align}\label{eq:hoeff}
@@
 samples where state-action couples are distributed according to $\nu$.
-Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b_{\bm{w}}\right]\right]$.
+Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b(\bm{w})\right]\right]$.
 Then, for any $\delta > 0$, with probability at least $1-\delta$:
@@
 samples distributed according to $\tau$ and $\nu$.
-Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b_{\bm{w}}\right]\right]$.
+Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b(\bm{w})\right]\right]$.
 Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
@@
 
-\subsection{Optimizing the TD Error}\label{app:b1}
+\subsection{Minimizing the TD Error}\label{app:b1}
 
@@
 Finally, we analyze the transfer performance as a function of how likely the target task is according to the prior.
-We consider a two-room version of the environment of Figure~\ref{f:rooms}.
+We consider a two-room version of the environment of Figure~\ref{fig:main}.
 Unlike before, we generate tasks by sampling the door position from a Gaussian with mean $5$ and standard deviation $1.8$, so that tasks with the door near the sides are very unlikely.
-Figure~\ref{f:likelihood} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
+Figure~\ref{fig:likelihood} shows the performance reached by GVT and 1-MGVT at fixed iterations as a function of how likely the target task is according to such distribution.
 As expected, GVT achieves poor performance on very unlikely tasks, even after many iterations.
@@
 \ref{sec:exp} are shown in Fig.~\ref{fig:mazes}.
-Our $20$ mazes have with varying degree of difficulty and are designed to hold few similarities that would be useful for transferring.
+Our $20$ mazes have varying degree of difficulty and are designed to hold few similarities that would be useful for transferring.
 Moreover, we ensure $4$ groups of mazes that are characterized by their goal position.
@@
   \label{fig:rew-maze13}
+
+    \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/lrev_maze8.pdf}
+    \caption{Expected Return during learning}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=4.5cm]{images/maze/erew_maze8.pdf}
+    \caption{Expected Return w.r.t. greedy policy}
+  \end{subfigure}
+  \caption{Performance in Maze \ref{fig:maze8} }
+  \label{fig:rew-maze8}
 \end{figure*}
@@
 \ref{fig:maze0}, Fig.
-\ref{fig:maze6} and Fig.
-\ref{fig:maze13} using both GVT and MGVT.
+\ref{fig:maze6}, Fig.
+\ref{fig:maze13}, and Fig.
+\ref{fig:maze8} using both GVT and MGVT.
 We show both the greedy and online performances.
@@
 In Fig.
-\ref{fig:maze0}, \ref{fig:maze6}, \ref{fig:maze13}, we can appreciate that in this more complex transfer setting, MGVT is able to provide significant speed-up in a consistent manner in this subset of mazes.
+\ref{fig:rew-maze0}, \ref{fig:rew-maze6}, \ref{fig:rew-maze13}, and \ref{fig:rew-maze8} we can appreciate that in this more complex transfer setting, MGVT is able to provide significant speed-up in a consistent manner in this subset of mazes.
 It is also noticeable the bad performance obtained with GVT in all cases.

### 2018-05-18 NIPS 2018/main.tex
Fixes

@@
 the corresponding $Q$-function (lines 7,8).
-After collecting the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and update the variational parameters (line 13).\\
+After collecting the new experience (lines 9-10), we draw a mini-batch of samples from the replay buffer (line 11), use this to estimate the objective function gradient (line 12), and update the variational parameters (line 13).
+
 The key property of our approach is the weight resampling at line 7, which resembles the well-known Thompson sampling approach adopted in multi-armed bandits \cite{bubeck2012regret} and closely relates to the recent value function randomization \cite{osband2014generalization,azizzadenesheli2018efficient}.
@@
 The expected log-likelihood, on the other hand, can be easily differentiated by adopting the reparameterization trick (e.g., \cite{hoffman2013stochastic,rezende2014stochastic}).
-We report these results in App.
-\ref{app:b2}.
+We report these results in Appendix \ref{app:b2}.
 
@@
 Finally, since the KL divergence between two mixtures of Gaussians has no closed-form expression, we rely on an upper bound to such quantity, so that the negative ELBO still upper bounds the KL between the approximate and the exact posterior.
-Among the many upper bounds available, we adopt the one proposed in \cite{hershey2007approximating} (see App.
-\ref{app:b3}).
+Among the many upper bounds available, we adopt the one proposed in \cite{hershey2007approximating} (see Appendix \ref{app:b3}).
 
@@
 $\bm{w}$.
-Further considerations on how to better optimize it are given in App.
-\ref{app:b1}.
+Further considerations on how to better optimize it are given in Appendix \ref{app:b1}.
 
@@
 
-The proof is provided in App.
-\ref{app:a1}.
+The proof is provided in Appendix \ref{app:a1}.
 Notice that $\wt{Q}$ converges to $Q^*$ exponentially fast as $\kappa$ (equivalently, $\beta_{\kappa}$) increases and the action gaps are all larger than zero.
@@
 The second question that we need to answer is whether we can provide any guarantee on our algorithm's performance when given limited data.
-To address this point, we consider the two variants of Algorithm~\ref{alg:transfer} from Sec.
-\ref{sec:gvt} and \ref{sec:mgvt} with linear approximators.
+To address this point, we consider the two variants of Algorithm~\ref{alg:transfer} from Section \ref{sec:gvt} and \ref{sec:mgvt} with linear approximators.
 We assume only a finite dataset is available and provide a finite-sample analysis bounding the expected (mellow) Bellman error under the variational distribution minimizing the objective \eqref{eq:elbo}.
-Due to space constraints, we provide only the result for mixtures of Gaussians, while referring the reader to App.
-\ref{app:a2} for the Gaussian case.
+Due to space constraints, we provide only the result for mixtures of Gaussians, while referring the reader to Appendix \ref{app:a2} for the Gaussian case.
 
@@
 
-We refer the reader to App.
-\ref{app:a2} for the proof and a specific definition of the constants.
+We refer the reader to Appendix \ref{app:a2} for the proof and a specific definition of the constants.
 Four main terms constitute our bound: the approximation error due to the limited hypothesis space (first term), the variance (second and third terms), the distance to the prior (third term), and a constant term decaying as $\mathcal{O}(N^2)$.
@@
 The latter is due to the fact that we minimize a biased estimator of the Bellman error and can be removed in cases where double sampling of the next state is possible (e.g., in simulation).
-Finally, we want to point out that the only difference between the bound of Thm.
-\ref{th:main-mixture} and the one for the Gaussian version of Alg.
-\ref{alg:transfer} (Thm.
-\ref{th:main-gaussian} in App.
-\ref{app:a2}) is, as expected, in the term bounding the distance to the prior.
-While in Thm.
-\ref{th:main-mixture} we have the (smoothened) minimum distance to the source tasks' weights, in the Gaussian case we have the distance to the mean of such weights, $\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$.
+Finally, we want to point out that the only difference between the bound of Theorem \ref{th:main-mixture} and the one for the Gaussian version of Alg.
+\ref{alg:transfer} (Theorem \ref{th:main-gaussian} in Appendix \ref{app:a2}) is, as expected, in the term bounding the distance to the prior.
+While in Theorem \ref{th:main-mixture} we have the (smoothened) minimum distance to the source tasks' weights, in the Gaussian case we have the distance to the mean of such weights, $\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$.
 This proves a remarkable advantage of using mixtures.
@@
 Each curve is the result of $20$ independent runs, each one resampling the target and source tasks, with $95\%$ confidence intervals.
-Further details on the parameters adopted in this experiment are given in App.
-\ref{app:c1}.
+Further details on the parameters adopted in this experiment are given in Appendix \ref{app:c1}.
 As expected, the no-transfer (NT) algorithm fails at learning the task in so few iterations due to the limited exploration provided by an $\epsilon$-greedy policy.
@@
 We parameterize $Q$-functions using neural networks with one layer of $32$ hidden units for Cartpole and $64$ for Mountain Car.
-A better description of these two environments and their parameters is given in App.
-\ref{app:c2}.
+A better description of these two environments and their parameters is given in Appendix \ref{app:c2}.
 In this experiment, we use a Double Deep Q-Network (DDQN) \cite{van2016deep} to provide a stronger no-transfer baseline for comparison.
@@
 From our considerations of Sections~\ref{sec:td} and~\ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method.
-We show the results for a fixed target maze in Figure~\ref{f:maze_results}, while referring the reader to App.
-\ref{app:c3} for the illustration of our mazes and additional results.
+We show the results for a fixed target maze in Figure~\ref{f:maze_results}, while referring the reader to Appendix  \ref{app:c3} for the illustration of our mazes and additional results.
 Once again, MGVT achieves a remarkable speed-up over (no-transfer) DDQN.
@@
 We begin by proving some important lemmas.
-Then, we use them to derive a finite-sample analysis of Algorithm~\ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Thm.
-\ref{th:main-gaussian}) and Gaussian mixture models (Thm.
-\ref{th:main-mixture}).
+Then, we use them to derive a finite-sample analysis of Algorithm~\ref{alg:transfer} with linearly parameterized value functions for both Gaussian distributions (Theorem \ref{th:main-gaussian}) and Gaussian mixture models (Theorem \ref{th:main-mixture}).
 We start by proving some important properties of the variational approximation introduced in Section~\ref{sec:alg}.
@@
 \begin{align*}
-\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}(\bm{w}^{*T}) + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2\right)^2\\ \leq\ & 2\wt{B}^2(\bm{w}^{*}) + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4,
+\mathbb{E}^2_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] \leq\ & \left(\wt{B}_{\bm{w}^*} + \frac{1}{2}\gamma\kappa c\bm{\phi}_{max}^2\right)^2\\ \leq\ & 2\wt{B}_{\bm{w}^{*}}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4,
 \end{align*}
@@
 \begin{align*}
-Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \bm{w}^T\bm{\phi}(s,a)\right]\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\left[\mm_{a'}\sqrt{c}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\right].
+Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\wt{T}Q_{\bm{w}}-Q_{\bm{w}}\right] =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[R(s,a) + \gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a')\right] - \bm{w}^T\bm{\phi}(s,a)\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\bm{\phi}(s',a') - \frac{1}{\gamma}\bm{w}^T\bm{\phi}(s,a)\right]\right]\\ =\ & Var_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\gamma\mathbb{E}_{s'}\left[\mm_{a'}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\right]\\ =\ & \gamma^2 Var_{\mathcal{N}(\bm{w}^*,\bm{I})}\left[\mathbb{E}_{s'}\left[\mm_{a'}\sqrt{c}\bm{w}^T\left(\bm{\phi}(s',a')-\frac{1}{\gamma}\bm{\phi}(s,a)\right)\right]\right].
 \end{align*}
@@
 %\end{align}
-%The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+%The only difference w.r.t. Eq. \eqref{eq:thg-4} of Theorem \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Theorem \ref{th:ukl} we have:
 %\begin{align}\label{eq:thmg-2}
@@
 %\end{align}
-%where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
-\ref{th:ukl}.
+%where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Theorem \ref{th:ukl}.
 Notice that, since we reduced the posterior to one component, the can get rid of the index $i$.
-Using the definitions of these two vectors from Sec.
-8 of \cite{hershey2007approximating}, we have:
+Using the definitions of these two vectors from Section 8 of \cite{hershey2007approximating}, we have:
 %\begin{align*}
@@
 %\end{align*}
-%Notice that, from now on, one can simply apply the proof of Thm.
-\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
+%Notice that, from now on, one can simply apply the proof of Theorem \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}} = \frac{1}{\sigma^2_p\abs{\mathcal{W}_s}}\sum_{j}\norm{\bm{w}^* - \bm{w}_{j}}$.
 Thus, by changing the three constants to $c_1 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^2 + \frac{\lambda d}{\sigma^2_p}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log(\sigma^2_p + \log N)$\todo{$c_2$ actually contains $N$.
@@
 \end{align}
-The only difference w.r.t. Eq. \eqref{eq:thg-4} of Thm. \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Thm. \ref{th:ukl} we have:
+The only difference w.r.t. Eq. \eqref{eq:thg-4} of Theorem \ref{th:main-gaussian} is the KL divergence term, which now contains a mixture distribution. From Theorem \ref{th:ukl} we have:
 \begin{align}\label{eq:thmg-2}
@@
 \end{align}
-where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Thm.
-\ref{th:ukl}.
+where the vectors $\chi^{(1)}$ and $\chi^{(2)}$ are the ones defined in Theorem \ref{th:ukl}.
 Notice that, since we reduced the posterior to one component, we can get rid of the index $i$.
-Using the definitions of these two vectors from Sec.
-8 of \cite{hershey2007approximating}, we have:
+Using the definitions of these two vectors from Section 8 of \cite{hershey2007approximating}, we have:
 \begin{align*}
@@
 \end{align*}
-Notice that, from now on, one can simply apply the proof of Thm.
-\ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)$.
+Notice that, from now on, one can simply apply the proof of Theorem \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)$.
 Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log\sigma^2_p + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-\delta$:
@@
 
-The mazes adopted in the experiments of Sec.
-\ref{sec:exp} are shown in Fig.~\ref{fig:mazes}.
+The mazes adopted in the experiments of Section \ref{sec:exp} are shown in Fig.~\ref{fig:mazes}.
 Our $20$ mazes have varying degree of difficulty and are designed to hold few similarities that would be useful for transferring.
@@
 
-Hereafter, we present additional results of transferring from $5$ source tasks to the mazes shown in Fig.
-\ref{fig:maze0}, Fig.
-\ref{fig:maze6}, Fig.
-\ref{fig:maze13}, and Fig.
-\ref{fig:maze8} using both GVT and MGVT.
+Hereafter, we present additional results of transferring from $5$ source tasks to the mazes shown in Figure \ref{fig:maze0}, Figure \ref{fig:maze6}, Figure \ref{fig:maze13}, and Figure \ref{fig:maze8} using both GVT and MGVT.
 We show both the greedy and online performances.
@@
 
-In Fig.
-\ref{fig:rew-maze0}, \ref{fig:rew-maze6}, \ref{fig:rew-maze13}, and \ref{fig:rew-maze8} we can appreciate that in this more complex transfer setting, MGVT is able to provide significant speed-up in a consistent manner in this subset of mazes.
+In Figure \ref{fig:rew-maze0}, \ref{fig:rew-maze6}, \ref{fig:rew-maze13}, and \ref{fig:rew-maze8} we can appreciate that in this more complex transfer setting, MGVT is able to provide significant speed-up in a consistent manner in this subset of mazes.
 It is also noticeable the bad performance obtained with GVT in all cases.

### 2018-05-18 NIPS 2018/main.tex
sjndks

@@
 We show our approach to be general, in the sense that it can be combined with complex parametric function approximators and distribution models, while providing two practical algorithms based on Gaussians and Gaussian mixtures.
-We theoretically analyze both by providing a finite-sample analysis and evaluate them empirically in four different domains.
+We theoretically analyze them by deriving a finite sample analysis and provide a comprehensive empirical evaluation in four different domains.
 \end{abstract}
@@
 As the learning process goes on, the algorithm will quickly figure out which task is solving, thus moving all the probability mass over the weights minimizing the TD error.
-From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.\\
+From that point, sampling from the posterior is approximately equivalent to deterministically taking such weights, and no more exploration will be performed.
+
 Finally, notice the generality of the proposed approach: as far as the objective $\mathcal{L}$ is differentiable in the variational parameters $\bm{\xi}$, and its gradients can be efficiently computed, any approximator for the $Q$-function and any prior/posterior distributions can be adopted.

### 2018-05-18 NIPS 2018/main.tex
delta

@@
 We show our approach to be general, in the sense that it can be combined with complex parametric function approximators and distribution models, while providing two practical algorithms based on Gaussians and Gaussian mixtures.
-We theoretically analyze them by deriving a finite sample analysis and provide a comprehensive empirical evaluation in four different domains.
+We theoretically analyze them by deriving a finite-sample analysis and provide a comprehensive empirical evaluation in four different domains.
 \end{abstract}
@@
 \begin{restatable}{theorem}{thmg} \label{th:main-mixture}
-Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Fix a target task $\mathcal{M}_{\tau}$.
 Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_2\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_2\leq \phi_{\max}$.
@@
 Let $\bm{w}^* = \arginf_{\bm{w}}||\wt{B}_{\bm{w}}||_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of the dataset $D$:
 \begin{equation}
 \resizebox{0.93\textwidth}{!}{$
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}$},
-\end{equation}
-where, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( x_j\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\Delta\right)}{N} + \frac{c_3}{N^2}$},
+\end{equation}
+where, $\Delta$ is a vector whose $j$-th components is $\Delta = \frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}$ and, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( \bm{x}\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
 \end{restatable}
@@
 \begin{restatable}{theorem}{thg} \label{th:main-gaussian}
-Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator.
+Fix a target task $\mathcal{M}_{\tau}$.
 Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_{2}\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_{2}\leq \phi_{\max}$.
@@
 Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt b(\bm{w})\right]\right]$.
-Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
+Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-\delta$ over the choice of the dataset $D$:
 \begin{equation}
@@
 \begin{align*}
-\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right).
-\end{align*}
-Putting the two terms together:
-\begin{align*}
-KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right).
-\end{align*}
-Notice that, from now on, one can simply apply the proof of Theorem \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)$.
+\sum_{j} \chi^{(2)}_{j}KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ \mathcal{N}(\bm{w}_j, \sigma_p^2\bm{I})) =\ & \frac{1}{2}\sum_{j} \chi^{(2)}_{j}\left( d\log\frac{\sigma^2_p}{c} + d\frac{c}{\sigma^2_p} + \frac{1}{\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j} - d\right)\\ \leq\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \sum_{j} \chi^{(2)}_{j}\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\\ =\ & \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\Delta\right).
+\end{align*}
+where we defined the vector $\Delta$ whose components are $\Delta_j = \frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}$. Putting the two terms together:
+\begin{align*}
+KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\Delta\right).
+\end{align*}
+Notice that, from now on, one can simply apply the proof of Theorem \ref{th:main-gaussian} with $\sigma_{max}=\sigma_{min}=\sigma^2_p$ and $\frac{1}{2}\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}$ replaced by $\varphi\left(\Delta\right)$.
 Thus, by redefining the three constants to $c_1 = \frac{8R_{max}^2}{\sqrt{2}(1-\gamma)^2}$, $c_2 = \bm{w}_{max}^2\bm{\phi}_{max}^2(1 + \gamma)^2 + \lambda d \log\sigma^2_p + 2\lambda\log\abs{\mathcal{W}_s}$, and $c_3 = \frac{1}{2}\gamma^2\kappa^2\bm{\phi}_{max}^4 + \frac{\lambda d}{\sigma^2_p}$, we can write that, with probability at least $1-\delta$:
@@
 \resizebox{0.93\textwidth}{!}{$
-\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}.$}
+\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\  2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + 2\lambda\varphi\left(\Delta\right)}{N} + \frac{c_3}{N^2}.$}
 \end{align*}

### 2018-05-18 NIPS 2018/main.tex
aaa

@@
 \end{equation}
-where, $\Delta$ is a vector whose $j$-th components is $\Delta = \frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}$ and, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( \bm{x}\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
+where, $\Delta$ is a vector whose $j$-th component is $\Delta_j = \frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}$ and, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( \bm{x}\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
 \end{restatable}
@@
 The reward is $1$ when reaching the goal (after which the process terminates) and $0$ otherwise, while the discount factor is $\gamma = 0.99$.
-In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.\\
+In this experiment, we consider linearly parameterized $Q$-functions with $121$ equally-spaced radial basis features.
+
 We generate a set of $50$ source tasks for the three-room environment of Figure~\ref{fig:main} by sampling both door locations uniformly in the allowed space, and solve all of them by directly minimizing the TD error as presented in Section~\ref{sec:td}.
@@
 We analyzed both from a theoretical and empirical perspectives, proving that the Gaussian version has severe limitations, while the mixture one is much better for our transfer settings.
+We evaluated the proposed algorithms in different domains, showing that both achieve excellent performance in simple tasks, while only the mixture version is able to handle complex environments.
 

### 2018-05-18 NIPS 2018/main.tex
Submitted version

@@
 \end{equation}
-where, $\Delta$ is a vector whose $j$-th component is $\Delta_j = \frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}$ and, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( \bm{x}\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
+where $\Delta$ is the vector of distances to the source tasks' weights, $\Delta_j = \frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}$, and, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( \bm{x}\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.
 \end{restatable}
